### 2016-04-27 analysis.Rmd
auc

---
title: "Psych 254 Replication Project Analysis"
author: "Eric Smith, Robert Hawkins, Michael C. Frank"
date: '`r Sys.Date()`'
output:
  html_document:
    number_sections: yes
    toc: yes
---

```{r}
library(dplyr)
library(ggplot2)
library(googlesheets)
```

Get project planning sheet straight from google docs.

```{r}
project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y")
project_plan <- gs_read_csv(project_plan_sheet)
```

### 2016-04-27 project_analyses/auc.R

@@ -1,0 +1,849 @@
+---
+title: Replication of \"What is Typical is Good&#58; The Influence of Face Typicality on Perceived Trustworthiness\"
+subtitle:
+  by Carmel Sofer, Ron Dotsch, Daniel H J Wigboldus & Alexander Todorov
+  (2015, Psychological Science)
+  
+author: "Carolyn Au"
+date: '`r Sys.Date()`'
+output:
+  html_document:
+    number_sections: yes
+    toc: yes
+  pdf_document:
+    toc: yes
+---
+
+<style type="text/css">
+body, td {
+   font-size: 14px;
+}
+h4 { font-size: 14px; }
+h3 { font-size: 16px; }
+h3.subtitle { font-size: 18px; }
+h2 { font-size: 18px; }
+h1 { font-size: 24px; }
+code, pre, blockquote, ol li {
+  font-size: 11px;
+}
+#composite-images img { width: 150px; }
+</style>
+
+```{r, echo=FALSE, include=FALSE}
+rm(list=ls())
+suppressPackageStartupMessages(c("dplyr","tidyr","ggplot2","lme4"))
+library(knitr)
+library(tidyr)
+library(dplyr)
+library(rjson)
+library(ggplot2)
+library(lme4)
+library(langcog) # devtools::install_github("langcog/langcog")
+
+opts_chunk$set(fig.width=8, fig.height=5, 
+               echo=TRUE, warning=FALSE, message=TRUE, cache=TRUE)
+theme_set(theme_bw())
+
+sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
+ci95 <- function(x) {sem(x) * 1.96}
+```
+
+```{r, echo=FALSE, include=FALSE}
+## Code in this block taken from: http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)
+
+## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
+##   data: a data frame.
+##   measurevar: the name of a column that contains the variable to be summariezed
+##   groupvars: a vector containing names of columns that contain grouping variables
+##   na.rm: a boolean that indicates whether to ignore NA's
+##   conf.interval: the percent range of the confidence interval (default is 95%)
+summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
+                      conf.interval=.95, .drop=TRUE) {
+    library(plyr)
[…]

### 2016-04-27 analysis.Rmd
auc + infrastructure

@@
 
+Libraries.
+
 ```{r}
@@
 library(googlesheets)
+library(readr)
 ```
@@
 project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y")
-project_plan <- gs_read_csv(project_plan_sheet)
+project_plan_raw <- gs_read_csv(project_plan_sheet)
 ```
+
+Exclude those to be excluded.
+
+```{r}
+project_plan <- project_plan_raw %>%
+  filter(`Include in final writeup?`==1) 
+```

### 2016-04-27 collect_values.R

@@ -1,0 +1,8 @@
+library(tidyr)
+library(dplyr)
+library(rjson)
+library(ggplot2)
+library(lme4)
+library(langcog) # devtools::install_github("langcog/langcog")
+sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
+ci95 <- function(x) {sem(x) * 1.96}

### 2016-04-27 project_analyses/auc.R

@@ -1,54 +1,7 @@
----
-title: Replication of \"What is Typical is Good&#58; The Influence of Face Typicality on Perceived Trustworthiness\"
-subtitle:
-  by Carmel Sofer, Ron Dotsch, Daniel H J Wigboldus & Alexander Todorov
-  (2015, Psychological Science)
-  
-author: "Carolyn Au"
-date: '`r Sys.Date()`'
-output:
-  html_document:
-    number_sections: yes
-    toc: yes
-  pdf_document:
-    toc: yes
----
-
-<style type="text/css">
-body, td {
-   font-size: 14px;
-}
-h4 { font-size: 14px; }
-h3 { font-size: 16px; }
-h3.subtitle { font-size: 18px; }
-h2 { font-size: 18px; }
-h1 { font-size: 24px; }
-code, pre, blockquote, ol li {
-  font-size: 11px;
-}
-#composite-images img { width: 150px; }
-</style>
-
-```{r, echo=FALSE, include=FALSE}
-rm(list=ls())
-suppressPackageStartupMessages(c("dplyr","tidyr","ggplot2","lme4"))
-library(knitr)
-library(tidyr)
+library(readr)
+library(jsonlite)
 library(dplyr)
-library(rjson)
-library(ggplot2)
-library(lme4)
-library(langcog) # devtools::install_github("langcog/langcog")
 
-opts_chunk$set(fig.width=8, fig.height=5, 
-               echo=TRUE, warning=FALSE, message=TRUE, cache=TRUE)
-theme_set(theme_bw())
-
-sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
-ci95 <- function(x) {sem(x) * 1.96}
-```
-
-```{r, echo=FALSE, include=FALSE}
 ## Code in this block taken from: http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)
 
 ## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
@@ -59,7 +12,6 @@ ci95 <- function(x) {sem(x) * 1.96}
 ##   conf.interval: the percent range of the confidence interval (default is 95%)
 summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
                       conf.interval=.95, .drop=TRUE) {
-    library(plyr)
     # New version of length which can handle NA's: if na.rm==T, don't count them
[…]

### 2016-04-27 project_analyses/salehi.R
salehi

@@ -1,0 +1,452 @@
+rm(list=ls())
+# library(tidyr)
+# library(dplyr)
+# library(ggplot2)
+# library(langcog) 
+# library(rjson)
+# library(tidyjson)
+# library(car)
+# library(effsize)
+# library(compute.es)
+# library(lme4)
+# library(lsr)
+# library(xlsx)
+# library(knitr)
+# library(png)
+# library(grid)
+# library(lmtest)
+# library(lmerTest)
+# library(gridExtra)
+
+#functions for se and CI
+sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
+ci95 <- function(x) {sem(x) * 1.96}
+
+path <- "data/salehi/"
+files <- dir(path, 
+             pattern = "*.json")
+d.raw <- data.frame()
+
+####Transforming data from JSON format to data.frame
+
+#reading the variables of interest for each participants from .json files and turning them into one data.frame
+for (f in files) {
+  jf <- paste0(path,f)
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- data.frame(workerid = jd$WorkerId, 
+                   trial_number_block=       as.factor(jd$answers$data$trial_number_block),
+                   rating = as.numeric(jd$answers$data$rating),
+                   gender = jd$answers$data$gender,
+                   age = jd$answers$data$age,
+                   sentence = jd$answers$data$sentence,
+                   definition = jd$answers$data$definition,
+                   political = jd$answers$data$political,
+                   condition = as.factor(jd$answers$data$condition),
+                   homelang = jd$answers$data$homelang,
+                   income = jd$answers$data$income,
+                   education = jd$answers$data$education,
+                   ethnicity = jd$answers$data$ethnicity,
+                   aim=jd$answers$data$expt_aim)
+  d.raw <- bind_rows(d.raw, id)
+}
+
+# Number of participants
+length(unique(d.b$workerid))
+
+d <- d.raw %>%
+  mutate(traitb = sentence %in% c('Decisive', 'Competitive', 'Self-reliant',   
+                                  'Willing to take risks' , 'Ambitious', 'Daring' ,
+                                  'Adventurous' , 'Courageous')) %>% 
+  mutate(traitType = factor(ifelse(traitb == TRUE, "Masculine", "Feminine"),  
+                            levels=c("Masculine","Feminine"))) %>%
+  mutate(trait = factor(sentence))  %>%
[…]

### 2016-04-27 project_analyses/auc.R
updates

@@ -181,6 +181,11 @@ model <- lm(centered_face_rating ~
             d)
 summary(model)
 
+project_info <- data.frame(project_key = "auc",
+                           n_final = length(unique(d.raw$workerid)),
+                           n_excluded = 0)
+                           
+
 #This results in $F(5, 16) = 91.11, p < 0.001, R^2 = 0.97$ which is the same
 #significance level and effect size as the original study. Comparing the
 #coeffecient estimates from this model with that of the original study, the

### 2016-04-27 project_analyses/smraposo.R
rmraposo

@@ -1,0 +1,150 @@
+rm(list=ls())
+library(rjson)
+library(plyr)
+library(splitstackshape)
+library(dplyr)
+library(tidyr)
+library(stringr)
+library(ggplot2)
+library(knitr)
+
+
+#Loading helpers
+sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
+ci95 <- function(x) {sem(x) * 1.96}
+theme_set(theme_linedraw())
+
+#Getting files
+path <- "~/replication_project/data/smraposo/"
+files <- dir(path, 
+             pattern = "*.json")
+d.raw <- data.frame()
+
+for (f in files) {
+  jf <- paste0(path, f)
+  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  id <- data.frame(workerid = jd$WorkerId, 
+                   ans = jd$answers)
+  d.raw <- bind_rows(d.raw, id)
+}
+
+# Cleaning up data
+
+#removing "ans.data." from all variable names
+names(d.raw) <- gsub("ans.data.", "", names(d.raw))
+
+# format data
+d0 <- d.raw %>% 
+  select(c(workerid, condition, timeMetric, incrAction, rt.2, rt.3),
+         contains("responses")) %>% 
+  rename(delay.rt = rt.2,
+         savings.rt = rt.3,
+         delaytime = responses,
+         savings = responses.1,
+         age = responses.2,
+         demos = responses.3,
+         comments = responses.4) %>%
+  mutate(workerid = as.factor(workerid),
+         condition = as.factor(condition),
+         timeMetric = as.factor(timeMetric),
+         incrAction = as.factor(incrAction))
+
+#cleaning json responses
+d0$delaytime <- gsub("Q0", "", d0$delaytime) #removing Q0 from responses
+d0$delaytime = gsub("([.])|[[:punct:]]", "\\1", d0$delaytime) #removing all punctuation except .
+d0$savings <- gsub("Q0", "", d0$savings) #removing Q0 from responses
+d0$savings = gsub("([.])|[[:punct:]]", "\\1", d0$savings) #removing all punctuation except "."
+d0$age <- gsub("Q0", "", d0$age) #removing Q0 from responses
+d0$age = gsub("([.])|[[:punct:]]", "\\1", d0$age) #removing all punctuation except "."
+d0$demos <- gsub("Q0", "", d0$demos) #removing Q0 from responses
[…]

### 2016-05-12 project_analyses/ehermann.R
Update Eric Paths

@@ -12,7 +12,7 @@ library(lme4)
 # write.csv(d_id,"~/Downloads/ehermann.csv",row.names=F)
 
 # Read in this data
-path <- "~/replication_project/processed_data/"
+path <- "processed_data/"
 df <- read.csv(file = paste0(path,"ehermann.csv")) #Check excel file for any issues with data
 
 

### 2016-05-12 project_analyses/jmarias.R

@@ -42,7 +42,7 @@ corstarsl <- function(x){
 #Temporarily changing wd to see where the error files are located within the vector of files in the json folder - to comment out
 
 #Reading the path
-path <- "~/replication_project/data/jmarias/"
+path <- "data/jmarias/"
 files <- dir(path, 
              pattern = "*.json")
 d <- data.frame()
@@ -223,7 +223,7 @@ z.pvthigh <- subjectmeans %>%
 
 # Save subjectmeans file
 # Save intermediate file
-path <- "~/replication_project/processed_data/"
+path <- "processed_data/"
 write.csv(subjectmeans, file = paste0(path,"jmarias.csv")) #Check excel file for any issues with data
 
 

### 2016-05-12 project_analyses/mkeil.R

@@ -11,7 +11,7 @@ library(png)
 sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
 ci95 <- function(x) {sem(x) * 1.96}
 
-path <- "~/replication_project/data/mkeil/"
+path <- "data/mkeil/"
 files <- dir(path, pattern = "*.json")
 d.raw <- data.frame()
 for (f in files) {
@@ -167,7 +167,7 @@ d1_bar <- d1 %>%
  #47 included
 
 # Save intermediate file
-path <- "~/replication_project/processed_data/"
+path <- "processed_data/"
 write.csv(d1, file = paste0(path,"mkeil.csv")) #Check excel file for any issues with data
 
 ###Confirmatory Analyses

### 2016-05-12 project_analyses/smraposo.R

@@ -15,7 +15,7 @@ ci95 <- function(x) {sem(x) * 1.96}
 theme_set(theme_linedraw())
 
 #Getting files
-path <- "~/replication_project/data/smraposo/"
+path <- "data/smraposo/"
 files <- dir(path, 
              pattern = "*.json")
 d.raw <- data.frame()
@@ -104,7 +104,7 @@ d.demos$delaytimeyrs = d.demos$delaytime / d.demos$delaydiv #Calculating time to
 d = d.demos
 
 # Write tidy file
-path <- "~/replication_project/processed_data/"
+path <- "processed_data/"
 write.csv(d.demos, file = paste0(path,"smraposo.csv")) #Check excel file for any issues with data
 
 

### 2016-05-12 project_analyses/ehermann.R
Small updates

@@ -32,7 +32,7 @@ itemQuestionsFirstData <- df[df$pfFirst == 0,]
 
 data.lm = lm(formula = scale(overclaimScore) ~ scale(pfClaimScore) + scale(accuracy), data = df)
 
-pval <- round(summary(data.lm)$coef["scale(pfClaimScore)","Pr(>|t|)"],7)
+pval <- summary(data.lm)$coef["scale(pfClaimScore)","Pr(>|t|)"]
 tval <- round(summary(data.lm)$coef["scale(pfClaimScore)","t value"],3)
 est <- round(summary(data.lm)$coef["scale(pfClaimScore)","Estimate"],3)
 degrees <- data.lm$df

### 2016-05-12 project_analyses/jmarias.R

@@ -233,7 +233,7 @@ write.csv(subjectmeans, file = paste0(path,"jmarias.csv")) #Check excel file for
 #################################################################################### 
 
 mathperflm4 <- lm(z.pvt ~ age + gender + z.genanx + I(z.genanx^2) + z.mathanx * z.mathmot + (I(z.mathanx^2) * z.mathmot), data = subjectmeans)
-pval <- round(summary(mathperflm4)$coef["z.mathmot:I(z.mathanx^2)","Pr(>|t|)"],3)
+pval <- summary(mathperflm4)$coef["z.mathmot:I(z.mathanx^2)","Pr(>|t|)"]
 tval <- round(summary(mathperflm4)$coef["z.mathmot:I(z.mathanx^2)","t value"],3)
 est <- round(summary(mathperflm4)$coef["z.mathmot:I(z.mathanx^2)","Estimate"],3)
 df <- mathperflm4$df

### 2016-05-12 project_analyses/smraposo.R

@@ -1,4 +1,3 @@
-rm(list=ls())
 library(rjson)
 library(plyr)
 library(splitstackshape)

### 2016-05-12 analysis.Rmd
Start analysis aggregation

@@
 ```{r}
-project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y")
+project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y") # Need lookup=T to initialize
 project_plan_raw <- gs_read_csv(project_plan_sheet)
@@
 project_plan <- project_plan_raw %>%
-  filter(`Include in final writeup?`==1) 
+  filter(`include_in_final_writeup`==1) 
 ```
+
+Read in project_info data from each project
+
+```{r}
+errors <- list()# Initialize an error var
+
+all_project_info <- data.frame( # initialize an empty dataframe
+  project_key = character()
+)
+
+project_keys <- list(project_plan$project_key) # Find user names that are included in analysis
+# For each user_
+
+temp_project_keys <- c("smraposo","jmarias","ehermann","mkeil.R")
+
+# Run all respective R code - need loop because project_keys same variable name
+for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
+  fp <- paste0("project_analyses/",project_key,".R")
+  source(fp)
+  if(exists("project_info")) { # If has project_info dataframe
+    all_project_info <- rbind.fill(all_project_info,project_info) # add to all data
+    rm("project_info") # In case other file does not same
+  } else {
+    errors <- c(errors,paste0(project_key," is missing project_info"))
+  }
+}
+
+```

### 2016-05-12 project_analyses/jsalloum.R
Add salloum analysis

@@ -1,0 +1,46 @@
+setwd("~/Repos/replication_project/")
+
+loadLibraries = function() {
+  library(tidyr)
+  library(dplyr)
+  library(ggplot2)
+  library(rjson)
+  library(tidyjson)
+  library(lme4)
+  library(lmerTest)
+  library(gridExtra)
+  library(lsr)
+}
+suppressMessages(loadLibraries())
+
+path <- "data/jsalloum/"
+files = dir(path, pattern = "*.json")
+
+d.raw = data.frame()
+
+for (f in files) {
+  jf = paste0(path, f)
+  jd = fromJSON(paste(readLines(jf), collapse=""))
+  for (elem in jd$answers$data) {
+    newRow = data.frame(workerId = jd$WorkerId,
+                        speakerId = elem$speakerId,
+                        speakerSex = elem$sex,
+                        plev = elem$plev,
+                        behaviorScore = ifelse(is.null(elem$behaviorScore), NA,
+                                               elem$behaviorScore))
+    d.raw = bind_rows(d.raw, newRow)
+  }
+}
+
+# d.af is the aggregated replication data 
+d.af = d.raw %>% 
+  mutate(workerId = as.factor(workerId),
+        speakerId = as.factor(speakerId),
+        speakerSex = ifelse(speakerSex == -1, "Male", "Female"),
+        plev = ifelse(plev == -1, "Low", "High")) %>%
+  group_by(speakerId, speakerSex, plev) %>%
+  summarise(behaviorScore = mean(behaviorScore, na.rm = T))
+
+# Additive model
+rs1.1 = aov(behaviorScore ~ plev * speakerSex, data = d.af)
+summary(rs1.1)

### 2016-06-24 project_analyses/salehi.R
analysis updates

@@ -1,6 +1,7 @@
 rm(list=ls())
-# library(tidyr)
-# library(dplyr)
+library(jsonlite)
+library(tidyr)
+library(dplyr)
 # library(ggplot2)
 # library(langcog) 
 # library(rjson)
@@ -80,9 +81,9 @@ summary(fitConTrait)
 project_info <- data.frame(project_key = "salehi",
                            rep_final_n = length(unique(d$workerid)),
                            rep_n_excluded = 0, 
-                           rep_es = , 
-                           rep_test_statistic = 
-                           rep_p_value = )
+                           rep_es = N, 
+                           rep_test_statistic = N,
+                           rep_p_value = N)
 
 
 # The result of mixed-model ANOVA for the original study was: A mixed-model
@@ -114,339 +115,3 @@ project_info <- data.frame(project_key = "salehi",
 # ANOVA's for each trait type across conditions to test the effect of condition
 # on the rating of each trait type. These follow-up tests have been repeated for
 # the replication data in the following.
-
-### Confirmatory analysis 2: repeated measure anova for each condition
-
-The authors have conducted a repeated measure ANOVA to compare the rating for masculine versus feminine traits within the divergent condition. this analysis for the replication data have been reported in the following:
-  
-  #### Confirmatory analysis 2.1: different trait types' rating within the divergent condition
-  
-  ```{r Confirmatory analysis 2.1: trait type rating within the divergent condition }
-#filtering the data points for the divergent condition
-divergent <- d.b2 %>% filter(condition == 'Divergent') 
-
-#effect of trait types in divergent condition: Within-subject anova
-# One Within Factor: fit <- aov(y~A+Error(Subject/A),data=mydataframe)
-fitDivergent <- aov(rating ~ traitType + Error(workerid/traitType), data=divergent)
-summary(fitDivergent)
-
-#effect size
-#filtering the data points for the masculine traits
-divergentMasculine <- divergent %>% filter(traitType == 'Masculine')
-
-#filtering the data points for the feminine traits
-divergentFeminine <- divergent %>% filter(traitType == 'Feminine')
-
-#effect size for the the difference in the rating of masculine and feminine traits within the divergent condition
-cohen.d(divergentMasculine$rating,divergentFeminine$rating)
-```
-
-
-Same as the divergent condition, for the convergent condition, the authors have conducted a repeated-measure ANOVA to compare the rating for masculine versus feminine traits in this condition. This analysis for the replicated data has been reported in the following:
-  
[…]

### 2016-06-24 paper.Rmd
paper outline

---
  title: "Psych 254 Replication Project Analysis"
author: "Eric Smith, Robert Hawkins, Michael C. Frank"
date: '`r Sys.Date()`'
output:
  html_document:
  number_sections: yes
toc: yes
---

Assessing the Replicability of Psychological Science Through Pedagogy

Contributions
Pedagogical recipe
Toolset (dplyr, ggplot, mturk, etc)
Author contact template
Course experiment templates
Extraction of key statistic, power analysis
Multiple reviews by team
Pre-registration
Proof of concept
Table w/ all included replications
Scatter plot of effect sizes?
Actual findings

Methods

Class Methods

Participants

IRB

Individual Replications

Preregistration

Project preregistration: https://osf.io/rxz8m/

  Results

Pedagogical assessment

how many replications were conducted to the intended standard, how many opted out etc.

Assessing the fidelity of replications to the original (in terms of same sample, same materials, same task parameters)

Scientific Assessment

Indices of replicability

Coding of previous years’ findings

Discussion

Importance of self-selected papers - these are the papers that interesting to next generation of researchers

How to archive and make searchable the results of this sort of class?
OSF - but need search tools
PsychFileDrawer
CurateScience

Supplemental

All materials that are needed for class to implement
Email templates
Spreadsheets
TA/prof auditing processes

### 2016-06-24 paper/paper.Rmd
paper folder

--- 2016-06-24 paper.Rmd
@@
 ---
-  title: "Psych 254 Replication Project Analysis"
-author: "Eric Smith, Robert Hawkins, Michael C. Frank"
-date: '`r Sys.Date()`'
-output:
-  html_document:
-  number_sections: yes
-toc: yes
+title: "Assessing the Replicability of Psychological Science Through Pedagogy"
+short-title: "Replication through pedagogy"
+output: kmr::apa_manuscript
+csl: apa6.csl
+bibliography: replication254.bib
+
+document-params: "a4paper,man,apacite,floatsintext"
+
+bib-tex: "library.bib"
+
+author-information:
+    - \author{Eric Smith*}
+    - \author{Robert X. D. Hawkins*}
+    - \author{Michael C. Frank}
+
+affiliation-information:
+    # Single affiliation
+    - \affiliation{Department of Psychology, Stanford University}
+
+author-note:
+    "The Author Note, containing contact information, acknowledgements, etc"
+
+abstract: 
+    "Abstract text."
+
+keywords:
+    "If provided, keywords will be displayed on a line beneath the abstract."
 ---
 
-Assessing the Replicability of Psychological Science Through Pedagogy
+```{r global_options, include=FALSE}
+rm(list=ls())
+knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = F, fig.path='figs/',
+                      echo=FALSE, warning=FALSE, cache=T, message=FALSE, sanitize = T)
+```
 
@@
 TA/prof auditing processes
+
+# Introduction 
+Cite fancy references [@Garnier2007].
+
+# Results 
+Results
+
+## Subsection 1 
+You can use R chunks directly to plot graphs.
+
+```{r, graph, echo=TRUE, message=FALSE, fig.height=4, fig.width=4, fig.align='center', fig.cap='Figure caption'}
+require("ggplot2")
+x <- 0:100
+y <- 2 * (x + rnorm(length(x), sd = 3) + 3)
+ggplot(data = data.frame(x, y), 
+       aes(x = x, y = y)) + 
+  geom_point() + 
+  geom_smooth(method = "lm")
+```
+
+## Subsection 2
+
+# Discussion
+
+# References

### 2016-06-24 project_analyses/lampinen.R
Extract lampinen project info

@@ -1,0 +1,98 @@
+library(rjson)
+library(knitr)
+library(dplyr)
+library(ggplot2)
+library(tidyr)
+library(lme4)
+
+data_location = "data/lampinen/"
+files = list.files(path = data_location,pattern="data_subject_.*.json")
+subject = vector()
+trial_type=vector()
+experiment_data=NULL
+practice_trial=vector()
+practice_trial=vector()
+for (i in 1:length(files)) { 
+  path = paste(data_location,files[i],sep="") #Path to file
+  c = file(path, "r")
+  l = readLines(c, -1L)
+  close(c)
+  these_data = lapply(X=l, fromJSON) #Convert list of json objects to list of R objects
+  
+  this_trial_data = list();
+  j = 1;
+  #For each trial in this experiment, extract data from it
+  for (trial_i in 1:length(these_data[[1]])) {
+    if(grepl("rotation",gsub(" ","",these_data[[1]][[trial_i]]$trial_type))) { #Only get data from rotation trials for this analysis, don't care about instructions, etc.
+      this_trial_data[[j]] = these_data[[1]][[trial_i]]
+      for (data_i in 1:length(this_trial_data[[j]])) {
+        if (length(this_trial_data[[j]][[data_i]]) > 1) { #Handle lists contained within a single trial's data
+          this_trial_data[[j]][[data_i]] = paste(this_trial_data[[j]][[data_i]],collapse='')
+        }
+      }
+      j = j+1
+    }
+  }
+  this_trial_data = do.call(bind_rows, lapply(this_trial_data, data.frame)); #convert to data frame
+  this_trial_data$subject = i #Anonymous subject ids
+  if (is.null(experiment_data)) {
+    experiment_data = bind_rows(this_trial_data)
+  }
+  else {
+    experiment_data = bind_rows(experiment_data,this_trial_data)
+  }
+}
+
+experiment_data = experiment_data %>% 
+  mutate(choiceStr = as.character(response_choices)) %>%
+  mutate(correct_response_key = ifelse(substr(as.character(experiment_data$response_mappings),1,7) == 'correct',
+                                       as.numeric(substr(choiceStr,1,2)),
+                                       as.numeric(substr(choiceStr,3,4))),
+         rotating = (rotation_speed != 0),
+         experiment_trial_type=gsub(" ","",experiment_trial_type)) %>%
[…]

### 2016-06-24 project_analyses/jsalloum.R
Package jsalloum results:

@@ -1,17 +1,8 @@
-setwd("~/Repos/replication_project/")
-
-loadLibraries = function() {
-  library(tidyr)
-  library(dplyr)
-  library(ggplot2)
-  library(rjson)
-  library(tidyjson)
-  library(lme4)
-  library(lmerTest)
-  library(gridExtra)
-  library(lsr)
-}
-suppressMessages(loadLibraries())
+library(tidyr)
+library(dplyr)
+library(ggplot2)
+library(rjson)
+library(tidyjson)
 
 path <- "data/jsalloum/"
 files = dir(path, pattern = "*.json")
@@ -42,5 +33,21 @@ d.af = d.raw %>%
   summarise(behaviorScore = mean(behaviorScore, na.rm = T))
 
 # Additive model
-rs1.1 = aov(behaviorScore ~ plev * speakerSex, data = d.af)
-summary(rs1.1)
+rs1.1 = lm(behaviorScore ~ plev + speakerSex, data = d.af)
+
+# Extract params
+params = anova(rs1.1)
+F_stat = params[1,4]
+p = params[1,5]
+dfnum = params$Df[1]
+dfdenom = params$Df[length(params$Df)]
+stat_descript <- paste0("F(",dfnum,", ",dfdenom,") = ",round(F_stat, 3))
+stat_descript
+
+project_info <- data.frame(
+  project_key = "jsalloum", 
+  rep_final_n = length(d.af$speakerId), 
+  rep_n_excluded = 0, 
+  rep_es = F_stat, 
+  rep_test_statistic = stat_descript,
+  rep_p_value = p)

### 2016-06-24 paper/paper.Rmd
paper drafting, intro + methods

--- 2016-06-24 paper.Rmd
@@
 ---
-  title: "Psych 254 Replication Project Analysis"
-author: "Eric Smith, Robert Hawkins, Michael C. Frank"
-date: '`r Sys.Date()`'
-output:
-  html_document:
-  number_sections: yes
-toc: yes
+title: "Assessing the Replicability of Psychological Science Through Pedagogy"
+short-title: "Replication Through Pedagogy"
+output: kmr::apa_manuscript
+csl: apa6.csl
+bibliography: replication254.bib
+
+document-params: "a4paper,man,apacite,floatsintext,longtable"
+
+bib-tex: "replication254.bib"
+
+author-information:
+    - \author{Eric Smith*, Robert X. D. Hawkins*, Michael C. Frank}
+
+affiliation-information:
+    - \affiliation{Department of Psychology, Stanford University}
+
+author-note:
+    "Thanks to the Stanford Department of Psychology and the Vice Provost for Undergraduate Education for funding to support the class."
+
+abstract: 
+    "Replications are important to science, but who will do them?
+One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs.
+We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level experimental methods.
+By a variety of measures, these replications were successful approximately half of the time, providing an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."
+
+keywords:
+    "Replication; Reproducibility; Pedagogy; Experimental Methods"
 ---
 
-Assessing the Replicability of Psychological Science Through Pedagogy
+```{r global_options, include=FALSE}
+rm(list=ls())
+library(knitr)
+knitr::opts_chunk$set(fig.width=6, fig.height=5, fig.crop = FALSE, 
+                      fig.path='figs/', echo=FALSE, warning = FALSE, 
+                      cache=FALSE, message = FALSE, sanitize = TRUE)
+library(googlesheets)
+library(dplyr)
+library(xtable)
+```
+
+Reproducibility is a core value for empirical research, but there is increasing concern throughout psychology that weak statistical standards and methodological practices have led to low empirical rates of replication [@osc2015].
+Under the current incentive structure for science, direct replication is not typically valued, however.
+One potential solution to this problem is to make direct replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
+Despite enthusiasm for this idea, however [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data -- beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] -- to support its efficacy.
+
+In the current article, we provide evidence on this issue by reporting the results of replication projects conducted in a single class (a graduate-level experimental methods course).
+As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*.
+These studies both provide insight into the process of pedagogical replication and give evidence about the state of replicability.
+
+With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy.
+This process is dramatically facilitated by the use of standardized (and free) technical tools for statistical analysis, data and code sharing, and creation of web experiments.
+Nevertheless, there are significant limitations on what can be done in the course of a single term and within the constraints of a course budget.
+We return in the Discussion to limitations on our approach.
+
+With respect to broader questions of meta-science, it is a challenging proposition to estimate the reproducibility of an entire literature [cf. @osc2015;@gilbert2016;@anderson2016].
+
+In sum, we view the contribution of the current work to be two-fold.
+First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
+Second, we provide an estimate of how likely it is for a graduate student to choose an article of interest in *Psychological Science* and -- within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fielility to be able to build on it in future work.
+We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
+Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.
+
+```{r}
+project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup=TRUE) # Need lookup=T to initialize
+project_plan_raw <- gs_read_csv(project_plan_sheet)
+```
+
+{\small 
+```{r, results='asis',  fig.pos = "t", fig.cap = "Summary of attempted replications."}
+
+project_plan <- project_plan_raw %>%
+  filter(`include_in_final_writeup`==1)
+
+ppt <- project_plan %>%
+        select(cite, expt_num, open_data,
+               open_materials, original_on_turk, original_n,collected_n)
+
+names(ppt) = c("Citation", "Expt Num", "Data", "Materials", "Turk?", 
+               "N (orig)","N (rep)")
+
+# print(xtable(ppt, caption = "Summary of attempted replications", 
+#        label = "tab:summary"), include.rownames=FALSE)
+```
+
+% latex table generated in R 3.3.0 by xtable 1.8-2 package
+% Fri Jun 24 12:02:11 2016
+\begin{table}[ht]
+\centering
+\begin{tabular}{lllllrr}
+  \hline
+Citation & Expt Num & Data & Materials & Turk? & N (orig) & N (rep) \\ 
+  \hline
+@storm2015 & 3 & No & No & No &  48 &  61 \\ 
+@lewis2015 & 4 & No & Yes & Yes & 122 & 128 \\ 
+@scopelliti2015 & 3 & No & Yes & Yes & 550 & 124 \\ 
+@liverence2015 & 1 & No & Some & No &  18 &  \\ 
+@wang2015 & 2 & No & No & No & 219 & 397 \\ 
+@sofer2015 & 1 & No & Yes & No &  48 &  95 \\ 
+@ko2015 & 2 & Yes & Some & No &  40 &  40 \\ 
+@dunning2015 & 1b & No & Yes & Yes & 202 &  50 \\ 
+@proudfoot2015 & 1 & No & No & Yes &  80 &  84 \\ 
+@zaval2015 & 1 & Yes & Yes & Yes & 312 & 328 \\ 
+@franconeri2015 & 1a & No & No & No &  12 &  27 \\ 
+   \hline
+\end{tabular}
+\caption{Summary of attempted replications} 
+\label{tab:summary}
+\end{table}
+
+# Methods
+
+We begin by describing the general method of the class, then discuss shared methods for the replications and the process of development for each project.
+
+## Class Outline
+
+All projects were completed as part of a class (syllabus and materials available at [http://psych254.stanford.edu]()).
+At the initiation of class, all students were told that they had the opportunity to participate in a group replication project to which they could contribute their class project.
+The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.
+
+Students selected projects based on interest, rather than via a systematic sampling strategy.
+Thus, all interpretation of our findings should be with respect to the distribution of student interest.
+Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general.
+This sampling strategy may thus bias our results towards more exciting or novel findings.
+
+Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that 2/3 of these opted out projects were judged by the instructor team to have been successful replications; thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
+
+## Participants
+
+All participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.
+Note that of the `{r} nrow(ppt)` studies included in the final sample, `{r} sum(project_plan$original_on_turk=="Yes")` (`{r} round(mean(ppt$original_on_turk), digits=2)`%) were originally conducted on Mechanical Turk.
+All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+
+## Materials and Methods
+
+Of the `{r} nrow(ppt)` studies included in the final sample, `{r} round(mean(ppt$open_materials == "Yes" | ppt$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
+For `{r} sum(!is.na(authors_contact))` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors).
+Responses were received in all but one case, usually within a matter of days.
+
+## Workflow
+
+All materials and methods for our replication studies are available at [https://github.com/StanfordPsych254]().
+All experiments were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
+All analyses were written using R, a free and open-source platform for statistical analysis.
+
+One part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices.
+Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
+Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g.
+statistical tests, figures).
+This document can be compiled into a variety of formats (e.g., HTML, PDF, Microsoft Word).
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by copying and pasting between analysis outputs and manuscripts.
+
+## Preregistration and Review
+
+To ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH).
+In addition to as-needed guidance, each student collected two pilot samples.
+The first, "pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
+The goal of this pilot was to ensure that all needed data were being logged by the experiment and that analytic scripts for the confirmatory analyses functioned appropriately.
+After pilot A was completed, the instructor or a TA reviewed the student's experiment (acting as a participant) and critiqued and reviewed the student's full analytic code and output.
+
+Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from Mechanical Turk.
+The goal of this pilot was to ensure that participants were able to complete the experiment and did not report any substantial issues with instructions or technical details of the experiment.
+(All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing text).
+At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analysis.
+The goal of this code review was to ensure that all planned analyses were
 
@@
 Pedagogical recipe
-Toolset (dplyr, ggplot, mturk, etc)
 Author contact template
@@
 Actual findings
+## Individual Replications
 
-Methods
+Details of individual replications are available in the supplementary materials.  
+### @storm2015
 
-Class Methods
+### @lewis2015
 
-Participants
+### @scopelliti2015
 
-IRB
+### @liverence2015
 
-Individual Replications
+### @wang2015
 
-Preregistration
+### @ko2015
 
-Project preregistration: https://osf.io/rxz8m/
+### @dunning2015
 
-  Results
+# Results
 
-Pedagogical assessment
+Analyses for the final project were pre-registered ([https://osf.io/rxz8m/]()).
+
+## Pedagogical assessment
 
@@
 
-Scientific Assessment
+## Scientific Assessment
 
-Indices of replicability
+### Indices of replicability
 
-Coding of previous years’ findings
+### Coding of previous years’ findings
 
-Discussion
+# Discussion
 
@@
 
-Supplemental
+# Supplemental
 
@@
 TA/prof auditing processes
+
+# References

### 2016-06-24 project_analyses/salehi.R
Remove annoying rm()s...

@@ -1,4 +1,3 @@
-rm(list=ls())
 library(jsonlite)
 library(tidyr)
 library(dplyr)

### 2016-06-24 paper/paper.Rmd
methods and intro

@@
 author-information:
-    - \author{Eric Smith*, Robert X. D. Hawkins*, Michael C. Frank}
+    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, & Michael C. Frank}
 
@@
 
-With respect to broader questions of meta-science, it is a challenging proposition to estimate the reproducibility of an entire literature [cf. @osc2015;@gilbert2016;@anderson2016].
+With respect to broader questions of meta-science, it is a challenging proposition to estimate the replicability of an entire literature [cf.
+@osc2015;@gilbert2016;@anderson2016].
+Making such an estimate requires determining a sampling strategy, a notion of what constitutes a direct replication, what constitutes a successful replication, among many other difficult decisions.
+In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, and within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work.
+We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
+Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.
 
@@
 First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
-Second, we provide an estimate of how likely it is for a graduate student to choose an article of interest in *Psychological Science* and -- within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fielility to be able to build on it in future work.
-We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
-Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.
+Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could easily be reproduced by a motivated student.
 
@@
 
-names(ppt) = c("Citation", "Expt Num", "Data", "Materials", "Turk?", 
+names(ppt) = c("Citation", "Expt", "Data", "Materials", "Turk?", 
                "N (orig)","N (rep)")
@@
   \hline
-Citation & Expt Num & Data & Materials & Turk? & N (orig) & N (rep) \\ 
+Citation & Expt & Data & Materials & Turk? & N (orig) & N (rep) \\ 
   \hline
@@
 At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analysis.
-The goal of this code review was to ensure that all planned analyses were
+The goal of this code review was to ensure that all planned analyses were specified correctly and with sufficient detail to permit inclusion in the broader analysis.
 
-Contributions
-Pedagogical recipe
-Author contact template
-Course experiment templates
-Extraction of key statistic, power analysis
-Multiple reviews by team
-Pre-registration
-Proof of concept
-Table w/ all included replications
-Scatter plot of effect sizes?
-Actual findings
+After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made the requested change.
+Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.
+(In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review).
+
+## Sample size determination and statistical approach
+
+After selecting a paper of interest, students selected a particular study from within that paper based on their judgment of interest and feasibility.
+The modal study chosen was the first, but several students chose later studies in a set as well.
+
+For purposes of planning and analysis, we asked stuents Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies.
+Often a wide variety of statistical tests were conducted, often within one or several regression models with multiple specifications.
+Thus, we interpret "key statistical test" results with caution.
+Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis.
+This test was determined by iterative discussion between the student, instructor, and TAs.
+
+Derermining appropriate sample sizes is a major challenge in replication research [@button2013,@simonsohn2015].
+Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;button2013], but -- especially with the constraints of a limited budget -- it may be impossible to follow more conservative guidelines in all cases.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or underpowered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
+
+We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated $1,500 but one student contributed personal research funds, leading to a total cost of \approx $1,700 for all studies.
+We attempted to set payment for our studies at approximately $6/hour based on timing estimated from pilot A sessions.] In `{r} sum(project_plan$power_standard == "80% power")} cases, we powered the replication attempt to 80% post-hoc power.
+In `{r} sum(project_plan$power_standard == "Original")` cases, we used the original sample size.
+In one case, the original experiment was apparently extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would apparently yield high power.
+In one case, we reduced the number of trials as part of the adaptation to mechanical turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in Supplemntal Materials).
+
 ## Individual Replications
@@
 Details of individual replications are available in the supplementary materials.
-### @storm2015
+Students chose findings from a wide variety of domains for replication.
+One group was nvestigations of memory and visual attention [e.g., @franconeri2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
+A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
+Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
 
-### @lewis2015
+## Analysis strategy
 
-### @scopelliti2015
-
-### @liverence2015
-
-### @wang2015
-
-### @ko2015
-
-### @dunning2015
+Analyses for the final project were pre-registered ([https://osf.io/rxz8m/]())
 
@@
 
-Analyses for the final project were pre-registered ([https://osf.io/rxz8m/]()).
+.
 

### 2016-06-24 analysis.Rmd
analysis updates

@@
 library(readr)
+library(tidyr)
 ```
@@
 
-temp_project_keys <- c("smraposo","jmarias","ehermann","mkeil.R")
+temp_project_keys <- c("mkeil","smraposo","jmarias","ehermann") # Only do users we have data for currently
+length(project_keys[[1]]) - length(temp_project_keys) # How many people missing
+
+##
 
 # Run all respective R code - need loop because project_keys same variable name
+rm("project_info") # In case var is saved
 for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"

### 2016-06-24 paper/paper.Rmd
formatting

@@
 author-information:
-    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, & Michael C. Frank}
+    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}
 
@@
                       fig.path='figs/', echo=FALSE, warning = FALSE, 
-                      cache=FALSE, message = FALSE, sanitize = TRUE)
+                      cache=TRUE, message = FALSE, sanitize = TRUE)
 library(googlesheets)
@@
 
-```{r}
+```{r, results='asis'}
 project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup=TRUE) # Need lookup=T to initialize
 project_plan_raw <- gs_read_csv(project_plan_sheet)
-```
-
-{\small 
-```{r, results='asis',  fig.pos = "t", fig.cap = "Summary of attempted replications."}
 
@@
 @zaval2015 & 1 & Yes & Yes & Yes & 312 & 328 \\ 
-@franconeri2015 & 1a & No & No & No &  12 &  27 \\ 
+@xu2015 & 1a & No & No & No &  12 &  27 \\ 
    \hline
@@
 
-We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated $1,500 but one student contributed personal research funds, leading to a total cost of \approx $1,700 for all studies.
-We attempted to set payment for our studies at approximately $6/hour based on timing estimated from pilot A sessions.] In `{r} sum(project_plan$power_standard == "80% power")} cases, we powered the replication attempt to 80% post-hoc power.
-In `{r} sum(project_plan$power_standard == "Original")` cases, we used the original sample size.
+We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
+^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from pilot A sessions.]
+In 
+`{r} sum(project_plan$power_standard == "80% power")} 
+cases, we powered the replication attempt to 80\% post-hoc power. In 
+`{r} sum(project_plan$power_standard == "Original")` 
+cases, we used the original sample size.
 In one case, the original experiment was apparently extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would apparently yield high power.
@@
 Students chose findings from a wide variety of domains for replication.
-One group was nvestigations of memory and visual attention [e.g., @franconeri2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
+One group was nvestigations of memory and visual attention [e.g., @xu2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
 A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].

### 2016-06-24 project_analyses/auc.R
deleted unnecesary packages

@@ -31,7 +31,7 @@ summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
     )
 
     # Rename the "mean" column    
-    datac <- plyr::rename(datac, c("mean" = measurevar))
+    datac <- rename(datac, mean = measurevar)
     datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
 
     # Confidence interval multiplier for standard error

### 2016-06-24 project_analyses/ehermann.R

@@ -2,7 +2,6 @@ library(knitr)
 library(ggplot2)
 library(tidyr)
 library(lme4)
-detach("package:dplyr")
 library(dplyr)
 
 ##Results

### 2016-06-24 project_analyses/jmarias.R

@@ -1,13 +1,13 @@
 library(tidyr)
-library(plyr)
+# library(plyr)
 library(dplyr)
 library(psych)
 library(ggplot2)
 library(Hmisc)
-library(xtable)
-library(knitr)
+# library(xtable)
+# library(knitr)
 library(rjson)
-library(tidyjson)
+# library(tidyjson)
 library(memisc)
 
 #Script for generating clean correlation table (bottom triangle only) with significance stars

### 2016-06-24 project_analyses/jreynolds.R

@@ -1,4 +1,4 @@
-rm(list=ls())
+# rm(list=ls())
 library(tidyr)
 library(dplyr)
 library(ggplot2)

### 2016-06-24 project_analyses/lampinen.R

@@ -1,9 +1,9 @@
 library(rjson)
-library(knitr)
+# library(knitr)
 library(dplyr)
 library(ggplot2)
 library(tidyr)
-library(lme4)
+# library(lme4)
 
 data_location = "data/lampinen/"
 files = list.files(path = data_location,pattern="data_subject_.*.json")

### 2016-06-24 project_analyses/mkeil.R

@@ -1,12 +1,11 @@
 library(ggplot2)
 library(tidyr)
-library(lme4)
+# library(lme4)
 library(rjson)
-library(effsize)
-library(compute.es)
-library(grid)
-library(png)
-detach("package:dplyr")
+# library(effsize)
+# library(compute.es)
+# library(grid)
+# library(png)
 library(dplyr)
 
 sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}

### 2016-06-24 project_analyses/auc.R
deleted unnecesary packages 2

@@ -1,5 +1,5 @@
-library(readr)
-library(jsonlite)
+# library(readr)
+library(rjson)
 library(dplyr)
 
 ## Code in this block taken from: http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)

### 2016-06-24 project_analyses/ehermann.R

@@ -1,7 +1,7 @@
-library(knitr)
+# library(knitr)
 library(ggplot2)
 library(tidyr)
-library(lme4)
+# library(lme4)
 library(dplyr)
 
 ##Results

### 2016-06-24 project_analyses/jmarias.R

@@ -1,14 +1,14 @@
 library(tidyr)
 # library(plyr)
 library(dplyr)
-library(psych)
+# library(psych)
 library(ggplot2)
-library(Hmisc)
+# library(Hmisc)
 # library(xtable)
 # library(knitr)
 library(rjson)
 # library(tidyjson)
-library(memisc)
+# library(memisc)
 
 #Script for generating clean correlation table (bottom triangle only) with significance stars
 corstarsl <- function(x){ 

### 2016-06-24 project_analyses/rhiac.R

@@ -10,7 +10,7 @@ library(tidyr)
 library(dplyr)
 library(ggplot2) 
 # library(langcog)
-library(jsonlite)
+library(rjson)
 # library(broom)
 # library(MBESS)
 # library(qdap)

### 2016-06-24 project_analyses/smraposo.R

@@ -1,11 +1,11 @@
 library(rjson)
-library(plyr)
-library(splitstackshape)
+# library(plyr)
+library(splitstackshape) # csplit is the call, can change to tidyr "separate"
 library(dplyr)
 library(tidyr)
 library(stringr)
 library(ggplot2)
-library(knitr)
+# library(knitr)
 
 
 #Loading helpers

### 2016-06-24 analysis.Rmd

--- 2016-05-12 analysis.Rmd
@@
 ```{r}
+library(plyr)
 library(dplyr)
@@
 
-temp_project_keys <- c("smraposo","jmarias","ehermann","mkeil.R")
+temp_project_keys <- c("mkeil","smraposo","jreynolds","jmarias","ehermann") # Only do users we have data for currently
+length(project_keys[[1]]) - length(temp_project_keys) # How many people missing
+
+##
 
 # Run all respective R code - need loop because project_keys same variable name
+rm("project_info") # In case var is saved
 for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
@@
   source(fp)
+  #tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
   if(exists("project_info")) { # If has project_info dataframe

### 2016-06-24 project_analyses/smraposo.R
Merged

@@ -1,5 +1,4 @@
 library(rjson)
-library(plyr)
 library(splitstackshape)
 library(dplyr)
 library(tidyr)

### 2016-06-24 collect_values.R
more cleanup

@@ -1,8 +1,0 @@
-library(tidyr)
-library(dplyr)
-library(rjson)
-library(ggplot2)
-library(lme4)
-library(langcog) # devtools::install_github("langcog/langcog")
-sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
-ci95 <- function(x) {sem(x) * 1.96}

### 2016-06-24 project_analyses/auc.R

@@ -1,4 +1,3 @@
-# library(readr)
 library(rjson)
 library(dplyr)
 

### 2016-06-24 project_analyses/ehermann.R

@@ -1,7 +1,5 @@
-# library(knitr)
 library(ggplot2)
 library(tidyr)
-# library(lme4)
 library(dplyr)
 
 ##Results

### 2016-06-24 project_analyses/jmarias.R

@@ -1,18 +1,10 @@
 library(tidyr)
-# library(plyr)
 library(dplyr)
-# library(psych)
 library(ggplot2)
-# library(Hmisc)
-# library(xtable)
-# library(knitr)
 library(rjson)
-# library(tidyjson)
-# library(memisc)
 
 #Script for generating clean correlation table (bottom triangle only) with significance stars
 corstarsl <- function(x){ 
-  require(Hmisc) 
   x <- as.matrix(x) 
   R <- rcorr(x)$r 
   p <- rcorr(x)$P 

### 2016-06-24 project_analyses/jsalloum.R

@@ -1,8 +1,6 @@
 library(tidyr)
 library(dplyr)
-library(ggplot2)
 library(rjson)
-# library(tidyjson)
 
 path <- "data/jsalloum/"
 files = dir(path, pattern = "*.json")

### 2016-06-24 project_analyses/lampinen.R

@@ -1,9 +1,7 @@
 library(rjson)
-# library(knitr)
 library(dplyr)
 library(ggplot2)
 library(tidyr)
-# library(lme4)
 
 data_location = "data/lampinen/"
 files = list.files(path = data_location,pattern="data_subject_.*.json")

### 2016-06-24 project_analyses/mkeil.R

@@ -1,11 +1,5 @@
-library(ggplot2)
 library(tidyr)
-# library(lme4)
 library(rjson)
-# library(effsize)
-# library(compute.es)
-# library(grid)
-# library(png)
 library(dplyr)
 
 sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}

### 2016-06-24 project_analyses/rhiac.R

@@ -9,11 +9,7 @@
 library(tidyr) 
 library(dplyr)
 library(ggplot2) 
-# library(langcog)
 library(rjson)
-# library(broom)
-# library(MBESS)
-# library(qdap)
 
 # Therefore, I've run power analysis on one of the key effects, 
 # the effect of condition on behavioral intentions (d=0.36)

### 2016-06-24 project_analyses/salehi.R

@@ -1,22 +1,7 @@
 library(jsonlite)
 library(tidyr)
 library(dplyr)
-# library(ggplot2)
-# library(langcog) 
-# library(rjson)
-# library(tidyjson)
-# library(car)
-# library(effsize)
-# library(compute.es)
-# library(lme4)
-# library(lsr)
-# library(xlsx)
-# library(knitr)
-# library(png)
-# library(grid)
-# library(lmtest)
-# library(lmerTest)
-# library(gridExtra)
+
 
 #functions for se and CI
 sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}

### 2016-06-24 project_analyses/smraposo.R

@@ -1,11 +1,8 @@
 library(rjson)
-# library(plyr)
 library(splitstackshape) # csplit is the call, can change to tidyr "separate"
 library(dplyr)
 library(tidyr)
 library(stringr)
-library(ggplot2)
-# library(knitr)
 
 
 #Loading helpers

### 2016-06-24 analysis.Rmd
Analysis update no plyr

@@
 ```{r}
-library(plyr)
 library(dplyr)
@@
   fp <- paste0("project_analyses/",project_key,".R")
-  source(fp)
-  #tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
+  #source(fp)
+  tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
   if(exists("project_info")) { # If has project_info dataframe
-    all_project_info <- rbind.fill(all_project_info,project_info) # add to all data
+    all_project_info <- bind_rows(all_project_info,project_info) # add to all data
     rm("project_info") # In case other file does not same

### 2016-06-24 analysis.Rmd
analysis

--- 2016-06-24 analysis.Rmd
@@
 ```{r}
-project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y") # Need lookup=T to initialize
+project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup = TRUE) # Need lookup=T to initialize
 project_plan_raw <- gs_read_csv(project_plan_sheet)
@@
 
-temp_project_keys <- c("mkeil","smraposo","jreynolds","jmarias","ehermann") # Only do users we have data for currently
+temp_project_keys <- c("smraposo","jreynolds","jmarias","ehermann", "mkeil") # Only do users we have data for currently
 length(project_keys[[1]]) - length(temp_project_keys) # How many people missing
@@
 for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
+  print(project_key)
   fp <- paste0("project_analyses/",project_key,".R")

### 2016-06-24 project_analyses/mkeil.R
mkeil

@@ -2,36 +2,32 @@ library(tidyr)
 library(rjson)
 library(dplyr)
 
-sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
-ci95 <- function(x) {sem(x) * 1.96}
-
 path <- "data/mkeil/"
 files <- dir(path, pattern = "*.json")
 d.raw <- data.frame()
 for (f in files) {
   jf <- paste0(path, f)
   jd <- fromJSON(paste(readLines(jf), collapse=""))
-  jd$answers$data[9]
+  # jd$answers$data[9]
   for(i in 1:8){
-    id <- data.frame(
-                   workerId = jd$WorkerId,
-                   trial_num = i,
-                   start_num = jd$answers$data[[i]]$start_number,
-                   digits = jd$answers$data[[i]]$digits,
-                   word_condition = jd$answers$data[[i]]$word_condition,
-                   save_choice = jd$answers$data[[i]]$save_choice,
-                   save_condition = jd$answers$data[[i]]$save_condition,
-                   FileB = jd$answers$data[[i]]$FileB,
-                   FileA = jd$answers$data[[i]]$FileA,
-                   B_Recall = jd$answers$data[[i]]$B_Recall,
-                   A_Recall = jd$answers$data[[i]]$A_Recall,
-                   time = jd$answers$data[[i]]$time,
-                   age = jd$answers$data[[9]]$age,
-                   gender = jd$answers$data[[9]]$gender,
-                   homelang = jd$answers$data[[9]]$homelang,
-                   race = jd$answers$data[[9]]$race
-                   # comments = jd$answers$data[[9]]$comments
-                   )
+    id <- data.frame(workerId = jd$WorkerId,
+                     trial_num = i,
+                     start_num = jd$answers$data[[i]]$start_number,
+                     digits = jd$answers$data[[i]]$digits,
+                     word_condition = jd$answers$data[[i]]$word_condition,
+                     save_choice = jd$answers$data[[i]]$save_choice,
+                     save_condition = jd$answers$data[[i]]$save_condition,
+                     FileB = jd$answers$data[[i]]$FileB,
+                     FileA = jd$answers$data[[i]]$FileA,
+                     B_Recall = jd$answers$data[[i]]$B_Recall,
[…]

### 2016-06-24 data/jedtan/anonymization.R
jed data

@@ -1,0 +1,13 @@
+#MCF anonymization
+rawDem$id <- paste0("anon",1:19)
+rdd <- left_join(rawD, select(rawDem, WorkerID, id))
+rdd$WorkerID <- rdd$id
+rdd <- select(rdd, -id)
+rawDem$WorkerID <- rawDem$id
+rawDem <- select(rawDem, -id)
+
+excluded <- rawD %>%
+  filter(Trial <= 2, Time > 30000, Block > 0)
+
+readr::write_csv(rdd, "data/jedtan/final_results_anon.csv")
+readr::write_csv(rawDem, "data/jedtan/final_demographics_anon.csv")

### 2016-06-24 project_analyses/jedtan.R
jed

@@ -1,0 +1,92 @@
+library(dplyr)
+# library(ggplot2)
+# library(lsr)
+# library(lme4)
+
+rawD <- read.csv("data/jedtan/final_results_anon.csv")
+rawDem <- read.csv("data/jedtan/final_demographics_anon.csv")
+
+d <- rawD %>%
+  filter(Time < 30000, Trial > 2, Block > 0) %>% 
+  mutate(epoch= floor((Trial-1)/10) + 1, keyPressesOver = KeyPresses-MinKeyPresses) %>% 
+  rename(Transition=Stimulus)
+d$Transition <- factor(d$Transition, levels=c(0, 1), labels=c("Slide", "Fade"))
+d$epoch <- factor(d$epoch)
+
+transition_means = d %>% 
+  group_by(WorkerID, Transition) %>% 
+  summarise(meanTime = mean(Time), meanKeyPressOver = mean(keyPressesOver)) %>% 
+  group_by(Transition) %>% 
+  summarise(meanTime = mean(meanTime), meanKeyPressOver = mean(meanKeyPressOver))
+transition_worker_means = d %>% 
+  group_by(WorkerID, Transition, Age) %>% 
+  summarise(meanTime = mean(Time), meanKeyPressOver = mean(keyPressesOver))
+
+slide_mean = round(transition_means$meanTime[1]/1000, digits=2)
+fade_mean =  round(transition_means$meanTime[2]/1000, digits=2)
+
+full_t.test <- t.test((transition_worker_means %>% filter(Transition == "Fade"))$meanTime, (transition_worker_means %>% filter(Transition == "Slide"))$meanTime, paired=TRUE)
+
+# epoch <- d %>% group_by(WorkerID, epoch, Transition) %>% 
+#   summarise(meanTime = mean(Time), meanPress = mean(KeyPresses))
+
+full_cohensDVal <- lsr::cohensD((epoch %>% filter(Transition == "Fade"))$meanTime, (epoch %>% filter(Transition == "Slide"))$meanTime)
+
+#As a key statistic, Liverence and Scholl report that "Across all trials, 
+# participants were on average 1.41 s faster per trial on slide-transition blocks
+# than on fade-transition blocks (9.27 s vs. 10.68 s, a difference of 15.2%), 
+#t(17) = 5.22, p< .001, d = 1.23." The same statistics generated over all trials 
[…]

### 2016-06-24 project_analyses/mkeil.R
Remove unnecessary missing functions

@@ -215,7 +215,7 @@ df <- ttestB8$parameter
 p.val <-ttestB8$p.val
 
 #effect size for difference in conditions
-cohens_d <- cohen.d(dword8Save$meanB,dword8Delete$meanB)
+# cohens_d <- cohen.d(dword8Save$meanB,dword8Delete$meanB)
 # 
 # The result of the 8-word File B recall for the original study was: 
 # 

### 2016-06-24 project_analyses/smraposo.R

@@ -8,7 +8,6 @@ library(stringr)
 #Loading helpers
 sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
 ci95 <- function(x) {sem(x) * 1.96}
-theme_set(theme_linedraw())
 
 #Getting files
 path <- "data/smraposo/"
@@ -140,7 +139,3 @@ project_info <- data.frame(
   rep_es = Fstat1, 
   rep_test_statistic = stat_descript,
   rep_p_value = pval1)
-
-
-
-

### 2016-06-24 analysis.Rmd
Get rid of list of project keys

@@
 
-project_keys <- list(project_plan$project_key) # Find user names that are included in analysis
+project_keys <- project_plan$project_key # Find user names that are included in analysis
 # For each user_
@@
 temp_project_keys <- c("smraposo","jreynolds","jmarias","ehermann", "mkeil") # Only do users we have data for currently
-length(project_keys[[1]]) - length(temp_project_keys) # How many people missing
-
-##
 
@@
 rm("project_info") # In case var is saved
-for(project_key in temp_project_keys) { # change from temp - test; project_key <- "smraposo"
+for(project_key in project_keys) { # change from temp - test; project_key <- "smraposo"
   print(project_key)

### 2016-06-24 analysis.Rmd
Fix catch error

@@
 for(project_key in project_keys) { # change from temp - test; project_key <- "smraposo"
-  print(project_key)
+  print(paste0("Running ",project_key))
   fp <- paste0("project_analyses/",project_key,".R")
   #source(fp)
-  tryCatch(source(fp), error=function(e) {errors <- c(errors,paste0(project_key," has an error in .R file"),print(fp))}) 
+  tryCatch(source(fp), error=function(e) {print(e)}) 
   if(exists("project_info")) { # If has project_info dataframe

### 2016-06-24 analysis.Rmd
updates

@@
 
-project_keys <- project_plan$project_key # Find user names that are included in analysis
-# For each user_
+project_keys <- project_plan$project_key # Find user names that are included in
 
-temp_project_keys <- c("smraposo","jreynolds","jmarias","ehermann", "mkeil") # Only do users we have data for currently
+passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
+             "jedtan", "lampinen", "salehi")
+failing <- c("sraposo", "auc", "rhiac")
 
 # Run all respective R code - need loop because project_keys same variable name
-rm("project_info") # In case var is saved
-for(project_key in project_keys) { # change from temp - test; project_key <- "smraposo"
-  print(paste0("Running ",project_key))
+for(project_key in passing) { # project_keys
   fp <- paste0("project_analyses/",project_key,".R")
-  #source(fp)
-  tryCatch(source(fp), error=function(e) {print(e)}) 
-  if(exists("project_info")) { # If has project_info dataframe
-    all_project_info <- bind_rows(all_project_info,project_info) # add to all data
-    rm("project_info") # In case other file does not same
+
+  print(fp)
+
+  tryCatch(source(fp), 
+           error = function(e) {
+             errors <- c(errors, paste0(project_key," has an error in .R file"))
+             }
+           )
+
+  # If has project_info dataframe, add to all data
+  if(exists("project_info")) { 
+    all_project_info <- bind_rows(all_project_info,project_info) 
+    # rm("project_info") # In case other file does not same
   } else {
@@
 }
-
 ```

### 2016-06-24 project_analyses/rhiac.R

@@ -4,8 +4,6 @@
 # MCF NOTE: this script runs over hand-deduped anonymized data. I removed by hand
 # the 7 datapoints that were accidentally run twice (all in the control
 # condition). There should be 321 participants (not 328).
-
-
 library(tidyr) 
 library(dplyr)
 library(ggplot2) 

### 2016-06-24 project_analyses/salehi.R

@@ -1,11 +1,10 @@
-library(jsonlite)
 library(tidyr)
 library(dplyr)
 
-
-#functions for se and CI
-sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
-ci95 <- function(x) {sem(x) * 1.96}
+## MCF: note that Shima chose the followup ANOVA to be the primary test for power 
+# analysis, and so that's what we're using as the outcome. but actually, on further 
+# reflection we think it's the interaction that is most theoretically central. 
+# in fact she gets the interaction, though. 
 
 path <- "data/salehi/"
 files <- dir(path, 
@@ -17,9 +16,9 @@ d.raw <- data.frame()
 #reading the variables of interest for each participants from .json files and turning them into one data.frame
 for (f in files) {
   jf <- paste0(path,f)
-  jd <- fromJSON(paste(readLines(jf), collapse=""))
+  jd <- jsonlite::fromJSON(paste(readLines(jf), collapse=""))
   id <- data.frame(workerid = jd$WorkerId, 
-                   trial_number_block=       as.factor(jd$answers$data$trial_number_block),
+                   trial_number_block=as.factor(jd$answers$data$trial_number_block),
                    rating = as.numeric(jd$answers$data$rating),
                    gender = jd$answers$data$gender,
                    age = jd$answers$data$age,
@@ -55,31 +54,51 @@ write_csv(d, "processed_data/salehi.csv")
 # creativity when divergence was emphasized, rather than convergence, F(1, 78) =
 # 10.21, p = .002, d = 0.71.
 
-# One Within Factors W1, One Between Factors B1  
-fitConTrait <- aov(rating ~ (traitType*condition) + 
-                     Error(workerid/(traitType)) + 
-                     (condition),
-                   data = d)
-summary(fitConTrait)
+#filtering data points for masculine data points
+masculine <- d %>% filter(traitType == 'Masculine')
 
+#averaging ratings for each participant
+masculine <- masculine %>%
+  group_by(condition, workerid) %>%
+  summarize(workermean=mean(rating))
+
+#one-way anova
+fitMasculine <- aov(workermean ~ condition, data = masculine)
+summary(fitMasculine)
+
+p <- summary(fitMasculine)[[1]][1,5]
+Fval <- summary(fitMasculine)[[1]][1,4]
+df1 <- summary(fitMasculine)[[1]][1,1]
[…]

### 2016-06-24 project_analyses/smraposo.R

@@ -4,12 +4,6 @@ library(dplyr)
 library(tidyr)
 library(stringr)
 
-
-#Loading helpers
-sem <- function(x) {sd(x, na.rm=TRUE) / sqrt(length(x))}
-ci95 <- function(x) {sem(x) * 1.96}
-theme_set(theme_linedraw())
-
 #Getting files
 path <- "data/smraposo/"
 files <- dir(path, 
@@ -140,7 +134,3 @@ project_info <- data.frame(
   rep_es = Fstat1, 
   rep_test_statistic = stat_descript,
   rep_p_value = pval1)
-
-
-
-

### 2016-06-24 analysis.Rmd
all

@@
              "jedtan", "lampinen", "salehi")
-failing <- c("sraposo", "auc", "rhiac")
+failing <- c("smraposo", "auc", "rhiac")
 
@@
   print(fp)
-
   tryCatch(source(fp), 
            error = function(e) {
-             errors <- c(errors, paste0(project_key," has an error in .R file"))
+             print(e)
              }

### 2016-07-01 analysis.Rmd
no googlesheets

@@
 library(ggplot2)
-library(googlesheets)
 library(readr)
@@
 
-Get project planning sheet straight from google docs.
+Get project planning sheet and exclude those to be excluded.
 
 ```{r}
-project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup = TRUE) # Need lookup=T to initialize
-project_plan_raw <- gs_read_csv(project_plan_sheet)
-```
+project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
 
-Exclude those to be excluded.
-
-```{r}
 project_plan <- project_plan_raw %>%
@@
 passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
-             "jedtan", "lampinen", "salehi")
-failing <- c("smraposo", "auc", "rhiac")
+              "lampinen")
+failing <- c("smraposo", "auc", "rhiac", "jedtan", "salehi")
 

### 2016-07-01 paper/paper.Rmd
analysis
no googlesheets

@@
 We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level experimental methods.
-By a variety of measures, these replications were successful approximately half of the time, providing an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."
+By a variety of measures, these replications were successful approximately half of the time, providing an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt.
+We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."
 
@@
                       cache=TRUE, message = FALSE, sanitize = TRUE)
-library(googlesheets)
 library(dplyr)
@@
 As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*.
-These studies both provide insight into the process of pedagogical replication and give evidence about the state of replicability.
+These studies both give evidence about the state of replicability in the field and provide insight into the process of pedagogical replication.
+
+It is a challenging proposition to estimate the replicability of an entire literature [cf.
+@osc2015].
+Making such an estimate requires determining a sampling strategy, a notion of what constitutes a direct replication, what constitutes a successful replication, among many other difficult decisions [@gilbert2016;@anderson2016].
+In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work.
+We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
+Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.
 
@@
 
-With respect to broader questions of meta-science, it is a challenging proposition to estimate the replicability of an entire literature [cf.
-@osc2015;@gilbert2016;@anderson2016].
-Making such an estimate requires determining a sampling strategy, a notion of what constitutes a direct replication, what constitutes a successful replication, among many other difficult decisions.
-In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, and within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work.
-We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
-Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.
-
 In sum, we view the contribution of the current work to be two-fold.
@@
 ```{r, results='asis'}
-project_plan_sheet <- gs_url("https://docs.google.com/spreadsheets/d/1KZw75xlypvtK0cDoOHqXfFd3HsrfJ4gbq8iEJ6LOa0Y", lookup=TRUE) # Need lookup=T to initialize
-project_plan_raw <- gs_read_csv(project_plan_sheet)
+project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
 
@@
 
-Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that 2/3 of these opted out projects were judged by the instructor team to have been successful replications; thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
-
 ## Participants
 
-All participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.
+All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.
 Note that of the `{r} nrow(ppt)` studies included in the final sample, `{r} sum(project_plan$original_on_turk=="Yes")` (`{r} round(mean(ppt$original_on_turk), digits=2)`%) were originally conducted on Mechanical Turk.
@@
 Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.
-(In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review).
 
@@
 
-For purposes of planning and analysis, we asked stuents Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies.
+Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies.
 Often a wide variety of statistical tests were conducted, often within one or several regression models with multiple specifications.
@@
 
-## Analysis strategy
+# Results
 
@@
 
-# Results
-
-.
-
 ## Pedagogical assessment
 
-how many replications were conducted to the intended standard, how many opted out etc.
+Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that 2/3 of these opted out projects were judged by the instructor team to have been successful replications; thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
+(In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review).
 
@@
 
-## Scientific Assessment
+## Confirmatory analyses
 
-### Indices of replicability
+### Subjective judgments of replication
 
-### Coding of previous years’ findings
+What’s the subjective “replication rating” given by MCF, ES, and RH?
+Criterion is based on the theoretical interpretation of the original finding.
+(0 = non-replication, .5 is substantial hints of the same pattern or a significant but different pattern, 1 = full replication).
+
+```{r}
+mean(project_plan$replicated_TA)
+```
+
+```{r}
+mean(project_plan$replicated_student, na.rm=TRUE)
+```
+
+### Significance of the key effect size
+
+### Original ES in the confidence interval of the replication
+
+### Bayes factor analysis
+
+@etz2016
+
+### Moderator analyses
+
+Turk vs. not-turk
+
+```{r}
+project_plan %>% 
+  group_by(original_on_turk) %>%
+  summarise(replicated_TA = mean(replicated_TA))
+```
+
+Coding of replication fidelity
+
+```{r}
+project_plan %>% 
+  group_by(fidelity) %>%
+  summarise(replicated = mean(replicated_TA))
+```
+
+Open materials/data vs. not
+
+```{r}
+project_plan %>% 
+  group_by(open_materials) %>%
+  summarise(replicated = mean(replicated_TA))
+```
+
+Demographics
+
+## Exploratory analysis
 

### 2016-07-01 analysis.Rmd
Minor changes to jedtan & salehi

@@
     all_project_info <- bind_rows(all_project_info,project_info) 
-    # rm("project_info") # In case other file does not same
+    rm("project_info") # In case other file does not same
   } else {

### 2016-07-01 project_analyses/jedtan.R

@@ -27,8 +27,8 @@ fade_mean =  round(transition_means$meanTime[2]/1000, digits=2)
 
 full_t.test <- t.test((transition_worker_means %>% filter(Transition == "Fade"))$meanTime, (transition_worker_means %>% filter(Transition == "Slide"))$meanTime, paired=TRUE)
 
-# epoch <- d %>% group_by(WorkerID, epoch, Transition) %>% 
-#   summarise(meanTime = mean(Time), meanPress = mean(KeyPresses))
+epoch <- d %>% group_by(WorkerID, epoch, Transition) %>% 
+ summarise(meanTime = mean(Time), meanPress = mean(KeyPresses))
 
 full_cohensDVal <- lsr::cohensD((epoch %>% filter(Transition == "Fade"))$meanTime, (epoch %>% filter(Transition == "Slide"))$meanTime)
 

### 2016-07-01 project_analyses/salehi.R

@@ -34,9 +34,6 @@ for (f in files) {
   d.raw <- bind_rows(d.raw, id)
 }
 
-# Number of participants
-length(unique(d.b$workerid))
-
 d <- d.raw %>%
   mutate(traitb = sentence %in% c('Decisive', 'Competitive', 'Self-reliant',   
                                   'Willing to take risks' , 'Ambitious', 'Daring' ,

### 2016-07-01 project_analyses/auc.R
fixed auc - plyr rename issue

@@ -30,7 +30,7 @@ summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
     )
 
     # Rename the "mean" column    
-    datac <- rename(datac, mean = measurevar)
+    datac <- plyr::rename(datac, c("mean" = measurevar))
     datac$se <- datac$sd / sqrt(datac$N)  # Calculate standard error of the mean
 
     # Confidence interval multiplier for standard error
@@ -161,6 +161,9 @@ for (f in files) {
   d.raw <- bind_rows(d.raw, id)
 }
 
+chr.rows <- sapply(d.raw, is.character)
+d.raw[,chr.rows] <- lapply(d.raw[,chr.rows], as.factor) # need to factorize character strings
+
 d <- summarySEwithin(d.raw, measurevar="face_rating", withinvars=c("face_dft", "exp_type"),
                             idvar="workerid", na.rm=FALSE, conf.interval=.95)
 
@@ -180,10 +183,22 @@ model <- lm(centered_face_rating ~
             d)
 summary(model)
 
+model_coef <- summary(model)$coefficients["exp_typetrustworthy:centered_dft","Estimate"]
+model_tval <- summary(model)$coefficients["exp_typetrustworthy:centered_dft","t value"]
+model_pval <- summary(model)$coefficients["exp_typetrustworthy:centered_dft","Pr(>|t|)"]
+model_df <- summary(model)$df[2]
+
+stat_descript <- paste0("t(",model_df,") = ",round(model_tval,2))
+
+
 project_info <- data.frame(project_key = "auc",
-                           n_final = length(unique(d.raw$workerid)),
-                           n_excluded = 0)
-                           
+                           rep_final_n = length(unique(d.raw$workerid)),
+                           rep_n_excluded = 0,
+                           rep_es = model_coef,
+                           rep_test_statistic = stat_descript,
+                           rep_p_value = pval1,
+                           note="based on writeup and article, assuming exp_typetrustworthy:centered_dft interaction is key stat of interest. Should clarify with Carolyn. Also make sure doing correct analysis from article."
+)
 
 #This results in $F(5, 16) = 91.11, p < 0.001, R^2 = 0.97$ which is the same
 #significance level and effect size as the original study. Comparing the
@@ -215,3 +230,5 @@ ms$face_dft <- as.factor(ms$face_dft)
 ms$exp_type <- as.factor(ms$exp_type) 
 
 summary(aov(mean_rating ~ face_dft + exp_type, ms))
+
+

### 2016-07-01 project_analyses/auc.R
small fixes rhiac and auc

@@ -163,6 +163,7 @@ for (f in files) {
 
 chr.rows <- sapply(d.raw, is.character)
 d.raw[,chr.rows] <- lapply(d.raw[,chr.rows], as.factor) # need to factorize character strings
+d.raw$face_dft <- as.factor(d.raw$face_dft)
 
 d <- summarySEwithin(d.raw, measurevar="face_rating", withinvars=c("face_dft", "exp_type"),
                             idvar="workerid", na.rm=FALSE, conf.interval=.95)

### 2016-07-01 paper/paper.Rmd
minor tweaks

@@
 
+Flag: in some cases (auc) we found that the key test statistic was not coded correctly.
+
 ## Confirmatory analyses
@@
 
+```{r}
+layout(matrix(1:22,nr=11,byr=T))
+for (key in project_plan$project_key) {
+  tryCatch(source(function() {
+  orig <- readPNG(paste0("figures/",key,"-original.png"))
+  rep <- readPNG(paste0("figures/",key,"-replication.png"))
+  plot(orig)
+  plot(rep)}
+  ))
+}
+```
+
 ## Exploratory analysis

### 2016-07-01 analysis.Rmd
Fix smraposo.R
fixed auc - plyr rename issue
ressults csv + mods

@@
 
-passing <- c("mkeil","jreynolds","jmarias","jsalloum","ehermann",
-              "lampinen")
-failing <- c("smraposo", "auc", "rhiac", "jedtan", "salehi")
+passing <- c("salehi","smraposo","jedtan","mkeil","jreynolds","jmarias","jsalloum","ehermann",
+              "lampinen","auc","rhiac")
+failing <- c( NA )
 
@@
 ```
+
+Save.
+
+```{r}
+write_csv(all_project_info, "data/all_project_info.csv")
+```

### 2016-07-01 paper/paper.Rmd
ressults csv + mods

@@
 
+results <- read_csv("data/all_project_info.csv")
+
+d <- left_join(project_plan, results)
+```
+
+```{r}
 ppt <- project_plan %>%
@@
 ```{r}
-mean(project_plan$replicated_TA)
+mean(d$replicated_TA)
 ```
@@
 ```{r}
-mean(project_plan$replicated_student, na.rm=TRUE)
+mean(d$replicated_student, na.rm=TRUE)
 ```
@@
 ```{r}
-project_plan %>% 
+d %>% 
   group_by(original_on_turk) %>%
@@
 ```{r}
-project_plan %>% 
+d %>% 
   group_by(fidelity) %>%

### 2016-07-01 paper/paper.Rmd
Start fixing up code snippets

--- 2016-07-01 paper/paper.Rmd
@@
 ```{r, results='asis'}
-project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
+project_plan_raw <- read.csv("data/planning_and_outcomes.csv")
 
@@
 
-% latex table generated in R 3.3.0 by xtable 1.8-2 package
-% Fri Jun 24 12:02:11 2016
+<!-- latex table generated in R 3.3.0 by xtable 1.8-2 package
+ Fri Jun 24 12:02:11 2016 -->
 \begin{table}[ht]
@@
 All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.
-Note that of the `{r} nrow(ppt)` studies included in the final sample, `{r} sum(project_plan$original_on_turk=="Yes")` (`{r} round(mean(ppt$original_on_turk), digits=2)`%) were originally conducted on Mechanical Turk.
+Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.
 All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
@@
 
-Of the `{r} nrow(ppt)` studies included in the final sample, `{r} round(mean(ppt$open_materials == "Yes" | ppt$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
-For `{r} sum(!is.na(authors_contact))` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors).
+Of the `r nrow(ppt)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
+For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors).
 Responses were received in all but one case, usually within a matter of days.
@@
 project_plan %>% 
-  group_by(fidelity) %>%
+  group_by(replication_fidelity_MCF) %>%
   summarise(replicated = mean(replicated_TA))

### 2016-07-01 paper/paper.Rmd

@@
 ```{r}
-project_plan %>% 
-  group_by(replication_fidelity_MCF) %>%
+d %>% 
+  group_by(fidelity) %>%
   summarise(replicated = mean(replicated_TA))
@@
 Demographics
+
+```{r}
+layout(matrix(1:22,nr=11,byr=T))
+for (key in project_plan$project_key) {
+  tryCatch(source(function() {
+  orig <- readPNG(paste0("figures/",key,"-original.png"))
+  rep <- readPNG(paste0("figures/",key,"-replication.png"))
+  plot(orig)
+  plot(rep)}
+  ))
+}
+```
 

### 2016-07-01 paper/paper.Rmd
finished review of student coding decisions
Initial analysis in paper

--- 2016-07-01 paper/paper.Rmd
@@
 library(xtable)
+library(readr)
+library(ggplot2)
 ```
@@
 ```{r, results='asis'}
+setwd("~/replication_project")
 project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
@@
 
-What’s the subjective “replication rating” given by MCF, ES, and RH?
+Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.
 Criterion is based on the theoretical interpretation of the original finding.
 (0 = non-replication, .5 is substantial hints of the same pattern or a significant but different pattern, 1 = full replication).
+We find that the these ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
+The average rating given by instructors and students was `r mean(d$replicated_TA, na.rm=TRUE)` and `r mean(d$replicated_student, na.rm=TRUE)` respectively.
 
+Flag: waiting for one student's subjective rating
 ```{r}
-mean(d$replicated_TA)
-```
-
-```{r}
-mean(d$replicated_student, na.rm=TRUE)
+table(d$replicated_TA,d$replicated_student) # Make prettier
 ```
@@
 
+```{r, echo=F}
+d$original_p_value_bins <- NA
+d$original_p_value_bins[d$original_p_value %in% c("<.05","0.04")] <- "<.05"
+d$original_p_value_bins[d$original_p_value %in% c("0.007","0.001")] <- "<.01"
+d$original_p_value_bins[d$original_p_value %in% c("<.001","< .001")] <- "<.001"
+d$rep_p_value_05 <- d$rep_p_value < .05
+```
+
+We assess the replication p-value to determine whether the key statistic found a significant effect at the traditional p=.05 level.
+We find this to be true for only `r sum(d$rep_p_value_05)` of the studies.
+However, the well-documented "dance of the p-values" [@cummings2011] suggests that the inference drawn from a single replication p-value may not be highly informative, and other metrics suchs as the confidence interval and Bayes factor analysis below can give the reader a better understanding of replication success.
+
+Flag: Are all effects in the hypothesized direction?
+
+```{r}
+ggplot(d,aes(x=original_p_value_bins,y=rep_p_value, color=as.factor(d$replicated_TA))) +
+  geom_jitter(height=0, width=.4) +
+  theme_bw() + 
+  geom_hline(yintercept=c(0.05,0.1,0.2), color="gray")
+```
+
 ### Original ES in the confidence interval of the replication
+
+We determine whether the original reported effect size is included in the 95\% confidence interval found in the replication studies.
+
+Flag: Original effect size not given for auc?
+```{r}
+d$original_ES <- as.numeric(gsub(".*=(.*)","\\1", d$original_ES_text))
+#Ensure that effect size is given in same units... Make beautiful ci chart here...
+
+```
 
@@
 
-```{r}
+```{r,eval=F}
+d$high_fidelity <- d$replication_fidelity_MCF > median(d$replication_fidelity_MCF)
 d %>%
-  group_by(fidelity) %>%
+  group_by(high_fidelity) %>%
   summarise(replicated = mean(replicated_TA))
@@
 
-```{r}
+```{r, eval=F}
 layout(matrix(1:22,nr=11,byr=T))

### 2016-07-01 project_preprocessing.R
renaming to preprocessing

@@ -1,41 +1,22 @@
----
-title: "Psych 254 Replication Project Analysis"
-author: "Eric Smith, Robert Hawkins, Michael C. Frank"
-date: '`r Sys.Date()`'
-output:
-  html_document:
-    number_sections: yes
-    toc: yes
----
 
-Libraries.
-
-```{r}
 library(dplyr)
-library(ggplot2)
 library(readr)
 library(tidyr)
-```
 
-Get project planning sheet and exclude those to be excluded. 
+project_plan <- read_csv("data/planning_and_outcomes.csv")
 
-```{r}
-project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
+# Read in project_info data from each project
 
-project_plan <- project_plan_raw %>%
-  filter(`include_in_final_writeup`==1) 
-```
+# Initialize an error var
+errors <- list()
 
-Read in project_info data from each project
-
-```{r}
-errors <- list()# Initialize an error var
-
-all_project_info <- data.frame( # initialize an empty dataframe
+# initialize an empty dataframe
+all_project_info <- data.frame( 
   project_key = character()
 )
 
-project_keys <- project_plan$project_key # Find user names that are included in 
+# Find user names that are included in 
+project_keys <- project_plan$project_key 
 
 passing <- c("salehi","smraposo","jedtan","mkeil","jreynolds","jmarias","jsalloum","ehermann",
               "lampinen","auc","rhiac")
@@ -60,10 +41,5 @@ for(project_key in passing) { # project_keys
     errors <- c(errors,paste0(project_key," is missing project_info"))
   }
 }
-```
 
-Save.
-
-```{r}
-write_csv(all_project_info, "data/all_project_info.csv")
-```
+write_csv(all_project_info, "data/project_data_summary.csv")

### 2016-07-01 project_preprocessing.R
further reorg of data summary

@@ -11,7 +11,7 @@ project_plan <- read_csv("data/planning_and_outcomes.csv")
 errors <- list()
 
 # initialize an empty dataframe
-all_project_info <- data.frame( 
+project_data_summary <- data.frame( 
   project_key = character()
 )
 
@@ -35,11 +35,11 @@ for(project_key in passing) { # project_keys
   
   # If has project_info dataframe, add to all data
   if(exists("project_info")) { 
-    all_project_info <- bind_rows(all_project_info,project_info) 
+    project_data_summary <- bind_rows(project_data_summary,project_info) 
     rm("project_info") # In case other file does not same
   } else {
     errors <- c(errors,paste0(project_key," is missing project_info"))
   }
 }
 
-write_csv(all_project_info, "data/project_data_summary.csv")
+write_csv(project_data_summary, "data/project_data_summary.csv")

### 2016-07-01 paper/paper.Rmd
renaming to preprocessing
further reorg of data summary

@@
 table(d$replicated_TA,d$replicated_student) # Make prettier
+#mean(d$replicated_team)
 ```

### 2016-07-01 project_analyses/auc.R
salehi and auc modified

@@ -196,7 +196,9 @@ project_info <- data.frame(project_key = "auc",
                            rep_final_n = length(unique(d.raw$workerid)),
                            rep_n_excluded = 0,
                            rep_es = model_coef,
-                           rep_test_statistic = stat_descript,
+                           rep_test_statistic_str = stat_descript,
+                           rep_t_stat = model_tval,
+                           rep_t_df = model_df,
                            rep_p_value = pval1,
                            note="based on writeup and article, assuming exp_typetrustworthy:centered_dft interaction is key stat of interest. Should clarify with Carolyn. Also make sure doing correct analysis from article."
 )
@@ -213,23 +215,23 @@ project_info <- data.frame(project_key = "auc",
 
 
 # Within-subjects means
-ms <- d.raw %>%
-  group_by(exp_type, face_dft, workerid) %>%
-  dplyr::summarise(mean_rating = mean(face_rating))
-
-ms$workerid <- as.factor(ms$workerid)
-ms$face_dft <- as.factor(ms$face_dft)
-ms$exp_type <- as.factor(ms$exp_type)
-
-summary(aov(mean_rating ~ face_dft * exp_type + Error(workerid / face_dft), ms))
-
-ms <- d.raw %>%
-  group_by(exp_type, face_dft) %>%
-  dplyr::summarise(mean_rating = mean(face_rating))
-
-ms$face_dft <- as.factor(ms$face_dft)
-ms$exp_type <- as.factor(ms$exp_type) 
-
-summary(aov(mean_rating ~ face_dft + exp_type, ms))
-
-
+# ms <- d.raw %>%
+#   group_by(exp_type, face_dft, workerid) %>%
+#   dplyr::summarise(mean_rating = mean(face_rating))
+# 
+# ms$workerid <- as.factor(ms$workerid)
+# ms$face_dft <- as.factor(ms$face_dft)
+# ms$exp_type <- as.factor(ms$exp_type)
+# 
+# summary(aov(mean_rating ~ face_dft * exp_type + Error(workerid / face_dft), ms))
+# 
+# ms <- d.raw %>%
+#   group_by(exp_type, face_dft) %>%
+#   dplyr::summarise(mean_rating = mean(face_rating))
+# 
+# ms$face_dft <- as.factor(ms$face_dft)
+# ms$exp_type <- as.factor(ms$exp_type) 
+# 
+# summary(aov(mean_rating ~ face_dft + exp_type, ms))
+# 
+# 

### 2016-07-01 project_analyses/salehi.R

@@ -2,9 +2,9 @@ library(tidyr)
 library(dplyr)
 
 ## MCF: note that Shima chose the followup ANOVA to be the primary test for power 
-# analysis, and so that's what we're using as the outcome. but actually, on further 
-# reflection we think it's the interaction that is most theoretically central. 
-# in fact she gets the interaction, though. 
+# analysis. but actually, on further 
+# reflection we think it's the interaction that is most theoretically central. so we have revised
+# to reflect that. (7/1/16)
 
 path <- "data/salehi/"
 files <- dir(path, 
@@ -52,34 +52,49 @@ write_csv(d, "processed_data/salehi.csv")
 # 10.21, p = .002, d = 0.71.
 
 #filtering data points for masculine data points
-masculine <- d %>% filter(traitType == 'Masculine')
+# masculine <- d %>% filter(traitType == 'Masculine')
 
 #averaging ratings for each participant
-masculine <- masculine %>%
-  group_by(condition, workerid) %>%
-  summarize(workermean=mean(rating))
+# masculine <- masculine %>%
+#   group_by(condition, workerid) %>%
+#   summarize(workermean=mean(rating))
 
 #one-way anova
-fitMasculine <- aov(workermean ~ condition, data = masculine)
-summary(fitMasculine)
-
-p <- summary(fitMasculine)[[1]][1,5]
-Fval <- summary(fitMasculine)[[1]][1,4]
-df1 <- summary(fitMasculine)[[1]][1,1]
-df2 <- summary(fitMasculine)[[1]][2,1]
+# fitMasculine <- aov(workermean ~ condition, data = masculine)
+# summary(fitMasculine)
 
 #effect size
-masculineDivergentMean <- masculine %>% filter(condition == 'Divergent')
-masculineConnvergentMean <- masculine %>% filter(condition == 'Convergent')
-cohens_d <- effsize::cohen.d(masculineDivergentMean$workermean, masculineConnvergentMean$workermean)$estimate
+# masculineDivergentMean <- masculine %>% filter(condition == 'Divergent')
+# masculineConnvergentMean <- masculine %>% filter(condition == 'Convergent')
+# cohens_d <- effsize::cohen.d(masculineDivergentMean$workermean, masculineConnvergentMean$workermean)$estimate
+
+### REVISED TO USE FULL ANOVA (MCF 7/1/16)
+fitConTrait <- aov(rating ~ traitType * condition + 
[…]

### 2016-07-01 project_analyses/jedtan.R
Add t stat & df, tag incorrect ES

@@ -48,10 +48,12 @@ stat_descript = paste0("t(",full_t.test$parameter,")=",round(full_t.test$statist
 
 project_info <- data.frame(
   project_key = "jedtan", 
+  rep_t_stat = full_t.test$parameter,
+  rep_t_df = full_t.test$statistic,
   rep_final_n = length(unique(d$WorkerID)), 
   rep_n_excluded = 0, 
   rep_es = full_cohensDVal, 
-  rep_test_statistic = stat_descript,
+  rep_test_statistic_str = stat_descript,
   rep_p_value = full_t.test$p.value)
 
 # 

### 2016-07-01 project_analyses/jmarias.R

@@ -230,17 +230,16 @@ tval <- round(summary(mathperflm4)$coef["z.mathmot:I(z.mathanx^2)","t value"],3)
 est <- round(summary(mathperflm4)$coef["z.mathmot:I(z.mathanx^2)","Estimate"],3)
 df <- mathperflm4$df
 
-
 stat_descript <- paste0("t(",df,") = ",tval)
-
-
 
 project_info <- data.frame(
   project_key = "jmarias", 
+  rep_t_stat = tval,
+  rep_t_df = df,
   rep_final_n = nrow(subjectmeans), 
   rep_n_excluded = length(unique(d$workerid))-nrow(subjectmeans) , 
-  rep_es = est, 
-  rep_test_statistic = stat_descript,
+  rep_es = NA, 
+  rep_test_statistic_str = stat_descript,
   rep_p_value = pval,
   notes= "double check participant summaries and exclusion criteria"
 )

### 2016-07-01 project_analyses/jreynolds.R

@@ -50,8 +50,10 @@ stat_descript <- paste0("t(",df,") = ",round(tval, 3))
 
 project_info <- data.frame(
   project_key = "jreynolds", 
+  rep_t_stat = tval,
+  rep_t_df = df,
   rep_final_n = length(unique(d$Participant)), 
   rep_n_excluded = 0, 
-  rep_es = tval, 
-  rep_test_statistic = stat_descript,
+  rep_es = NA, 
+  rep_test_statistic_str = stat_descript,
   rep_p_value = pval)

### 2016-07-01 project_analyses/mkeil.R

@@ -191,10 +191,12 @@ stat_descript <- paste0("F(",df1,",",df2,") = ",F_test)
 
 project_info <- data.frame(
   project_key = "mkeil", 
+  rep_t_stat = sqrt(F_stat),
+  rep_t_df = df2,
   rep_final_n = length(unique(d1$workerId)), 
   rep_n_excluded = length(unique(d.raw$workerId))-length(unique(d1$workerId)), 
-  rep_es = F_test, 
-  rep_test_statistic = stat_descript,
+  rep_es = NA, 
+  rep_test_statistic_str = stat_descript,
   rep_p_value = p.val,
   notes= "double check the aov mixed model- same as original authors? And different result than stated in report. This doesn't seem right collapsing by multiple trials first...?"
 )

### 2016-07-01 project_analyses/salehi.R

@@ -75,12 +75,14 @@ cohens_d <- effsize::cohen.d(masculineDivergentMean$workermean, masculineConnver
 
 test_stat <- paste0("F(",df1,",",df2,")=",round(Fval, digits=3))
   
-project_info <- data.frame(project_key = "salehi",
-                           rep_final_n = length(unique(d$workerid)),
-                           rep_n_excluded = 0, 
-                           rep_es = cohens_d, 
-                           rep_test_statistic = test_stat,
-                           rep_p_value = p)
+project_info <- data.frame(
+  project_key = "salehi",
+  rep_final_n = length(unique(d$workerid)),
+  rep_n_excluded = 0, 
+  rep_es = cohens_d, 
+  rep_test_statistic_str = test_stat,
+  rep_p_value = p
+)
 
 
 # The result of mixed-model ANOVA for the original study was: A mixed-model

### 2016-07-01 paper/paper.Rmd
Add codebox for bayes factor

--- 2016-07-01 paper/paper.Rmd
@@
                       cache=TRUE, message = FALSE, sanitize = TRUE)
+library(readr)
 library(dplyr)
@@
 ```{r, results='asis'}
-project_plan_raw <- read.csv("data/planning_and_outcomes.csv")
+project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
 
@@
 
+```{r}
+BayesFactor::meta.ttestBF(d$origin_t_stat, d$original_t_df)
+BayesFactor::meta.ttestBF(d$rep_t_stat, d$rep_t_df)
+```
 @etz2016

### 2016-07-01 paper/paper.Rmd

--- 2016-07-01 paper/paper.Rmd
@@
 ```{r, results='asis'}
-setwd("~/replication_project")
 project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
@@
 
-results <- read_csv("data/all_project_info.csv")
+project_data_summary <- read_csv("data/project_data_summary.csv")
 
-d <- left_join(project_plan, results)
+d <- left_join(project_plan, project_data_summary)
 ```

### 2016-07-02 project_analyses/auc.R
Change auc 'notes' tag to prevent joining problems

@@ -200,7 +200,7 @@ project_info <- data.frame(project_key = "auc",
                            rep_t_stat = model_tval,
                            rep_t_df = model_df,
                            rep_p_value = pval1,
-                           note="based on writeup and article, assuming exp_typetrustworthy:centered_dft interaction is key stat of interest. Should clarify with Carolyn. Also make sure doing correct analysis from article."
+                           notes="based on writeup and article, assuming exp_typetrustworthy:centered_dft interaction is key stat of interest. Should clarify with Carolyn. Also make sure doing correct analysis from article."
 )
 
 #This results in $F(5, 16) = 91.11, p < 0.001, R^2 = 0.97$ which is the same

### 2016-07-02 project_analyses/jedtan.R
Fix jed tan project_info (swapped stat and df)

@@ -30,7 +30,8 @@ full_t.test <- t.test((transition_worker_means %>% filter(Transition == "Fade"))
 epoch <- d %>% group_by(WorkerID, epoch, Transition) %>% 
  summarise(meanTime = mean(Time), meanPress = mean(KeyPresses))
 
-full_cohensDVal <- lsr::cohensD((epoch %>% filter(Transition == "Fade"))$meanTime, (epoch %>% filter(Transition == "Slide"))$meanTime)
+full_cohensDVal <- lsr::cohensD((epoch %>% filter(Transition == "Fade"))$meanTime, 
+                                (epoch %>% filter(Transition == "Slide"))$meanTime)
 
 #As a key statistic, Liverence and Scholl report that "Across all trials, 
 # participants were on average 1.41 s faster per trial on slide-transition blocks
@@ -48,8 +49,8 @@ stat_descript = paste0("t(",full_t.test$parameter,")=",round(full_t.test$statist
 
 project_info <- data.frame(
   project_key = "jedtan", 
-  rep_t_stat = full_t.test$parameter,
-  rep_t_df = full_t.test$statistic,
+  rep_t_stat = full_t.test$statistic,
+  rep_t_df = full_t.test$parameter,
   rep_final_n = length(unique(d$WorkerID)), 
   rep_n_excluded = 0, 
   rep_es = full_cohensDVal, 

### 2016-07-02 project_analyses/mkeil.R
Fix typo in mkeil

@@ -191,7 +191,7 @@ stat_descript <- paste0("F(",df1,",",df2,") = ",F_test)
 
 project_info <- data.frame(
   project_key = "mkeil", 
-  rep_t_stat = sqrt(F_stat),
+  rep_t_stat = sqrt(F_test),
   rep_t_df = df2,
   rep_final_n = length(unique(d1$workerId)), 
   rep_n_excluded = length(unique(d.raw$workerId))-length(unique(d1$workerId)), 

### 2016-07-02 paper/paper.Rmd
Make bayes factor plot

@@
 
-d <- left_join(project_plan, project_data_summary)
+d <- left_join(project_plan, project_data_summary, by = c("project_key"))
 ```
@@
 ```{r}
-BayesFactor::meta.ttestBF(d$origin_t_stat, d$original_t_df)
-BayesFactor::meta.ttestBF(d$rep_t_stat, d$rep_t_df)
+getBF <- function(t_stat, t_df) {
+  return(log10(ttest.tstat(t = t_stat, n1 = t_df, rscale = 1, simple = T)))
+};
+
+tstatDF <- d %>%
+  filter(original_t_stat != "NA") %>%
+  select(project_key, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
+  rowwise() %>%
+  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
+  rowwise() %>%
+  mutate(repBF = getBF(rep_t_stat, rep_t_df))
+
+ggplot(tstatDF, aes(x = origBF, y = repBF, size = rep_t_df/original_t_df)) +
+  geom_point()+
+  theme_bw()+
+  xlim(-2, 30) +
+  ylim(-2, 30) +
+  geom_hline(aes(yintercept = 10), linetype = 2)+
+  geom_hline(aes(yintercept = 3), linetype = 2)+
+  geom_hline(aes(yintercept = 1/3), linetype = 2)+
+  geom_hline(aes(yintercept = 1/10), linetype = 2)+
+  geom_vline(aes(xintercept = 10), linetype = 2)+
+  geom_vline(aes(xintercept = 3), linetype = 2)+
+  geom_vline(aes(xintercept = 1/3), linetype = 2)+
+  geom_vline(aes(xintercept = 1/10), linetype = 2)
+
+  # scale_x_log10(limits = c(-50, 100)) +
+  # scale_y_log10(limits = c(-50, 10))
+
 ```

### 2016-07-08 paper/paper.Rmd

--- 2016-07-01 paper/paper.Rmd
@@
 ```{r}
-BayesFactor::meta.ttestBF(d$origin_t_stat, d$original_t_df)
-BayesFactor::meta.ttestBF(d$rep_t_stat, d$rep_t_df)
+getBF <- function(t_stat, t_df) {
+  return(ttest.tstat(t = t_stat, n1 = t_df, rscale = 1, simple = T))
+};
+
+tstatDF <- d %>%
+  filter(original_t_stat != "NA") %>%
+  select(project_key, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
+  rowwise() %>%
+  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
+  rowwise() %>%
+  mutate(repBF = getBF(rep_t_stat, rep_t_df))
+
+ggplot(tstatDF, aes(x = origBF, y = repBF, size = rep_t_df/original_t_df)) +
+  geom_point()+
+  theme_bw()+
+  # xlim(-2, 30) +
+  # ylim(-2, 30) +
+  geom_hline(aes(yintercept = 10), linetype = 2)+
+  geom_hline(aes(yintercept = 3), linetype = 2)+
+  geom_hline(aes(yintercept = 1/3), linetype = 2)+
+  geom_hline(aes(yintercept = 1/10), linetype = 2)+
+  geom_vline(aes(xintercept = 10), linetype = 2)+
+  geom_vline(aes(xintercept = 3), linetype = 2)+
+  geom_vline(aes(xintercept = 1/3), linetype = 2)+
+  geom_vline(aes(xintercept = 1/10), linetype = 2) +
+  scale_x_log10(limits = c(10**-1.75, 10**11), 
+                breaks = c(1/10, 1/3, 3, 10),
+                labels = c("1/10", "1/3", "3", "10")) +
+  scale_y_log10(limits = c(10**-1.75, 10**11),
+                breaks = c(1/10, 1/3, 3, 10),
+                labels = c("1/10", "1/3", "3", "10"))
+
 ```

### 2016-07-08 paper/paper.Rmd
cleanup of results

--- 2016-07-01 paper/paper.Rmd
@@
 library(readr)
+library(tidyr)
 library(ggplot2)
+library(BayesFactor)
+#devtools::install_github("langcog/langcog")
+library(langcog)
 ```
@@
 ```{r, results='asis'}
-project_plan_raw <- read_csv("data/planning_and_outcomes.csv")
+project_plan_raw <- read.csv("../data/planning_and_outcomes.csv")
 
@@
 
-project_data_summary <- read_csv("data/project_data_summary.csv")
+project_data_summary <- read_csv("../data/project_data_summary.csv")
 
-d <- left_join(project_plan, project_data_summary)
+d <- left_join(project_plan, project_data_summary, by = c("project_key"))
 ```
@@
 \begin{table}[ht]
+\footnotesize
 \centering
@@
   \hline
-@storm2015 & 3 & No & No & No &  48 &  61 \\ 
-@lewis2015 & 4 & No & Yes & Yes & 122 & 128 \\ 
-@scopelliti2015 & 3 & No & Yes & Yes & 550 & 124 \\ 
-@liverence2015 & 1 & No & Some & No &  18 &  \\ 
-@wang2015 & 2 & No & No & No & 219 & 397 \\ 
-@sofer2015 & 1 & No & Yes & No &  48 &  95 \\ 
-@ko2015 & 2 & Yes & Some & No &  40 &  40 \\ 
-@dunning2015 & 1b & No & Yes & Yes & 202 &  50 \\ 
-@proudfoot2015 & 1 & No & No & Yes &  80 &  84 \\ 
-@zaval2015 & 1 & Yes & Yes & Yes & 312 & 328 \\ 
-@xu2015 & 1a & No & No & No &  12 &  27 \\ 
+Storm \& Stone (2015) & 3 & No & No & No &  48 &  61 \\ 
+Lewis \& Oyserman (2015) & 4 & No & Yes & Yes & 122 & 128 \\ 
+Scopelliti, Loewenstein, \& Vosgerau (2015) & 3 & No & Yes & Yes & 550 & 124 \\ 
+Liverence \& Scholl (2015) & 1 & No & Some & No &  18 &  \\ 
+Wang et al. (2015) & 2 & No & No & No & 219 & 397 \\ 
+Sofer et al. (2015) & 1 & No & Yes & No &  48 &  95 \\ 
+Ko, Sadler, \& Galinksy (2015) & 2 & Yes & Some & No &  40 &  40 \\ 
+Atir, Rosenzweig, \& Dunning (2015) & 1b & No & Yes & Yes & 202 &  50 \\ 
+Proudfoot, Kay, \& Koval (2015) & 1 & No & No & Yes &  80 &  84 \\ 
+Zaval, Markowitz, \& Weber (2015) & 1 & Yes & Yes & Yes & 312 & 328 \\ 
+Xu \& Franconeri (2015) & 1a & No & No & No &  12 &  27 \\ 
    \hline
 \end{tabular}
-\caption{Summary of attempted replications} 
+\caption{\label{tab:summary} Summary of attempted replications.} 
 \label{tab:summary}
@@
 This sampling strategy may thus bias our results towards more exciting or novel findings.
+A summary of the original findings is given in Table \ref{tab:summary}.
 
@@
 In addition to as-needed guidance, each student collected two pilot samples.
-The first, "pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
+The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
 The goal of this pilot was to ensure that all needed data were being logged by the experiment and that analytic scripts for the confirmatory analyses functioned appropriately.
@@
 Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.
+In addition, prior to data collection, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).
 
@@
 Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis.
-This test was determined by iterative discussion between the student, instructor, and TAs.
 
-Derermining appropriate sample sizes is a major challenge in replication research [@button2013,@simonsohn2015].
-Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;button2013], but -- especially with the constraints of a limited budget -- it may be impossible to follow more conservative guidelines in all cases.
+Derermining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015].
+Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially with the constraints of a limited budget -- it may be impossible to follow more conservative guidelines in all cases.
 For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or underpowered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
@@
 In 
-`{r} sum(project_plan$power_standard == "80% power")} 
+`r sum(project_plan$power_standard == "80% power")`
 cases, we powered the replication attempt to 80\% post-hoc power. In 
-`{r} sum(project_plan$power_standard == "Original")` 
+`r sum(project_plan$power_standard == "Original")` 
 cases, we used the original sample size.
@@
 Students chose findings from a wide variety of domains for replication.
-One group was nvestigations of memory and visual attention [e.g., @xu2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
+One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
 A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
@@
 
-Analyses for the final project were pre-registered ([https://osf.io/rxz8m/]())
-
 ## Pedagogical assessment
 
-Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that 2/3 of these opted out projects were judged by the instructor team to have been successful replications; thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
+Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and  2/3 projects were judged by the instructor team to have been successful replications.
+Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
 (In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review).
 
-Assessing the fidelity of replications to the original (in terms of same sample, same materials, same task parameters)
+The instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
+Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the modal rating was `r round(mean(d$replication_fidelity_MCF), digits = 2)`.
+Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might have an effect on the results.
 
-Flag: in some cases (auc) we found that the key test statistic was not coded correctly.
+In two cases, in final review of the projects (after data collection), the instructor team decided that the student's choice of key statisical test was not in fact a strong test of the original authors' primary theoretical claim.
+In both of these cases [@sofer2015;@proudfoot2015], the original authors had fit a multiple regression model to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
+After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest.
+We report results from these corrected tests here.
+We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research.
 
@@
 We find that the these ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
-The average rating given by instructors and students was `r mean(d$replicated_TA, na.rm=TRUE)` and `r mean(d$replicated_student, na.rm=TRUE)` respectively.
+The average rating given by instructors and students were `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.
 
-Flag: waiting for one student's subjective rating
 ```{r}
-table(d$replicated_TA,d$replicated_student) # Make prettier
+d$high_fidelity <- d$replication_fidelity_MCF > median(d$replication_fidelity_MCF)
+# table(d$replicated_TA,d$replicated_student) # Make prettier
 #mean(d$replicated_team)
+
+replicated <- d %>% 
+  group_by(replicated_TA) %>%
+  summarise(n= n()) %>%
+  spread(replicated_TA, n) %>%
+  mutate(measure = "replicated",
+         value = "")
+
+turk <- d %>% 
+  group_by(original_on_turk, replicated_TA) %>%
+  summarise(n= n()) %>%
+  spread(replicated_TA, n) %>%
+  rename(value = original_on_turk) %>%
+  mutate(measure = "original on turk")
+
+fidelity <- d %>% 
+  group_by(high_fidelity,replicated_TA) %>%
+  summarise(n= n()) %>%
+  spread(replicated_TA, n) %>%
+  mutate(measure = "high fidelity") %>%
+  rename(value = high_fidelity) %>%
+  ungroup() %>%
+  mutate(value = c("Yes","No")[as.numeric(value) + 1])
+
+open_materials <- d %>% 
+  group_by(open_materials,replicated_TA) %>%
+  summarise(n= n()) %>%
+  spread(replicated_TA, n) %>%
+  mutate(measure = "open materials") %>%
+  rename(value = open_materials)
+
+outcomes <- bind_rows(replicated, turk, fidelity, open_materials) 
+names(outcomes) <- c("No","Partial","Full", "Mediator","Value")
+outcomes <- outcomes %>%
+  select(Mediator, Value, No, Partial, Full)
+
+# print(xtable(outcomes), include.rownames = FALSE)
 ```
+
+\begin{table}[ht]
+\centering
+\begin{tabular}{llrrr|r}
+  \hline
+Mediator & Value & No & Partial & Full & Total\\ 
+  \hline
+Replicated? &  &   2 &   6 &   3 & 11 \\ 
+\hline
+  Original on turk & Yes &   1 &   2 &   2 & 5 \\ 
+   & No &   1 &   4 &   1 & 6\\ 
+\hline
+  High fidelity replication? & Yes &   2 &   3 &   1  & 6\\ 
+   & No &  &   3 &   2 & 5\\ 
+\hline
+  Open materials? & Yes &   1 &   3 &   1  & 4\\ 
+   & Some &  &   1 &   1 & 2\\ 
+   &  No &   1 &   2 &   1 & 4\\ 
+\hline
+\end{tabular}
+\caption{\label{tab:results} Counts of instructor team replication ratings, split by various different mediating variables.}
+\end{table}
+
+The modal replication project in our sample was judged to be a "partial" replication, meaning that some aspects of the observed findings were different from those reported by the original authors.
+While this conclusion is dispiriting, it is also perhaps unsurprising given the complexity of the analyses reported in many of the original papers.
+In addition, `r sum(d$original_test=="interaction")` of the tests were interactions, which tend to have lower statistical power [@mcclelland1993] and have fared poorly in previous replication studies [@osc2015].
+
+The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest.
+Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically underpowered after correcting for multiple comparisons).
+Overall, projects had a somewhat larger probability of being judged successful if it was judged to be closer to the original:
+\%`r round(mean(d$replicated_TA[d$high_fidelity]), digits=2)` 
+vs. 
+\%`r round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`.
+There were small numerical effects of being run on Mechanical Turk (
+\%`r round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)` 
+vs. 
+\%`r round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`. 
+) and having open materials (
+\%`r round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)` 
+vs. 
+\%`r round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`), though we do not believe these differences are interpretable given our sample size.
 
@@
 
-```{r, echo=F}
-d$original_p_value_bins <- NA
+We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level.
+Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value.
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+
+```{r}
+d$original_p_value_bins <- .1
 d$original_p_value_bins[d$original_p_value %in% c("<.05","0.04")] <- "<.05"
@@
 d$rep_p_value_05 <- d$rep_p_value < .05
-```
 
-We assess the replication p-value to determine whether the key statistic found a significant effect at the traditional p=.05 level.
-We find this to be true for only `r sum(d$rep_p_value_05)` of the studies.
-However, the well-documented "dance of the p-values" [@cummings2011] suggests that the inference drawn from a single replication p-value may not be highly informative, and other metrics suchs as the confidence interval and Bayes factor analysis below can give the reader a better understanding of replication success.
-
-Flag: Are all effects in the hypothesized direction?
-
-```{r}
-ggplot(d,aes(x=original_p_value_bins,y=rep_p_value, color=as.factor(d$replicated_TA))) +
-  geom_jitter(height=0, width=.4) +
+d$replicated_TA_factor <- factor(d$replicated_TA, levels = c(0, .5, 1), 
+                                 labels = c("No","Partial","Yes"))
+ggplot(d,aes(x=original_p_value_bins,y=rep_p_value, 
+             color=d$replicated_TA_factor)) +
+  geom_jitter(height=0, width=.2) +
+  geom_hline(yintercept=c(0.05), lty = 2) + 
+  geom_hline(yintercept=c(0.1), lty = 3) + 
+  ylim(c(0,1)) +
+  xlab("Original p-value (binned)") + 
+  ylab("Instructor replication rating") + 
   theme_bw() + 
-  geom_hline(yintercept=c(0.05,0.1,0.2), color="gray")
+  scale_color_solarized(name = "Subjective replication rating") + 
+  theme(legend.position = "bottom")
 ```
@@
 Flag: Original effect size not given for auc?
+
 ```{r}
@@
 #Ensure that effect size is given in same units... Make beautiful ci chart here...
-
 ```
@@
 
-```{r}
-BayesFactor::meta.ttestBF(d$origin_t_stat, d$original_t_df)
-BayesFactor::meta.ttestBF(d$rep_t_stat, d$rep_t_df)
-```
-@etz2016
-
-### Moderator analyses
-
-Turk vs. not-turk
+Next, following @etz2016, we conducted a Bayesian analysis.
 
 ```{r}
-d %>% 
-  group_by(original_on_turk) %>%
-  summarise(replicated_TA = mean(replicated_TA))
+getBF <- function(t_stat, t_df) {
+  return(ttest.tstat(t = t_stat, n1 = t_df, rscale = 1, simple = T))
+};
+
+tstatDF <- d %>%
+  filter(original_t_stat != "NA") %>%
+  select(project_key, replicated_TA_factor, first_author_name, original_t_stat, original_t_df, rep_t_stat, rep_t_df) %>%
+  rowwise() %>%
+  mutate(origBF = getBF(original_t_stat, original_t_df)) %>%
+  rowwise() %>%
+  mutate(repBF = getBF(rep_t_stat, rep_t_df), 
+         t_ratio = rep_t_df/original_t_df)
+
+ggplot(tstatDF, aes(x = origBF, y = repBF)) +
+  geom_point(alpha = .8, aes(size = t_ratio, 
+                             col = replicated_TA_factor)) +
+  geom_abline(slope = 1, lty = 2) + 
+  geom_smooth(method = "lm", se=FALSE) + 
+  xlab("Original Bayes Factor") + 
+  ylab("Replication Bayes Factor") + 
+  scale_x_log10(limits = c(10**-1.75, 10**11), 
+                breaks = c(1/10, 1/3, 3, 10, 100),
+                labels = c("1/10", "1/3", "3", "10")) +
+  scale_y_log10(limits = c(10**-1.75, 10**11),
+                breaks = c(1/10, 1/3, 3, 10, 100),
+                labels = c("1/10", "1/3", "3", "10")) + 
+  scale_size_continuous(name = "Ratio of replication to original t value") + 
+  scale_color_solarized(name = "Subjective replication rating") + 
+  theme_bw() +
+  theme(legend.position="bottom")
+
+  # xlim(-2, 30) +
+  # ylim(-2, 30) +
+  # geom_hline(aes(yintercept = 10), linetype = 2)+
+  # geom_hline(aes(yintercept = 3), linetype = 2)+
+  # geom_hline(aes(yintercept = 1/3), linetype = 2)+
+  # geom_hline(aes(yintercept = 1/10), linetype = 2)+
+  # geom_vline(aes(xintercept = 10), linetype = 2)+
+  # geom_vline(aes(xintercept = 3), linetype = 2)+
+  # geom_vline(aes(xintercept = 1/3), linetype = 2)+
+  # geom_vline(aes(xintercept = 1/10), linetype = 2) +
 ```
 
-Coding of replication fidelity
-
-```{r,eval=F}
-d$high_fidelity <- d$replication_fidelity_MCF > median(d$replication_fidelity_MCF)
-d %>%
-  group_by(high_fidelity) %>%
-  summarise(replicated = mean(replicated_TA))
-```
-
-Open materials/data vs. not
-
-```{r}
-project_plan %>% 
-  group_by(open_materials) %>%
-  summarise(replicated = mean(replicated_TA))
-```
-
-Demographics
+<!-- Demographics -->
 
@@
 
+The single effect-size paradigm is deeply broken.
+
 How to archive and make searchable the results of this sort of class?

### 2016-07-08 paper/paper.Rmd
paper

@@
                       fig.path='figs/', echo=FALSE, warning = FALSE, 
-                      cache=TRUE, message = FALSE, sanitize = TRUE)
+                      cache=FALSE, message = FALSE, sanitize = TRUE)
 library(readr)
@@
 library(BayesFactor)
+library(ggrepel)
 #devtools::install_github("langcog/langcog")
@@
 
+tstatDF$origBF[7] <- 1e+11
+
 ggplot(tstatDF, aes(x = origBF, y = repBF)) +
@@
   geom_smooth(method = "lm", se=FALSE) + 
+  geom_text_repel(aes(label = first_author_name), size = 3) + 
   xlab("Original Bayes Factor") + 
@@
   scale_x_log10(limits = c(10**-1.75, 10**11), 
-                breaks = c(1/10, 1/3, 3, 10, 100),
-                labels = c("1/10", "1/3", "3", "10")) +
+                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
+                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) +
   scale_y_log10(limits = c(10**-1.75, 10**11),
-                breaks = c(1/10, 1/3, 3, 10, 100),
-                labels = c("1/10", "1/3", "3", "10")) + 
+                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
+                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) + 
   scale_size_continuous(name = "Ratio of replication to original t value") + 
@@
   theme(legend.position="bottom")
-
-  # xlim(-2, 30) +
-  # ylim(-2, 30) +
-  # geom_hline(aes(yintercept = 10), linetype = 2)+
-  # geom_hline(aes(yintercept = 3), linetype = 2)+
-  # geom_hline(aes(yintercept = 1/3), linetype = 2)+
-  # geom_hline(aes(yintercept = 1/10), linetype = 2)+
-  # geom_vline(aes(xintercept = 10), linetype = 2)+
-  # geom_vline(aes(xintercept = 3), linetype = 2)+
-  # geom_vline(aes(xintercept = 1/3), linetype = 2)+
-  # geom_vline(aes(xintercept = 1/10), linetype = 2) +
 ```
@@
 ```
-
-## Exploratory analysis
 

### 2016-07-08 paper/paper.Rmd
bayes plot updates

@@
   mutate(repBF = getBF(rep_t_stat, rep_t_df), 
-         t_ratio = rep_t_df/original_t_df)
+         df_ratio = rep_t_df/original_t_df)
 
@@
 ggplot(tstatDF, aes(x = origBF, y = repBF)) +
-  geom_point(alpha = .8, aes(size = t_ratio, 
+  geom_point(alpha = .8, aes(size = df_ratio, 
                              col = replicated_TA_factor)) +
@@
   geom_smooth(method = "lm", se=FALSE) + 
+  # geom_smooth(data = filter(tstatDF, 
+  #                           !(first_author_name %in% c("Atir","Ko"))), 
+  #                           method = "lm", se=FALSE, lty = 2, size = .5) + 
   geom_text_repel(aes(label = first_author_name), size = 3) + 
@@
   scale_x_log10(limits = c(10**-1.75, 10**11), 
-                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
-                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) +
+                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
+                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
+                           "1,000,000","1,000,000,000")) +
   scale_y_log10(limits = c(10**-1.75, 10**11),
-                breaks = c(1/10, 1/3, 3, 10, 100, 100000),
-                labels = c("1/10", "1/3", "3", "10","100", "1,000,000")) + 
-  scale_size_continuous(name = "Ratio of replication to original t value") + 
+                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
+                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
+                           "1,000,000","1,000,000,000")) + 
+  scale_size_continuous(name = "Ratio of replication df to original df") + 
   scale_color_solarized(name = "Subjective replication rating") + 
@@
   theme(legend.position="bottom")
+
+# note: fix slope on trend line, because the atir finding is a hack right now so it fits in the axes. 
 ```

### 2016-07-15 paper/paper.Rmd
updates for sofer + paper

@@
   xlab("Original p-value (binned)") + 
-  ylab("Instructor replication rating") + 
+  ylab("Replication p-value (exact)") + 
   theme_bw() + 
@@
 
+In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*.
+We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
+Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing.
+The modal outcome of our projects was an incomplete replication, in which some hint of the original pattern was observed but results were not statistically significance and had both smaller effect size and lower evidential value than the originals.
+
+Our findings are largely congruent with the results of @osc2015
+
+we believe these findings
+
 Importance of self-selected papers - these are the papers that interesting to next generation of researchers
@@
 
-# Supplemental
+Pitfalls of doing the sort of analysis here.
+Even open data posed significant challenges in reproducing effect sizes.
+Data were stored in proprietary formats, model specifications were unclear from text.
+Reproducing individual numbers was challenging or impossible.
 
-All materials that are needed for class to implement
-Email templates
-Spreadsheets
-TA/prof auditing processes
+<!-- # Supplemental -->
+
+<!-- All materials that are needed for class to implement -->
+<!-- Email templates -->
+<!-- Spreadsheets -->
+<!-- TA/prof auditing processes -->
 

### 2016-07-15 subsidiary_analysis/compute_sofer_es.R

@@ -1,0 +1,57 @@
+rm(list=ls())
+library(readr)
+library(dplyr)
+library(tidyr)
+library(lsr)
+sofer <- read_csv("subsidiary_analysis/Experiment_1_Rps.csv")
+
+d <- sofer %>%
+  mutate(subid = 1:n()) %>%
+  gather(datapoint, rating, starts_with("dft")) %>%
+  separate(datapoint, into = c("foo","DFT","trial_num"), sep = "_") %>%
+  mutate(condition = ifelse(Trust1Attrc2 == 1, "Trustworthiness", "Attractiveness"), 
+         DFT = factor(DFT)) %>%
+  select(-foo, -Trust1Attrc2) %>% 
+  arrange(subid)
+
+# Repeated measures
+mod <- aov(rating ~ DFT * condition + Error(subid / DFT), data = d)
+summary(mod)
+
+# By subjects
+subs <- d %>%
+  group_by(condition, DFT, subid) %>%
+  summarise(rating = mean(rating))
+
+mod_subs <- aov(rating ~ DFT * condition, data = subs)
+summary(mod_subs)
+
+# By "items"
+items <- d %>%
+  group_by(condition, DFT) %>%
+  summarise(rating = mean(rating))
+
+mod_items <- aov(rating ~ DFT * condition, data = items)
+summary(mod_items)
+
+
+# linear model by items
+items$nDFT <- scale(as.numeric(as.character(items$DFT)), scale=FALSE)
+items$condition_e <- factor(items$condition)
+contrasts(items$condition_e) <- c(-.5,.5)
+
+mod_lm_items <- lm(rating ~ nDFT * condition_e + I(nDFT^2) * condition_e, data=items)
+anova(mod_lm_items)
+summary(mod_lm_items)
+
+# linear models by subs 
+items$nDFT <- scale(as.numeric(as.character(items$DFT)), scale=TRUE)
+items$condition_e <- factor(items$condition)
+contrasts(items$condition_e) <- c(-.5,.5)
+
+mod_lm_items <- lm(rating ~ nDFT * condition_e + I(nDFT^2) * condition_e, data=items)
+anova(mod_lm_items)
+summary(mod_lm_items)
+etaSquared(mod_lm_items)
+
+# original t value on coefficient 

### 2016-07-15 paper/paper.Rmd
discussion section

@@
 
-```{r, eval=F}
-layout(matrix(1:22,nr=11,byr=T))
-for (key in project_plan$project_key) {
-  tryCatch(source(function() {
-  orig <- readPNG(paste0("figures/",key,"-original.png"))
-  rep <- readPNG(paste0("figures/",key,"-replication.png"))
-  plot(orig)
-  plot(rep)}
-  ))
-}
-```
-
 # Discussion
@@
 Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing.
-The modal outcome of our projects was an incomplete replication, in which some hint of the original pattern was observed but results were not statistically significance and had both smaller effect size and lower evidential value than the originals.
+The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but results were not statistically significant and had both smaller effect size and lower evidential value than the originals.
 
-Our findings are largely congruent with the results of @osc2015
+Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project.
+While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources.
+Indeed, the majority of the projects in our report were relativley close replications and included the same or greater numbers of participants.
+Yet, despite these virtues, our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests.
+In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015].
+What are the causes of this relatively low rate of replication?
 
-we believe these findings
+Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013,@ioannidis2005].
+On the other hand, an alternative viewpoint is that -- especially for studies that leverage social constructs -- exact replication may be difficult across contexts [@gilbert2016;@vanbavel2016].
+For both reasons of design and scale, our study here cannot disentangle these factors empirically.
+Nevertheless, the consistent descreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that intial publications tend to over-estimate effects.
+And although our sample was too small for statistical inference, numerically our results do not support replication fidelity in terms of sample and procedure as a primary driver of success.
 
-Importance of self-selected papers - these are the papers that interesting to next generation of researchers
+Our experiences performing and compiling the studies here sheds light on one further concern that we believe has been under-reported in past studies [including @osc2015].
+Our standard model of replication is based on the notion of a single statistical test -- and its associated effect size -- being the key properties of a study that can be targeted for replication.
+Yet, as we mentioned above, selecting this key statistical test was difficult for most of the projects in our sample, and virtually impossible for some.
+We were often forced to consult other sections of the papers (e.g., abstracts, discussion sections) to gain clarity on what test was considered the critical one for the authors' interpretation.
+It is likely that some of our decisions would not be ratified by the original authors.
 
-The single effect-size paradigm is deeply broken.
+Indeed, by the standards of clinical trials research, every single study we replicated in this report would be classified as exploratory research.
+No protocol was pre-registered, and the pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
+Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications.
+And in many cases, there are no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf.
+@bakeman2005].
+This set of features -- which, in our experience, are endemic to published psychological work -- makes replication research within the conventional statistical paradigm extremely challenging.
 
-How to archive and make searchable the results of this sort of class?
-OSF - but need search tools
-PsychFileDrawer
-CurateScience
+In our view, two recommendations will improve this situation dramatically.
+First, pre-registration typically requires the selection of one or a small number of statistical analyses to be designated as critical for interpretation.
+Were this information available, it would have simplified the problem of selecting effects to replicate in several cases.
+Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here, in a number of ways.
+In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archving data and analytic code is often critical for other investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is a way of allowing more flexible reuse.
 
-Pitfalls of doing the sort of analysis here.
-Even open data posed significant challenges in reproducing effect sizes.
-Data were stored in proprietary formats, model specifications were unclear from text.
-Reproducing individual numbers was challenging or impossible.
+In conclusion, our results here demonstrate the practical possibility of performing replication research in the classroom.
+There are many challenges for ensuring high-quality replications in a pedagogical setting -- from checking experimental methods to reviewing analytic code for errors -- but we would argue that these are not just pedagogical challenges.
+They are challenges for psychological science.
+We believe that the openness and transparency we pursued here as part of our pedagogical goals should be models not just for other classes but for future research more broadly.
+
+# Supplemental Materials: Project-By-Project Methods Addendum
+
+```{r, fig.height=9, fig.width=6}
+library(png)
+layout(matrix(1:24,nr=6,byr=T))
+for (key in project_plan$project_key) {
+  orig <- readPNG(paste0("../figures/",key,"-original.png"))
+  rep <- readPNG(paste0("../figures/",key,"-replication.png"))
+
+  par(mai=c(0,0,0,0))
+  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
+  rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
+
+  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
+  rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
+
+}
+```
+
+For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication. Side-by-side visualizations are presented in Figure SM1.
+
+## Sofer et al. (2015)
+
+- key statistic in original 
+-
+
+##
+
+# References
 
@@
 <!-- Spreadsheets -->
-<!-- TA/prof auditing processes -->
-
-# References
+<!-- TA/prof auditing processes --

### 2016-07-15 project_analyses/jsalloum.R
Compute approximation to cohens d

@@ -42,12 +42,15 @@ dfdenom = params$Df[length(params$Df)]
 stat_descript <- paste0("F(",dfnum,", ",dfdenom,") = ",round(F_stat, 3))
 stat_descript
 
+## lsr::etaSquared(rs1.1) => d = 2.3758
+cohensD <- 2*sqrt(F_stat)/sqrt(dfdenom)
+
 project_info <- data.frame(
   project_key = "jsalloum", 
   rep_t_stat = sqrt(F_stat),
   rep_t_df = dfdenom,
   rep_final_n = length(d.af$speakerId), 
   rep_n_excluded = 0, 
-  rep_es = NA, 
+  rep_es = cohensD, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = p)

### 2016-07-15 project_analyses/lampinen.R

@@ -78,7 +78,11 @@ write.csv(subject_aggregated_data, file = paste0(path,"lampinen.csv"),
           row.names = F, quote = F) 
 
 n_subjects = length(unique(subject_aggregated_data$subject))
-t_res = t.test(subject_aggregated_data[!subject_aggregated_data$rotating,]$K,subject_aggregated_data[subject_aggregated_data$rotating,]$K,paired=T)
+nonRotatingK = subject_aggregated_data[!subject_aggregated_data$rotating,]$K
+rotatingK = subject_aggregated_data[subject_aggregated_data$rotating,]$K
+t_res = t.test(nonRotatingK, rotatingK, paired=T)
+cohensD = cohensD(nonRotatingK, rotatingK, method='paired')
+
 F_stat = (t_res$statistic)^2
 p = pf(F_stat,1,n_subjects-1,lower.tail=F)
 stat_descript <- paste0("F(",1,", ",t_res$parameter,") = ",round(F_stat, 3))
@@ -89,7 +93,7 @@ project_info <- data.frame(
   rep_t_df = t_res$parameter,
   rep_final_n = n_subjects, 
   rep_n_excluded = length(files) - n_subjects, 
-  rep_es = NA, 
+  rep_es = cohensD, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = p)
 

### 2016-07-15 project_analyses/salehi.R

@@ -70,7 +70,7 @@ write_csv(d, "processed_data/salehi.csv")
 
 ### REVISED TO USE FULL ANOVA (MCF 7/1/16)
 fitConTrait <- aov(rating ~ traitType * condition + 
-                     Error(workerid/(traitType))+(condition), data=d)
+                   Error(workerid/(traitType))+(condition), data=d)
 summary(fitConTrait)
 
 p <- summary(fitConTrait)[[2]][[1]][2,5]
@@ -87,11 +87,12 @@ df2 <- summary(fitConTrait)[[2]][[1]][3,1]
 # cohens_d <- effsize::cohen.d(masculineDivergentMean$workermean, masculineConnvergentMean$workermean)$estimate
 
 test_stat <- paste0("F(",df1,",",df2,")=",round(Fval, digits=3))
-  
+cohensd = 2*sqrt(Fval)/sqrt(df2)
+
 project_info <- data.frame(project_key = "salehi",
                            rep_final_n = length(unique(d$workerid)),
                            rep_n_excluded = 0, 
-                           rep_es = NA, 
+                           rep_es = cohensd, 
                            rep_test_statistic_str = test_stat,
                            rep_t_stat = sqrt(Fval), #http://www.tc.umn.edu/~oakes007/Files/Comm%20Trials/F%20and%20t%20statistics.pdf
                            rep_t_df = df2,

### 2016-07-22 paper/paper.Rmd
various

@@
 One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs.
-We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level experimental methods.
-By a variety of measures, these replications were successful approximately half of the time, providing an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt.
+We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
+The modal outcome was a partial replication, with most yielding weaker evidence than the original study.
+This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt.
 We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."

### 2016-07-23 project_analyses/salehi.R
remove old effsize calls

@@ -66,7 +66,6 @@ write_csv(d, "processed_data/salehi.csv")
 #effect size
 # masculineDivergentMean <- masculine %>% filter(condition == 'Divergent')
 # masculineConnvergentMean <- masculine %>% filter(condition == 'Convergent')
-# cohens_d <- effsize::cohen.d(masculineDivergentMean$workermean, masculineConnvergentMean$workermean)$estimate
 
 ### REVISED TO USE FULL ANOVA (MCF 7/1/16)
 fitConTrait <- aov(rating ~ traitType * condition + 
@@ -84,7 +83,6 @@ df2 <- summary(fitConTrait)[[2]][[1]][3,1]
 #   summarise(mean 
 # masculineDivergentMean <- masculine %>% filter(condition == 'Divergent')
 # masculineConnvergentMean <- masculine %>% filter(condition == 'Convergent')
-# cohens_d <- effsize::cohen.d(masculineDivergentMean$workermean, masculineConnvergentMean$workermean)$estimate
 
 test_stat <- paste0("F(",df1,",",df2,")=",round(Fval, digits=3))
 cohensd = 2*sqrt(Fval)/sqrt(df2)

### 2016-07-23 paper/paper.Rmd
Add effect size plot

--- 2016-07-15 paper/paper.Rmd
@@
 Overall, projects had a somewhat larger probability of being judged successful if it was judged to be closer to the original:
-\%`r round(mean(d$replicated_TA[d$high_fidelity]), digits=2)` 
+`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
 vs. 
-\%`r round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`.
+`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
 There were small numerical effects of being run on Mechanical Turk (
-\%`r round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)` 
+`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\%
 vs. 
-\%`r round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`. 
+`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%. 
 ) and having open materials (
-\%`r round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)` 
+`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
 vs. 
-\%`r round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`), though we do not believe these differences are interpretable given our sample size.
+`r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.
 
@@
 
-Flag: Original effect size not given for auc?
+```{r}
+# Note that the sofer paper is off the charts (d > 16) and excluded
+ggplot(d,aes(x=original_ES_d,y=rep_es, 
+             color=d$replicated_TA_factor)) +
+  geom_jitter(height=0, width=.2) +
+  geom_vline(xintercept=c(0.2), lty = 5) +
+  geom_vline(xintercept=c(0.5), lty = 2) +
+  geom_vline(xintercept=c(0.8), lty = 3) +
+  # geom_hline(yintercept=c(0.2), lty = 5) +
+  # geom_hline(yintercept=c(0.5), lty = 2) +
+  # geom_hline(yintercept=c(0.8), lty = 3) +
+  geom_abline(slope = 1, intercept = 0, linetype = 2) +
+  xlab("Original effect size (cohen's d)") + 
+  ylab("Replication effect size (cohen's d)") + 
+  theme_bw() + 
+  scale_color_solarized(name = "Subjective replication rating") + 
+  xlim(0, 4) +
+  ylim(0, 4) +
+  theme(legend.position = "bottom")
 
-```{r}
-d$original_ES <- as.numeric(gsub(".*=(.*)","\\1", d$original_ES_text))
-#Ensure that effect size is given in same units... Make beautiful ci chart here...
+# Make beautiful ci chart here...
+
 ```
@@
 ```{r, fig.height=9, fig.width=6}
-library(png)
-layout(matrix(1:24,nr=6,byr=T))
-for (key in project_plan$project_key) {
-  orig <- readPNG(paste0("../figures/",key,"-original.png"))
-  rep <- readPNG(paste0("../figures/",key,"-replication.png"))
-
-  par(mai=c(0,0,0,0))
-  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
-  rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
-
-  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
-  rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
-
-}
+# library(png)
+# layout(matrix(1:24,nr=6,byr=T))
+# for (key in project_plan$project_key) {
+#   orig <- readPNG(paste0("../figures/",key,"-original.png"))
+#   rep <- readPNG(paste0("../figures/",key,"-replication.png"))
+# 
+#   par(mai=c(0,0,0,0))
+#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
+#   rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
+# 
+#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
+#   rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
+# 
+# }
 ```
@@
 - key statistic in original
--
-
-##
 
@@
 <!-- Spreadsheets -->
-<!-- TA/prof auditing processes --
+<!-- TA/prof auditing processes -->

### 2016-07-23 project_analyses/auc.R
Add mixed models to sofer

@@ -138,7 +138,7 @@ summarySEwithin <- function(data=NULL, measurevar, betweenvars=NULL, withinvars=
 
 ## The planned sample would be US-based mTurkers, with 45 participants in each condition. We will not be able to replicate the exclusion criteria and instead will restrict the locale to US participants of all genders and all ages. We will collect light demographic information to analyze this difference.
 
-path <- "data/auc/"
+path <- "../data/auc/"
 files <- dir(path, pattern = "*.json")
 d.raw <- data.frame()
 d.balance <- data.frame()
@@ -163,7 +163,9 @@ for (f in files) {
 
 chr.rows <- sapply(d.raw, is.character)
 d.raw[,chr.rows] <- lapply(d.raw[,chr.rows], as.factor) # need to factorize character strings
-d.raw$face_dft <- as.factor(d.raw$face_dft)
+d.raw <- d.raw %>%
+    mutate(face_dft = as.factor(face_dft))
+
 
 d <- summarySEwithin(d.raw, measurevar="face_rating", withinvars=c("face_dft", "exp_type"),
                             idvar="workerid", na.rm=FALSE, conf.interval=.95)
@@ -182,6 +184,14 @@ model <- lm(centered_face_rating ~
               centered_dft * exp_type + 
               I(centered_dft**2) * exp_type,
             d)
+
+
+mixedModel <- lmer(face_rating ~ exp_type + nDFT + I(nDFT^2) 
+                   + exp_type:nDFT + exp_type:I(nDFT^2) 
+                   + (1 + nDFT + I(nDFT^2)| workerid), 
+                   d.raw %>% mutate(nDFT = scale(as.numeric(as.character(face_dft)), scale=TRUE)))
+                   
+
 summary(model)
 
 model_coef <- summary(model)$coefficients["exp_typetrustworthy:centered_dft","Estimate"]
@@ -192,6 +202,7 @@ lsr::etaSquared(model)
 cohensd <- abs(2*model_tval/sqrt(model_df))
 
 stat_descript <- paste0("t(",model_df,") = ",round(model_tval,2))
+
 
 
 project_info <- data.frame(project_key = "auc",

### 2016-07-23 subsidiary_analysis/compute_sofer_es.R

@@ -3,7 +3,7 @@ library(readr)
 library(dplyr)
 library(tidyr)
 library(lsr)
-sofer <- read_csv("subsidiary_analysis/Experiment_1_Rps.csv")
+sofer <- read_csv("../subsidiary_analysis/Experiment_1_Rps.csv")
 
 d <- sofer %>%
   mutate(subid = 1:n()) %>%
@@ -46,12 +46,18 @@ summary(mod_lm_items)
 
 # linear models by subs 
 items$nDFT <- scale(as.numeric(as.character(items$DFT)), scale=TRUE)
-items$condition_e <- factor(items$condition)
-contrasts(items$condition_e) <- c(-.5,.5)
+items$condition_e <- scale(ifelse(items$condition == "Trustworthiness", 1, 0), scale = F)
+#contrasts(items$condition_e) <- c(-.5,.5)
 
-mod_lm_items <- lm(rating ~ nDFT * condition_e + I(nDFT^2) * condition_e, data=items)
+mod_lm_items <- lm(scale(rating) ~ condition_e + nDFT + I(nDFT^2) + condition_e:nDFT + condition_e:I(nDFT^2) , data=items)
 anova(mod_lm_items)
 summary(mod_lm_items)
 etaSquared(mod_lm_items)
 
 # original t value on coefficient 
+mixedModel <- lmer(rating ~ condition_e + nDFT + I(nDFT^2) + condition_e:nDFT + condition_e:I(nDFT^2) 
+                   + (1 + nDFT + I(nDFT^2)| subid), 
+                   data = d %>% 
+                     mutate(nDFT = scale(as.numeric(as.character(DFT)), scale=TRUE)) %>%
+                     mutate(condition_e = factor(condition)))
+summary(mixedModel)

### 2016-08-03 paper/paper.Rmd
some minor paper/bib updates

@@
 output: kmr::apa_manuscript
+
 csl: apa6.csl
@@
     "Replications are important to science, but who will do them?
-One proposal is that students can conduct direct replications as part of their training; but to date there is limited evidence that this proposal can result in high-quality research outputs.
-We report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
-The modal outcome was a partial replication, with most yielding weaker evidence than the original study.
+One proposal is that students can conduct direct replications as part of their training.
+As a proof-of-concept for this idea, here we report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
 This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt.
-We describe the workflow and pedagogical methods that were used in the class (providing access to all materials) and discuss challenges for adoption of this model more broadly."
+Congruent with previous findings, replication studies typically yielded smaller effects than originals, though the modal outcome was some support for the original claim.
+We describe the workflow and pedagogical methods that were used in the class and discuss challenges for adoption of this pedagogical model and replication research more broadly."
 
@@
 
-Reproducibility is a core value for empirical research, but there is increasing concern throughout psychology that weak statistical standards and methodological practices have led to low empirical rates of replication [@osc2015].
+Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
 Under the current incentive structure for science, direct replication is not typically valued, however.
@@
 @osc2015].
-Making such an estimate requires determining a sampling strategy, a notion of what constitutes a direct replication, what constitutes a successful replication, among many other difficult decisions [@gilbert2016;@anderson2016].
+Making such an estimate minimally requires determining a sampling strategy, a notion of what constitutes a direct replication, and a standard for what constitutes a successful replication, among many other difficult decisions [@gilbert2016;@anderson2016].
 In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work.
@@
 
-d <- left_join(project_plan, project_data_summary, by = c("project_key"))
+d <- left_join(project_plan, project_data_summary, by = c("project_key")) %>%
+  rowwise() %>%
+  mutate(fidelity = (replication_fidelity_MCF + replication_fidelity_ES) / 2) %>%
+  ungroup
 ```
@@
 
-All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.
-Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.
-All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
 
@@
 For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors).
-Responses were received in all but one case, usually within a matter of days.
+Responses were received in all but one case, all within a matter of days.
 
@@
 In one case, the original experiment was apparently extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would apparently yield high power.
-In one case, we reduced the number of trials as part of the adaptation to mechanical turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in Supplemntal Materials).
+In one case, we reduced the number of trials as part of the adaptation to mechanical turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
 
@@
 
-Details of individual replications are available in the supplementary materials.
 Students chose findings from a wide variety of domains for replication.
@@
 Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
+Details of individual replications are available in SOM.
 
@@
 Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
-(In one case, a student failed to complete the pre-registration but nevertheless submitted a pre-specified analysis plan to the instructors for review).
+(In one case, a student failed to complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review).
 
-The instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
-Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the modal rating was `r round(mean(d$replication_fidelity_MCF), digits = 2)`.
+Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
+Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)`.
 Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might have an effect on the results.
@@
 ```{r}
-d$high_fidelity <- d$replication_fidelity_MCF > median(d$replication_fidelity_MCF)
+d$high_fidelity <- d$fidelity > median(d$fidelity)
 # table(d$replicated_TA,d$replicated_student) # Make prettier
@@
 
-- key statistic in original
+key statistic in original
 

### 2016-08-22 paper/paper.Rmd
merged plots

@@
 This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt.
-Congruent with previous findings, replication studies typically yielded smaller effects than originals, though the modal outcome was some support for the original claim.
+Congruent with previous findings, replication studies typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
 We describe the workflow and pedagogical methods that were used in the class and discuss challenges for adoption of this pedagogical model and replication research more broadly."
@@
 library(langcog)
+library(cowplot)
 ```
@@
 We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
-Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is reproducible in some more abstract sense.
+Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is replicable in some more abstract sense.
 
@@
                                  labels = c("No","Partial","Yes"))
-ggplot(d,aes(x=original_p_value_bins,y=rep_p_value, 
-             color=d$replicated_TA_factor)) +
-  geom_jitter(height=0, width=.2) +
-  geom_hline(yintercept=c(0.05), lty = 2) + 
-  geom_hline(yintercept=c(0.1), lty = 3) + 
-  ylim(c(0,1)) +
-  xlab("Original p-value (binned)") + 
-  ylab("Replication p-value (exact)") + 
-  theme_bw() + 
-  scale_color_solarized(name = "Subjective replication rating") + 
-  theme(legend.position = "bottom")
+# ggplot(d,aes(x=original_p_value_bins,y=rep_p_value, 
+#              color=d$replicated_TA_factor)) +
+#   geom_jitter(height=0, width=.2) +
+#   geom_hline(yintercept=c(0.05), lty = 2) + 
+#   geom_hline(yintercept=c(0.1), lty = 3) + 
+#   ylim(c(0,1)) +
+#   xlab("Original p-value (binned)") + 
+#   ylab("Replication p-value (exact)") + 
+#   theme_bw() + 
+#   scale_color_solarized(name = "Subjective replication rating") + 
+#   theme(legend.position = "bottom")
 ```
@@
 
-```{r}
-# Note that the sofer paper is off the charts (d > 16) and excluded
-ggplot(d,aes(x=original_ES_d,y=rep_es, 
-             color=d$replicated_TA_factor)) +
-  geom_jitter(height=0, width=.2) +
-  geom_vline(xintercept=c(0.2), lty = 5) +
-  geom_vline(xintercept=c(0.5), lty = 2) +
-  geom_vline(xintercept=c(0.8), lty = 3) +
-  # geom_hline(yintercept=c(0.2), lty = 5) +
-  # geom_hline(yintercept=c(0.5), lty = 2) +
-  # geom_hline(yintercept=c(0.8), lty = 3) +
-  geom_abline(slope = 1, intercept = 0, linetype = 2) +
-  xlab("Original effect size (cohen's d)") + 
-  ylab("Replication effect size (cohen's d)") + 
-  theme_bw() + 
-  scale_color_solarized(name = "Subjective replication rating") + 
-  xlim(0, 4) +
-  ylim(0, 4) +
-  theme(legend.position = "bottom")
-
-# Make beautiful ci chart here...
-
-```
-
 ### Bayes factor analysis
@@
 ```{r}
+# Note that the sofer paper is off the charts (d > 16) and excluded
+p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
+  geom_point(alpha = .8, 
+             aes(color=replicated_TA_factor, size = collected_n)) +
+  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
+  scale_x_continuous(limits = c(0, 3.5), 
+                breaks = c(.2, .5, .8, 1, 2, 3)) +
+  scale_y_continuous(limits = c(0, 3.5), 
+                breaks = c(.2, .5, .8, 1, 2, 3)) +
+  geom_abline(slope = 1, intercept = 0, linetype = 2) +
+  geom_smooth(method = "lm", se=FALSE) +
+  xlab("Orig. effect size (d)") + 
+  ylab("Rep. effect size (d)") + 
+  theme_bw(base_size=10) + theme(legend.position="bottom") + 
+  scale_size(name = "Rep. N") +
+  scale_color_solarized(name = "Subjective rep. rating")
+
 getBF <- function(t_stat, t_df) {
@@
 
-ggplot(tstatDF, aes(x = origBF, y = repBF)) +
+p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
   geom_point(alpha = .8, aes(size = df_ratio, 
@@
   geom_smooth(method = "lm", se=FALSE) +
-  # geom_smooth(data = filter(tstatDF,
-  #                           !(first_author_name %in% c("Atir","Ko"))),
-  #                           method = "lm", se=FALSE, lty = 2, size = .5) +
-  geom_text_repel(aes(label = first_author_name), size = 3) +
-  xlab("Original Bayes Factor") + 
-  ylab("Replication Bayes Factor") + 
+  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
+  xlab("Orig. Bayes factor") + 
+  ylab("Rep. Bayes factor") + 
   scale_x_log10(limits = c(10**-1.75, 10**11), 
-                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
-                           "1,000,000","1,000,000,000")) +
+                breaks = c(1/10, .3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
+                labels = c("1e-1", "3e-1", "3", "1e1","1e2", "1e3", 
+                           "1e6","1e9")) +
   scale_y_log10(limits = c(10**-1.75, 10**11),
-                breaks = c(1/10, 1/3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c("1/10", "1/3", "3", "10","100", "1,000", 
-                           "1,000,000","1,000,000,000")) + 
-  scale_size_continuous(name = "Ratio of replication df to original df") + 
-  scale_color_solarized(name = "Subjective replication rating") + 
-  theme_bw() +
-  theme(legend.position="bottom")
+                breaks = c(1/10, .3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
+                labels = c("1e-1", "3e-1", "3", "1e1","1e2", "1e3", 
+                           "1e6","1e9")) + 
+  theme_bw(base_size=10) + theme(legend.position="bottom") + 
+  scale_size_continuous(name = "Ratio of rep. df to orig. df") + 
+  scale_color_solarized(name = "Subjective rep. rating")
 
 # note: fix slope on trend line, because the atir finding is a hack right now so it fits in the axes.
+
+plot_grid(p1, p2, labels = c("A", "B"))
 ```

### 2016-08-22 paper/paper.Rmd
discussion tweaks

@@
 While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources.
-Indeed, the majority of the projects in our report were relativley close replications and included the same or greater numbers of participants.
-Yet, despite these virtues, our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests.
+Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants.
+Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on available samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects.
+
+Our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests.
 In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015].

### 2016-08-22 paper/paper.Rmd
crop pipeline pdf, some appendix/bib

@@
 
+## Storm & Stone (2015)
+
+This paper found that when participants had the opportunity to save a file containing a list of target words before studying another file, they retained more information from the second study session.
+Our target for replication was Experiment 3, in which the effect was found to depend on the amount of information that was studied in the first file, with a greater effect for an eight-word list than a two-word list.
+The key statistical test we selected was the interaction in a 2x2 mixed-design ANOVA (save vs.
+no-save condition and two- vs.
+eight-word condition).
+The replication study failed to find evidence of the interaction, but ironically this was because we found evidence for a main effect of save condition: The authors' key manipulation succeeded for both load conditions.
+Perhaps even two words was sufficient to create interference for our online sample.
+
+## Lewis & Oyserman (2015)
+
+## Scopelliti, Lowenstein & Vosgerau (2015)
+
+## Liverence & Scholl (2015)
+
+## Wang et al. (2015)
+
 ## Sofer et al. (2015)
@@
 key statistic in original
+
+## Ko, Sadler, & Galinksy (2015)
+
+## Atir, Rosenzweig, & Dunning (2015)
+
+## Proudfoot, Kay, & Koval (2015)
+
+## Zaval, Markowitz, & Weber (2015)
+
+## Xu & Franconeri (2015)
 

### 2016-08-22 project_analyses/lampinen.R
Simple bar comparisons (lampinen rhiac smraposo)

@@ -97,4 +97,55 @@ project_info <- data.frame(
   rep_test_statistic_str = stat_descript,
   rep_p_value = p)
 
+# Original plot
+se <- function(x) sd(x, na.rm=T)/sqrt(length(x[!is.na(x)]))
+
+plot_mean = c(0.96,1.86)
+plot_se = c(0.1,0.15)
+plot_rotating = c("Rotating","Static")
+o_plot <- data.frame(plot_mean,plot_se,plot_rotating)
+colnames(o_plot) <- c('mean', 'se', 'rotating')
+o_plot <- o_plot %>%
+  mutate(upper = mean + se,
+         lower = mean - se)
+
+ggplot(o_plot, aes(x=rotating, y = mean,fill = rotating)) + 
+  geom_bar(stat="identity") +
+  geom_errorbar(aes(ymin=lower, ymax=upper),
+                size=.3,
+                width=.3) +
+  coord_cartesian(ylim=c(0,2.5)) + #to match original study
+  xlab("Condition") +
+  ylab("Feature-Part Capacity (K)") +
+  ggtitle("Xu - Original") +
+  theme_bw(base_size = 6) +
+  scale_fill_grey(start=.4) +
+  theme(legend.position="none")
+
+ggsave("figures/lampinen-original.png",width = 1.5,height=1.5,units="in")
+
+# Replication plot
+
+d_plot <- subject_aggregated_data %>% 
+  group_by(rotating) %>%
+  summarise(mean = mean(as.numeric(K),na.rm=T),
+            se = se(as.numeric(K)),
+            upper = mean + se,
+            lower = mean - se)
+d_plot$rotating <- c("Static","Rotating")
+
+ggplot(d_plot, aes(x=rotating, y = mean,fill = rotating)) + 
+  geom_bar(stat="identity") +
+  geom_errorbar(aes(ymin=lower, ymax=upper),
+                size=.3,
+                width=.3) +
+  coord_cartesian(ylim=c(0,2.5)) + #to match original study
+  xlab("Condition") +
+  ylab("Feature-Part Capacity (K)") +
+  ggtitle("Xu - Replication") +
+  theme_bw(base_size = 6) +
+  scale_fill_grey(start=.4) +
+  theme(legend.position="none")
+
+ggsave("figures/lampinen-replication.png",width = 1.5,height=1.5,units="in")
 

### 2016-08-22 paper/paper.Rmd
appendix

@@
 
+This paper investigated motivations to save for retirement, and specifically whether changing participants' relationships to the future (making it feel more immanent) would cause them to save more.
+Our target was Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner, even controlling for age, education, and income in a linear model (there was also a manipulation of whether saving was incremental that did not result in an effect).
+We failed to find a significant relationship between the time metric manipulation and saving time.
+However, when we did not include demographic controls, we did find a marginally-significant relationship.
+In exploratory analyses, we also observed an un-predicted effect of income such that participants who reported higher income selected to start saving sooner.
+
 ## Scopelliti, Lowenstein & Vosgerau (2015)
+
+The goal of this paper was to examine whether people are accurately calibrated in their estimates of how others will respond to their attempts at self-promotion.
+Our target was Experiment 3, which showed that participants, who were instructed to describe themself in such a way that others would like them, expected to be liked more -- but were actually liked less -- than participants who were asked to describe themselves but not additionally instructed to maximize others’ interest in meeting them.
+The authors performed a series of regressions on four dependent variables capturing judgements about profile writers (interest, liking, bragging, and success), analyzing these as a function of condition (control vs.
+"maximize interest") and who the evaluator was (the writer vs.
+an independent sample).
+Power analysis for this design was quite complex because the procedure had two stages: in a first stage participants generated descriptions and predicted judgments, while in a second stage a separate sample rated the descriptions.
+
+We were faced with a choice: either we could have re-rated the descriptions gathered in the original study (by contacting the author and treating these as "materials" for the study), effectively replicating only stage two, or we could redo the entire two-step procedure.
+We elected to conduct a replication of the full procedure, but in our replication to decrease cost we focused on the liking judgments, which appeared to be central to the authors' conclusions.
+Our key test was the interaction of rater (writer vs.
+independent) and condition.^[We note that this project was submitted late and the student failed to preregister this analysis formally; however, the pre-written analysis protocol went through pre-data collection review by MCF.]  However, to power even this smaller study adequately was outside of our budget, so instead of having each judge rate a subset of 10 out of 100 total profiles, we collected a smaller sample of profiles (18) and had every profile rated by each judge.
+We failed to find the predicted interaction in this new sample.
+Instead, we found a main effect such that stage one participants predicted that raters would like them more than the stage two participants actually did.
+Despite our relatively high statistical power in the main test, however, we may have suffered from low power at the item level due to the relatively small number of profiles we collected in the replication study.
 
@@
 
+This paper tested the theory that persistent object representations could assist in spatial navigation, using a navigation paradigm in which participants used keypresses to move though a grid of pictures that were visible only one at a time.
+In Experiment 1, our target, found that participants located targets faster when navigation involved persistence cues (via sliding animations) than when persistence was disrupted (via temporally matched fading animations).
+The key test for our replication was a simple *t*-test comparing speed to find the target in the two conditions (slide vs.
+fade), not controlling for learning across the duration of the experiment.
+We failed to find this overall difference.
+However, in an exploratory followup analysis using a linear mixed effect model, we did find a highly-significant effect of condition when controlling for learning epoch.
+We speculate that the very large effect found by the original authors may have led them to select a simpler analysis that did not control for learning effects.
+Our data -- which were more variable -- required this control.
+
 ## Wang et al. (2015)
+
+This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among college undergraduate students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation.
+We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiet and completed a math task to measure performance.
+The key effect we targeted was the interaction of math anxiety squared and math motivation in predicting performance.
+We failed to find evidence for this effect.
+In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups.
 
@@
 
-key statistic in original
+This paper tested the hypothesis that face typicality affects trustworthiness judgements such that the most typical face will be judged to be the most trustworth.
+In Study 1, our target, faces of varying typicality were rated on their trustworthiness and attractiveness; while trustworthiness peaked at the most typical face, less typical faces were judged more attractive.
+While the original class projects selected a global, item-wise regression model as the key statistical test of interest, the instructor team (post-data collection) determined that the fit of this model did not in fact correspond most closely with the authors' stated hypothesis.
+We thus selected the interaction between face typicality and rating condition as our key test statistic and used the more standard by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model.
+Our replication study successfully showed this same interaction.
+We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face.
+Thus, despite replicating one key statistical test, our results are at odds with some of the original papers' claims.
 
@@
 
+This paper investigated vocal cues to social hierarchy.
+Our target for replication was Experiment 2, which assessed whether participants used particular acoustic cues to make inferences about speakers' level of social hierarchy, particularly that participants from the high-rank condition in Experiment 1 were rated as more highly ranking.
+This paper employed a two-stage procedure in which participant-generated materials were rated by an independent sample.
+However, in contrast to the study of Scopelliti, Lowenstein & Vosgerau (2015), because materials were collected in Experiment 1 and were available openly, we elected to replicate only Experiment 2, the judgment study.
+The key test statistic was the main effect of hierarchy condition on "behavior score" (an index of whether speakers would engage in high-status behaviors).
+The authors were also interested in which particular vocal cues predicted participants judgments, but we judged these analyses to be more descriptive and exploratory.
+We successfully replicated the main effect of condition on hierarchy judgment, and additionally found a comparable main effect of speaker gender.
+
 ## Atir, Rosenzweig, & Dunning (2015)
+
+This paper investigated how perceived knowledge affects "overclaiming" (claiming knowledge that you do not have.
+We targeted Study 1b, which asked participants to rate their knowledge about finances, and then asked them to rate their knowledge about a set of financial terms, some of which were invented (and hence for which a positive knowledge statement would necessarily be an overclaim).
+The original study found that participants with higher self-rated financial knowledge also overclaimed at a higher rate.
+The key test statistic for this study was the coefficient in a regression model predicting overclaiming as a function of claimed personal financial knowledge, controlling for accuracy in the true finacial knowledge questions.
+We successfully replicated this effect, despite our use of a much smaller sample (due to the extremely high post-hoc power of the original study).
 
@@
 
+This paper examined whether judgments of creativity are influenced by the gender of the creator.
+In Study 1, they tested the hypothesis that "out of the box" creativity was more associated with masculine traits than feminine traits by manipulating the definition of creativity that participants saw (convergent vs.
+divergent) and asking participants to judge the centrality of different traits to that definition.
+The original pre-registration selected a subsidiary analysis of a main effect as the key test statistic, but in post-data collection review the instructor team decided that a test of the interaction between trait gender and definition condition was closer to the central theoretical claim of the paper; we use this latter test as the key test statistic.
+Our replication study found an significant interaction of similar magnitude.
+
 ## Zaval, Markowitz, & Weber (2015)
 
+This paper investigated whether encouraging participants to think about their personal legacy could increase concern for the environment.
+The main study of the paper investigated whether a legacy priming writing exercise would increase a variety of environmental measures, including donations to an environmental charity, proenvironmental intentions, and climate change beliefs.
+The key test we selected was the effect of condition (priming vs.
+control) on behavioral intentions in an analysis of variance.
+We observed a marginally significant effect in the same direction in our replication, as well as support for the mediating relationship of legacy motives on beahvioral intentions.
+Our study may have been underpowered due to budgetary constraints; we ran a sample of comparable size to the original sample of 312 participants.
+We also may have observed a smaller effect size due to the relatively smaller amount of time our participants spent on the legacy prime writing exercise.
+
 ## Xu & Franconeri (2015)
+
+This paper explored constraints on visual working memory in the context of mental rotation.
+In Experiment 1a, participants perfomed a verbal suppression task to control for use of verbal encoding while attempting to remember a cross with four colored bars, which sometimes switched colors; performing mental rotation significantly impaired ability to detect these bar swaps.
+To port the task to an online framework we decreased the number of trials and increased the number of participants we tested.
+The key test statistic was a comparison of K (a metric of the number of visual features remembered) between the rotation and no-rotation conditions.
+We observed a marginally-significant effect in our replication study.
+Our study showed a floor effect on capacity such that participants remembered on average very little; it is possible that small details in the displays (or the differing sample available online) led to this floor effect.
 

### 2016-08-22 paper/paper.Rmd
Add short discussion & references for BF

--- 2016-08-22 paper/paper.Rmd
@@
 
-We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level.
-Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
-
 ```{r}
@@
 
-### Original ES in the confidence interval of the replication
+We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level.
+Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value.
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
+This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included.
 
-We determine whether the original reported effect size is included in the 95\% confidence interval found in the replication studies.
+### Bayes factor and effect size analysis
 
-### Bayes factor analysis
-
-Next, following @etz2016, we conducted a Bayesian analysis.
+Next, following @etz2016, we compared Bayes Factors between the original and replication.
+The Bayes Factor is an alternative to classical null hypothesis significance testing; it quantifies the evidence in favor of a hypothesis as the ratio of the likelihood of the data under that hypothesis relative to another [@jeffreys1961].
+Its proponents point to many advantages over classical $p$-values.
+For example, it does not privilege the null hypothesis and can provide evidence either *for* or *against* it [see also @scheibehenne2016, @wagenmakers2016].
+While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
 

### 2016-08-22 paper/paper.Rmd
spell check

--- 2016-08-22 paper/paper.Rmd
@@
 
-Derermining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015].
+Determining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015].
 Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially with the constraints of a limited budget -- it may be impossible to follow more conservative guidelines in all cases.
-For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or underpowered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
 
@@
 
-In two cases, in final review of the projects (after data collection), the instructor team decided that the student's choice of key statisical test was not in fact a strong test of the original authors' primary theoretical claim.
+In two cases, in final review of the projects (after data collection), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
 In both of these cases [@sofer2015;@proudfoot2015], the original authors had fit a multiple regression model to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
@@
 The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest.
-Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically underpowered after correcting for multiple comparisons).
+Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
 Overall, projects had a somewhat larger probability of being judged successful if it was judged to be closer to the original:
@@
 For both reasons of design and scale, our study here cannot disentangle these factors empirically.
-Nevertheless, the consistent descreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that intial publications tend to over-estimate effects.
+Nevertheless, the consistent decreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that initial publications tend to over-estimate effects.
 And although our sample was too small for statistical inference, numerically our results do not support replication fidelity in terms of sample and procedure as a primary driver of success.
@@
 Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here, in a number of ways.
-In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archving data and analytic code is often critical for other investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is a way of allowing more flexible reuse.
+In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data and analytic code is often critical for other investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is a way of allowing more flexible reuse.
 
@@
 The goal of this paper was to examine whether people are accurately calibrated in their estimates of how others will respond to their attempts at self-promotion.
-Our target was Experiment 3, which showed that participants, who were instructed to describe themself in such a way that others would like them, expected to be liked more -- but were actually liked less -- than participants who were asked to describe themselves but not additionally instructed to maximize others’ interest in meeting them.
-The authors performed a series of regressions on four dependent variables capturing judgements about profile writers (interest, liking, bragging, and success), analyzing these as a function of condition (control vs.
+Our target was Experiment 3, which showed that participants, who were instructed to describe themselves in such a way that others would like them, expected to be liked more -- but were actually liked less -- than participants who were asked to describe themselves but not additionally instructed to maximize others’ interest in meeting them.
+The authors performed a series of regressions on four dependent variables capturing judgments about profile writers (interest, liking, bragging, and success), analyzing these as a function of condition (control vs.
 "maximize interest") and who the evaluator was (the writer vs.
@@
 
-This paper tested the theory that persistent object representations could assist in spatial navigation, using a navigation paradigm in which participants used keypresses to move though a grid of pictures that were visible only one at a time.
+This paper tested the theory that persistent object representations could assist in spatial navigation, using a navigation paradigm in which participants used key presses to move though a grid of pictures that were visible only one at a time.
 In Experiment 1, our target, found that participants located targets faster when navigation involved persistence cues (via sliding animations) than when persistence was disrupted (via temporally matched fading animations).
@@
 This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among college undergraduate students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation.
-We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiet and completed a math task to measure performance.
+We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiety and completed a math task to measure performance.
 The key effect we targeted was the interaction of math anxiety squared and math motivation in predicting performance.
@@
 
-This paper tested the hypothesis that face typicality affects trustworthiness judgements such that the most typical face will be judged to be the most trustworth.
+This paper tested the hypothesis that face typicality affects trustworthiness judgments such that the most typical face will be judged to be the most trustworthy.
 In Study 1, our target, faces of varying typicality were rated on their trustworthiness and attractiveness; while trustworthiness peaked at the most typical face, less typical faces were judged more attractive.
@@
 The original study found that participants with higher self-rated financial knowledge also overclaimed at a higher rate.
-The key test statistic for this study was the coefficient in a regression model predicting overclaiming as a function of claimed personal financial knowledge, controlling for accuracy in the true finacial knowledge questions.
+The key test statistic for this study was the coefficient in a regression model predicting overclaiming as a function of claimed personal financial knowledge, controlling for accuracy in the true financial knowledge questions.
 We successfully replicated this effect, despite our use of a much smaller sample (due to the extremely high post-hoc power of the original study).
@@
 This paper investigated whether encouraging participants to think about their personal legacy could increase concern for the environment.
-The main study of the paper investigated whether a legacy priming writing exercise would increase a variety of environmental measures, including donations to an environmental charity, proenvironmental intentions, and climate change beliefs.
+The main study of the paper investigated whether a legacy priming writing exercise would increase a variety of environmental measures, including donations to an environmental charity, pro-environmental intentions, and climate change beliefs.
 The key test we selected was the effect of condition (priming vs.
 control) on behavioral intentions in an analysis of variance.
-We observed a marginally significant effect in the same direction in our replication, as well as support for the mediating relationship of legacy motives on beahvioral intentions.
-Our study may have been underpowered due to budgetary constraints; we ran a sample of comparable size to the original sample of 312 participants.
+We observed a marginally significant effect in the same direction in our replication, as well as support for the mediating relationship of legacy motives on behavioral intentions.
+Our study may have been under-powered due to budgetary constraints; we ran a sample of comparable size to the original sample of 312 participants.
 We also may have observed a smaller effect size due to the relatively smaller amount of time our participants spent on the legacy prime writing exercise.
@@
 This paper explored constraints on visual working memory in the context of mental rotation.
-In Experiment 1a, participants perfomed a verbal suppression task to control for use of verbal encoding while attempting to remember a cross with four colored bars, which sometimes switched colors; performing mental rotation significantly impaired ability to detect these bar swaps.
+In Experiment 1a, participants performed a verbal suppression task to control for use of verbal encoding while attempting to remember a cross with four colored bars, which sometimes switched colors; performing mental rotation significantly impaired ability to detect these bar swaps.
 To port the task to an online framework we decreased the number of trials and increased the number of participants we tested.

### 2016-08-22 paper/paper.Rmd
pipeline figure and other fig tweaking

@@
 library(cowplot)
+library(png)
 ```
@@
 All analyses were written using R, a free and open-source platform for statistical analysis.
+A schematic of our class workflow is shown in Figure 1.
+
+```{r, fig.cap="A schematic view of our class timeline for replication projects.
+R indicates the approximate timing of instructor team reviews of student materials.", fig.height=4, fig.width=6, fig.align="center", fig.pos="t"}
+
+img <- readPNG(source = "../figures/pipeline.png")
+plot.new()
+plot.window(0:1, 0:1)
+
+#fill plot with image
+usr<-par("usr")    
+rasterImage(img, usr[1], usr[3], usr[2], usr[4])
+```
 
@@
 Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication *p*-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included.
+This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 
-### Bayes factor and effect size analysis
+### Effect size and Bayes Factor analysis
 
-Next, following @etz2016, we compared Bayes Factors between the original and replication.
+We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
+(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
+(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)`]).
+This estimate should be viewed with caution, however, due to its dependence on one very large effect size estimate ($d > 15$) from a single study.
+
+Next, following @etz2016, we compared Bayes Factors between the original and replication (Figure 2B).
 The Bayes Factor is an alternative to classical null hypothesis significance testing; it quantifies the evidence in favor of a hypothesis as the ratio of the likelihood of the data under that hypothesis relative to another [@jeffreys1961].
@@
 
-```{r}
+```{r, fig.cap="Replication effect size (A) and Bayes factor (B), plotted by the original effect size and Bayes factor, respectively.
+Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors.
+Note that the Sofer et al.
+(2015) replication showed ES and BF too large to plot easily on these axes and is hence excluded.", fig.pos="ht", fig.height=4}
+
 # Note that the sofer paper is off the charts (d > 16) and excluded
@@
   scale_size(name = "Rep. N") +
+  # scale_color_solarized(guide = FALSE)
   scale_color_solarized(name = "Subjective rep. rating")
@@
   geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
-  xlab("Orig. Bayes factor") + 
-  ylab("Rep. Bayes factor") + 
+  xlab("Orig. Bayes Factor") + 
+  ylab("Rep. Bayes Factor") + 
   scale_x_log10(limits = c(10**-1.75, 10**11), 
@@
 
-For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication. Side-by-side visualizations are presented in Figure SM1.
+For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication.
 

### 2016-08-22 paper/paper.Rmd
lots of figure tweaking + au redo

@@
 We thus selected the interaction between face typicality and rating condition as our key test statistic and used the more standard by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model.
-Our replication study successfully showed this same interaction.
-We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face.
-Thus, despite replicating one key statistical test, our results are at odds with some of the original papers' claims.
+Our replication study successfully showed this same interaction.^[We were unable to reproduce the numerical results from this model using the data from the original study, but we report the (larger) test statistics from our recomputed version.] We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face.
+Thus, despite replicating one key statistical test, our results are at odds with some of the original paper's claims.
 

### 2016-08-22 project_analyses/auc.R

@@ -1,142 +1,26 @@
 library(rjson)
 library(dplyr)
+library(readr)
+library(tidyr)
+library(ggrepel)
+library(lme4)
 
-## Code in this block taken from: http://www.cookbook-r.com/Graphs/Plotting_means_and_error_bars_(ggplot2)
+##### DATA --------------------------------------------------
 
-## Gives count, mean, standard deviation, standard error of the mean, and confidence interval (default 95%).
-##   data: a data frame.
-##   measurevar: the name of a column that contains the variable to be summariezed
-##   groupvars: a vector containing names of columns that contain grouping variables
-##   na.rm: a boolean that indicates whether to ignore NA's
-##   conf.interval: the percent range of the confidence interval (default is 95%)
-summarySE <- function(data=NULL, measurevar, groupvars=NULL, na.rm=FALSE,
-                      conf.interval=.95, .drop=TRUE) {
-    # New version of length which can handle NA's: if na.rm==T, don't count them
-    length2 <- function (x, na.rm=FALSE) {
-        if (na.rm) sum(!is.na(x))
-        else       length(x)
-    }
+## ORIGINAL
 
-    # This does the summary. For each group's data frame, return a vector with
-    # N, mean, and sd
-    datac <- plyr::ddply(data, groupvars, .drop=.drop,
-      .fun = function(xx, col) {
-        c(N    = length2(xx[[col]], na.rm=na.rm),
-          mean = mean   (xx[[col]], na.rm=na.rm),
-          sd   = sd     (xx[[col]], na.rm=na.rm)
-        )
-      },
-      measurevar
-    )
+sofer <- read_csv("subsidiary_analysis/Experiment_1_Rps.csv")
+sofer <- sofer %>%
+  mutate(subid = 1:n()) %>%
+  gather(datapoint, rating, starts_with("dft")) %>%
+  separate(datapoint, into = c("foo","DFT","trial_num"), sep = "_") %>%
+  mutate(condition = ifelse(Trust1Attrc2 == 1, "Trustworthiness", "Attractiveness"), 
+         face_dft = as.numeric(DFT)) %>%
+  select(-foo, -Trust1Attrc2, -DFT) %>% 
+  group_by(subid, condition, face_dft) %>%
+  summarize(rating = mean(rating))
 
-    # Rename the "mean" column    
-    datac <- plyr::rename(datac, c("mean" = measurevar))
[…]

### 2016-08-22 project_analyses/smraposo.R

@@ -148,7 +148,7 @@ ggplot(o_plot, aes(x=timeMetric, y = mean,fill = timeMetric)) +
   coord_cartesian(ylim=c(0,6.1)) + #to match original study
   xlab("Time metric condition") +
   ylab("Years to start saving") +
-  ggtitle("Sofer - Original") +
+  ggtitle("Lewis - Original") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
   theme(legend.position="none")
@@ -176,7 +176,7 @@ ggplot(d_plot, aes(x=timeMetric, y = mean,fill = timeMetric)) +
   coord_cartesian(ylim=c(0,6.1)) + #to match original study
   xlab("Time metric condition") +
   ylab("Years to start saving") +
-  ggtitle("Sofer - Replication") +
+  ggtitle("Lewis - Replication") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
   theme(legend.position="none")

### 2016-08-22 paper/paper.Rmd
ehermann + add all plots

@@
 ```{r, fig.height=9, fig.width=6}
-# library(png)
-# layout(matrix(1:24,nr=6,byr=T))
-# for (key in project_plan$project_key) {
-#   orig <- readPNG(paste0("../figures/",key,"-original.png"))
-#   rep <- readPNG(paste0("../figures/",key,"-replication.png"))
-# 
-#   par(mai=c(0,0,0,0))
-#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
-#   rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
-# 
-#   plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
-#   rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
-# 
-# }
+library(png)
+layout(matrix(1:24,nr=6,byr=T))
+for (key in project_plan$project_key) {
+  orig <- readPNG(paste0("../figures/",key,"-original.png"))
+  rep <- readPNG(paste0("../figures/",key,"-replication.png"))
+
+  par(mai=c(0,0,0,0))
+  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
+  rasterImage(orig, 0, 0, 100, 100, interpolate=FALSE)
+
+  plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=FALSE)
+  rasterImage(rep, 0, 0, 100, 100, interpolate=FALSE)
+
+}
 ```

### 2016-08-22 project_analyses/ehermann.R

@@ -47,3 +47,35 @@ project_info <- data.frame(
   rep_p_value = pval,
   notes= ""
 )
+
+# Original plot
+data_slope <- 0.09
+data_intercept <- .305 - (4.43 * .09)# get intercept using scale means
+
+ggplot(df, aes(x=pfClaimScore, y = overclaimScore)) + 
+geom_abline(intercept = data_intercept, slope=data_slope) +
+theme_bw(base_size = 6) +
+ggtitle("Atir - Original") + 
+xlab("Perceived Financial Knowledge") + 
+ylab("Overclaiming") +
+scale_y_continuous(limits = c(0,0.8)) +
+scale_x_continuous(limits = c(1,7),breaks=1:7)
+
+ggsave("figures/ehermann-original.png",width = 1.5,height=1.5,units="in")
+
+# Replication plot
+
+data.lm.raw = lm(formula = overclaimScore ~ pfClaimScore + scale(accuracy), data = df)
+data_intercept <- data.lm.raw$coefficients[1]
+data_slope <- data.lm.raw$coefficients[2]
+ggplot(df, aes(x=pfClaimScore, y = overclaimScore)) + 
+  geom_point(alpha=.3) + 
+  geom_abline(intercept = data_intercept, slope=data_slope) +
+  theme_bw(base_size = 6) +
+  ggtitle("Atir - Replication") + 
+  xlab("Perceived Financial Knowledge") + 
+  ylab("Overclaiming") +
+  scale_y_continuous(limits = c(0,0.8)) +
+  scale_x_continuous(limits = c(1,7),breaks=1:7)
+
+ggsave("figures/ehermann-replication.png",width = 1.5,height=1.5,units="in")

### 2016-08-22 project_analyses/jedtan.R
jedtan figures

@@ -57,39 +57,57 @@ project_info <- data.frame(
   rep_test_statistic_str = stat_descript,
   rep_p_value = full_t.test$p.value)
 
-# 
-# time_differences <- d %>%
-#   group_by(epoch) %>% 
-#   summarise(meanTime = mean(Time))
-# 
-# 
-# overTrial <- d %>% group_by(Trial, Transition, epoch) %>% 
-#   summarise(meanTime = t.test(Time)$estimate, timeLow = t.test(Time)$conf.int[1], timeHigh = t.test(Time)$conf.int[2], meanPress = t.test(KeyPresses)$estimate, meanLow = t.test(KeyPresses)$conf.int[1], meanHigh = t.test(KeyPresses)$conf.int[2], meanKeyPressOver = t.test(keyPressesOver)$estimate, overLow = t.test(keyPressesOver)$conf.int[1], overHigh = t.test(keyPressesOver)$conf.int[2])
-# totalMeans <- d %>% group_by(Transition, epoch) %>% 
-#   summarise(meanTime = t.test(Time)$estimate, timeLow = t.test(Time)$conf.int[1], timeHigh = t.test(Time)$conf.int[2], meanPress = t.test(KeyPresses)$estimate, meanLow = t.test(KeyPresses)$conf.int[1], meanHigh = t.test(KeyPresses)$conf.int[2], meanKeyPressOver = t.test(keyPressesOver)$estimate, overLow = t.test(keyPressesOver)$conf.int[1], overHigh = t.test(keyPressesOver)$conf.int[2])
-# 
-# test_statistics <- data.frame(Epoch=c(1,2,3,4,5)) %>% 
-#   mutate(Statistic = 0, PValue = 0)
-# 
-# for(i in 1:5)
-# {
-#   temp_t.test = t.test((epoch %>% filter(epoch == i, Transition == "Fade"))$meanTime, (epoch %>% filter(epoch == i, Transition == "Slide"))$meanTime, paired=TRUE)
-#   test_statistics[i, 2] = temp_t.test$statistic
-#   test_statistics[i, 3] = temp_t.test$p.value
-# }
-# test_statistics
-# 
-# 
-# 
-# ggplot(data=totalMeans, aes(x=epoch, y=meanTime, group = Transition, colour = Transition)) +
-#   geom_line() +
-#   geom_errorbar(aes(ymin=timeLow, ymax=timeHigh), width=.2) + 
[…]

### 2016-08-22 project_analyses/jedtan.R
paper update

@@ -64,7 +64,10 @@ se <- function(x) sd(x, na.rm=T)/sqrt(length(x[!is.na(x)]))
 ms <- epoch %>%
   group_by(epoch, Transition) %>%
   summarise(se = se(meanTime)/1000, 
-            time = mean(meanTime)/1000)
+            time = mean(meanTime)/1000) %>%
+  ungroup %>%
+  mutate(Transition = factor(Transition, 
+                             levels = c("Fade","Slide")))
 
 ggplot(ms, aes(x=epoch, y = time, col = Transition, group=Transition)) + 
   geom_line() + 

### 2016-08-23 project_analyses/auc.R
Use cor coef es measure

@@ -199,7 +199,11 @@ model_tval <- summary(model)$coefficients["exp_typetrustworthy:centered_dft","t 
 model_pval <- summary(model)$coefficients["exp_typetrustworthy:centered_dft","Pr(>|t|)"]
 model_df <- summary(model)$df[2]
 lsr::etaSquared(model)
-cohensd <- abs(2*model_tval/sqrt(model_df))
+
+source("project_analyses/computeES.R")
+es <- esComp(model_tval, df2 = model_df, esType = "t")
+
+# cohensd <- abs(2 * model_tval/sqrt(model_df))
 
 stat_descript <- paste0("t(",model_df,") = ",round(model_tval,2))
 
@@ -208,7 +212,7 @@ stat_descript <- paste0("t(",model_df,") = ",round(model_tval,2))
 project_info <- data.frame(project_key = "auc",
                            rep_final_n = length(unique(d.raw$workerid)),
                            rep_n_excluded = 0,
-                           rep_es = cohensd ,
+                           rep_es = es ,
                            rep_test_statistic_str = stat_descript,
                            rep_t_stat = model_tval,
                            rep_t_df = model_df,

### 2016-08-23 project_analyses/ehermann.R

@@ -34,7 +34,8 @@ degrees <- data.lm$df
 
 stat_descript <- paste0("t(",degrees,") = ",tval)
 
-cohensd <- 2 * tval / sqrt(degrees)
+source("project_analyses/computeES.R")
+es <- esComp(tval, df2 = degrees, esType = "t")
 
 project_info <- data.frame(
   project_key = "ehermann", 
@@ -42,7 +43,7 @@ project_info <- data.frame(
   rep_t_df = degrees,
   rep_final_n = nrow(df), 
   rep_n_excluded = 0 , 
-  rep_es = cohensd, 
+  rep_es = es,
   rep_test_statistic_str = stat_descript,
   rep_p_value = pval,
   notes= ""

### 2016-08-23 project_analyses/jedtan.R

@@ -25,13 +25,16 @@ transition_worker_means = d %>%
 slide_mean = round(transition_means$meanTime[1]/1000, digits=2)
 fade_mean =  round(transition_means$meanTime[2]/1000, digits=2)
 
-full_t.test <- t.test((transition_worker_means %>% filter(Transition == "Fade"))$meanTime, (transition_worker_means %>% filter(Transition == "Slide"))$meanTime, paired=TRUE)
+full_t.test <- t.test((transition_worker_means %>% filter(Transition == "Fade"))$meanTime, 
+                      (transition_worker_means %>% filter(Transition == "Slide"))$meanTime, 
+                      paired=TRUE)
+
+source("project_analyses/computeES.R")
+es <- esComp(full_t.test$statistic, df2 = full_t.test$parameter, esType = "t")
 
 epoch <- d %>% group_by(WorkerID, epoch, Transition) %>% 
  summarise(meanTime = mean(Time), meanPress = mean(KeyPresses))
 
-full_cohensDVal <- lsr::cohensD((epoch %>% filter(Transition == "Fade"))$meanTime, 
-                                (epoch %>% filter(Transition == "Slide"))$meanTime)
 
 #As a key statistic, Liverence and Scholl report that "Across all trials, 
 # participants were on average 1.41 s faster per trial on slide-transition blocks
@@ -53,7 +56,7 @@ project_info <- data.frame(
   rep_t_df = full_t.test$parameter,
   rep_final_n = length(unique(d$WorkerID)), 
   rep_n_excluded = 0, 
-  rep_es = full_cohensDVal, 
+  rep_es = es,
   rep_test_statistic_str = stat_descript,
   rep_p_value = full_t.test$p.value)
 

### 2016-08-23 project_analyses/jsalloum.R

@@ -43,14 +43,16 @@ stat_descript <- paste0("F(",dfnum,", ",dfdenom,") = ",round(F_stat, 3))
 stat_descript
 
 ## lsr::etaSquared(rs1.1) => d = 2.3758
-cohensD <- 2*sqrt(F_stat)/sqrt(dfdenom)
-
+#cohensD <- 2*sqrt(F_stat)/sqrt(dfdenom)
+source("project_analyses/computeES.R")
+es <- esComp(F_stat, df1 = dfnum, df2 = dfdenom, esType = "F")
+es
 project_info <- data.frame(
   project_key = "jsalloum", 
   rep_t_stat = sqrt(F_stat),
   rep_t_df = dfdenom,
   rep_final_n = length(d.af$speakerId), 
   rep_n_excluded = 0, 
-  rep_es = cohensD, 
+  rep_es = es, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = p)

### 2016-08-23 project_analyses/computeES.R
use function from osf supp

@@ -1,0 +1,27 @@
+esComp <- function(
+x,
+df1,
+df2,
+N,
+esType){
+esComp <- ifelse(esType=="t",
+sqrt((x^2*(1 / df2)) / (((x^2*1) / df2) + 1)),
+ifelse(
+esType=="F",
+sqrt((x*(df1 / df2)) / (((x*df1) / df2) + 1))*sqrt(1/df1),
+ifelse(
+esType=="r",
+x,
+ifelse(
+esType=="Chi2",
+sqrt(x/N),
+ifelse(
+esType == "z",
+tanh(x * sqrt(1/(N-3))),
+NA
+)
+)
+)
+))
+return(esComp)
+}

### 2016-08-23 project_analyses/jmarias.R
Convert jmarias es

@@ -232,7 +232,10 @@ df <- mathperflm4$df
 
 
 # Note that this is the same as converting eta^2 to d:
-cohensd = 2*tval/sqrt(df)
+source("project_analyses/computeES.R")
+es <- esComp(tval, df2 = df, esType = "t")
+
+# cohensd = 2*tval/sqrt(df)
 # etaSquared(mathperflm4)[9,2]
 
 stat_descript <- paste0("t(",df,") = ",tval)
@@ -243,7 +246,7 @@ project_info <- data.frame(
   rep_t_df = df,
   rep_final_n = nrow(subjectmeans), 
   rep_n_excluded = length(unique(d$workerid))-nrow(subjectmeans) , 
-  rep_es = cohensd, 
+  rep_es = es, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = pval,
   notes= "double check participant summaries and exclusion criteria"

### 2016-08-23 paper/paper.Rmd
Add more prose about es/bf

--- 2016-08-22 paper/paper.Rmd
@@
 library(cowplot)
-library(png)
 ```
@@
 All analyses were written using R, a free and open-source platform for statistical analysis.
-A schematic of our class workflow is shown in Figure 1.
-
-```{r, fig.cap="A schematic view of our class timeline for replication projects.
-R indicates the approximate timing of instructor team reviews of student materials.", fig.height=4, fig.width=6, fig.align="center", fig.pos="t"}
-
-img <- readPNG(source = "../figures/pipeline.png")
-plot.new()
-plot.window(0:1, 0:1)
-
-#fill plot with image
-usr<-par("usr")    
-rasterImage(img, usr[1], usr[3], usr[2], usr[4])
-```
 
@@
 
-### Significance of the key effect size
+### Significance of the key effect
 
@@
 Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication *p*-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
-While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
 
-### Effect size and Bayes Factor analysis
+### Effect size and Bayes factor analysis
 
-We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
-(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
-(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)`]).
-This estimate should be viewed with caution, however, due to its dependence on one very large effect size estimate ($d > 15$) from a single study.
-
-Next, following @etz2016, we compared Bayes Factors between the original and replication (Figure 2B).
-The Bayes Factor is an alternative to classical null hypothesis significance testing; it quantifies the evidence in favor of a hypothesis as the ratio of the likelihood of the data under that hypothesis relative to another [@jeffreys1961].
-Its proponents point to many advantages over classical $p$-values.
-For example, it does not privilege the null hypothesis and can provide evidence either *for* or *against* it [see also @scheibehenne2016, @wagenmakers2016].
+Effect sizes and Bayes factors improve upon inferences drawn from $p$-values in different ways.
+The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes and allows for a more fine-grained comparison across studies than a binary significance criterion.
+The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961].
+Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016, @wagenmakers2016].
 While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
 
-```{r, fig.cap="Replication effect size (A) and Bayes factor (B), plotted by the original effect size and Bayes factor, respectively.
-Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors.
-Note that the Sofer et al.
-(2015) replication showed ES and BF too large to plot easily on these axes and is hence excluded.", fig.pos="ht", fig.height=4}
+These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility.
+To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom Following @etz2016, we compared Bayes Factors between the original and replication.
+While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
+This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included.
 
+```{r}
 # Note that the sofer paper is off the charts (d > 16) and excluded
@@
   scale_size(name = "Rep. N") +
-  # scale_color_solarized(guide = FALSE)
   scale_color_solarized(name = "Subjective rep. rating")
@@
   geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
-  xlab("Orig. Bayes Factor") + 
-  ylab("Rep. Bayes Factor") + 
+  xlab("Orig. Bayes factor") + 
+  ylab("Rep. Bayes factor") + 
   scale_x_log10(limits = c(10**-1.75, 10**11), 
@@
 
-For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication.
+For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication. Side-by-side visualizations are presented in Figure SM1.
 

### 2016-08-23 paper/paper.Rmd

--- 2016-08-22 paper/paper.Rmd
@@
 Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication *p*-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
-While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be  informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
 
-### Effect size and Bayes Factor analysis
+### Effect size and Bayes factor analysis
 
-We first compared effect sizes from the original and replication studies (Figure 2A). Effect sizes were highly correlated between the two sets of studies 
+Effect sizes and Bayes factors improve upon inferences drawn from $p$-values in different ways.
+The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes and allows for a more fine-grained comparison across studies than a binary significance criterion.
+The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961].
+Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016, @wagenmakers2016].
+While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
+
+These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility.
+To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom.
+We first compared effect sizes from the original and replication studies (Figure 2A).
+Effect sizes were highly correlated between the two sets of studies
 (r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
@@
 
-Next, following @etz2016, we compared Bayes Factors between the original and replication (Figure 2B).
-The Bayes Factor is an alternative to classical null hypothesis significance testing; it quantifies the evidence in favor of a hypothesis as the ratio of the likelihood of the data under that hypothesis relative to another [@jeffreys1961].
-Its proponents point to many advantages over classical $p$-values.
-For example, it does not privilege the null hypothesis and can provide evidence either *for* or *against* it [see also @scheibehenne2016, @wagenmakers2016].
-While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
+Next, following @etz2016, we compared Bayes Factors between the original and replication.
+While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
+This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 

### 2016-08-23 project_analyses/jmarias.R
Color changes jmarias

@@ -272,15 +272,16 @@ dat <- dat %>% rowwise() %>%
   gather(anx,value,-x) %>%
   mutate(anx = paste0(anx," Motivation"))
 ggplot(dat, aes(x,value,group=anx)) + 
-  stat_function(fun=my_func, colour="black") +
-  stat_function(fun=my_func2, colour="grey50",linetype=2) +
+  stat_function(fun=my_func, colour="grey80") +
+  stat_function(fun=my_func2, colour="grey40") +
   theme_bw(base_size = 6) +
+  scale_colour_grey(start=.4, guide=FALSE) + 
   ggtitle("Wang - Original") +
   xlab("Math Anxiety") +
   ylab("PVT Performance (SD)") +
   scale_y_continuous(limits = c(0,1)) +
   scale_x_continuous(limits = c(-1,1),breaks=c(-1,1),labels=c("Low","High")) +
-  geom_label_repel(data = filter(dat, x==0),aes(label = anx), size = 2,nudge_y = c(-.2,+.2), nudge_x = c(-.4,+.4)) 
+  geom_label_repel(data = filter(dat, x==0),aes(label = anx,color=anx), size = 2,nudge_y = c(-.2,+.2), nudge_x = c(-.4,+.4)) 
 
 ggsave("figures/jmarias-original.png",width = 1.5,height=1.5,units="in")
 
@@ -296,18 +297,20 @@ above_lmeq <- function(x) above_lmcoefs[1] + above_lmcoefs[7] * x  + above_lmcoe
 
 below_lmeq <- function(x) below_lmcoefs[1] + below_lmcoefs[7] * x  + above_lmcoefs[9]*x^2
 
-plot_points <- data.frame(z.mathanx=c(0,0), z.pvt=c(above_lmeq(0),below_lmeq(0)),label=c("High Motivation","Low M."),stringsAsFactors = F)
+plot_points <- data.frame(z.mathanx=c(0,0), z.pvt=c(above_lmeq(0),below_lmeq(0)),label=c("High Motivation","Low Motivation"),stringsAsFactors = F)
 
 ggplot(subjectmeans, aes(x = z.mathanx, y = z.pvt)) + 
-  stat_function(fun=below_lmeq, colour="black") +
-  stat_function(fun=above_lmeq, colour="grey50",linetype=2) +
+  stat_function(fun=below_lmeq, colour="grey80") +
+  stat_function(fun=above_lmeq, colour="grey40") +
[…]

### 2016-08-24 paper/paper.Rmd
Color of rep graphs

@@
 ```{r, fig.height=9, fig.width=6}
+  # colors:268bd2 859900 dc322f
 library(png)
 layout(matrix(1:24,nr=6,byr=T))
-for (key in project_plan$project_key) {
+project_key_sorted <- c(
+  "jsalloum","ehermann","salehi", # rep = 1
+  "mkeil","smraposo","jedtan","rhiac","lampinen", # rep=.5
+  "jreynolds","jmarias","auc" #rep = 0
+)
+for (key in project_key_sorted) {
   orig <- readPNG(paste0("../figures/",key,"-original.png"))
@@
 }
+# Add legend
+legend <- readPNG(paste0("../figures/Replication-Legend.png"))
+
+plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=F)
+  rasterImage(legend, 0, 0, 100, 100, interpolate=FALSE)
 ```

### 2016-08-24 project_analyses/auc.R

@@ -77,7 +77,8 @@ ggplot(d_plot_rep, aes(x=face_dft, y = rating, col = condition, group=condition)
   xlab("Distance from Typical") + 
   scale_y_continuous(name = "Rating", 
                      limits = c(1, 9), 
-                     breaks = c(1, 3, 5, 7, 9))
+                     breaks = c(1, 3, 5, 7, 9)) +
+  theme( plot.title = element_text(color="#dc322f"))
 
 ggsave("figures/auc-replication.png", width = 1.5, height=1.5,units="in")
 
@@ -106,7 +107,8 @@ ggplot(d_plot_orig, aes(x=face_dft, y = face_rating, col = condition, group=cond
   xlab("Distance from Typical") + 
   scale_y_continuous(name = "Rating", 
                      limits = c(1,9), 
-                     breaks = c(1,3, 5, 7, 9))
+                     breaks = c(1,3, 5, 7, 9)) +
+  theme( plot.title = element_text(color="#dc322f"))
 
 ggsave("figures/auc-original.png",width = 1.5, height=1.5, units="in")
 

### 2016-08-24 project_analyses/jmarias.R

@@ -281,7 +281,8 @@ ggplot(dat, aes(x,value,group=anx)) +
   ylab("PVT Performance (SD)") +
   scale_y_continuous(limits = c(0,1)) +
   scale_x_continuous(limits = c(-1,1),breaks=c(-1,1),labels=c("Low","High")) +
-  geom_label_repel(data = filter(dat, x==0),aes(label = anx,color=anx), size = 2,nudge_y = c(-.2,+.2), nudge_x = c(-.4,+.4)) 
+  geom_label_repel(data = filter(dat, x==0),aes(label = anx,color=anx), size = 2,nudge_y = c(-.2,+.2), nudge_x = c(-.4,+.4)) +
+  theme(plot.title = element_text(color="#dc322f"))
 
 ggsave("figures/jmarias-original.png",width = 1.5,height=1.5,units="in")
 
@@ -309,7 +310,8 @@ ggplot(subjectmeans, aes(x = z.mathanx, y = z.pvt)) +
   ylab("PVT Performance (SD)") +
   scale_y_continuous(limits = c(0,1)) +
   scale_x_continuous(limits = c(-1,1),breaks=c(-1,1),labels=c("Low","High")) +
-  geom_label_repel(data=plot_points,aes(label = label,color=label), size = 2, nudge_y = c(.2,-.12), nudge_x = c(.4,-.7))
+  geom_label_repel(data=plot_points,aes(label = label,color=label), size = 2, nudge_y = c(.2,-.12), nudge_x = c(.4,-.7)) +
+  theme(plot.title = element_text(color="#dc322f"))
   
 
 ggsave("figures/jmarias-replication.png",width = 1.5,height=1.5,units="in")

### 2016-08-24 project_analyses/lampinen.R

@@ -120,7 +120,8 @@ ggplot(o_plot, aes(x=rotating, y = mean,fill = rotating)) +
   ggtitle("Xu - Original") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none")
+  theme(legend.position="none",
+        plot.title = element_text(color="#859900"))
 
 ggsave("figures/lampinen-original.png",width = 1.5,height=1.5,units="in")
 
@@ -145,7 +146,8 @@ ggplot(d_plot, aes(x=rotating, y = mean,fill = rotating)) +
   ggtitle("Xu - Replication") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none")
+  theme(legend.position="none",
+        plot.title = element_text(color="#859900"))
 
 ggsave("figures/lampinen-replication.png",width = 1.5,height=1.5,units="in")
 

### 2016-08-24 project_analyses/rhiac.R

@@ -142,7 +142,8 @@ ggplot(o_plot, aes(x=condition, y = mean,fill = condition)) +
   ggtitle("Zaval - Original") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none") +
+  theme(legend.position="none",
+        plot.title = element_text(color="#859900")) +
   scale_y_continuous(breaks=1:6)
 
 ggsave("figures/rhiac-original.png",width = 1.5,height=1.5,units="in")
@@ -168,7 +169,8 @@ ggplot(d_plot, aes(x=condition, y = mean,fill = condition)) +
   ggtitle("Zaval - Replication") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none") +
+  theme(legend.position="none",
+        plot.title = element_text(color="#859900")) +
   scale_y_continuous(breaks=1:6)
 
 ggsave("figures/rhiac-replication.png",width = 1.5,height=1.5,units="in")

### 2016-08-24 project_analyses/smraposo.R

@@ -151,7 +151,8 @@ ggplot(o_plot, aes(x=timeMetric, y = mean,fill = timeMetric)) +
   ggtitle("Lewis - Original") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none")
+  theme(legend.position="none",
+        plot.title = element_text(color="#859900"))
 
 ggsave("figures/smraposo-original.png",width = 1.5,height=1.5,units="in")
 
@@ -179,6 +180,7 @@ ggplot(d_plot, aes(x=timeMetric, y = mean,fill = timeMetric)) +
   ggtitle("Lewis - Replication") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none")
+  theme(legend.position="none",
+        plot.title = element_text(color="#859900"))
 
 ggsave("figures/smraposo-replication.png",width = 1.5,height=1.5,units="in")

### 2016-08-24 project_analyses/auc.R
Use MANOVA to reproduce sofer

@@ -113,51 +113,68 @@ ggsave("figures/auc-original.png",width = 1.5, height=1.5, units="in")
 
 ##### STATS --------------------------------------------------
 # we select the more standard "by subjects" analysis for the final.
+library(car)
+idata = data.frame(dft = c("dft_0", "dft_10", "dft_20", "dft_30", "dft_40", "dft_50", 
+                           "dft_60", "dft_70", "dft_80", "dft_90", "dft_100"))
 
 ## ORIGINAL 
-sofer <- sofer %>%
+shortForm.orig = sofer %>%
   ungroup %>%
   mutate(dft = factor(face_dft), 
          condition = factor(condition), 
-         subid = factor(subid))
+         subid = factor(subid)) %>%
+  select(dft, condition, subid, rating) %>%
+  group_by(subid) %>%
+  spread(dft, rating, sep = "_")
 
-# Repeated measures
-orig.mod <- aov(rating ~ dft * condition +
-           + Error(subid / dft), data = sofer)
-summary(orig.mod)
+manova.orig = lm(cbind(dft_0, dft_10, dft_20, dft_30, dft_40, dft_50,
+                      dft_60, dft_70, dft_80, dft_90, dft_100) ~ condition, 
+                data = shortForm.orig)
+manova.res.orig = Anova(manova.orig, idata= idata, idesign = ~dft)
+manova.res.orig
 
 ## REPLICATION
-rep <- rep %>%
+shortForm.rep = rep %>%
   ungroup %>%
   mutate(dft = factor(face_dft), 
          condition = factor(condition), 
-         workerid = factor(workerid))
-    
-rep.mod <- aov(rating ~ dft * condition +
-             + Error(workerid / dft), data = rep)
-summary(rep.mod)
+         workerid = factor(workerid)) %>%
+  select(dft, condition, workerid, rating) %>%
+  group_by(workerid) %>%
+  spread(dft, rating, sep = "_")
 
-model_coef <- summary(rep.model)$coefficients["exp_typetrustworthy:centered_dft","Estimate"]
-model_tval <- summary(rep.model)$coefficients["exp_typetrustworthy:centered_dft","t value"]
-model_pval <- summary(rep.model)$coefficients["exp_typetrustworthy:centered_dft","Pr(>|t|)"]
-model_df <- summary(rep.model)$df[2]
-# lsr::etaSquared(model)
[…]

### 2016-08-24 project_analyses/auc.R
Add effect size computations (+ figure out eta squared in sofer)

@@ -133,7 +133,11 @@ manova.orig = lm(cbind(dft_0, dft_10, dft_20, dft_30, dft_40, dft_50,
                       dft_60, dft_70, dft_80, dft_90, dft_100) ~ condition, 
                 data = shortForm.orig)
 manova.res.orig = Anova(manova.orig, idata= idata, idesign = ~dft)
-manova.res.orig
+# Effect size from Steyn Jr, H. S., & Ellis, S. M. (2009). 
+# Estimating an effect size in one-way multivariate analysis of variance (MANOVA). 
+# Multivariate Behavioral Research, 44(1), 106-129.
+# Note that the formula used in esComp (by the OSF people) corrects this by a factor sqrt(1/df1) to get "explained variance by predictor"
+etasq(manova.res.orig)
 
 ## REPLICATION
 shortForm.rep = rep %>%
@@ -162,6 +166,7 @@ manova.res.rep
 model_Fval = 3.2
 model_dfnum = 10
 model_dfdenom = 84
+model_pval = 0.001594
 
 source("project_analyses/computeES.R")
 es <- esComp(model_Fval, df1 = model_dfnum, df2 = model_dfdenom, esType = "F")
@@ -176,7 +181,7 @@ project_info <- data.frame(project_key = "auc",
                            rep_test_statistic_str = stat_descript,
                            rep_t_stat = NA,
                            rep_t_df = NA,
-                           rep_p_value = pval1,
+                           rep_p_value = model_pval,
                            notes="based on writeup and article, assuming conditiontrustworthy:centered_dft interaction is key stat of interest. Should clarify with Carolyn. Also make sure doing correct analysis from article (i.e. MANOVA)."
 )
 

### 2016-08-24 project_analyses/jreynolds.R

@@ -46,7 +46,8 @@ tval = interactionRow[3]
 pval = interactionRow[4]
 df = rs1[[2]][1,]$Res.Df
 
-cohensd <- 2*tval/sqrt(df)
+source("project_analyses/computeES.R")
+es <- esComp(tval, df2 = df, esType = "t")
 
 stat_descript <- paste0("t(",df,") = ",round(tval, 3))
 
@@ -56,7 +57,7 @@ project_info <- data.frame(
   rep_t_df = df,
   rep_final_n = length(unique(d$Participant)), 
   rep_n_excluded = 0, 
-  rep_es = cohensd, 
+  rep_es = es,
   rep_test_statistic_str = stat_descript,
   rep_p_value = pval)
 

### 2016-08-24 project_analyses/lampinen.R

@@ -81,11 +81,13 @@ n_subjects = length(unique(subject_aggregated_data$subject))
 nonRotatingK = subject_aggregated_data[!subject_aggregated_data$rotating,]$K
 rotatingK = subject_aggregated_data[subject_aggregated_data$rotating,]$K
 t_res = t.test(nonRotatingK, rotatingK, paired=T)
-cohensd = lsr::cohensD(nonRotatingK, rotatingK, method='paired')
 
 F_stat = (t_res$statistic)^2
 p = pf(F_stat,1,n_subjects-1,lower.tail=F)
 stat_descript <- paste0("F(",1,", ",t_res$parameter,") = ",round(F_stat, 3))
+
+source("project_analyses/computeES.R")
+es <- esComp(F_stat, df1 = 1, df2 = t_res$parameter, esType = "F")
 
 project_info <- data.frame(
   project_key = "lampinen", 
@@ -93,7 +95,7 @@ project_info <- data.frame(
   rep_t_df = t_res$parameter,
   rep_final_n = n_subjects, 
   rep_n_excluded = length(files) - n_subjects, 
-  rep_es = cohensd, 
+  rep_es = es, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = p)
 

### 2016-08-24 project_analyses/mkeil.R

@@ -186,7 +186,8 @@ F_test<- round(stat_sum[[1]][2,"F value"],3)
 
 stat_descript <- paste0("F(",df1,",",df2,") = ",F_test)
 
-cohensd <- 2 * sqrt(F_test) / sqrt(df2)
+source("project_analyses/computeES.R")
+es <- esComp(F_test, df1 = df1, df2 = df2, esType = "F")
 
 project_info <- data.frame(
   project_key = "mkeil", 
@@ -194,7 +195,7 @@ project_info <- data.frame(
   rep_t_df = df2,
   rep_final_n = length(unique(d1$workerId)), 
   rep_n_excluded = length(unique(d.raw$workerId))-length(unique(d1$workerId)), 
-  rep_es = cohensd, 
+  rep_es = es, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = p.val,
   notes= ""

### 2016-08-24 project_analyses/rhiac.R

@@ -106,7 +106,8 @@ pval1 = modres[1,5]
 
 stat_descript <- paste0("F(",dfnum1,", ",dfdenom1,") = ",round(Fstat1, 3))
 
-cohensd <- 2 * sqrt(Fstat1) / sqrt(dfdenom1)
+source("project_analyses/computeES.R")
+es <- esComp(Fstat1, df1 = dfnum1, df2 = dfdenom1, esType = "F")
 
 project_info <- data.frame(
   project_key = "rhiac", 
@@ -114,7 +115,7 @@ project_info <- data.frame(
   rep_t_df = dfdenom1,
   rep_final_n = 321, 
   rep_n_excluded = 7, 
-  rep_es = cohensd, 
+  rep_es = es, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = pval1)
 

### 2016-08-24 project_analyses/salehi.R

@@ -85,12 +85,13 @@ df2 <- summary(fitConTrait)[[2]][[1]][3,1]
 # masculineConnvergentMean <- masculine %>% filter(condition == 'Convergent')
 
 test_stat <- paste0("F(",df1,",",df2,")=",round(Fval, digits=3))
-cohensd = 2*sqrt(Fval)/sqrt(df2)
+source("project_analyses/computeES.R")
+es <- esComp(Fval, df1 = df1, df2 = df2, esType = "F")
 
 project_info <- data.frame(project_key = "salehi",
                            rep_final_n = length(unique(d$workerid)),
                            rep_n_excluded = 0, 
-                           rep_es = cohensd, 
+                           rep_es = es, 
                            rep_test_statistic_str = test_stat,
                            rep_t_stat = sqrt(Fval), #http://www.tc.umn.edu/~oakes007/Files/Comm%20Trials/F%20and%20t%20statistics.pdf
                            rep_t_df = df2,

### 2016-08-24 project_analyses/smraposo.R

@@ -118,7 +118,8 @@ n_final <- dim(d[d$exclude=="include",])
 key_stat <- Fstat1
 stat_descript <- paste0("F(",dfnum1,", ",dfdenom1,") = ",round(Fstat1, 3))
 
-cohensd <- 2 * sqrt(Fstat1) / sqrt(dfdenom1)
+source("project_analyses/computeES.R")
+es <- esComp(Fstat1, df1 = dfnum1, df2 = dfdenom1, esType = "F")
 
 project_info <- data.frame(
   project_key = "smraposo", 
@@ -126,7 +127,7 @@ project_info <- data.frame(
   rep_t_df = dfdenom1,
   rep_final_n = nrow(d[d$exclude=="include",]), 
   rep_n_excluded = nrow(d[d$exclude!="include",]), 
-  rep_es = cohensd, 
+  rep_es = es, 
   rep_test_statistic_str = stat_descript,
   rep_p_value = pval1)
 

### 2016-08-24 paper/paper.Rmd
Updated effect size plot, caption

@@
 (`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)`]).
-This estimate should be viewed with caution, however, due to its dependence on one very large effect size estimate ($d > 15$) from a single study.
 
@@
 Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors.
-Note that the Sofer et al.
-(2015) replication showed ES and BF too large to plot easily on these axes and is hence excluded.", fig.pos="ht", fig.height=4}
+Note that the key statistic in the Sofer et al.
+(2015) replication was a multivariate $F$ test, hence a default Bayes factor could not be computed.", fig.pos="ht", fig.height=4}
 
-# Note that the sofer paper is off the charts (d > 16) and excluded
 p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
@@
   geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
-  scale_x_continuous(limits = c(0, 3.5), 
-                breaks = c(.2, .5, .8, 1, 2, 3)) +
-  scale_y_continuous(limits = c(0, 3.5), 
-                breaks = c(.2, .5, .8, 1, 2, 3)) +
+  scale_x_continuous(limits = c(0, 1), 
+                breaks = c(.1, .3, .5)) +
+  scale_y_continuous(limits = c(0, 1), 
+                breaks = c(.1, .3, .5)) +
   geom_abline(slope = 1, intercept = 0, linetype = 2) +

### 2016-08-24 paper/paper.Rmd
fixes from student comments

@@
 author-note:
-    "Thanks to the Stanford Department of Psychology and the Vice Provost for Undergraduate Education for funding to support the class."
+    "Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
 
@@
 
+\newcommand{\specialcell}[2][c]{%
+  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
+
 <!-- latex table generated in R 3.3.0 by xtable 1.8-2 package
@@
   \hline
-Citation & Expt & Data & Materials & Turk? & N (orig) & N (rep) \\ 
+Citation & Expt & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{Original\\on Turk?} & N (orig) & N (rep) \\ 
   \hline
@@
 Scopelliti, Loewenstein, \& Vosgerau (2015) & 3 & No & Yes & Yes & 550 & 124 \\ 
-Liverence \& Scholl (2015) & 1 & No & Some & No &  18 &  \\ 
+Liverence \& Scholl (2015) & 1 & No & Some & No &  18 &  19 \\ 
 Wang et al. (2015) & 2 & No & No & No & 219 & 397 \\ 
@@
 \end{tabular}
-\caption{\label{tab:summary} Summary of attempted replications.} 
+\caption{\label{tab:summary} Summary of papers and experiments that were targets for replication in our projects.} 
 \label{tab:summary}
@@
 (All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing text).
-At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analysis.
+At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
 The goal of this code review was to ensure that all planned analyses were specified correctly and with sufficient detail to permit inclusion in the broader analysis.
@@
 cases, we used the original sample size.
-In one case, the original experiment was apparently extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would apparently yield high power.
-In one case, we reduced the number of trials as part of the adaptation to mechanical turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
+In one case, the original experiment was  extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
+In one case, we reduced the number of trials as part of the adaptation to Mechanical Turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
 
@@
 Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.
-Criterion is based on the theoretical interpretation of the original finding.
-(0 = non-replication, .5 is substantial hints of the same pattern or a significant but different pattern, 1 = full replication).
-We find that the these ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
+Our rating system was based on the theoretical interpretation of the original finding, with 0 = no support for the original interpretation, .5 = some support for the original interpretation, 1 = full replication).
+We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
 The average rating given by instructors and students were `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.
@@
 \centering
-\begin{tabular}{llrrr|r}
+\begin{tabular}{rllllllll}
   \hline
-Mediator & Value & No & Partial & Full & Total\\ 
+\multicolumn{2}{c}{Replicated} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
   \hline
-Replicated? &  &   2 &   6 &   3 & 11 \\ 
+   &  & No & Yes & Yes & No & No & Some & Yes \\ 
+  No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
+  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
+  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
   \hline
-  Original on turk & Yes &   1 &   2 &   2 & 5 \\ 
-   & No &   1 &   4 &   1 & 6\\ 
-\hline
-  High fidelity replication? & Yes &   2 &   3 &   1  & 6\\ 
-   & No &  &   3 &   2 & 5\\ 
-\hline
-  Open materials? & Yes &   1 &   3 &   1  & 4\\ 
-   & Some &  &   1 &   1 & 2\\ 
-   &  No &   1 &   2 &   1 & 4\\ 
+  Total & 11 & 6 & 5 & 5 & 6 & 4 & 2 & 5 \\
    \hline
 \end{tabular}
-\caption{\label{tab:results} Counts of instructor team replication ratings, split by various different mediating variables.}
+\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables.}
 \end{table}
+
+<!-- \begin{table}[ht] -->
+<!-- \centering -->
+<!-- \begin{tabular}{llrrr|r} -->
+<!--   \hline -->
+<!-- Mediator & Value & No & Partial & Full & Total\\  -->
+<!--   \hline -->
+<!-- Replicated? &  &   2 &   6 &   3 & 11 \\  -->
+<!-- \hline -->
+<!--   Original on turk & Yes &   1 &   2 &   2 & 5 \\  -->
+<!--    & No &   1 &   4 &   1 & 6\\  -->
+<!-- \hline -->
+<!--   High fidelity replication? & Yes &   2 &   3 &   1  & 6\\  -->
+<!--    & No &  &   3 &   2 & 5\\  -->
+<!-- \hline -->
+<!--   Open materials? & Yes &   1 &   3 &   1  & 4\\  -->
+<!--    & Some &  &   1 &   1 & 2\\  -->
+<!--    &  No &   1 &   2 &   1 & 4\\  -->
+<!-- \hline -->
+<!-- \end{tabular} -->
+<!-- \caption{\label{tab:results} Counts of instructor team replication ratings, split by various different mediating variables.} -->
+<!-- \end{table} -->
 
@@
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
-Overall, projects had a somewhat larger probability of being judged successful if it was judged to be closer to the original:
+Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original:
 `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
@@
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent discussions of the utility and validity of interpretating confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 
@@
 
-This paper investigated motivations to save for retirement, and specifically whether changing participants' relationships to the future (making it feel more immanent) would cause them to save more.
+This paper investigated motivations to save for retirement, and specifically whether changing participants' relationships to the future (making it feel more imminent) would lead them to report that they would begin saving for retirement sooner.
 Our target was Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner, even controlling for age, education, and income in a linear model (there was also a manipulation of whether saving was incremental that did not result in an effect).

### 2016-08-24 paper/paper.Rmd
paper tweaks

@@
 author-note:
-    "Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
+    "These authors contributed equally. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
 
@@
                       fig.path='figs/', echo=FALSE, warning = FALSE, 
-                      cache=FALSE, message = FALSE, sanitize = TRUE)
+                      cache=TRUE, message = FALSE, sanitize = TRUE)
 library(readr)
@@
 This process is dramatically facilitated by the use of standardized (and free) technical tools for statistical analysis, data and code sharing, and creation of web experiments.
-Nevertheless, there are significant limitations on what can be done in the course of a single term and within the constraints of a course budget.
+Nevertheless, there are significant limitations on what can be done in a single term and within the constraints of a course budget.
 We return in the Discussion to limitations on our approach.
@@
 First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
-Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could easily be reproduced by a motivated student.
+Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- at least as far as support for the same theoretical claims -- by a motivated student.
 
@@
 Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general.
-This sampling strategy may thus bias our results towards more exciting or novel findings.
+This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
 A summary of the original findings is given in Table \ref{tab:summary}.
@@
 The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
-The goal of this pilot was to ensure that all needed data were being logged by the experiment and that analytic scripts for the confirmatory analyses functioned appropriately.
-After pilot A was completed, the instructor or a TA reviewed the student's experiment (acting as a participant) and critiqued and reviewed the student's full analytic code and output.
+The goal of this pilot was to ensure that all needed data were being logged by the experiment script and that analytic scripts for the confirmatory analyses functioned appropriately.
+After Pilot A was completed, the instructor or a TA reviewed the student's experimental script (acting as a participant) and critiqued and reviewed the student's full analytic code and output.
 
@@
 
-After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made the requested change.
+After Pilot B review was completed, students were given authorization to collect the full sample of participants, contingent on having made any requested changes.
 Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.
@@
 Determining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015].
-Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially with the constraints of a limited budget -- it may be impossible to follow more conservative guidelines in all cases.
+Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
 For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
@@
 ^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from pilot A sessions.]
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
 In 
@@
 Students chose findings from a wide variety of domains for replication.
-One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], including in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
-A second cluster came from studies of social perception, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
+One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
+A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
 Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
@@
 
-Of the 15 students in the class, all completed projects (two with extensions), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 projects were judged by the instructor team to have been successful replications.
+Of the 15 students in the class, all completed projects (two with extensions, one short and one more significant), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
 Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
@@
 We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
-The average rating given by instructors and students were `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.
+The average rating given by instructors and students was `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.
 
@@
 \centering
-\begin{tabular}{rllllllll}
+\begin{tabular}{rl|ccccccc}
   \hline
@@
    &  & No & Yes & Yes & No & No & Some & Yes \\ 
+  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
+  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
   No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
-  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
-  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
   \hline
-  Total & 11 & 6 & 5 & 5 & 6 & 4 & 2 & 5 \\
+  Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\
    \hline
@@
 `r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
-There were small numerical effects of being run on Mechanical Turk (
-`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\%
-vs. 
-`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%. 
-) and having open materials (
-`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\% 
-vs. 
-`r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.
+There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs.
+`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\%
+vs. `r 100 *round(mean(d$replicated_TA[d$open_materials=="No"]), digits=2)`\%), though we do not believe these differences are interpretable given our sample size.
 
@@
 The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961].
-Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016, @wagenmakers2016].
+Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016;@wagenmakers2016].
 While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
@@
 (r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
-(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)`]).
+(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).
 
@@
 This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+
+This analysis revealed a number of interesting findings.
+First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals.
+Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments as well.
+Finally, we note that the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g.
+BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.
 
@@
 Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing.
-The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but results were not statistically significant and had both smaller effect size and lower evidential value than the originals.
+The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.
 
@@
 Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on available samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
-In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects.
+In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests.
 
@@
 In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015].
-What are the causes of this relatively low rate of replication?
+What are the causes of this relatively low rate?
 
@@
 Nevertheless, the consistent decreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that initial publications tend to over-estimate effects.
-And although our sample was too small for statistical inference, numerically our results do not support replication fidelity in terms of sample and procedure as a primary driver of success.
+However, in addition, although our sample was too small for statistical inference, numerically our results support replication fidelity in terms of sample and procedure as having some effects on success.
 
@@
 
-Indeed, by the standards of clinical trials research, every single study we replicated in this report would be classified as exploratory research.
-No protocol was pre-registered, and the pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
+Indeed, by the standards of clinical trials research, nearly every study we replicated in this report would be classified as exploratory research.
+No protocol was pre-registered, and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
 Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications.
-And in many cases, there are no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf.
+And in many cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf.
 @bakeman2005].
@@
 
-# Supplemental Materials: Project-By-Project Methods Addendum
+# Appendix: Project-By-Project Methods Addendum
 
-```{r, fig.height=9, fig.width=6}
+```{r, fig.height=9, fig.width=6, fig.cap="Side-by-side comparison of plots for each attempted replication.
+All error bars are standard error of the mean.
+Original data were estimated from figures when not otherwise available.
+Replications are sorted and color coded by subjective replication success."}
   # colors:268bd2 859900 dc322f
@@
 
-For each project, we present a summary of the finding, the key statistical test, and the outcomes of the replication.
+For each project, we present a summary of the finding, the key statistical test, and the impressionistic outcomes of the replication.
+Figure 3 shows a side-by-side comparison of the key visualization for each study.
 

### 2016-08-24 project_analyses/rhiac.R

@@ -1,12 +1,6 @@
 # Replication of "How Will I Be Remembered? Conserving the Environment for the Sake of One's Legacy" by Zaval, Markowitz & Weber (2015, Psychological Science)
 # Rhia Catapano
 
-# MCF NOTE: this script runs over hand-deduped anonymized data. I removed by hand
-# the 7 datapoints that were accidentally run twice (all in the control
-# condition). There should be 321 participants (not 328).
-
-# RXDH NOTE: Numbers still don't match up
-
 library(tidyr) 
 library(dplyr)
 library(ggplot2) 
@@ -137,7 +131,7 @@ ggplot(o_plot, aes(x=condition, y = mean,fill = condition)) +
   geom_errorbar(aes(ymin=lower, ymax=upper),
                 size=.3,
                 width=.3) +
-  coord_cartesian(ylim=c(1.2,6)) + #to match original study
+  coord_cartesian(ylim=c(0,4)) + # 1.2 - 6 matches original study but looks terrible
   xlab("Condition") +
   ylab("Behavioral Intentions") +
   ggtitle("Zaval - Original") +
@@ -164,7 +158,7 @@ ggplot(d_plot, aes(x=condition, y = mean,fill = condition)) +
   geom_errorbar(aes(ymin=lower, ymax=upper),
                 size=.3,
                 width=.3) +
-  coord_cartesian(ylim=c(1.2,6)) + #to match original study
+  coord_cartesian(ylim=c(0,4)) + 
   xlab("Condition") +
   ylab("Behavioral Intentions") +
   ggtitle("Zaval - Replication") +
@@ -175,12 +169,12 @@ ggplot(d_plot, aes(x=condition, y = mean,fill = condition)) +
   scale_y_continuous(breaks=1:6)
 
 ggsave("figures/rhiac-replication.png",width = 1.5,height=1.5,units="in")
-
-ggplot(ms_beh, aes(x=condition, y=meanBeh)) + 
-  geom_bar(stat = "identity") + 
-  ylim(0, 6) +
-  geom_errorbar(aes(ymin = meanBeh - ci95, 
-                    ymax = meanBeh + ci95), width=0.25)
+# 
+# ggplot(ms_beh, aes(x=condition, y=meanBeh)) + 
+#   geom_bar(stat = "identity") + 
+#   ylim(0, 6) +
+#   geom_errorbar(aes(ymin = meanBeh - ci95, 
[…]

### 2016-08-24 paper/paper.Rmd
paper tweaks

@@
 
-```{r, fig.height=9, fig.width=6, fig.cap="Side-by-side comparison of plots for each attempted replication.
-All error bars are standard error of the mean.
-Original data were estimated from figures when not otherwise available.
+```{r, fig.height=9, fig.width=6, fig.cap="Side-by-side plots for each attempted replication.
+Error bars show standard error of the mean.
+Original data estimated from figures when not otherwise available.
 Replications are sorted and color coded by subjective replication success."}

### 2016-09-02 paper/paper.Rmd
Add text about ES & BF

@@
 These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility.
-To compute a standardized effect size, we converted all one-sample $t$-statistics into a Cohen's $d$ using the formula $d = t/\sqrt{df}$, where $df$ is the degrees of freedom.
+To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
+Other formulas are given in @osc2015, supplemental].
 We first compared effect sizes from the original and replication studies (Figure 2A).
@@
 
-Next, following @etz2016, we compared Bayes Factors between the original and replication.
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
@@
 
+Next, following @etz2016, we compared Bayes Factors between the original and replication.
+We used the default  test suggested by @rouder2009 and did not attempt to correct for publication bias.
 This analysis revealed a number of interesting findings.

### 2016-09-02 paper/paper.Rmd
student comments

@@
 Proudfoot, Kay, \& Koval (2015) & 1 & No & No & Yes &  80 &  84 \\ 
-Zaval, Markowitz, \& Weber (2015) & 1 & Yes & Yes & Yes & 312 & 328 \\ 
+Zaval, Markowitz, \& Weber (2015) & 1 & Yes & Yes & Yes & 312 & 321 \\ 
 Xu \& Franconeri (2015) & 1a & No & No & No &  12 &  27 \\ 
@@
 
-One part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices.
 Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
+This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices.
 Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g.
 statistical tests, figures).
-This document can be compiled into a variety of formats (e.g., HTML, PDF, Microsoft Word).
+These documents could be compiled into a variety of formats (e.g., HTML, PDF, Microsoft Word).
 This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by copying and pasting between analysis outputs and manuscripts.
@@
 
-To ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH).
-In addition to as-needed guidance, each student collected two pilot samples.
+In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH).
+Each student collected two pilot samples and review was coordinated with these.
 The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
@@
 
-After selecting a paper of interest, students selected a particular study from within that paper based on their judgment of interest and feasibility.
+After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility.
 The modal study chosen was the first, but several students chose later studies in a set as well.
@@
   scale_x_log10(limits = c(10**-1.75, 10**11), 
-                breaks = c(1/10, .3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c("1e-1", "3e-1", "3", "1e1","1e2", "1e3", 
+                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
+                labels = c("1e-1", "1", "1e1","1e2", "1e3", 
                            "1e6","1e9")) +
   scale_y_log10(limits = c(10**-1.75, 10**11),
-                breaks = c(1/10, .3, 3, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c("1e-1", "3e-1", "3", "1e1","1e2", "1e3", 
+                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
+                labels = c("1e-1", "1", "1e1","1e2", "1e3", 
                            "1e6","1e9")) + 
@@
 
-Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013,@ioannidis2005].
+Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013;@ioannidis2005].
 On the other hand, an alternative viewpoint is that -- especially for studies that leverage social constructs -- exact replication may be difficult across contexts [@gilbert2016;@vanbavel2016].
@@
 
-This paper investigated how perceived knowledge affects "overclaiming" (claiming knowledge that you do not have.
+This paper investigated how perceived knowledge affects "overclaiming" (claiming knowledge that you do not have).
 We targeted Study 1b, which asked participants to rate their knowledge about finances, and then asked them to rate their knowledge about a set of financial terms, some of which were invented (and hence for which a positive knowledge statement would necessarily be an overclaim).

### 2016-09-02 paper/paper.Rmd
minor fig cleanup

@@
 To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
-Other formulas are given in @osc2015, supplemental].
+Other formulas are given in @osc2015, Supplemental Information].
 We first compared effect sizes from the original and replication studies (Figure 2A).
@@
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in reporting effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in the reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 
@@
                 breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c("1e-1", "1", "1e1","1e2", "1e3", 
+                labels = c(".1", "1", "10","100", "1e3", 
                            "1e6","1e9")) +
@@
                 breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c("1e-1", "1", "1e1","1e2", "1e3", 
+                labels = c(".1", "1", "10","100", "1e3", 
                            "1e6","1e9")) + 
@@
   scale_color_solarized(name = "Subjective rep. rating")
-
-# note: fix slope on trend line, because the atir finding is a hack right now so it fits in the axes.
 
@@
 
-Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013;@ioannidis2005].
+Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013;  @ioannidis2005].
 On the other hand, an alternative viewpoint is that -- especially for studies that leverage social constructs -- exact replication may be difficult across contexts [@gilbert2016;@vanbavel2016].

### 2016-09-06 paper/paper.Rmd
Wording changes

@@
 author-information:
-    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}
+    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}
 
@@
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
-Under the current incentive structure for science, direct replication is not typically valued, however.
+Yet under the current incentive structure for science, direct replication is not typically valued.
 One potential solution to this problem is to make direct replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
-Despite enthusiasm for this idea, however [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data -- beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] -- to support its efficacy.
+Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.
 
@@
 We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
-Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is replicable in some more abstract sense.
+Whether an independent scientist can build on a published result is perhaps as important as whether the work is replicable in a more conceptual sense -- and in many cases easier to determine.
 
-With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy.
-This process is dramatically facilitated by the use of standardized (and free) technical tools for statistical analysis, data and code sharing, and creation of web experiments.
+With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy so that other institutions may adapt these practices.
+This process is dramatically facilitated by the use of free standardized tools for statistical analysis (R), data and code sharing (Git, R Markdown), and creation of web experiments (HTML, CSS, JavaScript).
 Nevertheless, there are significant limitations on what can be done in a single term and within the constraints of a course budget.
@@
 First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
-Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- at least as far as support for the same theoretical claims -- by a motivated student.
+Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- supporting the same theoretical claims -- by a motivated student.
 
@@
 
-All projects were completed as part of a class (syllabus and materials available at [http://psych254.stanford.edu]()).
-At the initiation of class, all students were told that they had the opportunity to participate in a group replication project to which they could contribute their class project.
+All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://psych254.stanford.edu]()).
+At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project.
 The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.
@@
 This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
-A summary of the original findings is given in Table \ref{tab:summary}.
+A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.
 
@@
 statistical tests, figures).
-These documents could be compiled into a variety of formats (e.g., HTML, PDF, Microsoft Word).
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by copying and pasting between analysis outputs and manuscripts.
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by transferring results between analysis outputs and manuscripts.
 
@@
 
-In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH).
+In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH).
 Each student collected two pilot samples and review was coordinated with these.
@@
 The goal of this pilot was to ensure that all needed data were being logged by the experiment script and that analytic scripts for the confirmatory analyses functioned appropriately.
-After Pilot A was completed, the instructor or a TA reviewed the student's experimental script (acting as a participant) and critiqued and reviewed the student's full analytic code and output.
+After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script (acting as a participant), analytic code, and resulting output.
 
@@
 cases, we used the original sample size.
+Three replications deviated from these two criteria.
 In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
-In one case, we reduced the number of trials as part of the adaptation to Mechanical Turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
+In another, we reduced the number of trials as part of the adaptation to Mechanical Turk.
+In the last case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
 
@@
 
-Of the 15 students in the class, all completed projects (two with extensions, one short and one more significant), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
+Of the 15 students in the class, all completed projects (two with extensions going beyond the class period), one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
 Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
-(In one case, a student failed to complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review).
+(In one case, a student did not complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review.
+Thus, this project remains included.)
 
 Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
-Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)`.
+Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`).
 Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might have an effect on the results.
@@
 \end{tabular}
-\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables.}
+\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables.
+High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).}
 \end{table}
@@
 Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original:
-`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
+replication rating `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
 vs. 
@@
 To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
-Other formulas are given in @osc2015, Supplemental Information].
+Other formulas are given in @osc2015, Supplemental Information.].
 We first compared effect sizes from the original and replication studies (Figure 2A).
@@
 (r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
-(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).
+(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).
 
@@
 Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants.
-Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on available samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on funding for samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
 In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests.

### 2016-09-06 paper/paper.Rmd
Fix ES plot axes

@@
   scale_x_continuous(limits = c(0, 1), 
-                breaks = c(.1, .3, .5)) +
+                breaks = c(.1, .3, .5, .7, .9)) +
   scale_y_continuous(limits = c(0, 1), 
-                breaks = c(.1, .3, .5)) +
+                breaks = c(.1, .3, .5, .7, .9)) +
   geom_abline(slope = 1, intercept = 0, linetype = 2) +

### 2016-09-08 paper/paper.Rmd
Intro restructuring
Change to percentage for ratings

@@
 
-## Class Outline
+## Study Selection
 
@@
 Students selected projects based on interest, rather than via a systematic sampling strategy.
+After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility.
+The modal study chosen was the first, but several students chose later studies in a set as well.
 Thus, all interpretation of our findings should be with respect to the distribution of student interest.
@@
 
+Students chose findings from a wide variety of domains for replication.
+One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
+A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
+Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
+Details of individual replications are available in SOM.
+
 ## Participants
@@
 All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+
+Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015].
+Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
+
+We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
+^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
+In 
+`r sum(project_plan$power_standard == "80% power")`
+cases, we powered the replication attempt to 80\% post-hoc power. In 
+`r sum(project_plan$power_standard == "Original")` 
+cases, we used the original sample size.
+Three replications deviated from these two criteria.
+In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
+In another, we reduced the number of trials as part of the adaptation to Mechanical Turk.
+In the last case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
 
@@
 
-## Sample size determination and statistical approach
-
-After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility.
-The modal study chosen was the first, but several students chose later studies in a set as well.
+## Statistical approach
 
@@
 Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis.
-
-Determining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015].
-Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
-For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
-
-We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
-^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
-In 
-`r sum(project_plan$power_standard == "80% power")`
-cases, we powered the replication attempt to 80\% post-hoc power. In 
-`r sum(project_plan$power_standard == "Original")` 
-cases, we used the original sample size.
-Three replications deviated from these two criteria.
-In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
-In another, we reduced the number of trials as part of the adaptation to Mechanical Turk.
-In the last case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
-
-## Individual Replications
-
-Students chose findings from a wide variety of domains for replication.
-One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
-A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
-Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
-Details of individual replications are available in SOM.
 
@@
 Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.
-Our rating system was based on the theoretical interpretation of the original finding, with 0 = no support for the original interpretation, .5 = some support for the original interpretation, 1 = full replication).
+Our three-point rating system was based on the theoretical interpretation of the original finding, with 0\% = no support for the original interpretation, 50\% = some support for the original interpretation, 100\% = full replication).
 We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
@@
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
-Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original:
-replication rating `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
+Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original: `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\%
 vs. 

### 2016-09-08 paper/paper.Rmd
Small updates to mediating table

@@
   \hline
-\multicolumn{2}{c}{Replicated} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
+\multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
   \hline
@@
 \end{tabular}
-\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables.
+\caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest.
 High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).}

### 2016-09-08 paper/paper.Rmd
Small wording changes to CI discussion

@@
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in the reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+This choice was motivated by recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], as well as discrepencies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 

### 2016-09-08 paper/paper.Rmd
Small discussion point.

@@
 We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
-Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing.
+Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were underwhelming and further suggests the need for more replication attempts as a means for cumulative scientific progress.
 The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.

### 2016-09-08 paper/paper.Rmd
Add class authors + pdf

@@
 author-information:
-    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}
+    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254**, and Michael C. Frank}
 
@@
 author-note:
-    "These authors contributed equally. Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
+    "*These authors contributed equally.
+**Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, Jed Tan.
+Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
 

### 2016-09-08 paper/paper.Rmd
Minor edits

@@
     "*These authors contributed equally.
-**Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, Jed Tan.
+**Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
@@
 
+100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%
+
 Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.
@@
 We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
-The average rating given by instructors and students was `r round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)` and `r round(mean(d$replicated_student, na.rm=TRUE), digits = 2)` respectively.
+The average rating given by instructors and students was `r 100 * round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)`\% and `r 100 * round(mean(d$replicated_student, na.rm=TRUE), digits = 2)`\% respectively.
 
@@
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
-Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original: `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\%
+Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original (`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\%
 vs. 
-`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%.
+`r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%).
 There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs.

### 2016-09-08 paper/paper.Rmd
Pasting error
minor updates

--- 2016-09-08 paper/paper.Rmd
@@
 author-information:
-    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}
+    - \author{Eric Smith*, Robert X. D. Hawkins*, the students of Psych 254, and Michael C. Frank}
 
@@
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
-Yet under the current incentive structure for science, direct replication is not typically valued.
+Under the current incentive structure for science, direct replication is not typically valued, however.
 One potential solution to this problem is to make direct replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
-Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.
+Despite enthusiasm for this idea, however [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data -- beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] -- to support its efficacy.
 
@@
 We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
-Whether an independent scientist can build on a published result is perhaps as important as whether the work is replicable in a more conceptual sense -- and in many cases easier to determine.
+Whether another independent scientist can build on a result is perhaps as important as -- and in many cases easier to measure -- whether the work is replicable in some more abstract sense.
 
-With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy so that other institutions may adapt these practices.
-This process is dramatically facilitated by the use of free standardized tools for statistical analysis (R), data and code sharing (Git, R Markdown), and creation of web experiments (HTML, CSS, JavaScript).
+With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy.
+This process is dramatically facilitated by the use of standardized (and free) technical tools for statistical analysis, data and code sharing, and creation of web experiments.
 Nevertheless, there are significant limitations on what can be done in a single term and within the constraints of a course budget.
@@
 First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
-Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- supporting the same theoretical claims -- by a motivated student.
+Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- at least as far as support for the same theoretical claims -- by a motivated student.
 
@@
 
-## Study Selection
+## Class Outline
 
-All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://psych254.stanford.edu]()).
-At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project.
+All projects were completed as part of a class (syllabus and materials available at [http://psych254.stanford.edu]()).
+At the initiation of class, all students were told that they had the opportunity to participate in a group replication project to which they could contribute their class project.
 The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.
@@
 Students selected projects based on interest, rather than via a systematic sampling strategy.
-After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility.
-The modal study chosen was the first, but several students chose later studies in a set as well.
 Thus, all interpretation of our findings should be with respect to the distribution of student interest.
@@
 This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
-A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.
-
-Students chose findings from a wide variety of domains for replication.
-One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
-A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
-Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
-Details of individual replications are available in SOM.
+A summary of the original findings is given in Table \ref{tab:summary}.
 
@@
 All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
-
-Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015].
-Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
-For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
-
-We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
-^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
-In 
-`r sum(project_plan$power_standard == "80% power")`
-cases, we powered the replication attempt to 80\% post-hoc power. In 
-`r sum(project_plan$power_standard == "Original")` 
-cases, we used the original sample size.
-Three replications deviated from these two criteria.
-In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
-In another, we reduced the number of trials as part of the adaptation to Mechanical Turk.
-In the last case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
 
@@
 statistical tests, figures).
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by transferring results between analysis outputs and manuscripts.
+These documents could be compiled into a variety of formats (e.g., HTML, PDF, Microsoft Word).
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by copying and pasting between analysis outputs and manuscripts.
 
@@
 
-In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH).
+In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ES and RXDH).
 Each student collected two pilot samples and review was coordinated with these.
@@
 The goal of this pilot was to ensure that all needed data were being logged by the experiment script and that analytic scripts for the confirmatory analyses functioned appropriately.
-After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script (acting as a participant), analytic code, and resulting output.
+After Pilot A was completed, the instructor or a TA reviewed the student's experimental script (acting as a participant) and critiqued and reviewed the student's full analytic code and output.
 
@@
 
-## Statistical approach
+## Sample size determination and statistical approach
+
+After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility.
+The modal study chosen was the first, but several students chose later studies in a set as well.
 
@@
 
+Determining appropriate sample sizes is a second major challenge in replication research [@button2013;@simonsohn2015].
+Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
+
+We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
+^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
+In 
+`r sum(project_plan$power_standard == "80% power")`
+cases, we powered the replication attempt to 80\% post-hoc power. In 
+`r sum(project_plan$power_standard == "Original")` 
+cases, we used the original sample size.
+In one case, the original experiment was  extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
+In one case, we reduced the number of trials as part of the adaptation to Mechanical Turk, and in one case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
+
+## Individual Replications
+
+Students chose findings from a wide variety of domains for replication.
+One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
+A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
+Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
+Details of individual replications are available in SOM.
+
 # Results
@@
 
-Of the 15 students in the class, all completed projects (two with extensions going beyond the class period), one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
+Of the 15 students in the class, all completed projects (two with extensions, one short and one more significant), but one failed to find a project of interest in the sampling frame and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
 Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
-(In one case, a student did not complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review.
-Thus, this project remains included.)
+(In one case, a student failed to complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review).
 
 Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
-Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`).
+Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)`.
 Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might have an effect on the results.
@@
 Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.
-Our three-point rating system was based on the theoretical interpretation of the original finding, with 0\% = no support for the original interpretation, 50\% = some support for the original interpretation, 100\% = full replication).
+Our rating system was based on the theoretical interpretation of the original finding, with 0 = no support for the original interpretation, .5 = some support for the original interpretation, 1 = full replication).
 We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
@@
   \hline
-\multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
+\multicolumn{2}{c}{Replicated} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
   \hline
@@
 \end{tabular}
-\caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest.
-High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).}
+\caption{\label{tab:results} Counts of instructor team replication ratings, split by mediating variables.}
 \end{table}
@@
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
-Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original: `r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\%
+Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original:
+`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\% 
 vs. 
@@
 To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
-Other formulas are given in @osc2015, Supplemental Information.].
+Other formulas are given in @osc2015, Supplemental Information].
 We first compared effect sizes from the original and replication studies (Figure 2A).
@@
 (r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
-(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).
+(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).
 
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], as well as discrepencies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+This choice was motivated by recent discussions of the utility and validity of interpreting confidence intervals in this manner [@morey2016], as well as discrepencies in the reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 
@@
   scale_x_continuous(limits = c(0, 1), 
-                breaks = c(.1, .3, .5, .7, .9)) +
+                breaks = c(.1, .3, .5)) +
   scale_y_continuous(limits = c(0, 1), 
-                breaks = c(.1, .3, .5, .7, .9)) +
+                breaks = c(.1, .3, .5)) +
   geom_abline(slope = 1, intercept = 0, linetype = 2) +
@@
 
-<!-- Demographics -->
-
 # Discussion
@@
 We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
-Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were underwhelming and further suggests the need for more replication attempts as a means for cumulative scientific progress.
+Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were disappointing.
 The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.
@@
 Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants.
-Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on funding for samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on available samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
 In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests.

### 2016-09-08 paper/paper.Rmd
authors

--- 2016-09-08 paper/paper.Rmd
@@
 author-information:
-    - \author{Eric N. Smith*, Robert X. D. Hawkins*, the students of Psych 254**, and Michael C. Frank}
+    - \author{Robert X. D. Hawkins*, Eric N. Smith*, the Psych 254 Students**, and Michael C. Frank}
 
@@
 author-note:
-    "*These authors contributed equally.
-**Project contributors included Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampien, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
+    "*These authors contributed equally and are listed alphabetically.
+**Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
@@
 
-100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%
-
 Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.

### 2016-09-08 paper/paper.Rmd
para fix

@@
     "*These authors contributed equally and are listed alphabetically.
-**Carolyn Au, Juan Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
+**Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
@@
 As a proof-of-concept for this idea, here we report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
-This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published finding of interest on a first attempt.
-Congruent with previous findings, replication studies typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
-We describe the workflow and pedagogical methods that were used in the class and discuss challenges for adoption of this pedagogical model and replication research more broadly."
+This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published result on a first attempt.
+Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
+We describe the workflow and pedagogical methods that were used in the class and discuss challenges both for the adoption of this pedagogical model and for replication research more broadly."
 
@@
 
-In the current article, we provide evidence on this issue by reporting the results of replication projects conducted in a single class (a graduate-level experimental methods course).
+In the current article, we report the results of replication projects conducted in a single class (a graduate-level experimental methods course).
 As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*.
-These studies both give evidence about the state of replicability in the field and provide insight into the process of pedagogical replication.
+These studies both give evidence about the state of replicability in the field and provide insight into the challenges and promise of pedagogical replication.
 
-It is a challenging proposition to estimate the replicability of an entire literature [cf.
-@osc2015].
-Making such an estimate minimally requires determining a sampling strategy, a notion of what constitutes a direct replication, and a standard for what constitutes a successful replication, among many other difficult decisions [@gilbert2016;@anderson2016].
-In the current work, we focus on a quantity that is easier to estimate: the probability that a graduate student can choose an article of interest in *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the basic pattern of findings with sufficient fidelity to be able to build on it in future work.
-We believe that this notion of whether a piece of research supports cumulative progress is an important construct.
-Whether an independent scientist can build on a published result is perhaps as important as whether the work is replicable in a more conceptual sense -- and in many cases easier to determine.
+Past work has attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016].
+Assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [@cites] and establishing a standard for replication success [@simonsohn2015].
+Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality.
+Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014].
+
+In the current work, we do not address these challenges directly; instead, our goal is more modest.
+We assess the probability that a graduate student can choose an article of interest in the 2015 volume of *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings.
+We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations.
+While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.
 
@@
 First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
-Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced -- supporting the same theoretical claims -- by a motivated student.
+Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced by a motivated student.
 
@@
 
-All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://psych254.stanford.edu]()).
+All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://http://web.stanford.edu/class/psych254/2016/]()).
 At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project.

### 2016-09-08 paper/paper.Rmd
more intro

@@
 In the current work, we do not address these challenges directly; instead, our goal is more modest.
-We assess the probability that a graduate student can choose an article of interest in the 2015 volume of *Psychological Science* and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings.
+We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings.
 We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations.
@@
 This process is dramatically facilitated by the use of free standardized tools for statistical analysis (R), data and code sharing (Git, R Markdown), and creation of web experiments (HTML, CSS, JavaScript).
-Nevertheless, there are significant limitations on what can be done in a single term and within the constraints of a course budget.
-We return in the Discussion to limitations on our approach.
+There are significant limitations on what can be done in a single term and within the constraints of a course budget; we return to these in the Discussion.
+Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.
 

### 2016-09-08 paper/paper.Rmd
New table 1

@@
 output: kmr::apa_manuscript
+
+header-includes:
+   - \usepackage{lscape}
 
@@
 
+\begin{landscape}
+\centering
+
 \newcommand{\specialcell}[2][c]{%
@@
 
-<!-- latex table generated in R 3.3.0 by xtable 1.8-2 package
- Fri Jun 24 12:02:11 2016 -->
 \begin{table}[ht]
@@
 \centering
-\begin{tabular}{lllllrr}
+\begin{tabular}{lllllr|lrcl}
   \hline
-Citation & Expt & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{Original\\on Turk?} & N (orig) & N (rep) \\ 
+\specialcell{Citation\\(Psychological Science; 2015)} & Expt.
+& \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Replication\\Support}\\
   \hline
-Storm \& Stone (2015) & 3 & No & No & No &  48 &  61 \\ 
-Lewis \& Oyserman (2015) & 4 & No & Yes & Yes & 122 & 128 \\ 
-Scopelliti, Loewenstein, \& Vosgerau (2015) & 3 & No & Yes & Yes & 550 & 124 \\ 
-Liverence \& Scholl (2015) & 1 & No & Some & No &  18 &  19 \\ 
-Wang et al. (2015) & 2 & No & No & No & 219 & 397 \\ 
-Sofer et al. (2015) & 1 & No & Yes & No &  48 &  95 \\ 
-Ko, Sadler, \& Galinksy (2015) & 2 & Yes & Some & No &  40 &  40 \\ 
-Atir, Rosenzweig, \& Dunning (2015) & 1b & No & Yes & Yes & 202 &  50 \\ 
-Proudfoot, Kay, \& Koval (2015) & 1 & No & No & Yes &  80 &  84 \\ 
-Zaval, Markowitz, \& Weber (2015) & 1 & Yes & Yes & Yes & 312 & 321 \\ 
-Xu \& Franconeri (2015) & 1a & No & No & No &  12 &  27 \\ 
+
+Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.50 & Full \\ 
+Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.50 & Full \\ 
+Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.25 & Partial \\ 
+Liverence \& Scholl & 1 & No & Some & No &  18 & Original &  19 & 4.75 & Partial \\ 
+Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.25 & Full \\ 
+Scopelliti, Loewenstein, \& Vosgerau & 3 & No & Yes & Yes & 550 & 80\% power & 124 & 4.75 & None \\ 
+Sofer et al. & 1 & No & Yes & No &  48 & Other &  95 & 4.50 & Partial \\ 
+Storm \& Stone & 3 & No & No & No &  48 & Original &  61 & 4.00 & Partial \\ 
+Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.00 & None \\ 
+Xu \& Franconeri & 1a & No & No & No &  12 & Original &  27 & 4.00 & Partial \\ 
+Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.25 & Partial \\ 
    \hline
 \end{tabular}
-\caption{\label{tab:summary} Summary of papers and experiments that were targets for replication in our projects.} 
+\caption{\label{tab:summary} Summary of original research papers and results of experiments that were targets for replication in our projects.} 
 \label{tab:summary}
 \end{table}
+
+\end{landscape}
 

### 2016-09-08 paper/paper.Rmd
finished ms pass

--- 2016-09-08 paper/paper.Rmd
@@
 Students selected projects based on interest, rather than via a systematic sampling strategy.
-After selecting a paper of interest, students chose a particular study from within that paper based on their judgment of interest and feasibility.
+After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility.
 The modal study chosen was the first, but several students chose later studies in a set as well.
-Thus, all interpretation of our findings should be with respect to the distribution of student interest.
-Any reproducibility estimates arising from our analyses are estimates of the probability of reproducing a finding that is of interest, rather than findings in general.
+Thus, all interpretation of our findings should be with respect to this non-probability sample.
 This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
+
 A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.
-
 Students chose findings from a wide variety of domains for replication.
@@
 In another, we reduced the number of trials as part of the adaptation to Mechanical Turk.
-In the last case of a multi-step procedure where the first step consisted of stimulus generation, we decreased the N in the first stage of the procedure (details available in SOM).
+In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage (details available in SOM).
 
@@
 This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices.
-Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g.
-statistical tests, figures).
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that many of these are likely introduced by transferring results between analysis outputs and manuscripts.
+Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g., statistical tests and figures).
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.
 
@@
 The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
-The goal of this pilot was to ensure that all needed data were being logged by the experiment script and that analytic scripts for the confirmatory analyses functioned appropriately.
-After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script (acting as a participant), analytic code, and resulting output.
+The goal of this pilot was to ensure that all needed data were being logged by the experiment software and that analytic scripts for the confirmatory analyses functioned appropriately.
+After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script, analytic code, and resulting output.
 
@@
 The goal of this pilot was to ensure that participants were able to complete the experiment and did not report any substantial issues with instructions or technical details of the experiment.
-(All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing text).
+(All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing).
 At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
@@
 
-Despite the general emphasis in meta-analytic and reproducibility efforts to aggregate a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test in studies.
-Often a wide variety of statistical tests were conducted, often within one or several regression models with multiple specifications.
+Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study.
+Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications.
 Thus, we interpret "key statistical test" results with caution.
@@
 (In one case, a student did not complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review.
-Thus, this project remains included.)
+We included this project in the final analysis.)
 
@@
 Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`).
-Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might have an effect on the results.
+Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might plausibly have an effect on the results.
 
@@
 
-\begin{table}[ht]
-\centering
-\begin{tabular}{rl|ccccccc}
-  \hline
-\multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\
-  \hline
-   &  & No & Yes & Yes & No & No & Some & Yes \\ 
-  Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\ 
-  Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\ 
-  No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\ 
-  \hline
-  Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\
-   \hline
-\end{tabular}
-\caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest.
-High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).}
-\end{table}
-
 <!-- \begin{table}[ht] -->
 <!-- \centering -->
-<!-- \begin{tabular}{llrrr|r} -->
+<!-- \begin{tabular}{rl|ccccccc} -->
 <!--   \hline -->
-<!-- Mediator & Value & No & Partial & Full & Total\\  -->
+<!-- \multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\ -->
 <!--   \hline -->
-<!-- Replicated? &  &   2 &   6 &   3 & 11 \\  -->
+<!--    &  & No & Yes & Yes & No & No & Some & Yes \\  -->
+<!--   Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\  -->
+<!--   Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\  -->
+<!--   No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\  -->
 <!--   \hline -->
-<!--   Original on turk & Yes &   1 &   2 &   2 & 5 \\  -->
-<!--    & No &   1 &   4 &   1 & 6\\  -->
-<!-- \hline -->
-<!--   High fidelity replication? & Yes &   2 &   3 &   1  & 6\\  -->
-<!--    & No &  &   3 &   2 & 5\\  -->
-<!-- \hline -->
-<!--   Open materials? & Yes &   1 &   3 &   1  & 4\\  -->
-<!--    & Some &  &   1 &   1 & 2\\  -->
-<!--    &  No &   1 &   2 &   1 & 4\\  -->
+<!--   Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\ -->
 <!--    \hline -->
 <!-- \end{tabular} -->
-<!-- \caption{\label{tab:results} Counts of instructor team replication ratings, split by various different mediating variables.} -->
+<!-- \caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest.
+High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).} -->
 <!-- \end{table} -->
@@
 
-The distribution of ratings are given in Table \ref{tab:results}, along with breakdowns by various factors of interest.
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
@@
 `r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%).
-There were small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs.
+This result is consistent with a reanalysis of @osc2015 that found identified variability across contexts as a potential factor mediating replication success [@vanbavel2016; cf.
+@inbar2016].
+There were also small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs.
 `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\%
@@
 
-These additional measures therefore give another sense in which replications can be successful: if we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the $p = 0.05$ threshold, we should have increased confidence in the effect's reproducibility.
+These additional measures therefore give another sense in which replications can be successful: If we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we should increase our confidence in the effect's replicability.
 To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
-Other formulas are given in @osc2015, Supplemental Information.].
+Other formulae are given in @osc2015, Supplemental Information.].
 We first compared effect sizes from the original and replication studies (Figure 2A).
@@
 Next, following @etz2016, we compared Bayes Factors between the original and replication.
-We used the default  test suggested by @rouder2009 and did not attempt to correct for publication bias.
-This analysis revealed a number of interesting findings.
+We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[A default BF for one paper could not be computed based on the statistical test that was used.] This analysis revealed a number of interesting findings.
 First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals.
-Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments as well.
-Finally, we note that the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g.
+Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments.
+Finally, the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g.
 BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.
@@
   geom_smooth(method = "lm", se=FALSE) +
-  xlab("Orig. effect size (d)") + 
-  ylab("Rep. effect size (d)") + 
+  xlab("Orig. effect size (r)") + 
+  ylab("Rep. effect size (r)") + 
   theme_bw(base_size=10) + theme(legend.position="bottom") + 
@@
 In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*.
-We had two interlocking goals: first, to create a proof of concept for high-quality pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
-Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, our results were underwhelming and further suggests the need for more replication attempts as a means for cumulative scientific progress.
-The modal outcome of our projects was partial replication, in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.
+We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
+Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project.
 
-Our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project.
-While these constraints might initially seem severe, our work here shows what is possible for motivated students using freely-available tools and resources.
-Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants.
-Nevertheless, they had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment [@lewis2016], 2) limits on funding for samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+Pedagogically, we view our findings as a success.
+Within relatively stringent constraints, our group was able to produce a set of high-quality projects.
+Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants as the originals.
+Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
+Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
+
+Scientifically, however, our results were underwhelming.
+Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
+These partial replications often were cases in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.
+We invite readers to browse the narrative descriptions of individual replication attempts in our SOM for an object lesson in the ways that patterns of experimental findings can differ from one another beyond the significance of a single test.
+
+Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
 In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests.
-
-Our findings were congruent with the results of @osc2015, revealing a relatively low rate of replicability by a number of tests.
+Despite these limitations, the replication rate in our study was roughly consistent with previous studies [@osc2015].
 In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015].
@@
 Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications.
-And in many cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf.
+And in some cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf.
 @bakeman2005].
-This set of features -- which, in our experience, are endemic to published psychological work -- makes replication research within the conventional statistical paradigm extremely challenging.
-
+This set of features -- which, in our experience, are endemic to published psychological work, including our own -- makes replication research within the conventional statistical paradigm extremely challenging.
 In our view, two recommendations will improve this situation dramatically.
@@
 Were this information available, it would have simplified the problem of selecting effects to replicate in several cases.
-Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here, in a number of ways.
-In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data and analytic code is often critical for other investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is a way of allowing more flexible reuse.
+Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here.
+In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.
 

### 2016-09-08 paper/paper.Rmd
Fix http typo

--- 2016-09-08 paper/paper.Rmd
@@
 output: kmr::apa_manuscript
-
-header-includes:
-   - \usepackage{lscape}
 
@@
 
-\begin{landscape}
-\centering
-
 \newcommand{\specialcell}[2][c]{%
@@
 
+<!-- latex table generated in R 3.3.0 by xtable 1.8-2 package
+ Fri Jun 24 12:02:11 2016 -->
 \begin{table}[ht]
@@
 \centering
-\begin{tabular}{lllllr|lrcl}
+\begin{tabular}{lllllrr}
   \hline
-\specialcell{Citation\\(Psychological Science; 2015)} & Expt.
-& \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Replication\\Support}\\
+Citation & Expt & \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{Original\\on Turk?} & N (orig) & N (rep) \\ 
   \hline
-
-Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.50 & Full \\ 
-Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.50 & Full \\ 
-Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.25 & Partial \\ 
-Liverence \& Scholl & 1 & No & Some & No &  18 & Original &  19 & 4.75 & Partial \\ 
-Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.25 & Full \\ 
-Scopelliti, Loewenstein, \& Vosgerau & 3 & No & Yes & Yes & 550 & 80\% power & 124 & 4.75 & None \\ 
-Sofer et al. & 1 & No & Yes & No &  48 & Other &  95 & 4.50 & Partial \\ 
-Storm \& Stone & 3 & No & No & No &  48 & Original &  61 & 4.00 & Partial \\ 
-Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.00 & None \\ 
-Xu \& Franconeri & 1a & No & No & No &  12 & Original &  27 & 4.00 & Partial \\ 
-Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.25 & Partial \\ 
+Storm \& Stone (2015) & 3 & No & No & No &  48 &  61 \\ 
+Lewis \& Oyserman (2015) & 4 & No & Yes & Yes & 122 & 128 \\ 
+Scopelliti, Loewenstein, \& Vosgerau (2015) & 3 & No & Yes & Yes & 550 & 124 \\ 
+Liverence \& Scholl (2015) & 1 & No & Some & No &  18 &  19 \\ 
+Wang et al. (2015) & 2 & No & No & No & 219 & 397 \\ 
+Sofer et al. (2015) & 1 & No & Yes & No &  48 &  95 \\ 
+Ko, Sadler, \& Galinksy (2015) & 2 & Yes & Some & No &  40 &  40 \\ 
+Atir, Rosenzweig, \& Dunning (2015) & 1b & No & Yes & Yes & 202 &  50 \\ 
+Proudfoot, Kay, \& Koval (2015) & 1 & No & No & Yes &  80 &  84 \\ 
+Zaval, Markowitz, \& Weber (2015) & 1 & Yes & Yes & Yes & 312 & 321 \\ 
+Xu \& Franconeri (2015) & 1a & No & No & No &  12 &  27 \\ 
    \hline
 \end{tabular}
-\caption{\label{tab:summary} Summary of original research papers and results of experiments that were targets for replication in our projects.} 
+\caption{\label{tab:summary} Summary of papers and experiments that were targets for replication in our projects.} 
 \label{tab:summary}
 \end{table}
-
-\end{landscape}
 
@@
 
-All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://http://web.stanford.edu/class/psych254/2016/]()).
+All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://web.stanford.edu/class/psych254/2016/]()).
 At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project.

### 2016-09-08 paper/paper.Rmd
minor tweaks to ms/comment cleanup

@@
   rowwise() %>%
-  mutate(fidelity = (replication_fidelity_MCF + replication_fidelity_ES) / 2) %>%
+  mutate(fidelity = (replication_fidelity_MCF + replication_fidelity_ES + replication_fidelity_RH) / 3) %>%
   ungroup
@@
 Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
-Coded on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), the mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`).
-Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might plausibly have an effect on the results.
+We coded projects independently on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), and then discussed our ratings and made adjustments (without coming to full consensus).
+The mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`).
+Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might plausibly have had an effect on the results.
 
@@
 d$high_fidelity <- d$fidelity > median(d$fidelity)
-# table(d$replicated_TA,d$replicated_student) # Make prettier
-#mean(d$replicated_team)
 
@@
   select(Mediator, Value, No, Partial, Full)
-
-# print(xtable(outcomes), include.rownames = FALSE)
 ```
-
-<!-- \begin{table}[ht] -->
-<!-- \centering -->
-<!-- \begin{tabular}{rl|ccccccc} -->
-<!--   \hline -->
-<!-- \multicolumn{2}{c}{Support} & \multicolumn{2}{c}{Original on Turk?} & \multicolumn{2}{c}{High fidelity?} & \multicolumn{3}{c}{Open Materials?} \\ -->
-<!--   \hline -->
-<!--    &  & No & Yes & Yes & No & No & Some & Yes \\  -->
-<!--   Full & 3 & 1 & 2 & 1 & 2 & 1 & 1 & 1 \\  -->
-<!--   Partial & 6 & 4 & 2 & 4 & 2 & 2 & 1 & 3 \\  -->
-<!--   No &  2 &  1 &  1 &  2 & 0 &  1 & 0 &  1 \\  -->
-<!--   \hline -->
-<!--   Total & 11 & 6 & 5 & 7 & 4 & 4 & 2 & 5 \\ -->
-<!--    \hline -->
-<!-- \end{tabular} -->
-<!-- \caption{\label{tab:results} Counts of instructor team ratings of replication support for the theoretical findings, split by variables of interest.
-High fidelity denotes replications judged to be above the median rating of fidelity ( >`r median(d$fidelity)` out of 7).} -->
-<!-- \end{table} -->
 

### 2016-09-08 paper/paper.Rmd
bib updates

@@
 Past work has attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016].
-Assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [@cites] and establishing a standard for replication success [@simonsohn2015].
+Assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [e.g., @stroebe2014] and establishing a standard for replication success [e.g., @simonsohn2015].
 Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality.
@@
 
-```{r}
-ppt <- project_plan %>%
-        select(cite, expt_num, open_data,
-               open_materials, original_on_turk, original_n,collected_n)
-
-names(ppt) = c("Citation", "Expt", "Data", "Materials", "Turk?", 
-               "N (orig)","N (rep)")
-
-# print(xtable(ppt, caption = "Summary of attempted replications", 
-#        label = "tab:summary"), include.rownames=FALSE)
-```
-
 \begin{landscape}
@@
 
-Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.50 & Full \\ 
-Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.50 & Full \\ 
-Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.25 & Partial \\ 
-Liverence \& Scholl & 1 & No & Some & No &  18 & Original &  19 & 4.75 & Partial \\ 
-Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.25 & Full \\ 
-Scopelliti, Loewenstein, \& Vosgerau & 3 & No & Yes & Yes & 550 & 80\% power & 124 & 4.75 & None \\ 
-Sofer et al. & 1 & No & Yes & No &  48 & Other &  95 & 4.50 & Partial \\ 
+Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & Full \\ 
+Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & Full \\ 
+Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & Partial \\ 
+Liverence \& Scholl & 1 & No & Some & No &  18 & Original &  19 & 5.33 & Partial \\ 
+Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & Full \\ 
+Scopelliti, Loewenstein, \& Vosgerau & 3 & No & Yes & Yes & 550 & 80\% power & 124 & 5.67 & None \\ 
+Sofer et al. & 1 & No & Yes & No &  48 & Other &  95 & 4.33 & Partial \\ 
 Storm \& Stone & 3 & No & No & No &  48 & Original &  61 & 4.00 & Partial \\ 
-Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.00 & None \\ 
-Xu \& Franconeri & 1a & No & No & No &  12 & Original &  27 & 4.00 & Partial \\ 
-Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.25 & Partial \\ 
+Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & None \\ 
+Xu \& Franconeri & 1a & No & No & No &  12 & Original &  27 & 5.00 & Partial \\ 
+Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & Partial \\ 
    \hline
@@
 
-All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(ppt)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
 
@@
 
-Of the `r nrow(ppt)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
+Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
 For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors).
@@
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
-Overall, projects had a somewhat larger probability of being judged successful if they were judged to be closer to the original (`r 100 * round(mean(d$replicated_TA[d$high_fidelity]), digits=2)`\%
+Overall, projects had a slightly larger probability of being judged successful if they were judged to be closer to the original (`r 100 * round(mean(d$replicated_TA[d$high_fidelity == TRUE]), digits=2)`\%
 vs. 
 `r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%). 
-This result is consistent with a reanalysis of @osc2015 that found identified variability across contexts as a potential factor mediating replication success [@vanbavel2016; cf.
-@inbar2016].
 There were also small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs.

### 2016-09-08 paper/paper.Rmd
5% additional sentence + minor change

@@
 We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
+For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved desired power if some participants skipped through or did not complete the experiment.
 ^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
@@
 Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.
-Our three-point rating system was based on the theoretical interpretation of the original finding, with 0\% = no support for the original interpretation, 50\% = some support for the original interpretation, 100\% = full replication).
+Our three-point rating system was based on the theoretical support for the original finding, "None" (no support; 0\%), "Partial" (some support; 50\%), and "Full" (replication consistent with original interpretation; 100\%).
 We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.

### 2016-09-09 paper/paper.Rmd
Fix fig. 2 caption, labels so not cut off

@@
 Note that the key statistic in the Sofer et al.
-(2015) replication was a multivariate $F$ test, hence a default Bayes factor could not be computed.", fig.pos="ht", fig.height=4}
+(2015) replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed.
+Additionally, the original Bayes factor for Atir et al (2015) was many orders of magnitude greater than the others, so we displayed it at the edge of the range for visibility.", fig.pos="ht", fig.height=3.6}
 
@@
   # scale_color_solarized(guide = FALSE)
-  scale_color_solarized(name = "Subjective rep. rating")
+  scale_color_solarized(name = "Subj. rep. rating")
 
@@
   theme_bw(base_size=10) + theme(legend.position="bottom") + 
-  scale_size_continuous(name = "Ratio of rep. df to orig. df") + 
-  scale_color_solarized(name = "Subjective rep. rating")
+  scale_size_continuous(name = "rep. df/orig. df") + 
+  scale_color_solarized(name = "Subj. rep. rating")
 

### 2016-09-22 paper/paper.Rmd
minor ms changes

--- 2016-09-08 paper/paper.Rmd
@@
     "*These authors contributed equally and are listed alphabetically.
-**Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Marty Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
+**Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Martin Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
@@
 
-All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] Each sample was recruited independently (using the same account); most were All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
 
@@
 
-# Appendix: Project-By-Project Methods Addendum
+# SOM-R: Project-By-Project Methods Addendum
 
@@
 eight-word condition).
-The replication study failed to find evidence of the interaction, but ironically this was because we found evidence for a main effect of save condition: The authors' key manipulation succeeded for both load conditions.
+The replication study failed to find evidence of the interaction, but ironically this failure was because of a main effect of save condition: The authors' key manipulation succeeded for both load conditions.
 Perhaps even two words was sufficient to create interference for our online sample.

### 2016-09-22 paper/paper.Rmd
responses to Greg and original authors

@@
 ---
-title: "Assessing the Replicability of Psychological Science Through Pedagogy"
+title: "Improving the Replicability of Psychological Science Through Pedagogy"
 short-title: "Replication Through Pedagogy"
@@
 **Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Martin Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
-Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class."
+Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
+We are grateful to the authors of the original studies for both providing materials and for their comments on a draft of this manuscript."
 
@@
 As a proof-of-concept for this idea, here we report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
-This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published result on a first attempt.
 Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
+This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published result on a first attempt, however, rather than a direct assessment of the truth of particular findings.
 We describe the workflow and pedagogical methods that were used in the class and discuss challenges both for the adoption of this pedagogical model and for replication research more broadly."
@@
 
-Past work has attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016].
-Assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [e.g., @stroebe2014] and establishing a standard for replication success [e.g., @simonsohn2015].
+Past work has explicitly attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016].
+Presupposing that this construct is even meaningful [cf.
+@gergen1973], assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [e.g., @stroebe2014] and establishing a standard for replication success [e.g., @simonsohn2015].
 Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality.
@@
 
-With respect to pedagogy, we describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy so that other institutions may adapt these practices.
-This process is dramatically facilitated by the use of free standardized tools for statistical analysis (R), data and code sharing (Git, R Markdown), and creation of web experiments (HTML, CSS, JavaScript).
-There are significant limitations on what can be done in a single term and within the constraints of a course budget; we return to these in the Discussion.
+We also describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy.
+Although mentorship in specific experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
+And replication research specifically illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- in a way that more open-ended projects, which require new conceptual development, often do not [see @frank2012 for a more extended argument].
+There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise, and we return to these in the Discussion.
 Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.
@@
 First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
-Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced by a motivated student.
+Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced by a motivated student on a first attempt.
 
@@
 \specialcell{Citation\\(Psychological Science; 2015)} & Expt.
-& \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Replication\\Support}\\
+& \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Project link} \\
   \hline
 
-Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & Full \\ 
-Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & Full \\ 
-Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & Partial \\ 
-Liverence \& Scholl & 1 & No & Some & No &  18 & Original &  19 & 5.33 & Partial \\ 
-Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & Full \\ 
-Scopelliti, Loewenstein, \& Vosgerau & 3 & No & Yes & Yes & 550 & 80\% power & 124 & 5.67 & None \\ 
-Sofer et al. & 1 & No & Yes & No &  48 & Other &  95 & 4.33 & Partial \\ 
-Storm \& Stone & 3 & No & No & No &  48 & Original &  61 & 4.00 & Partial \\ 
-Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & None \\ 
-Xu \& Franconeri & 1a & No & No & No &  12 & Original &  27 & 5.00 & Partial \\ 
-Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & Partial \\ 
+Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & https://osf.io/uegk5/ \\ 
+Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & https://osf.io/g6k2u/\\ 
+Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & https://osf.io/rdw6e/ \\ 
+Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & https://osf.io/sfxrb/ \\ 
+Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & https://osf.io/ne8ph/ \\ 
+Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & https://osf.io/32wsm/ \\ 
+Sofer et al. & 1 & No & Yes & No &  48 & Other &  95 & 4.33 & https://osf.io/5wmhn/ \\ 
+Storm \& Stone & 3 & No & No & No &  48 & Original &  61 & 4.00 & https://osf.io/9cgpq/ \\ 
+Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & https://osf.io/ng96w/ \\ 
+Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & https://osf.io/cgvzs/ \\ 
+Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & https://osf.io/degwa/ \\ 
    \hline
 \end{tabular}
-\caption{\label{tab:summary} Summary of original research papers and results of experiments that were targets for replication in our projects.} 
+\caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects.
+* marks projects where the number of trials was modified.}
 \label{tab:summary}
@@
 
-## Study Selection
+## General Class Outline
 
@@
 
+We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.
+This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knwoledge.
+Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some results.
+
 A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.
@@
 
-All study participants were recruited on Amazon Mechanical Turk; individual samples are given in Table \ref{tab:summary}.^[Note that of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on Mechanical Turk.] Each sample was recruited independently (using the same account); most were All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+All study participants were recruited on AMT.
+Individual sample sizes are given in Table \ref{tab:summary}.
+Each sample was recruited independently, using the same account but a different title.
+All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+
+Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT.
+For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see SOM for more discussion of this issue in individual cases.
+
+Repeat administration of experiments on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
+We did not ask participants whether they had participated in similar research previously, however.
+First, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see SOM for discussion of one particular paradigm that has been used more recently).
+Second, we suspected that asking this sort of question would lead to a large number of innaccurate responses.
 
@@
 We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
-In 
-`r sum(project_plan$power_standard == "80% power")`
-cases, we powered the replication attempt to 80\% post-hoc power. In 
-`r sum(project_plan$power_standard == "Original")` 
+In three cases, we powered the replication attempt to 80\% post-hoc power. In four
 cases, we used the original sample size.
-Three replications deviated from these two criteria.
 In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
-In another, we reduced the number of trials as part of the adaptation to Mechanical Turk.
-In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage (details available in SOM).
+In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).
+In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.
 
@@
 
-In addition to as-needed guidance on projects, to ensure high quality replications, students went through a rigorous process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH).
+In addition to as-needed guidance on projects, students went through a process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH).
 Each student collected two pilot samples and review was coordinated with these.
@@
 Thus, we interpret "key statistical test" results with caution.
-Nevertheless, despite this interpretive difficulty, we attempted to use a single statistical test as our target for experiment planning and analysis.
+Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for experiment planning and analysis.
 
@@
 Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
-(In one case, a student did not complete the pre-registration procedure correctly but nevertheless submitted a pre-specified analysis plan to the instructors for review.
+(In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review.
 We included this project in the final analysis.)
@@
 
-In two cases, in final review of the projects (after data collection), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
+In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
 In both of these cases [@sofer2015;@proudfoot2015], the original authors had fit a multiple regression model to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
@@
 We report results from these corrected tests here.
-We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research.
+We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].
 
@@
 
-Students of the class and the instructors gave independent “replication ratings” to assess subjective judgement of the replication.
+After data analysis, for each experiment, the student carrying out each experiment and the instructors all gave independent "replication ratings" to assess the subjective success of the replication.
 Our three-point rating system was based on the theoretical support for the original finding, "None" (no support; 0\%), "Partial" (some support; 50\%), and "Full" (replication consistent with original interpretation; 100\%).
@@
 The modal replication project in our sample was judged to be a "partial" replication, meaning that some aspects of the observed findings were different from those reported by the original authors.
-While this conclusion is dispiriting, it is also perhaps unsurprising given the complexity of the analyses reported in many of the original papers.
+While this conclusion is somewhat dispiriting, it is also perhaps unsurprising given the complexity of the analyses reported in many of the original papers.
 In addition, `r sum(d$original_test=="interaction")` of the tests were interactions, which tend to have lower statistical power [@mcclelland1993] and have fared poorly in previous replication studies [@osc2015].
@@
 `r 100 * round(mean(d$replicated_TA[d$high_fidelity == FALSE]), digits=2)`\%). 
-There were also small numerical effects of being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs.
+There were also small numerical effects of the original study being run on Mechanical Turk (`r 100 *round(mean(d$replicated_TA[d$original_on_turk == "Yes"]), digits=2)`\% vs.
 `r 100 *round(mean(d$replicated_TA[d$original_on_turk == "No"]), digits=2)`\%) and having open materials (`r 100 *round(mean(d$replicated_TA[d$open_materials!="No"]), digits=2)`\%
@@
 Effect sizes and Bayes factors improve upon inferences drawn from $p$-values in different ways.
-The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes and allows for a more fine-grained comparison across studies than a binary significance criterion.
+The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes (assuming a constant experimental procedure, of course) and allows for a more fine-grained comparison across studies than a binary significance criterion.
 The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961].
@@
 Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments.
-Finally, the Bayes Factors for a number of the original effects did not appear to show strong evidential value (e.g.
-BF < 3); thus, it would have been somewhat surprising for our replications to show stronger evidence.
+Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3); it would have been somewhat surprising for our replications to show stronger evidence than the original.
 
@@
              aes(color=replicated_TA_factor, size = collected_n)) +
-  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
+  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
   scale_x_continuous(limits = c(0, 1), 
@@
   geom_smooth(method = "lm", se=FALSE) +
-  geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
+  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
   xlab("Orig. Bayes Factor") + 
@@
 We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
-Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated with the time, money, and effort constraints of a course project.
+Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated within the constraints of a course project.
 
-Pedagogically, we view our findings as a success.
-Within relatively stringent constraints, our group was able to produce a set of high-quality projects.
-Indeed, the majority of the projects in our report were relatively close replications and included the same or greater numbers of participants as the originals.
+Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+But within these relatively stringent constraints, our group was able to produce a set of close replications with generally good statistical power.
 Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
@@
 
-Scientifically, however, our results were underwhelming.
-Despite our relatively tight adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
+Statistically, however, our results were underwhelming.
+Despite our relatively close adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
 These partial replications often were cases in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.
-We invite readers to browse the narrative descriptions of individual replication attempts in our SOM for an object lesson in the ways that patterns of experimental findings can differ from one another beyond the significance of a single test.
+We invite readers to browse the narrative descriptions of individual replication attempts in our SOM to see the ways that patterns of experimental findings can differ from one another beyond the significance of a single test.
 
-Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
-In addition, many papers published within our notional sampling frame (the 2015 volume of *Psychological Science*) were not feasible as projects, and students in our course were asked to take feasibility into account in choosing their projects as well as their own interests.
-Despite these limitations, the replication rate in our study was roughly consistent with previous studies [@osc2015].
-In addition, in informal assessments of previous years' findings, we see a similar rate of replicability [@frank2015].
-What are the causes of this relatively low rate?
+These statistical findings mask a more optimistic message, however: In most of our projects, the next step for a motivated experimenter is clear.
+For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials [@liverence2015;@storm2015;@xu2015].
+In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample [@zaval015;@lewis2015;@scopelliti2015].
+And in some, differences of population would mean that followups would require further stimulus or task adaptation [@sofer2015;@wang2015].
+More generally, we believe that our work here underscores the importance of iterated replication [@lewis2016].
 
-Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, publication bias, and low statistical power among others [e.g., @button2013;  @ioannidis2005].
-On the other hand, an alternative viewpoint is that -- especially for studies that leverage social constructs -- exact replication may be difficult across contexts [@gilbert2016;@vanbavel2016].
+Many statistical factors leading to lowered replicability have been discussed in past work, including analytic flexibility, context dependency, publication bias, and low statistical power among others [e.g., @button2013; @vanbavel2016; @ioannidis2005].
 For both reasons of design and scale, our study here cannot disentangle these factors empirically.
-Nevertheless, the consistent decreases in effect size and evidential value we report seem consistent with a "winner's curse" -- that initial publications tend to over-estimate effects.
-However, in addition, although our sample was too small for statistical inference, numerically our results support replication fidelity in terms of sample and procedure as having some effects on success.
+Nevertheless, the decreases in effect size and evidential value we report seem consistent with two explanations.
+First, we likely saw a "winner's curse," with initial publications tending to over-estimate effects.
+Second, we also see evidnece that specific details of studies vary from context to context; creating successful adaptations can be challenging [@vanbavel2016].
+Both of these explain our observations, and we suspect both are present to some degree.
 
@@
 In our view, two recommendations will improve this situation dramatically.
-First, pre-registration typically requires the selection of one or a small number of statistical analyses to be designated as critical for interpretation.
+First, pre-registration typically requires the selection of particular statistical analyses to be designated as critical for interpretation.
 Were this information available, it would have simplified the problem of selecting effects to replicate in several cases.
@@
 Original data estimated from figures when not otherwise available.
-Replications are sorted and color coded by subjective replication success."}
+Replications are sorted by subjective replication success."}
   # colors:268bd2 859900 dc322f
@@
 # Add legend
-legend <- readPNG(paste0("../figures/Replication-Legend.png"))
+# legend <- readPNG(paste0("../figures/Replication-Legend.png"))
 
-plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=F)
-  rasterImage(legend, 0, 0, 100, 100, interpolate=FALSE)
+# plot(c(0, 100), c(0, 100), type = "n", xlab="", ylab="", axes=F)
+  # rasterImage(legend, 0, 0, 100, 100, interpolate=FALSE)
 ```
@@
 Our target was Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner, even controlling for age, education, and income in a linear model (there was also a manipulation of whether saving was incremental that did not result in an effect).
-We failed to find a significant relationship between the time metric manipulation and saving time.
+We failed to find a significant relationship between the time metric manipulation and saving time when including demographic controls (the key test we selected).
 However, when we did not include demographic controls, we did find a marginally-significant relationship.
@@
 an independent sample).
-Power analysis for this design was quite complex because the procedure had two stages: in a first stage participants generated descriptions and predicted judgments, while in a second stage a separate sample rated the descriptions.
+Power analysis for this design was complex because the procedure had two stages: In a first stage participants generated descriptions and predicted judgments, while in a second stage a separate sample rated the descriptions.
 
-We were faced with a choice: either we could have re-rated the descriptions gathered in the original study (by contacting the author and treating these as "materials" for the study), effectively replicating only stage two, or we could redo the entire two-step procedure.
+We were faced with a choice: Either we could have re-rated the descriptions gathered in the original study (by contacting the author and treating these as "materials" for the study), effectively replicating only stage two, or we could redo the entire two-step procedure.
 We elected to conduct a replication of the full procedure, but in our replication to decrease cost we focused on the liking judgments, which appeared to be central to the authors' conclusions.
 Our key test was the interaction of rater (writer vs.
-independent) and condition.^[We note that this project was submitted late and the student failed to preregister this analysis formally; however, the pre-written analysis protocol went through pre-data collection review by MCF.]  However, to power even this smaller study adequately was outside of our budget, so instead of having each judge rate a subset of 10 out of 100 total profiles, we collected a smaller sample of profiles (18) and had every profile rated by each judge.
+independent) and condition.^[We note that this project was submitted late and the student failed to preregister this analysis formally; however, the pre-written analysis protocol went through pre-data collection review.]  However, to power even this smaller study adequately was outside of our budget, so instead of having each judge rate a subset of 10 out of 100 total profiles, we collected a smaller sample of profiles (18) and had every profile rated by each judge.
 We failed to find the predicted interaction in this new sample.
-Instead, we found a main effect such that stage one participants predicted that raters would like them more than the stage two participants actually did.
+Consistent with the original report, though, we found a main effect such that stage one participants predicted that raters would like them more than the stage two participants actually did.
 Despite our relatively high statistical power in the main test, however, we may have suffered from low power at the item level due to the relatively small number of profiles we collected in the replication study.
@@
 In Experiment 1, our target, found that participants located targets faster when navigation involved persistence cues (via sliding animations) than when persistence was disrupted (via temporally matched fading animations).
+The original authors did not report training effects either within or across testing epochs (groups of 50 trials), so in our adaptation we decreased the length of the paradigm from four to two epochs.
+
 The key test for our replication was a simple *t*-test comparing speed to find the target in the two conditions (slide vs.
 fade), not controlling for learning across the duration of the experiment.
-We failed to find this overall difference.
-However, in an exploratory followup analysis using a linear mixed effect model, we did find a highly-significant effect of condition when controlling for learning epoch.
-We speculate that the very large effect found by the original authors may have led them to select a simpler analysis that did not control for learning effects.
-Our data -- which were more variable -- required this control.
+We failed to find this overall difference, but, in an exploratory followup analysis using a linear mixed effect model, we did find a highly-significant effect of condition when controlling for learning epoch.
+Our data may have been more variable for a number of reasons: unlike in the original paradigm, our participants were not required to click when they found targets; our stimuli differed slightly (images were different and featured thin black borders); and our participants differed in age and educational status from the undergraduates in the original study.
 
@@
 In Study 1, our target, faces of varying typicality were rated on their trustworthiness and attractiveness; while trustworthiness peaked at the most typical face, less typical faces were judged more attractive.
+The original sample was Israeli women, and typical faces were constructed to be typical for that sample.
+Rather than attempting to construct a typical face for AMT workers, we instead used the stimuli provided by the original authors, recognizing that this decision limits the interpretation of our findings.
+
 While the original class projects selected a global, item-wise regression model as the key statistical test of interest, the instructor team (post-data collection) determined that the fit of this model did not in fact correspond most closely with the authors' stated hypothesis.
@@
 Our replication study successfully showed this same interaction.^[We were unable to reproduce the numerical results from this model using the data from the original study, but we report the (larger) test statistics from our recomputed version.] We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face.
-Thus, despite replicating one key statistical test, our results are at odds with some of the original paper's claims.
+This result was plausibly caused by the difference in the typicality of the faces we used given our AMT participants.
 
@@
 We also may have observed a smaller effect size due to the relatively smaller amount of time our participants spent on the legacy prime writing exercise.
+We enforced a four minute writing time and a 20 word minimum; we found that most participants stayed relatively closer to these limits than participants in the original study.
 
@@
 # References
-
-<!-- # Supplemental -->
-
-<!-- All materials that are needed for class to implement -->
-<!-- Email templates -->
-<!-- Spreadsheets -->
-<!-- TA/prof auditing processes -->

### 2016-09-23 paper/paper.Rmd
removed footnote about reproducing sofer result

@@
 We thus selected the interaction between face typicality and rating condition as our key test statistic and used the more standard by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model.
-Our replication study successfully showed this same interaction.^[We were unable to reproduce the numerical results from this model using the data from the original study, but we report the (larger) test statistics from our recomputed version.] We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face.
+Our replication study successfully showed this same interaction.
+We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face.
 This result was plausibly caused by the difference in the typicality of the faces we used given our AMT participants.

### 2016-09-23 paper/paper.Rmd
eric suggestions

--- 2016-09-22 paper/paper.Rmd
@@
 
-In the current work, we do not address these challenges directly; instead, our goal is more modest.
+In the current work, we do not address these challenges; instead, our goal is more modest.
 We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings.
@@
 While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.
+As we discuss below, these replications may have different interpretations: While some are more direct replication, others differ on theoretically-relevant dimensions.
+Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing boundary conditions of a particular effect.
+Even in these cases, however, our work provides contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.
 
@@
 Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.
-
-In sum, we view the contribution of the current work to be two-fold.
-First, we provide a proof-of-concept and pedagogical model for conducting replications in the classroom.
-Second, we provide an initial estimate of what proportion of studies from the most recent volume of *Psychological Science* could be reproduced by a motivated student on a first attempt.
 
@@
 
+One of the barriers to more reproducible work in psychology is pedagogical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
+Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web experiments or literate, reproducible data analysis.
+Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
+This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environemnt -- students can quickly learn to use a reproducible toolset.
+
 Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.

### 2016-09-23 paper/paper.Rmd
eric changes typos

@@
 While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.
-As we discuss below, these replications may have different interpretations: While some are more direct replication, others differ on theoretically-relevant dimensions.
-Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing boundary conditions of a particular effect.
+As we discuss below, these replications may have different interpretations: While some are more direct replications, others differ on theoretically-relevant dimensions.
+Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly.
 Even in these cases, however, our work provides contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.

### 2016-09-23 paper/paper.Rmd
eric changes typos

@@
 Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly.
-Even in these cases, however, our work provides contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.
+Even in these cases, however, our work contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.
 

### 2016-09-23 paper/paper.Rmd
wang paper changes

@@
 In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups.
+Population differences provide one plausible explanation for the differences we found: Math performance was overall lower in our AMT sample than in the original undergraduate sample.
+It is possible that either the inverted U was undetectable given this lower level of performance, or that levels of motivation differed enough that the posited relationship did not hold.
 

### 2016-09-23 paper/paper.Rmd
spell check

@@
 We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.
-This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knwoledge.
+This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
 Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some results.
@@
 First, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see SOM for discussion of one particular paradigm that has been used more recently).
-Second, we suspected that asking this sort of question would lead to a large number of innaccurate responses.
+Second, we suspected that asking this sort of question would lead to a large number of inaccurate responses.
 
@@
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], as well as discrepencies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+This choice was motivated by recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], as well as discrepancies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 
@@
 Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
-This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environemnt -- students can quickly learn to use a reproducible toolset.
+This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
 
@@
 For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials [@liverence2015;@storm2015;@xu2015].
-In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample [@zaval015;@lewis2015;@scopelliti2015].
+In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample [@zaval2015;@lewis2015;@scopelliti2015].
 And in some, differences of population would mean that followups would require further stimulus or task adaptation [@sofer2015;@wang2015].
@@
 First, we likely saw a "winner's curse," with initial publications tending to over-estimate effects.
-Second, we also see evidnece that specific details of studies vary from context to context; creating successful adaptations can be challenging [@vanbavel2016].
+Second, we also see evidence that specific details of studies vary from context to context; creating successful adaptations can be challenging [@vanbavel2016].
 Both of these explain our observations, and we suspect both are present to some degree.
@@
 However, when we did not include demographic controls, we did find a marginally-significant relationship.
-In exploratory analyses, we also observed an un-predicted effect of income such that participants who reported higher income selected to start saving sooner.
+In exploratory analyses, we also observed an unpredicted effect of income such that participants who reported higher income selected to start saving sooner.
 

### 2016-09-23 paper/paper.Rmd
meeting changes

@@
 Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
-This work provides an estimate of the probability that a motivated graduate student can reproduce a previously published result on a first attempt, however, rather than a direct assessment of the truth of particular findings.
+This work documents the challenges facing motivated students in reproducing previously published results on a first attempt.
 We describe the workflow and pedagogical methods that were used in the class and discuss challenges both for the adoption of this pedagogical model and for replication research more broadly."
@@
 In the current article, we report the results of replication projects conducted in a single class (a graduate-level experimental methods course).
-As part of the required work of the course, students conducted high-power, direct replications of published articles from the 2015 volume of the journal *Psychological Science*.
+As part of the required work of the course, students conducted high-power replications of published articles from the 2015 volume of the journal *Psychological Science*.
 These studies both give evidence about the state of replicability in the field and provide insight into the challenges and promise of pedagogical replication.
@@
 
-In the current work, we do not address these challenges; instead, our goal is more modest.
-We assess the probability that a graduate student can choose an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproduce the findings.
+In the current work, we do not address these issues; instead, our goal is more modest.
+We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings.
 We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations.
 While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.
-As we discuss below, these replications may have different interpretations: While some are more direct replications, others differ on theoretically-relevant dimensions.
+But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions.
 Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly.
@@
   \hline
-
 Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & https://osf.io/uegk5/ \\ 
@@
 
-All projects were completed as part of a graduate-level methodology class (syllabus and materials available at [http://web.stanford.edu/class/psych254/2016/]()).
+All projects were completed as part of a graduate-level methodology class (syllabus and materials, as well as code and data for this paper, available at [https://osf.io/98ta4](https://osf.io/98ta4)).
 At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project.
@@
 Each sample was recruited independently, using the same account but a different title.
-All experiments were approved by the Stanford University institutional review board under protocol \#23274, "Reproducibility of psychological science and instruction."
+All experiments were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction."
 
@@
 The modal replication project in our sample was judged to be a "partial" replication, meaning that some aspects of the observed findings were different from those reported by the original authors.
-While this conclusion is somewhat dispiriting, it is also perhaps unsurprising given the complexity of the analyses reported in many of the original papers.
-In addition, `r sum(d$original_test=="interaction")` of the tests were interactions, which tend to have lower statistical power [@mcclelland1993] and have fared poorly in previous replication studies [@osc2015].
-
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
@@
 Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors.
-Note that the key statistic in the Sofer et al.
+Note that the key statistic in Sofer et al.
 (2015) replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed.
-Additionally, the original Bayes factor for Atir et al (2015) was many orders of magnitude greater than the others, so we displayed it at the edge of the range for visibility.", fig.pos="ht", fig.height=3.6}
+Additionally, the original Bayes factor for Atir et al.
+(2015) was many orders of magnitude greater than the others, so we displayed it at the edge of the range.", fig.pos="ht", fig.height=3.6}
 
@@
 
-In this paper, we reported the results of a series of 11 direct replications of previously-published experiments from the 2015 volume of *Psychological Science*.
+In this paper, we reported the results of a series of 11 student replications of previously-published experiments from the 2015 volume of *Psychological Science*.
 We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
-Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the probability that a finding -- selected on grounds of feasibility and interest -- would be replicated within the constraints of a course project.
+Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
+Despite this narrower scope, we believe that insights from our approach are applicable to the broader goal of assessing replicability at scale [cf.
+@osc2015]
 
@@
 Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
-But within these relatively stringent constraints, our group was able to produce a set of close replications with generally good statistical power.
+But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
 Thus, our work here shows what is possible for motivated students using freely-available tools and resources.

### 2016-09-23 paper/paper.Rmd
plot updates

@@
 Point size shows replication N (A) and ratio of test degrees of freedom (B), color indicates subjective replication assessments by the authors.
-Note that the key statistic in Sofer et al.
-(2015) replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed.
-Additionally, the original Bayes factor for Atir et al.
-(2015) was many orders of magnitude greater than the others, so we displayed it at the edge of the range.", fig.pos="ht", fig.height=3.6}
+Note that the key statistic for one replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed.
+Additionally, the original Bayes factor for another was many orders of magnitude greater than the others so it is not displayed.", fig.pos="ht", fig.height=3.6}
 
@@
 
-tstatDF$origBF[7] <- 1e+11
+# exclude atir
+tstatDF$origBF[7] <- NA
 
@@
                              col = replicated_TA_factor)) +
-  geom_abline(slope = 1, lty = 2) + 
-  geom_smooth(method = "lm", se=FALSE) +
-  # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
+  geom_smooth(method = "lm", se = FALSE) +
+  geom_abline(slope = 1, intercept = 0, linetype = 2) +
   xlab("Orig. Bayes Factor") + 

### 2016-09-23 paper/paper.Rmd
Change size legend vals

--- 2016-09-23 paper/paper.Rmd
@@
 Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments.
-Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3); it would have been somewhat surprising for our replications to show stronger evidence than the original.
+Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis is more than three times more likely than the null); it would have been somewhat surprising for our replications to show stronger evidence than the original.
 
@@
   theme_bw(base_size=10) + theme(legend.position="bottom") + 
-  scale_size_continuous(name = "rep. df/orig. df") + 
+    scale_size_continuous(breaks=c(.5, 2, 5),name = "rep. df/orig. df") + 
   scale_color_solarized(name = "Subj. rep. rating")

### 2016-09-23 project_analyses/smraposo.R
Un-color supplemental plot

@@ -152,8 +152,7 @@ ggplot(o_plot, aes(x=timeMetric, y = mean,fill = timeMetric)) +
   ggtitle("Lewis - Original") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none",
-        plot.title = element_text(color="#859900"))
+  theme(legend.position="none")
 
 ggsave("figures/smraposo-original.png",width = 1.5,height=1.5,units="in")
 
@@ -181,7 +180,6 @@ ggplot(d_plot, aes(x=timeMetric, y = mean,fill = timeMetric)) +
   ggtitle("Lewis - Replication") +
   theme_bw(base_size = 6) +
   scale_fill_grey(start=.4) +
-  theme(legend.position="none",
-        plot.title = element_text(color="#859900"))
+  theme(legend.position="none")
 
 ggsave("figures/smraposo-replication.png",width = 1.5,height=1.5,units="in")

### 2016-09-23 project_preprocessing.R

@@ -1,7 +1,7 @@
-
 library(dplyr)
 library(readr)
 library(tidyr)
+library(ggplot2)
 
 project_plan <- read_csv("data/planning_and_outcomes.csv")
 

### 2016-09-23 paper/paper.Rmd
Fix legend order
Compile large SOM plot

--- 2016-09-23 paper/paper.Rmd
@@
 Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments.
-Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis is more than three times more likely than the null); it would have been somewhat surprising for our replications to show stronger evidence than the original.
+Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3); it would have been somewhat surprising for our replications to show stronger evidence than the original.
 
@@
   theme_bw(base_size=10) + theme(legend.position="bottom") + 
-    scale_size_continuous(breaks=c(.5, 2, 5),name = "rep. df/orig. df") + 
+  scale_size_continuous(name = "rep. df/orig. df") + 
   scale_color_solarized(name = "Subj. rep. rating")
@@
 Error bars show standard error of the mean.
-Original data estimated from figures when not otherwise available.
-Replications are sorted by subjective replication success."}
+Original data estimated from figures when not otherwise available."}
   # colors:268bd2 859900 dc322f
@@
 layout(matrix(1:24,nr=6,byr=T))
-project_key_sorted <- c(
-  "jsalloum","ehermann","salehi", # rep = 1
-  "mkeil","smraposo","jedtan","rhiac","lampinen", # rep=.5
-  "jreynolds","jmarias","auc" #rep = 0
-)
+project_key_sorted <- c("ehermann", "jsalloum", "smraposo", "jedtan", "salehi", "jreynolds","auc","mkeil","jmarias","lampinen","rhiac") #alphabetical by author
+
 for (key in project_key_sorted) {

### 2016-09-23 paper/paper.Rmd
Merge remote-tracking branch 'origin/master'
# Conflicts:
#	paper/paper.pdf

--- 2016-09-23 paper/paper.Rmd
@@
   scale_size_continuous(breaks=c(.5, 2, 5),name = "rep. df/orig. df") + 
-  scale_color_solarized(name = "Subj. rep. rating")
+  scale_color_solarized(name = "Subj. rep. rating") +
+  guides(size=guide_legend(order = 1), 
+         color=guide_legend(order = 2))
 

### 2016-09-23 paper/paper.Rmd
minor tweaks plus update of spreadsheet to match table

--- 2016-09-23 paper/paper.Rmd
@@
 At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
+All planned analyses were specified on the basis of the key test selected in the original article, and included all exclusion criteria, manipulation checks, etc.
+specified by the authors.
 The goal of this code review was to ensure that all planned analyses were specified correctly and with sufficient detail to permit inclusion in the broader analysis.
@@
 
-Statistically, however, our results were underwhelming.
+From a purely statistical point of view, our results were underwhelming.
 Despite our relatively close adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
@@
 This set of features -- which, in our experience, are endemic to published psychological work, including our own -- makes replication research within the conventional statistical paradigm extremely challenging.
+
 In our view, two recommendations will improve this situation dramatically.
@@
 This paper investigated motivations to save for retirement, and specifically whether changing participants' relationships to the future (making it feel more imminent) would lead them to report that they would begin saving for retirement sooner.
-Our target was Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner, even controlling for age, education, and income in a linear model (there was also a manipulation of whether saving was incremental that did not result in an effect).
-We failed to find a significant relationship between the time metric manipulation and saving time when including demographic controls (the key test we selected).
+Our target was Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner.
+The original reported this analysis both with and without demographic controls.
+We chose as our key analysis the version of this regression which controlled for age, education, and income (there was also a manipulation of whether saving was incremental that did not result in an effect).
+
+We failed to find a significant relationship between the time metric manipulation and saving time when including demographic controls.
 However, when we did not include demographic controls, we did find a marginally-significant relationship.
@@
 independent) and condition.^[We note that this project was submitted late and the student failed to preregister this analysis formally; however, the pre-written analysis protocol went through pre-data collection review.]  However, to power even this smaller study adequately was outside of our budget, so instead of having each judge rate a subset of 10 out of 100 total profiles, we collected a smaller sample of profiles (18) and had every profile rated by each judge.
+
 We failed to find the predicted interaction in this new sample.
@@
 Despite our relatively high statistical power in the main test, however, we may have suffered from low power at the item level due to the relatively small number of profiles we collected in the replication study.
+In addition, a small number of profile writers produced language in a manipulation check suggesting that the maximize interest manipulation had not succeeded fully, but since there was no specified exclusion criterion in the original study, we included these participants.
 

### 2016-09-23 paper/paper.Rmd
capitalize legend

--- 2016-09-23 paper/paper.Rmd
@@
   theme_bw(base_size=10) + theme(legend.position="bottom") + 
-  scale_size_continuous(breaks=c(.5, 2, 5),name = "rep. df/orig. df") + 
+  scale_size_continuous(breaks=c(.5, 2, 5),name = "Rep. df/Orig. df") + 
   scale_color_solarized(name = "Subj. rep. rating") +
@@
 Error bars show standard error of the mean.
-Original data estimated from figures when not otherwise available."}
+Original data estimated from figures when not otherwise available.
+Replications are sorted by subjective replication success."}
   # colors:268bd2 859900 dc322f
@@
 layout(matrix(1:24,nr=6,byr=T))
-project_key_sorted <- c("ehermann", "jsalloum", "smraposo", "jedtan", "salehi", "jreynolds","auc","mkeil","jmarias","lampinen","rhiac") #alphabetical by author
-
+project_key_sorted <- c(
+  "jsalloum","ehermann","salehi", # rep = 1
+  "mkeil","smraposo","jedtan","rhiac","lampinen", # rep=.5
+  "jreynolds","jmarias","auc" #rep = 0
+)
 for (key in project_key_sorted) {

### 2016-09-23 paper/paper.Rmd
removed direct from replications

--- 2016-09-23 paper/paper.Rmd
@@
     "Replications are important to science, but who will do them?
-One proposal is that students can conduct direct replications as part of their training.
-As a proof-of-concept for this idea, here we report a series of 11 pre-registered, direct replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
+One proposal is that students can conduct replications as part of their training.
+As a proof-of-concept for this idea, here we report a series of 11 pre-registered replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
 Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
@@
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
-Yet under the current incentive structure for science, direct replication is not typically valued.
-One potential solution to this problem is to make direct replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
+Yet under the current incentive structure for science, replication is not typically valued.
+One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
 Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.
@@
 
-We also describe our process for conducting well-powered, high-quality, direct replications as part of classroom pedagogy.
+We also describe our process for conducting replications as part of classroom pedagogy.
 Although mentorship in specific experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
@@
 
-## Storm & Stone (2015)
+## Atir, Rosenzweig, & Dunning (2015)
 
-This paper found that when participants had the opportunity to save a file containing a list of target words before studying another file, they retained more information from the second study session.
-Our target for replication was Experiment 3, in which the effect was found to depend on the amount of information that was studied in the first file, with a greater effect for an eight-word list than a two-word list.
-The key statistical test we selected was the interaction in a 2x2 mixed-design ANOVA (save vs.
-no-save condition and two- vs.
-eight-word condition).
-The replication study failed to find evidence of the interaction, but ironically this failure was because of a main effect of save condition: The authors' key manipulation succeeded for both load conditions.
-Perhaps even two words was sufficient to create interference for our online sample.
+This paper investigated how perceived knowledge affects "overclaiming" (claiming knowledge that you do not have).
+We targeted Study 1b, which asked participants to rate their knowledge about finances, and then asked them to rate their knowledge about a set of financial terms, some of which were invented (and hence for which a positive knowledge statement would necessarily be an overclaim).
+The original study found that participants with higher self-rated financial knowledge also overclaimed at a higher rate.
+The key test statistic for this study was the coefficient in a regression model predicting overclaiming as a function of claimed personal financial knowledge, controlling for accuracy in the true financial knowledge questions.
+We successfully replicated this effect, despite our use of a much smaller sample (due to the extremely high post-hoc power of the original study).
+
+## Ko, Sadler, & Galinksy (2015)
+
+This paper investigated vocal cues to social hierarchy.
+Our target for replication was Experiment 2, which assessed whether participants used particular acoustic cues to make inferences about speakers' level of social hierarchy, particularly that participants from the high-rank condition in Experiment 1 were rated as more highly ranking.
+This paper employed a two-stage procedure in which participant-generated materials were rated by an independent sample.
+However, in contrast to the study of Scopelliti, Lowenstein & Vosgerau (2015), because materials were collected in Experiment 1 and were available openly, we elected to replicate only Experiment 2, the judgment study.
+The key test statistic was the main effect of hierarchy condition on "behavior score" (an index of whether speakers would engage in high-status behaviors).
+The authors were also interested in which particular vocal cues predicted participants judgments, but we judged these analyses to be more descriptive and exploratory.
+We successfully replicated the main effect of condition on hierarchy judgment, and additionally found a comparable main effect of speaker gender.
 
@@
 In exploratory analyses, we also observed an unpredicted effect of income such that participants who reported higher income selected to start saving sooner.
+
+## Liverence & Scholl (2015)
+
+This paper tested the theory that persistent object representations could assist in spatial navigation, using a navigation paradigm in which participants used key presses to move though a grid of pictures that were visible only one at a time.
+In Experiment 1, our target, found that participants located targets faster when navigation involved persistence cues (via sliding animations) than when persistence was disrupted (via temporally matched fading animations).
+The original authors did not report training effects either within or across testing epochs (groups of 50 trials), so in our adaptation we decreased the length of the paradigm from four to two epochs.
+
+The key test for our replication was a simple *t*-test comparing speed to find the target in the two conditions (slide vs.
+fade), not controlling for learning across the duration of the experiment.
+We failed to find this overall difference, but, in an exploratory followup analysis using a linear mixed effect model, we did find a highly-significant effect of condition when controlling for learning epoch.
+Our data may have been more variable for a number of reasons: unlike in the original paradigm, our participants were not required to click when they found targets; our stimuli differed slightly (images were different and featured thin black borders); and our participants differed in age and educational status from the undergraduates in the original study.
+
+## Proudfoot, Kay, & Koval (2015)
+
+This paper examined whether judgments of creativity are influenced by the gender of the creator.
+In Study 1, they tested the hypothesis that "out of the box" creativity was more associated with masculine traits than feminine traits by manipulating the definition of creativity that participants saw (convergent vs.
+divergent) and asking participants to judge the centrality of different traits to that definition.
+The original pre-registration selected a subsidiary analysis of a main effect as the key test statistic, but in post-data collection review the instructor team decided that a test of the interaction between trait gender and definition condition was closer to the central theoretical claim of the paper; we use this latter test as the key test statistic.
+Our replication study found an significant interaction of similar magnitude.
 
@@
 
-## Liverence & Scholl (2015)
-
-This paper tested the theory that persistent object representations could assist in spatial navigation, using a navigation paradigm in which participants used key presses to move though a grid of pictures that were visible only one at a time.
-In Experiment 1, our target, found that participants located targets faster when navigation involved persistence cues (via sliding animations) than when persistence was disrupted (via temporally matched fading animations).
-The original authors did not report training effects either within or across testing epochs (groups of 50 trials), so in our adaptation we decreased the length of the paradigm from four to two epochs.
-
-The key test for our replication was a simple *t*-test comparing speed to find the target in the two conditions (slide vs.
-fade), not controlling for learning across the duration of the experiment.
-We failed to find this overall difference, but, in an exploratory followup analysis using a linear mixed effect model, we did find a highly-significant effect of condition when controlling for learning epoch.
-Our data may have been more variable for a number of reasons: unlike in the original paradigm, our participants were not required to click when they found targets; our stimuli differed slightly (images were different and featured thin black borders); and our participants differed in age and educational status from the undergraduates in the original study.
-
-## Wang et al. (2015)
-
-This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among college undergraduate students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation.
-We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiety and completed a math task to measure performance.
-The key effect we targeted was the interaction of math anxiety squared and math motivation in predicting performance.
-We failed to find evidence for this effect.
-In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups.
-Population differences provide one plausible explanation for the differences we found: Math performance was overall lower in our AMT sample than in the original undergraduate sample.
-It is possible that either the inverted U was undetectable given this lower level of performance, or that levels of motivation differed enough that the posited relationship did not hold.
-
 ## Sofer et al. (2015)
@@
 
-## Ko, Sadler, & Galinksy (2015)
+## Storm & Stone (2015)
 
-This paper investigated vocal cues to social hierarchy.
-Our target for replication was Experiment 2, which assessed whether participants used particular acoustic cues to make inferences about speakers' level of social hierarchy, particularly that participants from the high-rank condition in Experiment 1 were rated as more highly ranking.
-This paper employed a two-stage procedure in which participant-generated materials were rated by an independent sample.
-However, in contrast to the study of Scopelliti, Lowenstein & Vosgerau (2015), because materials were collected in Experiment 1 and were available openly, we elected to replicate only Experiment 2, the judgment study.
-The key test statistic was the main effect of hierarchy condition on "behavior score" (an index of whether speakers would engage in high-status behaviors).
-The authors were also interested in which particular vocal cues predicted participants judgments, but we judged these analyses to be more descriptive and exploratory.
-We successfully replicated the main effect of condition on hierarchy judgment, and additionally found a comparable main effect of speaker gender.
+This paper found that when participants had the opportunity to save a file containing a list of target words before studying another file, they retained more information from the second study session.
+Our target for replication was Experiment 3, in which the effect was found to depend on the amount of information that was studied in the first file, with a greater effect for an eight-word list than a two-word list.
+The key statistical test we selected was the interaction in a 2x2 mixed-design ANOVA (save vs.
+no-save condition and two- vs.
+eight-word condition).
+The replication study failed to find evidence of the interaction, but ironically this failure was because of a main effect of save condition: The authors' key manipulation succeeded for both load conditions.
+Perhaps even two words was sufficient to create interference for our online sample.
 
-## Atir, Rosenzweig, & Dunning (2015)
+## Wang et al. (2015)
 
-This paper investigated how perceived knowledge affects "overclaiming" (claiming knowledge that you do not have).
-We targeted Study 1b, which asked participants to rate their knowledge about finances, and then asked them to rate their knowledge about a set of financial terms, some of which were invented (and hence for which a positive knowledge statement would necessarily be an overclaim).
-The original study found that participants with higher self-rated financial knowledge also overclaimed at a higher rate.
-The key test statistic for this study was the coefficient in a regression model predicting overclaiming as a function of claimed personal financial knowledge, controlling for accuracy in the true financial knowledge questions.
-We successfully replicated this effect, despite our use of a much smaller sample (due to the extremely high post-hoc power of the original study).
+This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among college undergraduate students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation.
+We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiety and completed a math task to measure performance.
+The key effect we targeted was the interaction of math anxiety squared and math motivation in predicting performance.
+We failed to find evidence for this effect.
+In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups.
+Population differences provide one plausible explanation for the differences we found: Math performance was overall lower in our AMT sample than in the original undergraduate sample.
+It is possible that either the inverted U was undetectable given this lower level of performance, or that levels of motivation differed enough that the posited relationship did not hold.
 
-## Proudfoot, Kay, & Koval (2015)
+## Xu & Franconeri (2015)
 
-This paper examined whether judgments of creativity are influenced by the gender of the creator.
-In Study 1, they tested the hypothesis that "out of the box" creativity was more associated with masculine traits than feminine traits by manipulating the definition of creativity that participants saw (convergent vs.
-divergent) and asking participants to judge the centrality of different traits to that definition.
-The original pre-registration selected a subsidiary analysis of a main effect as the key test statistic, but in post-data collection review the instructor team decided that a test of the interaction between trait gender and definition condition was closer to the central theoretical claim of the paper; we use this latter test as the key test statistic.
-Our replication study found an significant interaction of similar magnitude.
+This paper explored constraints on visual working memory in the context of mental rotation.
+In Experiment 1a, participants performed a verbal suppression task to control for use of verbal encoding while attempting to remember a cross with four colored bars, which sometimes switched colors; performing mental rotation significantly impaired ability to detect these bar swaps.
+To port the task to an online framework we decreased the number of trials and increased the number of participants we tested.
+The key test statistic was a comparison of K (a metric of the number of visual features remembered) between the rotation and no-rotation conditions.
+We observed a marginally-significant effect in our replication study.
+Our study showed a floor effect on capacity such that participants remembered on average very little; it is possible that small details in the displays (or the differing sample available online) led to this floor effect.
 
@@
 
-## Xu & Franconeri (2015)
-
-This paper explored constraints on visual working memory in the context of mental rotation.
-In Experiment 1a, participants performed a verbal suppression task to control for use of verbal encoding while attempting to remember a cross with four colored bars, which sometimes switched colors; performing mental rotation significantly impaired ability to detect these bar swaps.
-To port the task to an online framework we decreased the number of trials and increased the number of participants we tested.
-The key test statistic was a comparison of K (a metric of the number of visual features remembered) between the rotation and no-rotation conditions.
-We observed a marginally-significant effect in our replication study.
-Our study showed a floor effect on capacity such that participants remembered on average very little; it is possible that small details in the displays (or the differing sample available online) led to this floor effect.
-
 # References

### 2016-09-23 paper/paper.Rmd
remove https:// from table

--- 2016-09-23 paper/paper.Rmd
@@
   \hline
-Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & https://osf.io/uegk5/ \\ 
-Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & https://osf.io/g6k2u/\\ 
-Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & https://osf.io/rdw6e/ \\ 
-Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & https://osf.io/sfxrb/ \\ 
-Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & https://osf.io/ne8ph/ \\ 
-Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & https://osf.io/32wsm/ \\ 
-Sofer et al. & 1 & No & Yes & No & 48 & Other &  95 & 4.33 & https://osf.io/5wmhn/ \\ 
-Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & https://osf.io/9cgpq/ \\ 
-Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & https://osf.io/ng96w/ \\ 
-Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & https://osf.io/cgvzs/ \\ 
-Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & https://osf.io/degwa/ \\ 
+Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & osf.io/uegk5/ \\ 
+Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & osf.io/g6k2u/\\ 
+Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & osf.io/rdw6e/ \\ 
+Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & osf.io/sfxrb/ \\ 
+Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & osf.io/ne8ph/ \\ 
+Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
+Sofer et al. & 1 & No & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
+Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
+Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & osf.io/ng96w/ \\ 
+Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & osf.io/cgvzs/ \\ 
+Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & osf.io/degwa/ \\ 
    \hline

### 2016-09-23 paper/paper.Rmd
further line edits

--- 2016-09-23 paper/paper.Rmd
@@
 This work documents the challenges facing motivated students in reproducing previously published results on a first attempt.
-We describe the workflow and pedagogical methods that were used in the class and discuss challenges both for the adoption of this pedagogical model and for replication research more broadly."
+We describe the workflow and pedagogical methods that were used in the class and discuss implications both for the adoption of this pedagogical model and for replication research more broadly."
 
@@
 In the current article, we report the results of replication projects conducted in a single class (a graduate-level experimental methods course).
-As part of the required work of the course, students conducted high-power replications of published articles from the 2015 volume of the journal *Psychological Science*.
-These studies both give evidence about the state of replicability in the field and provide insight into the challenges and promise of pedagogical replication.
+As part of the required work of the course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*.
+These studies give evidence about the state of replicability in the field.
+They also provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.
 
@@
 Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality.
-Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014].
+Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014;@wagenmakers2016].
 
@@
 Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly.
-Even in these cases, however, our work contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.
+Even in these cases, however, replication research of the type we conduct here contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.
 
 We also describe our process for conducting replications as part of classroom pedagogy.
-Although mentorship in specific experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
-And replication research specifically illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- in a way that more open-ended projects, which require new conceptual development, often do not [see @frank2012 for a more extended argument].
-There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise, and we return to these in the Discussion.
+Although mentorship in experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
+And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- in a way that more open-ended projects, which require new conceptual development, often do not [see @frank2012 for a more extended argument].
+There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise.
 Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.

### 2016-09-23 paper/paper.Rmd
Small wording changes

--- 2016-09-23 paper/paper.Rmd
@@
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
-We are grateful to the authors of the original studies for both providing materials and for their comments on a draft of this manuscript."
+We are grateful to the authors of the original studies who provided materials and gave comments on a draft of this manuscript."
 
@@
   \hline
-Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & osf.io/uegk5/ \\ 
-Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & osf.io/g6k2u/\\ 
-Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & osf.io/rdw6e/ \\ 
-Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & osf.io/sfxrb/ \\ 
-Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & osf.io/ne8ph/ \\ 
-Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
-Sofer et al. & 1 & No & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
-Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
-Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & osf.io/ng96w/ \\ 
-Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & osf.io/cgvzs/ \\ 
-Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & osf.io/degwa/ \\ 
+Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & https://osf.io/uegk5/ \\ 
+Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & https://osf.io/g6k2u/\\ 
+Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & https://osf.io/rdw6e/ \\ 
+Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & https://osf.io/sfxrb/ \\ 
+Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & https://osf.io/ne8ph/ \\ 
+Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & https://osf.io/32wsm/ \\ 
+Sofer et al. & 1 & No & Yes & No & 48 & Other &  95 & 4.33 & https://osf.io/5wmhn/ \\ 
+Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & https://osf.io/9cgpq/ \\ 
+Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & https://osf.io/ng96w/ \\ 
+Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & https://osf.io/cgvzs/ \\ 
+Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & https://osf.io/degwa/ \\ 
    \hline
@@
 Repeat administration of experiments on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
-We did not ask participants whether they had participated in similar research previously, however.
-First, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see SOM for discussion of one particular paradigm that has been used more recently).
-Second, we suspected that asking this sort of question would lead to a large number of inaccurate responses.
+We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses.
+In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see SOM for discussion of one particular paradigm that has been used more recently).
 
@@
 
-We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
-For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved desired power if some participants skipped through or did not complete the experiment.
-^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
-In three cases, we powered the replication attempt to 80\% post-hoc power. In four
+We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved desired power if some participants skipped through or did not complete the experiment.
+In three cases, we powered the replication attempt to 80\% post-hoc power.
+In four
 cases, we used the original sample size.
@@
 Since our sample only includes 11 studies, we describe general trends here rather than attempting to conduct statistical tests (which would be dramatically under-powered after correcting for multiple comparisons).
-Overall, projects had a slightly larger probability of being judged successful if they were judged to be closer to the original (`r 100 * round(mean(d$replicated_TA[d$high_fidelity == TRUE]), digits=2)`\%
+Overall, projects had a slightly larger probability of being judged successful if they were judged to be closer to the original (above the median subjective rating; `r 100 * round(mean(d$replicated_TA[d$high_fidelity == TRUE]), digits=2)`\%
 vs. 
@@
 The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961].
-Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016;@wagenmakers2016].
+Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* a hypothesis [see also @scheibehenne2016;@wagenmakers2016].
 While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
@@
 Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments.
-Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis is more than three times more likely than the null); it would have been somewhat surprising for our replications to show stronger evidence than the original.
+Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis is less than three times more likely than the null).
 
@@
 In this paper, we reported the results of a series of 11 student replications of previously-published experiments from the 2015 volume of *Psychological Science*.
-We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
+We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate recent findings in a top journal.
 Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.

### 2016-09-23 paper/paper.Rmd
main text final pass

--- 2016-09-23 paper/paper.Rmd
@@
 Although mentorship in experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
-And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- in a way that more open-ended projects, which require new conceptual development, often do not [see @frank2012 for a more extended argument].
+And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- more directly than open-ended projects, which require new conceptual development [see @frank2012 for extended argument].
 There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise.
@@
 Students chose findings from a wide variety of domains for replication.
-One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transition between locations on smartphone apps [@liverence2015].
-A second cluster came from studies of social perception and judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
+One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transitions between locations on smartphone apps [@liverence2015].
+A second cluster came from studies of social perception and social judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
 Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
@@
 We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
-For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved desired power if some participants skipped through or did not complete the experiment.
+For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the experiment.
 ^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
 We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
-In three cases, we powered the replication attempt to 80\% post-hoc power. In four
+In four cases, we powered the replication attempt to 80\% post-hoc power. In four
 cases, we used the original sample size.
@@
 
-All materials and methods for our replication studies are available at [https://github.com/StanfordPsych254]().
 All experiments were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
@@
 Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g., statistical tests and figures).
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single platform.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [which appear to be regrettably common; @nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.
 
@@
 
-Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from Mechanical Turk.
+Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from AMT.
 The goal of this pilot was to ensure that participants were able to complete the experiment and did not report any substantial issues with instructions or technical details of the experiment.
-(All students were instructed to give participants a way to leave free-form comments at the end of the experiment but prior to debriefing).
+(All students were instructed to give participants a way to leave free-form comments at the end of the experiment, prior to debriefing).
 At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
-All planned analyses were specified on the basis of the key test selected in the original article, and included all exclusion criteria, manipulation checks, etc.
-specified by the authors.
-The goal of this code review was to ensure that all planned analyses were specified correctly and with sufficient detail to permit inclusion in the broader analysis.
+The goal of this code review was to ensure that all planned analyses were specified for the key test selected in the original article, and that all relevant exclusion criteria, manipulation checks, etc.
+specified by the original authors were implemented correctly.
 
@@
 Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.
-In addition, prior to data collection, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).
+In addition, prior to data collection for all projects, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).
 
@@
 
-Of the 15 students in the class, all completed projects (two with extensions going beyond the class period), one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
-Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations and materials to the final product.
+All of the 15 students in the class completed projects (two with extensions going beyond the class period).
+Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
+Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations, and materials to the final product.
 (In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review.
@@
 We coded projects independently on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), and then discussed our ratings and made adjustments (without coming to full consensus).
-The mean rating was `r round(mean(d$fidelity), digits = 2)` (Range = `r round(min(d$fidelity), digits = 2)` to `r round(max(d$fidelity), digits = 2)`).
-Several studies were essentially identical to the originals, but there was a group of others that included differences in population or number of trials that might plausibly have had an effect on the results.
+The mean rating was `r round(mean(d$fidelity), digits = 2)` (range: `r round(min(d$fidelity), digits = 2)` -- `r round(max(d$fidelity), digits = 2)`).
+Several studies were essentially identical to the originals, but there was a group of others that included differences in population, number of trials, or method that might plausibly have had an effect on the results.
 
@@
 We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level.
-Only `r sum(d$rep_p_value_05)` of the studies yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication p-value may not be informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+Only `r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value.
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
 
@@
 The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes (assuming a constant experimental procedure, of course) and allows for a more fine-grained comparison across studies than a binary significance criterion.
-The Bayes Factor is an alternative hypothesis testing method that quantifies the *evidence* in favor of a hypothesis [@jeffreys1961].
-Among other advantages, it does not privilege the null hypothesis and can provide evidence either *for* or *against* [see also @scheibehenne2016;@wagenmakers2016].
+The Bayes Factor is an alternative hypothesis testing method that quantifies the evidence in favor of a hypothesis [@jeffreys1961].
+Among other advantages, it does not privilege the null hypothesis and can provide evidence either for or against [see also @scheibehenne2016;@wagenmakers2016].
 While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
@@
 These additional measures therefore give another sense in which replications can be successful: If we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we should increase our confidence in the effect's replicability.
-To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
-Other formulae are given in @osc2015, Supplemental Information.].
-We first compared effect sizes from the original and replication studies (Figure 2A).
+To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1.^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
+Other formulae are given in @osc2015, Supplemental Information.] We first compared effect sizes from the original and replication studies (Figure 2A).
 Effect sizes were highly correlated between the two sets of studies
@@
 While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
-This choice was motivated by recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], as well as discrepancies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
+This choice was motivated by the lack of consensus on how to conduct such a test [@anderson2016;@gilbert2016], recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], and discrepancies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 
@@
 Note that the key statistic for one replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed.
-Additionally, the original Bayes factor for another was many orders of magnitude greater than the others so it is not displayed.", fig.pos="ht", fig.height=3.6}
+Additionally, the original Bayes factor for oen finding was many orders of magnitude greater than the others so it is not displayed.", fig.pos="ht", fig.height=3.6}
 
@@
 
-In this paper, we reported the results of a series of 11 student replications of previously-published experiments from the 2015 volume of *Psychological Science*.
+In this paper, we reported a series of 11 student replications of previously-published experiments from the 2015 volume of *Psychological Science*.
 We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
-Importantly, rather than attempting to assess the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
-Despite this narrower scope, we believe that insights from our approach are applicable to the broader goal of assessing replicability at scale [cf.
-@osc2015]
+Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
+Despite this narrower scope, we believe that insights from our approach are applicable to the broader goal of assessing replicability at scale.
+
+Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
+Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
+Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
 
@@
 
-Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
-But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
-Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
-Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
-
-From a purely statistical point of view, our results were underwhelming.
+From a purely statistical point of view, though, our results were underwhelming.
 Despite our relatively close adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
@@
 These statistical findings mask a more optimistic message, however: In most of our projects, the next step for a motivated experimenter is clear.
-For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials [@liverence2015;@storm2015;@xu2015].
-In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample [@zaval2015;@lewis2015;@scopelliti2015].
-And in some, differences of population would mean that followups would require further stimulus or task adaptation [@sofer2015;@wang2015].
+For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials.
+In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample.
+And in some, differences of population would mean that followups would require further stimulus or task adaptation.
 More generally, we believe that our work here underscores the importance of iterated replication [@lewis2016].
@@
 First, we likely saw a "winner's curse," with initial publications tending to over-estimate effects.
-Second, we also see evidence that specific details of studies vary from context to context; creating successful adaptations can be challenging [@vanbavel2016].
-Both of these explain our observations, and we suspect both are present to some degree.
+Second, we also might have seen a reduction in effect size because the original studies were tailored to their specific context and population, whereas our replications may not have been [@vanbavel2016].
+Both of these explain our observations, and we suspect both effects are present to some degree.
 
@@
 
-Indeed, by the standards of clinical trials research, nearly every study we replicated in this report would be classified as exploratory research.
-No protocol was pre-registered, and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
+Indeed, no experiment we attempted to replicate was pre-registered (though some were internal replications), and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
 Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications.

### 2016-09-23 paper/paper.Rmd

@@
 
-We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.
-For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the experiment.
-^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.]
-In four cases, we powered the replication attempt to 80\% post-hoc power. In four
-cases, we used the original sample size.
+We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the experiment.
+In four cases, we powered the replication attempt to 80\% post-hoc power.
+In four cases, we used the original sample size.
 In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
@@
 The Bayes Factor is an alternative hypothesis testing method that quantifies the evidence in favor of a hypothesis [@jeffreys1961].
-Among other advantages, it does not privilege the null hypothesis and can provide evidence either for or against [see also @scheibehenne2016;@wagenmakers2016].
+Among other advantages, it does not privilege the null hypothesis and can provide evidence either for or against a hypothesis [see also @scheibehenne2016;@wagenmakers2016].
 While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
@@
 In this paper, we reported a series of 11 student replications of previously-published experiments from the 2015 volume of *Psychological Science*.
-We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students replicate important, recent findings in a top journal.
+We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students to replicate recent findings in a top journal.
 Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.

### 2016-09-24 paper/paper.Rmd
SOM edits

@@
 
-For each project, we present a summary of the finding, the key statistical test, and the impressionistic outcomes of the replication.
+For each project, we present a summary of the finding, the key statistical test, the impressionistic outcomes of the replication, and -- where applicable -- our assessement of the source of differences in results (often composed with the advice of the original authors).
 Figure 3 shows a side-by-side comparison of the key visualization for each study.
@@
 This paper investigated how perceived knowledge affects "overclaiming" (claiming knowledge that you do not have).
-We targeted Study 1b, which asked participants to rate their knowledge about finances, and then asked them to rate their knowledge about a set of financial terms, some of which were invented (and hence for which a positive knowledge statement would necessarily be an overclaim).
+We replicated Study 1b, which asked participants to rate their knowledge about finances, and then asked them to rate their knowledge about a set of financial terms, some of which were invented (and hence for which a positive knowledge statement would necessarily be an overclaim).
 The original study found that participants with higher self-rated financial knowledge also overclaimed at a higher rate.
@@
 This paper employed a two-stage procedure in which participant-generated materials were rated by an independent sample.
-However, in contrast to the study of Scopelliti, Lowenstein & Vosgerau (2015), because materials were collected in Experiment 1 and were available openly, we elected to replicate only Experiment 2, the judgment study.
+However -- in contrast to the study of Scopelliti, Lowenstein & Vosgerau (2015), see below -- because materials were collected in Experiment 1 (and were available for reuse), we elected to replicate only Experiment 2, the judgment study.
 The key test statistic was the main effect of hierarchy condition on "behavior score" (an index of whether speakers would engage in high-status behaviors).
@@
 This paper investigated motivations to save for retirement, and specifically whether changing participants' relationships to the future (making it feel more imminent) would lead them to report that they would begin saving for retirement sooner.
-Our target was Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner.
+We replicated Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner.
 The original reported this analysis both with and without demographic controls.
@@
 We failed to find a significant relationship between the time metric manipulation and saving time when including demographic controls.
-However, when we did not include demographic controls, we did find a marginally-significant relationship.
+However, when we did not include demographic controls, we found a marginally-significant relationship.
 In exploratory analyses, we also observed an unpredicted effect of income such that participants who reported higher income selected to start saving sooner.
@@
 This paper tested the theory that persistent object representations could assist in spatial navigation, using a navigation paradigm in which participants used key presses to move though a grid of pictures that were visible only one at a time.
-In Experiment 1, our target, found that participants located targets faster when navigation involved persistence cues (via sliding animations) than when persistence was disrupted (via temporally matched fading animations).
+Experiment 1, our target for replication, found that participants located targets faster when navigation involved persistence cues (via sliding animations) than when persistence was disrupted (via temporally-matched fading animations).
 The original authors did not report training effects either within or across testing epochs (groups of 50 trials), so in our adaptation we decreased the length of the paradigm from four to two epochs.
@@
 fade), not controlling for learning across the duration of the experiment.
-We failed to find this overall difference, but, in an exploratory followup analysis using a linear mixed effect model, we did find a highly-significant effect of condition when controlling for learning epoch.
-Our data may have been more variable for a number of reasons: unlike in the original paradigm, our participants were not required to click when they found targets; our stimuli differed slightly (images were different and featured thin black borders); and our participants differed in age and educational status from the undergraduates in the original study.
+We failed to find this overall difference.
+In an exploratory followup analysis using a linear mixed effects model, however, we did find a highly-significant effect of condition (when controlling for learning epoch).
+Our data may have been more variable for a number of reasons: unlike in the original paradigm, our participants were not required to click when they found targets; our stimuli differed slightly (the images were different and featured thin black borders); and our participants differed in age and educational status from the undergraduates in the original study.
 
@@
 This paper examined whether judgments of creativity are influenced by the gender of the creator.
-In Study 1, they tested the hypothesis that "out of the box" creativity was more associated with masculine traits than feminine traits by manipulating the definition of creativity that participants saw (convergent vs.
+In Study 1, our replication target, they tested the hypothesis that "out of the box" creativity was more associated with masculine traits than feminine traits by manipulating the definition of creativity that participants saw (convergent vs.
 divergent) and asking participants to judge the centrality of different traits to that definition.
-The original pre-registration selected a subsidiary analysis of a main effect as the key test statistic, but in post-data collection review the instructor team decided that a test of the interaction between trait gender and definition condition was closer to the central theoretical claim of the paper; we use this latter test as the key test statistic.
+The original pre-registration of our replication selected a secondary analysis as the key test statistic (an ANOVA over two of the four cells), but in post-data collection review the instructor team decided that a test of the interaction between trait gender and definition condition was closer to the central theoretical claim of the paper.
+We use this latter test as the key test statistic.
 Our replication study found an significant interaction of similar magnitude.
@@
 The goal of this paper was to examine whether people are accurately calibrated in their estimates of how others will respond to their attempts at self-promotion.
-Our target was Experiment 3, which showed that participants, who were instructed to describe themselves in such a way that others would like them, expected to be liked more -- but were actually liked less -- than participants who were asked to describe themselves but not additionally instructed to maximize others’ interest in meeting them.
+Our replication target was Experiment 3, which showed that participants, who were instructed to describe themselves in such a way that others would like them, expected to be liked more -- but were actually liked less -- than participants who were asked to describe themselves but not additionally instructed to maximize others’ interest in meeting them.
 The authors performed a series of regressions on four dependent variables capturing judgments about profile writers (interest, liking, bragging, and success), analyzing these as a function of condition (control vs.
@@
 We were faced with a choice: Either we could have re-rated the descriptions gathered in the original study (by contacting the author and treating these as "materials" for the study), effectively replicating only stage two, or we could redo the entire two-step procedure.
-We elected to conduct a replication of the full procedure, but in our replication to decrease cost we focused on the liking judgments, which appeared to be central to the authors' conclusions.
+We elected to conduct a replication of the full procedure.
+In our replication, to decrease cost we focused on the liking judgments, which appeared to be central to the authors' conclusions.
 Our key test was the interaction of rater (writer vs.
-independent) and condition.^[We note that this project was submitted late and the student failed to preregister this analysis formally; however, the pre-written analysis protocol went through pre-data collection review.]  However, to power even this smaller study adequately was outside of our budget, so instead of having each judge rate a subset of 10 out of 100 total profiles, we collected a smaller sample of profiles (18) and had every profile rated by each judge.
+independent) and condition.^[We note that this project was submitted late and the student failed to preregister this analysis formally; the pre-written analysis protocol went through pre-data collection instructor review just as with other projects, however.]  However, to power even this smaller study adequately was outside of our budget, so instead of having each judge rate a subset of 10 out of 100 total profiles, we collected a smaller sample of profiles (18) and had every profile rated by each judge.
 
@@
 Consistent with the original report, though, we found a main effect such that stage one participants predicted that raters would like them more than the stage two participants actually did.
-Despite our relatively high statistical power in the main test, however, we may have suffered from low power at the item level due to the relatively small number of profiles we collected in the replication study.
-In addition, a small number of profile writers produced language in a manipulation check suggesting that the maximize interest manipulation had not succeeded fully, but since there was no specified exclusion criterion in the original study, we included these participants.
+We may have suffered from low power due to the relatively small number of profiles we collected in the replication study.
+In addition, a small number of our profile writers produced language in a manipulation check suggesting that the "maximize interest" manipulation had not succeeded fully; since there was no specified exclusion criterion in the original study, we included these participants.
 
@@
 This paper tested the hypothesis that face typicality affects trustworthiness judgments such that the most typical face will be judged to be the most trustworthy.
-In Study 1, our target, faces of varying typicality were rated on their trustworthiness and attractiveness; while trustworthiness peaked at the most typical face, less typical faces were judged more attractive.
+In Study 1, our replication target, faces of varying typicality were rated on their trustworthiness and attractiveness; while trustworthiness peaked at the most typical face, less typical faces were judged more attractive.
 The original sample was Israeli women, and typical faces were constructed to be typical for that sample.
-Rather than attempting to construct a typical face for AMT workers, we instead used the stimuli provided by the original authors, recognizing that this decision limits the interpretation of our findings.
+Rather than attempting to construct a typical face for AMT workers, we instead used the stimuli provided by the original authors, recognizing that this decision limited the interpretation of our findings.
 
@@
 We note that, despite the significant interaction, in our study trustworthiness judgments did not change substantially with typicality (though attractiveness did) and trustworthiness did not peak numerically at the most typical face.
-This result was plausibly caused by the difference in the typicality of the faces we used given our AMT participants.
+This result was plausibly caused by the fact that the "typical" faces were probably not typical for many of our AMT participants (who were of both genders and likely from a diverse range of ethnic backgrounds).
 
@@
 eight-word condition).
-The replication study failed to find evidence of the interaction, but ironically this failure was because of a main effect of save condition: The authors' key manipulation succeeded for both load conditions.
+The replication study failed to find evidence of the interaction.
+There was a main effect of save condition, however, hence the authors' key manipulation succeeded for both load conditions.
 Perhaps even two words was sufficient to create interference for our online sample.
@@
 
-This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among college undergraduate students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation.
-We targeted Study 2, the authors' own replication study, in which participants filled out three surveys about their math motivation and anxiety and completed a math task to measure performance.
+This paper reported that the relationship between math anxiety and math performance follows an inverted-U pattern among students with higher intrinsic math motivation, whereas this same relationship is linearly negative among students with lower intrinsic math motivation.
+Our replication target was Study 2, the authors' own replication study, in which college undergraduates filled out three surveys about their math motivation and anxiety and completed a math task to measure performance.
 The key effect we targeted was the interaction of math anxiety squared and math motivation in predicting performance.
 We failed to find evidence for this effect.
+
 In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups.
@@
 This paper explored constraints on visual working memory in the context of mental rotation.
-In Experiment 1a, participants performed a verbal suppression task to control for use of verbal encoding while attempting to remember a cross with four colored bars, which sometimes switched colors; performing mental rotation significantly impaired ability to detect these bar swaps.
+In Experiment 1a, our replication target, participants performed a verbal suppression task to control for use of verbal encoding while attempting to remember a cross with four colored bars, which sometimes switched colors; performing mental rotation significantly impaired ability to detect these bar swaps.
 To port the task to an online framework we decreased the number of trials and increased the number of participants we tested.
-The key test statistic was a comparison of K (a metric of the number of visual features remembered) between the rotation and no-rotation conditions.
+The key test statistic was a comparison of $K$ (a metric of the number of visual features remembered) between the rotation and no-rotation conditions.
 We observed a marginally-significant effect in our replication study.
-Our study showed a floor effect on capacity such that participants remembered on average very little; it is possible that small details in the displays (or the differing sample available online) led to this floor effect.
+Our study showed a floor effect on capacity such that participants remembered on average very little; it is possible that small details in the displays or the differing AMT participant population led to this floor effect.
 
@@
 We also may have observed a smaller effect size due to the relatively smaller amount of time our participants spent on the legacy prime writing exercise.
-We enforced a four minute writing time and a 20 word minimum; we found that most participants stayed relatively closer to these limits than participants in the original study.
+We enforced a four minute writing time and a 20 word minimum; we found that most participants stayed relatively closer to these limits than participants in the original study, leading to an overall shorter priming phase with less writing.
 

### 2016-09-26 paper/paper.Rmd
Sofer response

@@
 Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
-Sofer et al. & 1 & No & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
+Sofer et al. & 1 & Yes & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
 Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
@@
 While the original class projects selected a global, item-wise regression model as the key statistical test of interest, the instructor team (post-data collection) determined that the fit of this model did not in fact correspond most closely with the authors' stated hypothesis.
-We thus selected the interaction between face typicality and rating condition as our key test statistic and used the more standard by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model.
+We thus selected the interaction between face typicality and rating condition as our key test statistic and used the by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model.
 Our replication study successfully showed this same interaction.

### 2016-09-30 paper/paper.Rmd
sofer comments 2

@@
 In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
-In both of these cases [@sofer2015;@proudfoot2015], the original authors had fit a multiple regression model to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
+In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
 After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest.

### 2016-09-30 paper/paper.Rmd
final tweaks

@@
 In contrast to the original study, we found a simple linear trend such that performance decreased with increasing math anxiety for both high and low math-motivation groups.
-Population differences provide one plausible explanation for the differences we found: Math performance was overall lower in our AMT sample than in the original undergraduate sample.
+Population differences provide one plausible explanation for the differences we found (especially since the original study was itself a replication): Math performance was overall lower in our AMT sample than in the original undergraduate sample.
 It is possible that either the inverted U was undetectable given this lower level of performance, or that levels of motivation differed enough that the posited relationship did not hold.

### 2017-05-17 paper/paper.Rmd
Add authors

@@
 author-information:
-    - \author{Robert X. D. Hawkins*, Eric N. Smith*, the Psych 254 Students**, and Michael C. Frank}
+    - \author{Robert X.
+D.
+Hawkins*, Eric N.
+Smith*, Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Martin Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, Jed Tan, and Michael C.
+Frank}
 
@@
     "*These authors contributed equally and are listed alphabetically.
-**Carolyn Au, Juan Miguel Arias, Rhia Catapano, Eric Hermann, Martin Keil, Andrew Lampinen, Sarah Raposo, Jesse Reynolds, Shima Salehi, Justin Salloum, and Jed Tan.
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
@@
 Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.
+And another sentence.
 
@@
   group_by(original_on_turk, replicated_TA) %>%
-  summarise(n= n()) %>%
+  summarise(n = n()) %>%
   spread(replicated_TA, n) %>%

### 2017-05-17 paper/paper.Rmd
Update to table 1 cols
pedagogy changes

--- 2016-09-30 paper/paper.Rmd
@@
 
-All projects were completed as part of a graduate-level methodology class (syllabus and materials, as well as code and data for this paper, available at [https://osf.io/98ta4](https://osf.io/98ta4)).
+All projects were completed as part of a graduate-level methodology class.
 At the initiation of class, all students were told that they had the opportunity to contribute their individual class assignment to a group replication project.
@@
 In addition, prior to data collection for all projects, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).
+All code and data to reproduce the analyses reported here are available at: [https://osf.io/98ta4](https://osf.io/98ta4).
 
@@
 
-Our projects had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+## Pedagogical Implications
+
+Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
 But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
@@
 
-One of the barriers to more reproducible work in psychology is pedagogical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
+While every course of this type will likely be tailored to the interests and instructional needs of a particular department and institution, there will also likely be some commonalities.
+To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4](https://osf.io/98ta4).
+In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
+We hope that others will share and reuse our materials as the consider how best to design a course customized to their context.
+
+One of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
 Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web experiments or literate, reproducible data analysis.
@@
 
-From a purely statistical point of view, though, our results were underwhelming.
+We end with a few recommendations for instructors designing such a course.
+First, plan as much as possible to make the project the centerpiece of the course, so that students begin the process as quickly as possible and do the maximal amount of skill learning in the context of their own goal-directed research.
+Second, rather than adopting the typical model of students turning in work at the end of the course and being assessed, consider a more collaborative model where the instructors provide iterative feedback on subcomponents of projects (e.g., sample analyses, parts of the experimental paradigm or materials).
+Such feedback can both save students time and frustration and provide a check on project quality before data are collected.
+Third and inally, try to share the excitement of discovery that is inherent in doing new research!
+We have found that the most rewarding part of teaching this class is the fun of getting to see the results of all the hard work at the end.
+
+## Implications for Replication Research
+
+From a purely statistical point of view, the results of our studies were underwhelming.
 Despite our relatively close adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
@@
 First, we likely saw a "winner's curse," with initial publications tending to over-estimate effects.
-Second, we also might have seen a reduction in effect size because the original studies were tailored to their specific context and population, whereas our replications may not have been [@vanbavel2016].
-Both of these explain our observations, and we suspect both effects are present to some degree.
+Second, we also might have seen a reduction in effect size because the original studies were tailored to their specific context and population, whereas our replications may not have been [@vanbavel2016, but cf.
+@inbar2016].
+Future work would benefit from a statement of constraints on generality so as to provide a guide to the conditions under which an effect is likely to be present [@simons2016].
+Both of these explanations are consistent with our observations, and we suspect both winner's curse and context effects are present to some degree.
 
@@
 
-In conclusion, our results here demonstrate the practical possibility of performing replication research in the classroom.
+## Conclusions
+
+Our results here demonstrate the practical possibility of performing replication research in the classroom.
 There are many challenges for ensuring high-quality replications in a pedagogical setting -- from checking experimental methods to reviewing analytic code for errors -- but we would argue that these are not just pedagogical challenges.
@@
 
-# SOM-R: Project-By-Project Methods Addendum
+# SOM: Project-By-Project Methods Addendum
 

### 2017-05-17 paper/paper.Rmd
Remover over-powered

--- 2016-09-30 paper/paper.Rmd
@@
    - \usepackage{lscape}
+   - \usepackage{multicol}
 
@@
   \hline
+
+ & \multicolumn{5}{c|}{\underline{Original Study}} & \multicolumn{4}{c}{\underline{Replication Study}} \\
+
 \specialcell{Citation\\(Psychological Science; 2015)} & Expt.
@@
 In four cases, we used the original sample size.
-In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
+In one case, the original experiment was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
 In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).

### 2017-05-17 paper/paper.Rmd
Experiment -> study

@@
 
-A summary of the original experiments chosen for replication is given in Table \ref{tab:summary}.
+A summary of the original empirical studies chosen for replication is given in Table \ref{tab:summary}.
 Students chose findings from a wide variety of domains for replication.
@@
 Each sample was recruited independently, using the same account but a different title.
-All experiments were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction."
+All replications were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction."
 
@@
 
-Repeat administration of experiments on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
+Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
 We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses.
@@
 Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
-For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for experiments that were initially large and/or adequately powered.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered.
 
 We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the experiment.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study.
 In four cases, we powered the replication attempt to 80\% post-hoc power.
 In four cases, we used the original sample size.
-In one case, the original experiment was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
+In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
 In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).
@@
 
-All experiments were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
+All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
 All analyses were written using R, a free and open-source platform for statistical analysis.
@@
 The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
-The goal of this pilot was to ensure that all needed data were being logged by the experiment software and that analytic scripts for the confirmatory analyses functioned appropriately.
+The goal of this pilot was to ensure that all needed data were being accurately logged and that analytic scripts for the confirmatory analyses functioned appropriately.
 After Pilot A was completed, the instructor or a TA critiqued and reviewed the student's experimental script, analytic code, and resulting output.
@@
 Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from AMT.
-The goal of this pilot was to ensure that participants were able to complete the experiment and did not report any substantial issues with instructions or technical details of the experiment.
-(All students were instructed to give participants a way to leave free-form comments at the end of the experiment, prior to debriefing).
+The goal of this pilot was to ensure that participants were able to complete the study and did not report any substantial issues with instructions or technical details of the study (All students were instructed to give participants a way to leave free-form comments at the end of the study, prior to debriefing).
 At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
@@
 Thus, we interpret "key statistical test" results with caution.
-Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for experiment planning and analysis.
+Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for replication planning and analysis.
 
@@
 
-After data analysis, for each experiment, the student carrying out each experiment and the instructors all gave independent "replication ratings" to assess the subjective success of the replication.
+After data analysis, for each replication, the student carrying out each study and the instructors all gave independent "replication ratings" to assess the subjective success of the replication.
 Our three-point rating system was based on the theoretical support for the original finding, "None" (no support; 0\%), "Partial" (some support; 50\%), and "Full" (replication consistent with original interpretation; 100\%).
@@
 
-In this paper, we reported a series of 11 student replications of previously-published experiments from the 2015 volume of *Psychological Science*.
+In this paper, we reported a series of 11 student replications of previously-published empirical studies from the 2015 volume of *Psychological Science*.
 We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students to replicate recent findings in a top journal.
@@
 One of the barriers to more reproducible work in psychology is pedagogical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
-Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web experiments or literate, reproducible data analysis.
+Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
 Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
@@
 From a purely statistical point of view, though, our results were underwhelming.
-Despite our relatively close adherence to the original experimental protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
+Despite our relatively close adherence to the original protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.
 These partial replications often were cases in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.
-We invite readers to browse the narrative descriptions of individual replication attempts in our SOM to see the ways that patterns of experimental findings can differ from one another beyond the significance of a single test.
+We invite readers to browse the narrative descriptions of individual replication attempts in our SOM to see the ways that patterns of empirical findings can differ from one another beyond the significance of a single test.
 
@@
 
-Indeed, no experiment we attempted to replicate was pre-registered (though some were internal replications), and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
+Indeed, no study we attempted to replicate was pre-registered (though some were internal replications), and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
 Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications.

### 2017-05-17 paper/paper.Rmd

@@
 
-One of the barriers to more reproducible work in psychology is pedagogical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
+While every course of this type will likely be tailored to the interests and instructional needs of a particular department and institution, there will also likely be some commonalities.
+To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4](https://osf.io/98ta4).
+In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
+We hope that others will share and reuse our materials as the consider how best to design a course customized to their context.
+
+One of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
 Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
@@
 
-From a purely statistical point of view, though, our results were underwhelming.
+We end with a few recommendations for instructors designing such a course.
+First, plan as much as possible to make the project the centerpiece of the course, so that students begin the process as quickly as possible and do the maximal amount of skill learning in the context of their own goal-directed research.
+Second, rather than adopting the typical model of students turning in work at the end of the course and being assessed, consider a more collaborative model where the instructors provide iterative feedback on subcomponents of projects (e.g., sample analyses, parts of the experimental paradigm or materials).
+Such feedback can both save students time and frustration and provide a check on project quality before data are collected.
+Third and inally, try to share the excitement of discovery that is inherent in doing new research!
+We have found that the most rewarding part of teaching this class is the fun of getting to see the results of all the hard work at the end.
+
+## Implications for Replication Research
+
+From a purely statistical point of view, the results of our studies were underwhelming.
 Despite our relatively close adherence to the original protocols and relatively large sample sizes, the modal outcome of our projects was partial replication.

### 2017-05-17 paper/paper.Rmd
fixed 'dividends' sentence

--- 2017-05-17 paper/paper.Rmd
@@
    - \usepackage{lscape}
-   - \usepackage{multicol}
 
@@
 There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise.
-Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole would be considerable.
+Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole---both scientific and educational---would be considerable.
 
@@
   \hline
-
- & \multicolumn{5}{c|}{\underline{Original Study}} & \multicolumn{4}{c}{\underline{Replication Study}} \\
-
 \specialcell{Citation\\(Psychological Science; 2015)} & Expt.
@@
 In four cases, we used the original sample size.
-In one case, the original experiment was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
+In one case, the original experiment was extremely over-powered in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
 In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).

### 2017-05-18 paper/paper.Rmd
Clarify prose in BF section

@@
 Effect sizes and Bayes factors improve upon inferences drawn from $p$-values in different ways.
-The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes (assuming a constant experimental procedure, of course) and allows for a more fine-grained comparison across studies than a binary significance criterion.
+The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes (assuming a constant experimental procedure) and allows for a more fine-grained comparison across studies than a binary significance criterion.
 The Bayes Factor is an alternative hypothesis testing method that quantifies the evidence in favor of a hypothesis [@jeffreys1961].
@@
 
-These additional measures therefore give another sense in which replications can be successful: If we find roughly the same effect size or Bayes factor despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we should increase our confidence in the effect's replicability.
+These additional measures therefore give additional criteria for evaluating replications: If the replication shows roughly the same effect size or Bayes factor as the original results despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we may nonetheless consider it a success.
 To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1.^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.

### 2017-05-18 paper/paper.Rmd
Fix Fig. 2 legends, color schemes

@@
 Note that the key statistic for one replication was a multivariate $F$ test, hence a comparable default Bayes factor could not be computed.
-Additionally, the original Bayes factor for oen finding was many orders of magnitude greater than the others so it is not displayed.", fig.pos="ht", fig.height=3.6}
+Additionally, the original Bayes factor for one finding was many orders of magnitude greater than the others so it is not displayed.", fig.pos="ht", fig.height=3.6}
+
+# Want semantically meaningful values for coding values
+colorMap <- c('No'='red', 'Partial'='#b58900', 'Yes'='green4')
 
@@
   geom_abline(slope = 1, intercept = 0, linetype = 2) +
-  geom_smooth(method = "lm", se=FALSE) +
+  geom_smooth(method = "lm", se=FALSE, colour="#657b83") +
   xlab("Orig. effect size (r)") + 
   ylab("Rep. effect size (r)") + 
-  theme_bw(base_size=10) + theme(legend.position="bottom") + 
+  theme_bw(base_size=10) + theme(legend.position="bottom", aspect.ratio = 1) + 
   scale_size(name = "Rep. N") +
-  # scale_color_solarized(guide = FALSE)
-  scale_color_solarized(name = "Subj. rep. rating")
+  scale_color_manual(values = colorMap, guide = FALSE)  +
+  #scale_color_solarized(name = "Subj. rep. rating") +
+  guides(size=guide_legend(order = 1, direction = "horizontal", byrow=TRUE))
 
@@
                              col = replicated_TA_factor)) +
-  geom_smooth(method = "lm", se = FALSE) +
+  geom_smooth(method = "lm", se = FALSE, colour="#657b83") +
   geom_abline(slope = 1, intercept = 0, linetype = 2) +
@@
                            "1e6","1e9")) + 
-  theme_bw(base_size=10) + theme(legend.position="bottom") + 
+  theme_bw(base_size=10) + 
   scale_size_continuous(breaks=c(.5, 2, 5),name = "Rep. df/Orig. df") + 
-  scale_color_solarized(name = "Subj. rep. rating") +
-  guides(size=guide_legend(order = 1), 
-         color=guide_legend(order = 2))
+  scale_color_manual(values = colorMap, guide = F) +
+  theme(legend.position="bottom", aspect.ratio = 1) + 
+  guides(size=guide_legend(direction = 'horizontal'))
 
-plot_grid(p1, p2, labels = c("A", "B"))
+plotrow <- plot_grid(p1, p2, labels = c("A", "B"))
+legend <- get_legend(
+  p2 + 
+    theme(legend.position="bottom") + 
+    guides(color = guide_legend(title = "Subjective replication rating", 
+                                direction = 'horizontal'),
+           size = FALSE)
+)
+plot_grid(plotrow, legend, ncol = 1, rel_heights = c(1, .2))
 ```

### 2017-05-18 paper/paper.Rmd
Adjust colors to be more distinguishable

@@
 # Want semantically meaningful values for coding values
-colorMap <- c('No'='red', 'Partial'='#b58900', 'Yes'='green4')
+colorMap <- c('No'=rgb(0.75, 0.2, 0.2), 
+              'Partial'=rgb(0.8, 0.8, 0.4), 
+              'Yes'=rgb(0.2, 0.6, 0.2))
 
@@
     guides(color = guide_legend(title = "Subjective replication rating", 
-                                direction = 'horizontal'),
+                                direction = 'horizontal',
+                                override.aes = list(size=10)),
            size = FALSE)

### 2017-05-18 paper/paper.Rmd
Put borders around points

@@
 p1 <- ggplot(d,aes(x=original_ES_d,y=rep_es)) +
-  geom_point(alpha = .8, 
-             aes(color=replicated_TA_factor, size = collected_n)) +
+  geom_point(alpha = .8, pch=21,
+             aes(fill=replicated_TA_factor, size = collected_n)) +
   # geom_text_repel(aes(label = first_author_name), size = 2, force = 2) +
@@
   scale_size(name = "Rep. N") +
-  scale_color_manual(values = colorMap, guide = FALSE)  +
+  scale_fill_manual(values = colorMap, guide = FALSE)  +
   #scale_color_solarized(name = "Subj. rep. rating") +
@@
 p2 <- ggplot(tstatDF, aes(x = origBF, y = repBF)) +
-  geom_point(alpha = .8, aes(size = df_ratio, 
-                             col = replicated_TA_factor)) +
+  geom_point(alpha = .8, pch=21, aes(size = df_ratio, 
+                             fill = replicated_TA_factor)) +
   geom_smooth(method = "lm", se = FALSE, colour="#657b83") +
@@
   scale_size_continuous(breaks=c(.5, 2, 5),name = "Rep. df/Orig. df") + 
-  scale_color_manual(values = colorMap, guide = F) +
+  scale_fill_manual(values = colorMap, guide = F) +
   theme(legend.position="bottom", aspect.ratio = 1) + 
@@
     theme(legend.position="bottom") + 
-    guides(color = guide_legend(title = "Subjective replication rating", 
+    guides(fill = guide_legend(title = "Subjective replication rating", 
                                 direction = 'horizontal',
-                                override.aes = list(size=10)),
+                                override.aes = list(size=8)),
            size = FALSE)

### 2017-05-19 paper/paper.Rmd
minor revs for mcf action items

@@
 
-These statistical findings mask a more optimistic message, however: In most of our projects, the next step for a motivated experimenter is clear.
+One potential concern about our project is that our replications might be of lower quality, due to the lead role played by inexperienced investigators.
+This issue should be taken seriously by any instructor interested in doing replications in the classroom, but we believe it is not a major concern in the current case.
+First, our experimenters were graduate students, conducting other research in addition to their work in our class.
+Many of them will go on to publish in top journals (often alongside more senior collaborators), and this work will be treated on its merits, not on the basis of the experience level of the lead author.
+Indeed, evaluation on the merits is even easier in our case, as all materials and methods for each project (including the full experiment) are easily accessible online.
+Second, the design of our course -- with multiple rounds of review by both more senior graduate students and a faculty member -- mirrors the typical structure of experimental work, where there are multiple sources of feedback from researchers at different career stages.
+In general, we don't see any reason why the career stage of the students in our class should be more of a concern in the current case than it is for other research.
+
+In addition, our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear.
 For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials.
@@
 Our experiences performing and compiling the studies here sheds light on one further concern that we believe has been under-reported in past studies [including @osc2015].
-Our standard model of replication is based on the notion of a single statistical test -- and its associated effect size -- being the key properties of a study that can be targeted for replication.
-Yet, as we mentioned above, selecting this key statistical test was difficult for most of the projects in our sample, and virtually impossible for some.
+Our standard model of replication is based on the notion of a single key statistical test -- and its associated effect size -- being the properties of a study that can be targeted for replication.
+Yet, as we mentioned above, selecting this "key test" was difficult for most of the projects in our sample, and virtually impossible for some.
 We were often forced to consult other sections of the papers (e.g., abstracts, discussion sections) to gain clarity on what test was considered the critical one for the authors' interpretation.
@@
 In our view, two recommendations will improve this situation dramatically.
-First, pre-registration typically requires the selection of particular statistical analyses to be designated as critical for interpretation.
-Were this information available, it would have simplified the problem of selecting effects to replicate in several cases.
-Second, the widespread adoption of open data practices can dramatically facilitate the type of meta-research pursued here.
+First, authors should specify their "key test" more clearly.
+Pre-registration might facilitate this step, as regstration typically requires the selection of particular statistical analyses to be designated as critical for interpretation, but we believe this designation is critical even in un-registered experiments.
+Had "key test" information been available, it would have dramatically simplified the problem of selecting the effect to replicate in several cases.
+Second, the widespread adoption of open data practices would dramatically facilitate the type of meta-research pursued here.
 In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.

### 2017-05-20 paper/paper.Rmd
Small edits and fixes

@@
 (r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
-(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]).
+(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]), consistent with findings from multi-study replication projects [e.g.
+@osc2015].
 
@@
 In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
-We hope that others will share and reuse our materials as the consider how best to design a course customized to their context.
+We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.
 
@@
 Such feedback can both save students time and frustration and provide a check on project quality before data are collected.
-Third and inally, try to share the excitement of discovery that is inherent in doing new research!
+Third and finally, try to share the excitement of discovery that is inherent in doing new research!
 We have found that the most rewarding part of teaching this class is the fun of getting to see the results of all the hard work at the end.
@@
 Many of them will go on to publish in top journals (often alongside more senior collaborators), and this work will be treated on its merits, not on the basis of the experience level of the lead author.
-Indeed, evaluation on the merits is even easier in our case, as all materials and methods for each project (including the full experiment) are easily accessible online.
-Second, the design of our course -- with multiple rounds of review by both more senior graduate students and a faculty member -- mirrors the typical structure of experimental work, where there are multiple sources of feedback from researchers at different career stages.
+Indeed, evaluation on merits is even easier in our case, as all materials and methods for each project (including the full experiment) are easily accessible online.
+Second, the design of our course -- with multiple rounds of review by both graduate student teaching assistants and a faculty member -- mirrors the typical structure of experimental work, where there are multiple sources of feedback from researchers at different career stages.
 In general, we don't see any reason why the career stage of the students in our class should be more of a concern in the current case than it is for other research.
@@
 Second, the widespread adoption of open data practices would dramatically facilitate the type of meta-research pursued here.
-In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.
+In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several authors of the papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.
 

### 2017-05-20 paper/paper.Rmd
SOM -> Supplemental Materials

--- 2017-05-18 paper/paper.Rmd
@@
 Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
-Details of individual replications are available in SOM.
+Details of individual replications are available in Supplemental Material.
 
@@
 Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT.
-For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see SOM for more discussion of this issue in individual cases.
+For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.
 
@@
 We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses.
-In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see SOM for discussion of one particular paradigm that has been used more recently).
+In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).
 
@@
 These partial replications often were cases in which some hint of the original pattern was observed but the key statistical test was not statistically significant and showed both smaller effect size and lower evidential value than the same test in the original.
-We invite readers to browse the narrative descriptions of individual replication attempts in our SOM to see the ways that patterns of empirical findings can differ from one another beyond the significance of a single test.
+We invite readers to browse the narrative descriptions of individual replication attempts in our Supplemental Material to see the ways that patterns of empirical findings can differ from one another beyond the significance of a single test.
 
@@
 
-# SOM: Project-By-Project Methods Addendum
+# Supplemental Material: Project-By-Project Methods Addendum
 
@@
 We replicated Study 1b, which asked participants to rate their knowledge about finances, and then asked them to rate their knowledge about a set of financial terms, some of which were invented (and hence for which a positive knowledge statement would necessarily be an overclaim).
-The original study found that participants with higher self-rated financial knowledge also overclaimed at a higher rate.
+The original study reported that participants with higher self-rated financial knowledge also overclaimed at a higher rate.
 The key test statistic for this study was the coefficient in a regression model predicting overclaiming as a function of claimed personal financial knowledge, controlling for accuracy in the true financial knowledge questions.
@@
 We replicated Study 4, which found that seeing the time to retirement in days (10,950) rather than years (30) caused participants to say they would begin saving sooner.
-The original reported this analysis both with and without demographic controls.
+The original study reported this analysis both with and without demographic controls.
 We chose as our key analysis the version of this regression which controlled for age, education, and income (there was also a manipulation of whether saving was incremental that did not result in an effect).
@@
 
-While the original class projects selected a global, item-wise regression model as the key statistical test of interest, the instructor team (post-data collection) determined that the fit of this model did not in fact correspond most closely with the authors' stated hypothesis.
+While the original course project selected a global, item-wise regression model as the key statistical test of interest, the instructor team (post-data collection) determined that the fit of this model did not in fact correspond most closely with the authors' stated hypothesis.
 We thus selected the interaction between face typicality and rating condition as our key test statistic and used the by-participant regression model (which the original paper also reported subsequent to the by-items model) as the target model.

### 2017-05-23 paper/paper.Rmd
paper for AMPPS submission

@@
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
-We are grateful to the authors of the original studies who provided materials and gave comments on a draft of this manuscript."
+We are grateful to the authors of the original studies who provided materials and gave comments on a draft of this manuscript.
+RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper.
+CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned their individual projects, programmed their studies, collected their data, and analyzed their data."
 
@@
                       cache=TRUE, message = FALSE, sanitize = TRUE)
+#devtools::install_github("kemacdonald/kmr")
 library(readr)
@@
 Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.
-And another sentence.
 
@@
 We begin by describing the general method of the class, then discuss shared methods for the replications and the process of development for each project.
+In general, we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
 
@@
 
-While every course of this type will likely be tailored to the interests and instructional needs of a particular department and institution, there will also likely be some commonalities.
+Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design, as these components were crucial to our success.
 To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4](https://osf.io/98ta4).
@@
 
-One of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
+Finally, one of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
 Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
@@
 This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
-
-We end with a few recommendations for instructors designing such a course.
-First, plan as much as possible to make the project the centerpiece of the course, so that students begin the process as quickly as possible and do the maximal amount of skill learning in the context of their own goal-directed research.
-Second, rather than adopting the typical model of students turning in work at the end of the course and being assessed, consider a more collaborative model where the instructors provide iterative feedback on subcomponents of projects (e.g., sample analyses, parts of the experimental paradigm or materials).
-Such feedback can both save students time and frustration and provide a check on project quality before data are collected.
-Third and finally, try to share the excitement of discovery that is inherent in doing new research!
-We have found that the most rewarding part of teaching this class is the fun of getting to see the results of all the hard work at the end.
 
@@
 And in some, differences of population would mean that followups would require further stimulus or task adaptation.
-More generally, we believe that our work here underscores the importance of iterated replication [@lewis2016].
+More generally, we believe that our work here underscores the importance of iterated replication for pinpointing empirical effects and refining theories [see e.g., @lewis2016 for an example of this strategy and some discussion].
 

### 2017-06-23 paper/paper.Rmd
mcf 23 - 33 changes

@@
 author-note:
-    "*These authors contributed equally and are listed alphabetically.
-Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
-We are grateful to the authors of the original studies who provided materials and gave comments on a draft of this manuscript.
-RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper.
-CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned their individual projects, programmed their studies, collected their data, and analyzed their data."
+    "*These authors contributed equally and are listed alphabetically."
 
@@
 
+To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4](https://osf.io/98ta4).
+In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
+We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.
+
 ```{r, results='asis'}
@@
 
+# Disclosures
+
+## Preregistration
+
+<!-- Preregistration: Provide a link to any preregistration documentation. If only a subset of reported studies were preregistered, indicate which ones were and which ones were not. -->
+
+As described below, our procedure for individual project preregistrations was to register the analytic script with specific key hypothesis tests clearly marked.
+Individual project preregistration links are given in Table 1.
+Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).
+
+## Data, Materials, and Online Resources
+
+<!-- Data, materials, and online resources: Provide a permanent, persisting link to a public archive where readers can access any code, materials, de-identified data, and other resources (e.g., osf.io, perma.cc, clinicaltrials.gov).
+If any materials or data are not publicly available, the article should explain why and should note how researchers can access them for research purposes.
+-->
+
+All code and data necessary to reproduce the analyses reported here are available at: [https://osf.io/98ta4](https://osf.io/98ta4).
+
+## Measures
+
+<!-- Measures: The text here should state “We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study” (see Simmons, Nelson, & Simonsohn, 2011).
+If any aspect of this statement is untrue, authors should explain why.
+All such details should be specified in the preregistration documentation as well.
+-->
+
+We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study (see @simmons2011).
+
+## Subjects
+
+<!-- Subjects: If the article reports research with human or animal subjects, authors should state that testing was conducted with the approval of an institutional review board or similar ethics committee (with the protocol number provided).
+For those involving human subjects, authors should state whether the research was conducted in accordance with the Declaration of Helsinki; note that the latest version of the Declaration of Helsinki requires preregistration before data collection begins.
+-->
+
+All replications were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction" and was conducted in accordance with the Declaration of Helsinki.
+
+## Conflicts of Interest
+
+<!-- Conflicts of Interest: Authors should identify any conflicts of interest here and should also report them during the submission process.
+If authors have no conflicts of interest, they should state, “” -->
+
+The authors declare that they have no conflicts of interest with respect to the authorship or the publication of this article.
+
+## Author Contributions
+
+<!-- Author Contributions: Authorship implies significant participation in the research reported or in writing the manuscript, including participation in the design and/or interpretation of reported experiments or results, participation in the acquisition and/or analysis of data, and participation in drafting and/or revising the manuscript.
+All authors must agree to the order in which the authors are listed and must have read the final manuscript and approved its submission.
+They must also agree to take responsibility for the work in the event that its integrity or veracity is questioned.
+Authors should precisely describe their contributions to the research and manuscript, identifying each author by his or her initials.
+For example, “DJS and AOH jointly generated the idea for the study.
+AOH programmed the study and collected the data.
+DJS wrote the analysis code and analyzed the data, and AOH verified the accuracy of those analyses.
+DJS wrote the first draft of the manuscript, and both authors critically edited it.
+Both authors approved the final submitted version of the manuscript.” -->
+
+RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper.
+CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned their individual projects, programmed their studies, collected their data, and analyzed their data.
+
+## Acknowledgements
+
+<!-- Acknowledgments: Authors should use this section to identify any people who should be credited for their assistance with the reported research. -->
+
+Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
+We are grateful to the authors of the original studies who provided materials and gave comments on a draft of this manuscript.
+
+## Prior Versions
+
+<!-- Prior versions: If part or all of a submitted manuscript was previously posted to a blog or to a preprint archive, provide a link to those sources and briefly indicate what aspects of the manuscript are shared between the submitted version and earlier versions.
+-->
+
+An earlier draft of this manuscript was posted at [https://osf.io/preprints/psyarxiv/p73he/](https://osf.io/preprints/psyarxiv/p73he/).
+
 # Methods
@@
 We begin by describing the general method of the class, then discuss shared methods for the replications and the process of development for each project.
-In general, we report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study.
 
@@
 
-All study participants were recruited on AMT.
-Individual sample sizes are given in Table \ref{tab:summary}.
-Each sample was recruited independently, using the same account but a different title.
-All replications were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction."
+All study participants were recruited on AMT. Individual sample sizes are given in Table \ref{tab:summary}. Each sample was recruited independently, using the same account but a different title.
 
@@
 Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.
-In addition, prior to data collection for all projects, we pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).
-All code and data to reproduce the analyses reported here are available at: [https://osf.io/98ta4](https://osf.io/98ta4).
 
@@
 In this paper, we reported a series of 11 student replications of previously-published empirical studies from the 2015 volume of *Psychological Science*.
-We had two interlocking goals: first, to create a proof of concept for pedagogical replications, and second, to provide evidence on the ability of students to replicate recent findings in a top journal.
+Our goal was to provide a proof of concept for pedagogical replications of recent findings in a top journal.
 Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
-Despite this narrower scope, we believe that insights from our approach are applicable to the broader goal of assessing replicability at scale.
+Despite this narrower scope, we believe that insights from our approach are applicable to the broader goal of assessing replicability at scale, with implications both for replication pedagogy and for the practice of replication more broadly.
+We address each in turn.
 
@@
 Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
+
 Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
+This kind of cross-class collaboration would require instructors to make class results more broadly discoverable.
+We can envision a number of possible avenues for this kind of sharing.
+For example, if some products are shared openly in a repository like the [Open Science Framework](http://osf.io) or [figshare](http://figshare.com) and tagged appropriately, they will be discoverable via search engines.
+Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like [PsychFileDrawer](http://psychfiledrawer.org) or CurateScience (http://curatescience.org/).
+Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible.
+For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/), selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
 
-Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design, as these components were crucial to our success.
-To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4](https://osf.io/98ta4).
-In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
-We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.
+One challenge for this kind of dissemination is how to curate which projects are released publicly.
+We are generally optimistic about the contributions of student work, but of course not every student project will be scientifically informative.
+To take an edge case, imagine a student makes an error in stimulus randomization that is not caught by the instructors until after data collection and that and creates a major confound in the collected data.
+In this case, we would argue that this work should not be deposited in a targeted replication repository.
+In the end, these decisions will be the responsibility of the course instructor -- much like decisions about when to publish other research.
+
+Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
+Without a central focus on the replication project, students would not have the time or motivation to complete a high quality project; without multiple opportunities for instructor feedback, we would have far less confidence in the quality of the final projects.
 
@@
 This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
+
+## Decision Points for Instructors
+
+- how to customize for different levels of instructor
+
+### Ethical approvals
+
+### Study selection
+
+- student expertise
+- group wiork
+- Strength of evidence in original, e.g. BF > 3
+
+### Contacting original authors
+
+### Results deposit
 
@@
 Future work would benefit from a statement of constraints on generality so as to provide a guide to the conditions under which an effect is likely to be present [@simons2016].
-Both of these explanations are consistent with our observations, and we suspect both winner's curse and context effects are present to some degree.
+Both of these explanations are consistent with our observations, and, based on the previous literature [@osf2015,@vanbavel2016], we speculate that both winner's curse and context effects were present to some degree.
 
@@
 Indeed, no study we attempted to replicate was pre-registered (though some were internal replications), and the general pattern of evidence across studies was often more important to the authors' conclusions than any particular test in any single study.
-Almost every study conducted multiple statistical tests, often associated with several statistical models with differing specifications.
+Almost every study conducted multiple statistical tests, often associated with several tersely-reported statistical models with differing specifications.
 And in some cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf.
 @bakeman2005].
-This set of features -- which, in our experience, are endemic to published psychological work, including our own -- makes replication research within the conventional statistical paradigm extremely challenging.
+This set of features -- which, in our experience, are endemic to published psychological work, including our own -- makes it extremely challenging to do replication research focused on the estimation of a single effect size.
 
-In our view, two recommendations will improve this situation dramatically.
+In our view, two recommendations will improve this situation.
 First, authors should specify their "key test" more clearly.
@@
 Had "key test" information been available, it would have dramatically simplified the problem of selecting the effect to replicate in several cases.
-Second, the widespread adoption of open data practices would dramatically facilitate the type of meta-research pursued here.
-In addition to clarifying the (often terse) reporting in a paper, the availability of data facilitates the computation of the relevant meta-analytic variables.^[We note that, although we were grateful that several authors of the papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.] No paper can perfectly predict the uses to which future investigators will put a piece of work; the availability of the source materials is thus an important route for more flexible reuse.
+Second, the widespread adoption of open data and open analytic code practices would facilitate replication research.
+In addition to clarifying the summary report of results in a paper, the availability of data dramatically facilitates the computation of the relevant meta-analytic effect size for power analysis and statistical comparison.^[We note that, although we were grateful that several authors of the papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.]
 

### 2017-06-23 paper/paper.Rmd
revisions

--- 2017-05-23 paper/paper.Rmd
@@
 In four cases, we used the original sample size.
-In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that still would yield high power.
+In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect.
 In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).
@@
 Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
-For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods (using a template email that was customized by the students and reviewed by the instructors).
+For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials).
 Responses were received in all but one case, all within a matter of days.
@@
 ## Workflow
-
-All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
-All analyses were written using R, a free and open-source platform for statistical analysis.
-A schematic of our class workflow is shown in Figure 1.
 
@@
 
+All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
+All analyses were written using R, a free and open-source platform for statistical analysis.
+A schematic of our class workflow is shown in Figure 1.
 Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
-This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices.
-Using the template developed by @osc2015 for replication reports, students created dynamic documents that included their proposed replication study, the code necessary to analyze their data, and the outputs of their data analysis (e.g., statistical tests and figures).
+This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
+
+Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods.
+Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures).
 This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.

### 2017-06-23 paper/paper.Rmd
proposed reorg

@@
 
-# Results
+# Pedagogy: Results and Discussion
 
-## Pedagogical assessment
+## Pedagogical Assessment
 
@@
 We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].
+
+## Pedagogical Implications
+
+Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
+Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
+
+Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
+Without a central focus on the replication project, students would not have the time or motivation to complete a high quality project; without multiple opportunities for instructor feedback, we would have far less confidence in the quality of the final projects.
+
+Finally, one of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
+Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
+Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
+This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
+
+## Decision Points for Instructors
+
+- how to customize for different levels of instructor
+
+### Ethical approvals
+
+### Study selection
+
+- student expertise
+- group wiork
+- Strength of evidence in original, e.g. BF > 3
+
+### Contacting original authors
+
+### Results deposit
+
+# Empirical Findings: Results and Discussion
 
@@
 
-# Discussion
+## Implications for Replication Research
 
-In this paper, we reported a series of 11 student replications of previously-published empirical studies from the 2015 volume of *Psychological Science*.
-Our goal was to provide a proof of concept for pedagogical replications of recent findings in a top journal.
-Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
-Despite this narrower scope, we believe that insights from our approach are applicable to the broader goal of assessing replicability at scale, with implications both for replication pedagogy and for the practice of replication more broadly.
-We address each in turn.
-
-## Pedagogical Implications
-
-Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
-But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
-Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
-
-Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
-This kind of cross-class collaboration would require instructors to make class results more broadly discoverable.
-We can envision a number of possible avenues for this kind of sharing.
-For example, if some products are shared openly in a repository like the [Open Science Framework](http://osf.io) or [figshare](http://figshare.com) and tagged appropriately, they will be discoverable via search engines.
-Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like [PsychFileDrawer](http://psychfiledrawer.org) or CurateScience (http://curatescience.org/).
-Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible.
-For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/), selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
-
-One challenge for this kind of dissemination is how to curate which projects are released publicly.
-We are generally optimistic about the contributions of student work, but of course not every student project will be scientifically informative.
-To take an edge case, imagine a student makes an error in stimulus randomization that is not caught by the instructors until after data collection and that and creates a major confound in the collected data.
-In this case, we would argue that this work should not be deposited in a targeted replication repository.
-In the end, these decisions will be the responsibility of the course instructor -- much like decisions about when to publish other research.
-
-Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
-Without a central focus on the replication project, students would not have the time or motivation to complete a high quality project; without multiple opportunities for instructor feedback, we would have far less confidence in the quality of the final projects.
-
-Finally, one of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
-Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
-Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
-This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
-
-## Decision Points for Instructors
-
-- how to customize for different levels of instructor
-
-### Ethical approvals
-
-### Study selection
-
-- student expertise
-- group wiork
-- Strength of evidence in original, e.g. BF > 3
-
-### Contacting original authors
-
-### Results deposit
-
-## Implications for Replication Research
+### Statistical Findings
 
@@
 
-One potential concern about our project is that our replications might be of lower quality, due to the lead role played by inexperienced investigators.
+<!-- One potential concern about our project is that our replications might be of lower quality, due to the lead role played by inexperienced investigators.
 This issue should be taken seriously by any instructor interested in doing replications in the classroom, but we believe it is not a major concern in the current case.
@@
 In general, we don't see any reason why the career stage of the students in our class should be more of a concern in the current case than it is for other research.
+-->
 
@@
 Both of these explanations are consistent with our observations, and, based on the previous literature [@osf2015,@vanbavel2016], we speculate that both winner's curse and context effects were present to some degree.
+
+### Key Tests
 
@@
 
-## Conclusions
+# General Discussion
 
-Our results here demonstrate the practical possibility of performing replication research in the classroom.
+In this paper, we reported a series of 11 student replications of previously-published empirical studies from the 2015 volume of *Psychological Science*.
+Our goal was to provide a proof of concept for pedagogical replications of recent findings in a top journal.
+Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
+Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
+
+This kind of cross-class collaboration would require instructors to make class results more broadly discoverable.
+We can envision a number of possible avenues for this kind of sharing.
+For example, if some products are shared openly in a repository like the [Open Science Framework](http://osf.io) or [figshare](http://figshare.com) and tagged appropriately, they will be discoverable via search engines.
+Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like [PsychFileDrawer](http://psychfiledrawer.org) or CurateScience (http://curatescience.org/).
+Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible.
+For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/), selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
+
+One challenge for this kind of dissemination is how to curate which projects are released publicly.
+We are generally optimistic about the contributions of student work, but of course not every student project will be scientifically informative.
+To take an edge case, imagine a student makes an error in stimulus randomization that is not caught by the instructors until after data collection and that and creates a major confound in the collected data.
+In this case, we would argue that this work should not be deposited in a targeted replication repository.
+In the end, these decisions will be the responsibility of the course instructor -- much like decisions about when to publish other research.
+
+In conclusion, our results here demonstrate the practical possibility of performing replication research in the classroom.
 There are many challenges for ensuring high-quality replications in a pedagogical setting -- from checking experimental methods to reviewing analytic code for errors -- but we would argue that these are not just pedagogical challenges.

### 2017-06-23 paper/paper.Rmd
more reorg

@@
 
-We begin by describing the general method of the class, then discuss shared methods for the replications and the process of development for each project.
-
-## General Class Outline
+We begin by describing the details of our course projects.
+Below, in the subsection on Pedagogical Implications, we discuss broader decision points for the course design that other instructors might consider.
 
@@
 The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.
-
-Students selected projects based on interest, rather than via a systematic sampling strategy.
-After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility.
-The modal study chosen was the first, but several students chose later studies in a set as well.
-Thus, all interpretation of our findings should be with respect to this non-probability sample.
-This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
-
-We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.
-This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
-Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some results.
-
-A summary of the original empirical studies chosen for replication is given in Table \ref{tab:summary}.
-Students chose findings from a wide variety of domains for replication.
-One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transitions between locations on smartphone apps [@liverence2015].
-A second cluster came from studies of social perception and social judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
-Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
-Details of individual replications are available in Supplemental Material.
-
-## Participants
-
-All study participants were recruited on AMT. Individual sample sizes are given in Table \ref{tab:summary}. Each sample was recruited independently, using the same account but a different title.
-
-Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT.
-For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.
-
-Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
-We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses.
-In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).
-
-Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015].
-Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
-For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered.
-
-We eventually used a hybrid, case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget.^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study.
-In four cases, we powered the replication attempt to 80\% post-hoc power.
-In four cases, we used the original sample size.
-In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect.
-In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).
-In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.
-
-## Materials and Methods
-
-Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
-For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials).
-Responses were received in all but one case, all within a matter of days.
-
-## Workflow
+A schematic of our class timeline is shown in Figure 1.
 
@@
 
-All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
-All analyses were written using R, a free and open-source platform for statistical analysis.
-A schematic of our class workflow is shown in Figure 1.
-Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
-This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
+A summary of the original empirical studies chosen for replication is given in Table \ref{tab:summary}.
+Students chose findings from a wide variety of domains for replication.
+One cluster of studies included investigations of memory and visual attention [e.g., @xu2015], for example in applied contexts like remembering "deleted" files [@storm2015] or tracking transitions between locations on smartphone apps [@liverence2015].
+A second cluster came from studies of social perception and social judgment, including judgments of faces and voices [@ko2015;@sofer2015], as well as studies of attributions of modesty, creativity, and expertise [@atir2015;@scopelliti2015;@proudfoot2015].
+Other studies investigated increasing retirement savings by orienting participants to the future [@lewis2015], legacy priming [@zaval2015], and the effects of math anxiety on performance [@wang2015].
+Details of individual replications are available in Supplemental Material.
 
-Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods.
-Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures).
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.
+## Participants
+
+All study participants were recruited on AMT.
+Individual sample sizes are given in Table \ref{tab:summary}.
+Each sample was recruited independently, using the same account but a different title.
+Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT.
+For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.
+
+We determined sample sizes using a case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget (see below for discussion).^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study.
+In four cases, we powered the replication attempt to 80\% post-hoc power.
+In four cases, we used the original sample size.
+In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect.
+In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).
+In the last case, the original study used a multi-step procedure where the first step consisted of stimulus generation; we decreased the N in the first stage of the procedure and focused on achieving high power at the second stage.
+
+## Materials and Methods
+
+Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
+For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials).
+Responses were received in all but one case, all within a matter of days.
 
@@
 
-## Statistical approach
+## Statistical Approach
 
@@
 Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications.
-Thus, we interpret "key statistical test" results with caution.
+Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below).
 Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for replication planning and analysis.
@@
 
-## Pedagogical Assessment
+## Results: Pedagogical Assessment
 
@@
 
-## Pedagogical Implications
+## Discussion: Pedagogical Implications
 
@@
 
+HOW CAN THIS BE GENERALIZED
+
+### Models for students of different levels
+
 Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
 Without a central focus on the replication project, students would not have the time or motivation to complete a high quality project; without multiple opportunities for instructor feedback, we would have far less confidence in the quality of the final projects.
+
++ every student a separate project
++ group projects
++ single class projects
+
+### Project selection
+
+Greater/lesser proejct curation
+
+Students selected projects based on interest, rather than via a systematic sampling strategy.
+After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility.
+The modal study chosen was the first, but several students chose later studies in a set as well.
+Thus, all interpretation of our findings should be with respect to this non-probability sample.
+This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
+
+### Subject population
+
+We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.
+This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
+Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some results.
+
+Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
+We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses.
+In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).
+
+Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015].
+Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered.
+
+### Ethical approvals
+
+We
+
+Contacting original authors
+
+### Workflow selection
 
@@
 
-## Decision Points for Instructors
+All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
+All analyses were written using R, a free and open-source platform for statistical analysis.
+Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
+This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
 
-- how to customize for different levels of instructor
-
-### Ethical approvals
-
-### Study selection
-
-- student expertise
-- group wiork
-- Strength of evidence in original, e.g. BF > 3
-
-### Contacting original authors
-
-### Results deposit
+Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods.
+Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures).
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.
 
@@
 
-## Confirmatory analyses
+## Results
+
+All reported results are from pre-registered, confirmatory analyses.
 
@@
 
-## Implications for Replication Research
+## Discussion: Implications for Replication Research
 
@@
 Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
+
+<!-- MORE INSPIRATIONAL MATERIAL  -->
 

### 2017-06-25 paper/paper.Rmd
some revisions

@@
 
-To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4](https://osf.io/98ta4).
+To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/).
 In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
@@
 
+Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, following the materials and methods specified by the original authors as closely as possible.
 Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
@@
 
-In addition to as-needed guidance on projects, students went through a process in which each student's work was reviewed several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH).
-Each student collected two pilot samples and review was coordinated with these.
+In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH).
+After selecting their replication targets, students' first milestone was to fill in the methods section of the @osc2015 replication report template, which was reviewed for feasability and concreteness.
+This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template).
+
+Further reviews were coordinated with completion of two pilot samples (see Fig.
+1).
 The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
@@
 Once requested changes were made, the student conducted "Pilot B," using a handful of naive participants recruited from AMT.
-The goal of this pilot was to ensure that participants were able to complete the study and did not report any substantial issues with instructions or technical details of the study (All students were instructed to give participants a way to leave free-form comments at the end of the study, prior to debriefing).
+The goal of this pilot was to ensure that participants were able to complete the study and did not report any substantial issues with instructions or technical details of the study (all students were instructed to give participants a way to leave free-form comments at the end of the study, prior to debriefing).
 At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
@@
 We included this project in the final analysis.)
-
-Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
-We coded projects independently on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), and then discussed our ratings and made adjustments (without coming to full consensus).
-The mean rating was `r round(mean(d$fidelity), digits = 2)` (range: `r round(min(d$fidelity), digits = 2)` -- `r round(max(d$fidelity), digits = 2)`).
-Several studies were essentially identical to the originals, but there was a group of others that included differences in population, number of trials, or method that might plausibly have had an effect on the results.
-
-In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
-In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
-After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest.
-We report results from these corrected tests here.
-We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].
 
@@
 
-### Subjective judgments of replication
+**rxdh: re: Dan Simons' comment about the results being cumbersome w/o Table 1 showing individual replication outcomes, maybe we should explicitly state our motivation behind presenting these results and say something along the lines of "to avoid targeting particular authors for potential criticism on the basis of a single replication, we only present summary evaluations aggregated across our replications"**
+
+**rxdh: this next paragraph seems a bit minor and might be better in a footnote?**
+
+In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
+In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
+After discussion, the instructor team converged on a statistical test that they thought better corresponded to the original authors' intended hypothesis of interest.
+We report results from these corrected tests here.
+We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].
+
+### Subjective fidelity of replications
+
+Each member of the instructor team coded the fidelity of replications, weighing whether the materials, sample, and task parameters differed from the original studies.
+We coded projects independently on a scale of 1 -- 7 (with 1 being a loose replication with substantive deviations from the original, and 7 being essentially identical), and then discussed our ratings and made adjustments (without coming to full consensus).
+The mean rating was `r round(mean(d$fidelity), digits = 2)` (range: `r round(min(d$fidelity), digits = 2)` -- `r round(max(d$fidelity), digits = 2)`).
+Several studies were essentially identical to the originals, but there was a group of others that included differences in population, number of trials, or method that might plausibly have had an effect on the results.
+
+### Subjective success of replications
 
@@
 Only `r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be informative, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may , however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
 

### 2017-06-25 paper/paper.Rmd
More revisions

@@
 Only `r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may , however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
 
@@
 
-Effect sizes and Bayes factors improve upon inferences drawn from $p$-values in different ways.
-The effect size is an estimate of the *magnitude* of an effect, which is stable across sample sizes (assuming a constant experimental procedure) and allows for a more fine-grained comparison across studies than a binary significance criterion.
-The Bayes Factor is an alternative hypothesis testing method that quantifies the evidence in favor of a hypothesis [@jeffreys1961].
+Effect sizes and Bayes factors supplement inferences drawn from $p$-values in different ways.
+The effect size is an estimate of the *magnitude* of an effect.
+Unlike the $p$-value, this underlying magnitude is stable across sample sizes (assuming a constant experimental procedure) though the estimate may be more or less noisy.
+It thus allows for a more fine-grained comparison across studies than a binary significance criterion.
+The Bayes Factor is an alternative hypothesis testing method that directly quantifies the evidence in favor of one hypothesis relative to another [@jeffreys1961].
 Among other advantages, it does not privilege the null hypothesis and can provide evidence either for or against a hypothesis [see also @scheibehenne2016;@wagenmakers2016].
@@
 
-These additional measures therefore give additional criteria for evaluating replications: If the replication shows roughly the same effect size or Bayes factor as the original results despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we may nonetheless consider it a success.
+These additional measures therefore give additional criteria for evaluating replications: If the replication shows roughly the same effect size or Bayes factor as the original results despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we may nonetheless consider it more of a success.
 To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1.^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.

### 2017-06-26 paper/paper.Rmd
Pandoc list fail...
First batch revisions

@@
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
-Yet under the current incentive structure for science, replication is not typically valued.
+Yet under the current incentive structure for science, replication is not typically valued replication is not typically valued for publication [@makel2012], or in metrics of research productivity [@koole2012].
 One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
-Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy.
+Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.
 
@@
 We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study.
-In four cases, we powered the replication attempt to 80\% post-hoc power.
+In four cases, we powered the replication attempt to 80\% power based on post-hoc power calculations of the original effect sizes.
 In four cases, we used the original sample size.
-In one case, the original study was powered well above what would be required to find the effect of interest in the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect.
+In one case, the original study was powered well above what would be required to find the effect of interest based on the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect.
 In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate).
@@
 
-+ every student a separate project
-+ group projects
-+ single class projects
+every student a separate project
+group projects
+single class projects
 
@@
 After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility.
+However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research.
 The modal study chosen was the first, but several students chose later studies in a set as well.
@@
 
+As much of psychological research is now conducted online, and we know of few PhD programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
+Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.
+
 ### Ethical approvals
 
-We
+**Add our own paragraph and IRB notes**
 
-Contacting original authors
+We are not familiar with the particularities of Institutional Review Boards across institutions, but suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
+We briefly highlight a few, with potential resolutions and comments.
+
+*IRB approval is not possible within the time constraints of a class.*  To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds.
+Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if said studies provide full open-source materials that can be used in the IRB protocol submitted.
+
+*There is a potential for harm given constraints of class.* Instructor review.
+Has been previously approved, and coercion/privacy confidentiality.
+Anonymizing codes; securing data.
+How much role instructors play in this dependent on student competence.
 
@@
 This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.
+
+## Funding and Power limitations
+
+(Eric -I think this should be addressed - maybe mention free participant pools, value of learning how to recruit.
+OR if lucky (like us) apply for a grant.
+Also call for OSF and other organizations devoted to replications to provide small grants of this sort.
+
+Case-by-case selection
 

### 2017-06-26 paper/paper.Rmd
Small revisions

@@
 \caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects.
+All project materials available publicly at osf.io/98ta4/files/.
 * marks projects where the number of trials was modified.}
@@
 
+Prerequisites - minimal
+
 ### Project selection
@@
 After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility.
+We encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design.
 However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research.
@@
 This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
+
+### Author contact
+
+Good faith replication based on the materials avaialble to an independent researcher.
+This was an active choice.
+Only to receive materials or information not possible to resolve from the published article.
+
+However, we acknowledge there are benefits of contacting all authors.  Even just to say "this is what we're doing"
+
+""
 

### 2017-06-26 paper/paper.Rmd
Intro and start to new discussion

@@
 
-In the current article, we report the results of replication projects conducted in a single class (a graduate-level experimental methods course).
-As part of the required work of the course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*.
-These studies give evidence about the state of replicability in the field.
-They also provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.
+In the current article, we address the practical barriers of completing replcations as part of required coursework and discuss the methodological decisions that replication projects must address more braodly.
+Towards this aim, report the results of replication projects conducted in a graduate-level experimental methods course.
+Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*.
+These studies provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.
 
-Past work has explicitly attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016].
-Presupposing that this construct is even meaningful [cf.
-@gergen1973], assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [e.g., @stroebe2014] and establishing a standard for replication success [e.g., @simonsohn2015].
-Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality.
-Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014;@wagenmakers2016].
-
-In the current work, we do not address these issues; instead, our goal is more modest.
 We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings.
@@
 
-We begin by describing the details of our course projects.
-Below, in the subsection on Pedagogical Implications, we discuss broader decision points for the course design that other instructors might consider.
+We begin by describing the details of our course projects to give a sense of what a classroom replication project entails.
+We then discuss broader decision points for the course design that other instructors might consider.
+Lastly, we report the results our replications, highlighting the importance of wide-scale replication.
 
@@
 
-All study participants were recruited on AMT.
+All study participants were recruited on Amazon Mechanical Turk (AMT).
 Individual sample sizes are given in Table \ref{tab:summary}.
@@
 
-## Discussion: Pedagogical Implications
-
 Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
@@
 
-HOW CAN THIS BE GENERALIZED
+## Discussion: Pedagogical Implications
+
+Above we have shown that classroom replication projects are possible.
+We now present information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of course work.
+This includes practical recommendations for implementation in a variety of classroom, key decision that instructors must make, and common issues that may arise throughout the projects and ways to mitigate or prevent these issues.
 

### 2017-06-26 paper/paper.Rmd
table of class models

@@
 Above we have shown that classroom replication projects are possible.
-We now present information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of course work.
+We now present information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of coursework.
 This includes practical recommendations for implementation in a variety of classroom, key decision that instructors must make, and common issues that may arise throughout the projects and ways to mitigate or prevent these issues.
@@
 
-every student a separate project
-group projects
-single class projects
+That said, we beleive there are many ways to adapt the project format based on the students and constraints of the class.
+In Table \ref{tab:classmodels} below, we present mulitple ways in which replication projects may be included in classrooms.
+Though we do not go into detail on the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.
 
-Prerequisites - minimal
+\begin{landscape}
+\centering
+
+\newcommand{\specialcell}[2][c]{%
+  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
+
+\begin{table}[ht]
+\footnotesize
+\centering
+
+\def\arraystretch{1.2}
+
+\begin{tabular}{l|lll}
+
+  \hline
+
+ & \multicolumn{3}{c}{\underline{Classroom Models}} \\
+
+ & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\
+
+Students & \multicolumn{1}{p{2in}}{\raggedright Undergraduate} & \multicolumn{1}{p{2in}}{\raggedright Advanced Undergraduate or Early Graduate} & \multicolumn{1}{p{2in}}{\raggedright Motivated Graduate} \\
+
+Goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Conduct collaborative research} & \multicolumn{1}{p{2in}}{\raggedright Learn best practices and tools} \\
+
+Grouping & \multicolumn{1}{p{2in}}{\raggedright Full Class OR Medium groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individual} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\
+
+Project Selection & \multicolumn{1}{p{2in}}{\raggedright One class replication OR pre-specified list} & \multicolumn{1}{p{2in}}{\raggedright Curated list to choose from} & \multicolumn{1}{p{2in}}{\raggedright Open to student choice*} \\
+
+Data source & \multicolumn{1}{p{2in}}{\raggedright University or classroom participant pool} & \multicolumn{1}{p{2in}}{\raggedright In-person or online convenience sample} & \multicolumn{1}{p{2in}}{\raggedright targetted sampling of original populations} \\
+
+Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use familiar or GUI tools OR instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach key tool plus introduction of others} & \multicolumn{1}{p{2in}}{\raggedright Teach full set of free open-source software} \\
+
+Review & \multicolumn{1}{p{2in}}{\raggedright Standardized format for submission} & \multicolumn{1}{p{2in}}{\raggedright Group and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\
+
+Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor (drafted by students)} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students (with instructor review)} \\
+
+Dissemination & \multicolumn{1}{p{2in}}{\raggedright If up to quality standard} & \multicolumn{1}{p{2in}}{\raggedright Upon review of instructors} & \multicolumn{1}{p{2in}}{\raggedright Discuss dissemination as a class} \\
+
+\hline
+
+\end{tabular}
+\caption{\label{tab:classmodels} *This can also be done with random selection with sampling criteria} 
+\label{tab:classmodels}
+\end{table}
+
+\end{landscape}
 

### 2017-06-26 paper/paper.Rmd
small table fixes

@@
 
- & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\
+\multicolumn{1}{p{1.5in}|}{\raggedright \underline{Course Attributes}} & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\
 
@@
 
-Data source & \multicolumn{1}{p{2in}}{\raggedright University or classroom participant pool} & \multicolumn{1}{p{2in}}{\raggedright In-person or online convenience sample} & \multicolumn{1}{p{2in}}{\raggedright targetted sampling of original populations} \\
+Data source & \multicolumn{1}{p{2in}}{\raggedright University or classroom participant pool} & \multicolumn{1}{p{2in}}{\raggedright In-person or online convenience sample} & \multicolumn{1}{p{2in}}{\raggedright Targetted sampling of original populations} \\
 

### 2017-06-26 paper/paper.Rmd
Selection and author contact

@@
 In Table \ref{tab:classmodels} below, we present mulitple ways in which replication projects may be included in classrooms.
-Though we do not go into detail on the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.
+Though we do not go into detail on all of the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.
+We next turn to detailed discussion on a few we believe most pertinent to instructors.
 
@@
 
-Greater/lesser proejct curation
-
-Students selected projects based on interest, rather than via a systematic sampling strategy.
+In our class, students selected projects based on interest, rather than via a systematic sampling strategy.
 After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility.
@@
 
+The set of studies could be curated more or less for students based on expertise and constraints.
+At the other extreme from our small graduate class, in a large undergraduate class it may make logistical sense for the instructors to choose 1-3 replication projects that students can select from.
+This would allow the instructor to be familiar with all replication projects taking place, and provide more structured discussion and problem-solving based on the challenges groups may run into.
+
 ### Author contact
 
-Good faith replication based on the materials avaialble to an independent researcher.
-This was an active choice.
-Only to receive materials or information not possible to resolve from the published article.
+Over half of our students reached out to original authors to request study materials or clafication on methods and/or analysis.
+For the purposes of this class, we chose not to require contact with all original authors.
+Methods and materials should be open to allow for replication and incremental science [@nosek2015], and hoped to make the pedagogical point that good research should not require a researcher to return your email, and make students feel empowered that they can engage with and build on the published literature directly.
+That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.
+Only in cases where there are issues about access to materials or ambiguities in design/analysis were authors contacted.
 
-However, we acknowledge there are benefits of contacting all authors.  Even just to say "this is what we're doing"
-
-""
+However, we acknowledge there are benefits of contacting all authors.
+There are two main methods of doing so.
+First is as a professional courtesy by letting the authors know that their study is being replicated.
+This not only provides goodwill (as replication are perceived by some to be adversarial; see Kahneman commentary?), it would also allow the original authors to pre-register their hypotheses or concerns with the replication study as experts in the underlying theory.
+Second is as a request for methodological feedback prior to replication.
+This is a trickier issue on many fronts.
+By requesting feedback, this perpetuates insider information or lab-specific folklore on methodology that produces the greatest effects.
+When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science.
+In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).
+In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies.
+Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.
 
@@
 Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some results.
+Other classes many find participant pools or recruitment of community samples more feasible and appropriate.
 

### 2017-06-26 paper/paper.Rmd
Mods and Ethics section

@@
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
-Yet under the current incentive structure for science, replication is not typically valued replication is not typically valued for publication [@makel2012], or in metrics of research productivity [@koole2012].
+Yet under the current incentive structure for science, replication is not typically valued valued for publication [@makel2012], or in metrics of research productivity [@koole2012].
 One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
@@
 
+As much of psychological research is now conducted online, and we know of few PhD programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
+Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.
+
 Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015].
@@
 
-As much of psychological research is now conducted online, and we know of few PhD programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
-Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.
-
-### Ethical approvals
-
-**Add our own paragraph and IRB notes**
-
-We are not familiar with the particularities of Institutional Review Boards across institutions, but suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
-We briefly highlight a few, with potential resolutions and comments.
-
-*IRB approval is not possible within the time constraints of a class.*  To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds.
-Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if said studies provide full open-source materials that can be used in the IRB protocol submitted.
-
-*There is a potential for harm given constraints of class.* Instructor review.
-Has been previously approved, and coercion/privacy confidentiality.
-Anonymizing codes; securing data.
-How much role instructors play in this dependent on student competence.
+In this set of replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies.
+Though we discussed these allocations and bartered allocations as a class, we had a few guiding principles.
+We first prioritized achieving the participants required for either 80% or original N (whichever was greater) for the maximum number of studies.
+This benefitted studies which were under the budget allocated for each individual project (i.e.
+studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power.
+This allowed us to reach our budget goals with the exception of one particularly expensive study.
+Fortunately, this student found external funding to reach 80% power.
+If this were not possible, we would have likely excluded this study from the pre-registration.
 
@@
 
-## Funding and Power limitations
+### Ethical approvals
 
-(Eric -I think this should be addressed - maybe mention free participant pools, value of learning how to recruit.
-OR if lucky (like us) apply for a grant.
-Also call for OSF and other organizations devoted to replications to provide small grants of this sort.
+Institutional Review Boards are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
+We address just two, with potential resolutions and comments.
 
-Case-by-case selection
+Instructors may first be concerned that IRB approval is not possible within the time constraints of the class.
+To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds.
+Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if these studies provide full open-source materials that can be used in the IRB protocol submitted.
+
+In addition, instructors and review boards may believe there is a greater potential for harm given constraints of class.
+That is, there may be less oversight to each individual project.
+However, we note that especially if the original studies have been previously approved by their respective institutional review board, the review process is similar to one might expect out of an advisee/advisor relationship.
+Particular consideration should be given to concerns of confidentiality of collected data, and we may suggest that for less experienced students, identifiable participant data should only be accessed by the instructor team.
+Lastly, this project can also be a useful tool to have class discussions around coersion, harm vs.
+benefit, and other ethical issues that may arise during reserach.
 

### 2017-06-27 paper/paper.Rmd
Small fixes

@@
 In the current article, we address the practical barriers of completing replcations as part of required coursework and discuss the methodological decisions that replication projects must address more braodly.
-Towards this aim, report the results of replication projects conducted in a graduate-level experimental methods course.
+Towards this aim, we report the results of replication projects conducted in a graduate-level experimental methods course.
 Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*.
@@
 Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole---both scientific and educational---would be considerable.
+
+We begin by describing the details of our course projects to give a sense of what a classroom replication project entails.
+We then discuss broader decision points for the course design that other instructors might consider.
+Lastly, we report the results our replications, highlighting the importance of wide-scale replication efforts.
 
@@
 
-We begin by describing the details of our course projects to give a sense of what a classroom replication project entails.
-We then discuss broader decision points for the course design that other instructors might consider.
-Lastly, we report the results our replications, highlighting the importance of wide-scale replication.
-
 All projects were completed as part of a graduate-level methodology class.
@@
 
-Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including at least: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
 But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
@@
 Though we do not go into detail on all of the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.
-We next turn to detailed discussion on a few we believe most pertinent to instructors.
+We next turn to detailed discussion on a subset of aspects we believe most pertinent to instructors.
 
@@
 
-Goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Conduct collaborative research} & \multicolumn{1}{p{2in}}{\raggedright Learn best practices and tools} \\
+Learning Goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Conduct collaborative research} & \multicolumn{1}{p{2in}}{\raggedright Learn best practices and tools} \\
 
-Grouping & \multicolumn{1}{p{2in}}{\raggedright Full Class OR Medium groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individual} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\
+Project Grouping & \multicolumn{1}{p{2in}}{\raggedright Full Class or Medium-sized groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individual} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\
 
-Project Selection & \multicolumn{1}{p{2in}}{\raggedright One class replication OR pre-specified list} & \multicolumn{1}{p{2in}}{\raggedright Curated list to choose from} & \multicolumn{1}{p{2in}}{\raggedright Open to student choice*} \\
+Project Selection & \multicolumn{1}{p{2in}}{\raggedright One class replication or pre-specified list} & \multicolumn{1}{p{2in}}{\raggedright Curated list to choose from} & \multicolumn{1}{p{2in}}{\raggedright Open to student choice*} \\
 
@@
 
-Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use familiar or GUI tools OR instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach key tool plus introduction of others} & \multicolumn{1}{p{2in}}{\raggedright Teach full set of free open-source software} \\
+Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use familiar or GUI tools or instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach key open-source tool plus introduce others} & \multicolumn{1}{p{2in}}{\raggedright Teach full set of free open-source software} \\
 
-Review & \multicolumn{1}{p{2in}}{\raggedright Standardized format for submission} & \multicolumn{1}{p{2in}}{\raggedright Group and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\
+Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\
 
@@
 \end{tabular}
-\caption{\label{tab:classmodels} *This can also be done with random selection with sampling criteria} 
+\caption{\label{tab:classmodels} The potential models for incorporating replication studies in required coursework. *This can also be done with a systematic sampling strategy} 
 \label{tab:classmodels}
@@
 The set of studies could be curated more or less for students based on expertise and constraints.
-At the other extreme from our small graduate class, in a large undergraduate class it may make logistical sense for the instructors to choose 1-3 replication projects that students can select from.
+For example, in a large undergraduate class it may be logistical simpler for the instructors to choose 1-3 replication projects that students can select from.
 This would allow the instructor to be familiar with all replication projects taking place, and provide more structured discussion and problem-solving based on the challenges groups may run into.
@@
 For the purposes of this class, we chose not to require contact with all original authors.
-Methods and materials should be open to allow for replication and incremental science [@nosek2015], and hoped to make the pedagogical point that good research should not require a researcher to return your email, and make students feel empowered that they can engage with and build on the published literature directly.
+We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to make students feel empowered that they can engage with and build on the published literature directly.
 That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.
-Only in cases where there are issues about access to materials or ambiguities in design/analysis were authors contacted.
+Only in cases where there were issues about access to materials or ambiguities in design or analysis were authors contacted.
 
-However, we acknowledge there are benefits of contacting all authors.
+However, we acknowledge there are benefits of contacting all original authors.
 There are two main methods of doing so.
@@
 
-As much of psychological research is now conducted online, and we know of few PhD programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
+As much of psychological research is now conducted online and we know of few graduate programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
 Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.
+
+### Sample size and power analyses
 

### 2017-06-27 paper/paper.Rmd
Add back paragraph

@@
 
+<!-- Past work has explicitly attempted to estimate the proportion of true effects in a particular literature [@ioannidis2005;@osc2015], but this goal is challenging -- perhaps even impossible [@gilbert2016;@anderson2016].
+Presupposing that this construct is even meaningful [cf.
+@gergen1973], assessing the truth of even an individual effect relies on delineating what constitutes an exact replication [e.g., @stroebe2014] and establishing a standard for replication success [e.g., @simonsohn2015].
+Estimating the proportion of true effects in a literature further requires a systematic sampling strategy to ensure generality.
+Furthermore, no single replication attempt is definitive, so multiple iterations are typically necessary to increase the evidential value of replication attempts [@lewis2016;@klein2014;@wagenmakers2016].
+-->
+
 <!-- One potential concern about our project is that our replications might be of lower quality, due to the lead role played by inexperienced investigators.

### 2017-06-27 paper/paper.Rmd
mcf pass

@@
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
-Yet under the current incentive structure for science, replication is not typically valued valued for publication [@makel2012], or in metrics of research productivity [@koole2012].
+Yet under the current incentive structure for science, replication is not typically valued for publication [@makel2012] or in metrics of research productivity [@koole2012].
 One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
@@
 There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise.
-Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole---both scientific and educational---would be considerable.
+Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole -- both scientific and educational -- would be considerable.
 
@@
 To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/).
-In addition, all of the most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
+In addition, all of our most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
 We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.
@@
 Individual project preregistration links are given in Table 1.
-Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper ([https://osf.io/rxz8m/](https://osf.io/rxz8m/)).
+Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper at [https://osf.io/rxz8m/](https://osf.io/rxz8m/).
 
@@
 
-All code and data necessary to reproduce the analyses reported here are available at: [https://osf.io/98ta4](https://osf.io/98ta4).
+All code and data necessary to reproduce the analyses reported here are available at [https://osf.io/98ta4](https://osf.io/98ta4).
 
@@
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
-We are grateful to the authors of the original studies who provided materials and gave comments on a draft of this manuscript.
+We are grateful to the authors of the original studies who provided materials and gave extensive comments on an earlier draft of this manuscript.
 
@@
 
-Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, following the materials and methods specified by the original authors as closely as possible.
+Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, following the methods specified by the original authors as closely as possible.
 Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
-For `r sum(project_plan$author_contact != "")` studies, however, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials).
+For `r sum(project_plan$author_contact != "")` studies, students contacted the authors to request either materials or clarification of methods using a template email that was customized by the students and reviewed by the instructors (this template is included in our course materials).
 Responses were received in all but one case, all within a matter of days.
 
-## Preregistration and Review
+## Writing, Preregistration, and Review
 
-In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor (MCF) and the teaching assistants (ENS and RXDH).
+Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods.
+Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures).
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors (@nuijten2015), given that errors are often introduced by transferring results between statistics and word-processing software packages.]
+
+In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants.
 After selecting their replication targets, students' first milestone was to fill in the methods section of the @osc2015 replication report template, which was reviewed for feasability and concreteness.
@@
 Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below).
-Despite this interpretive difficulty, following previous work, we attempted to use a single statistical test as our target for replication planning and analysis.
+Despite this interpretive difficulty, we followed previous work and attempted to use a single statistical test as our target for replication planning and analysis.
 
@@
 
-Above we have shown that classroom replication projects are possible.
-We now present information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of coursework.
-This includes practical recommendations for implementation in a variety of classroom, key decision that instructors must make, and common issues that may arise throughout the projects and ways to mitigate or prevent these issues.
+Our findings demonstrate that classroom replication projects are possible in one particular context.
+In the following subsections, we provide information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of coursework in their courses.
+We discuss practical recommendations for implementation in a variety of classroom settings, key decisions that instructors must make, and common issues that arise during replication projects.
 
@@
 
-That said, we beleive there are many ways to adapt the project format based on the students and constraints of the class.
-In Table \ref{tab:classmodels} below, we present mulitple ways in which replication projects may be included in classrooms.
-Though we do not go into detail on all of the specifics of what each of these courses might entail, we hope this provides an overview of the possibilities inherent in including replication work as part of student learning.
-We next turn to detailed discussion on a subset of aspects we believe most pertinent to instructors.
+That said, depending on the student population and class constraints, there are many ways to include a replication project in a course.
+Table \ref{tab:classmodels} presents three different possible models of replication projects, for general undergraduate classes, advanced undergraduate/early graduate classes, and more advanced graduate classes.
+These models are not meant to be binding suggestions, but we hope that they inspire instructors to consider how replication research could be included in their own teaching practice.
+The sections below provide some discussion of individual choice-points.
 
@@
 
-\begin{tabular}{l|lll}
+\begin{tabular}{lccc}
+
+ & \multicolumn{3}{c}{\underline{Classroom Models}} \\
+
+\multicolumn{1}{p{1.5in}}{\raggedright \underline{Course Attributes}} & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\
+
+Student group & \multicolumn{1}{p{2in}}{\raggedright General Undergraduate} & \multicolumn{1}{p{2in}}{\raggedright Advanced Undergraduate or Graduate} & \multicolumn{1}{p{2in}}{\raggedright Sophisticated Graduate} \\
 
@@
 
- & \multicolumn{3}{c}{\underline{Classroom Models}} \\
+Learning goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Gain research independence} & \multicolumn{1}{p{2in}}{\raggedright Master best practices and tools} \\
 
-\multicolumn{1}{p{1.5in}|}{\raggedright \underline{Course Attributes}} & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\
+Group size & \multicolumn{1}{p{2in}}{\raggedright Full class / medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\
 
-Students & \multicolumn{1}{p{2in}}{\raggedright Undergraduate} & \multicolumn{1}{p{2in}}{\raggedright Advanced Undergraduate or Early Graduate} & \multicolumn{1}{p{2in}}{\raggedright Motivated Graduate} \\
-
-Learning Goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Conduct collaborative research} & \multicolumn{1}{p{2in}}{\raggedright Learn best practices and tools} \\
-
-Project Grouping & \multicolumn{1}{p{2in}}{\raggedright Full Class or Medium-sized groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individual} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\
-
-Project Selection & \multicolumn{1}{p{2in}}{\raggedright One class replication or pre-specified list} & \multicolumn{1}{p{2in}}{\raggedright Curated list to choose from} & \multicolumn{1}{p{2in}}{\raggedright Open to student choice*} \\
+Project selection & \multicolumn{1}{p{2in}}{\raggedright Single class replication or small curated list} & \multicolumn{1}{p{2in}}{\raggedright Curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection*} \\
 
@@
 
-Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use familiar or GUI tools or instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach key open-source tool plus introduce others} & \multicolumn{1}{p{2in}}{\raggedright Teach full set of free open-source software} \\
+Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use GUI tools / instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key open-source tool (e.g., R)} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key open-source tools} \\
 
-Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\
+<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->
 
@@
 
-Dissemination & \multicolumn{1}{p{2in}}{\raggedright If up to quality standard} & \multicolumn{1}{p{2in}}{\raggedright Upon review of instructors} & \multicolumn{1}{p{2in}}{\raggedright Discuss dissemination as a class} \\
-
-\hline
+Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default (subject to disucssion)} \\
 
 \end{tabular}
-\caption{\label{tab:classmodels} The potential models for incorporating replication studies in required coursework. *This can also be done with a systematic sampling strategy} 
+\caption{\label{tab:classmodels} Three potential models for incorporating replication projects into classes of different levels.} 
 \label{tab:classmodels}
@@
 We encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design.
-However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research.
+This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at other levels.
+For example, in a large undergraduate class it may be logistically simpler for the instructors to choose 1 -- 3 replication projects that students can select from.
+This step would both give instructors a greater degree of familiarity with the literature and allow for the development of more scaffolding with respect to the development of experimental materials.
+A mid-level course might split the difference between these two models, providing students with a broader -- but still curated -- list of potential projects.
+
+<!-- However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research.
 The modal study chosen was the first, but several students chose later studies in a set as well.
@@
 This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
-
-The set of studies could be curated more or less for students based on expertise and constraints.
-For example, in a large undergraduate class it may be logistical simpler for the instructors to choose 1-3 replication projects that students can select from.
-This would allow the instructor to be familiar with all replication projects taking place, and provide more structured discussion and problem-solving based on the challenges groups may run into.
+-->
 
@@
 
-Over half of our students reached out to original authors to request study materials or clafication on methods and/or analysis.
-For the purposes of this class, we chose not to require contact with all original authors.
-We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to make students feel empowered that they can engage with and build on the published literature directly.
+Over half of our students contacted original authors to request study materials or clafication on methods and/or analysis, but for the purposes of our class, we chose not to require contact with all original authors.
+We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to empower students to engage with and build on the published literature directly -- without personal relationships or even personal contact.
 That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.
-Only in cases where there were issues about access to materials or ambiguities in design or analysis were authors contacted.
+Authors were contacted only in cases where there were issues about access to materials or ambiguities in design or analysis.
+There are benefits of contacting original authors, however.
+In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition).
+In the end, it is up to individual instructors to decide what they believe is best for their students.
 
-However, we acknowledge there are benefits of contacting all original authors.
-There are two main methods of doing so.
-First is as a professional courtesy by letting the authors know that their study is being replicated.
-This not only provides goodwill (as replication are perceived by some to be adversarial; see Kahneman commentary?), it would also allow the original authors to pre-register their hypotheses or concerns with the replication study as experts in the underlying theory.
-Second is as a request for methodological feedback prior to replication.
-This is a trickier issue on many fronts.
-By requesting feedback, this perpetuates insider information or lab-specific folklore on methodology that produces the greatest effects.
+<!-- First, contact is a professional courtesy that lets the authors know that their study is being replicated and in some cases allows the original authors to pre-register their hypotheses or concerns with the replication study.
+Second, original authors can provide methodological feedback prior to replication.
+This second is a trickier issue on many fronts.
+By requesting feedback, discussion with authors perpetuates the dissemination of insider information or lab-specific folklore on methodology that produces the greatest effects.
 When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science.
@@
 Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.
+-->
 
@@
 
-We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.
-This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
-Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some results.
+We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.^[Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
+We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses due to failures to distinguish between related experimental paradigms.
+In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).] This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
+As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
+Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers.
+Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some of our results.
 Other classes many find participant pools or recruitment of community samples more feasible and appropriate.
-
-Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
-We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses.
-In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).
-
-As much of psychological research is now conducted online and we know of few graduate programs that require explicit training in online programming and methods, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
-Even if students’ research does not generally consist of online studies, these replications allow students to build a skillset that can be utilized throughout their academic careers.
 
@@
 Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015].
-Post-hoc power analyses are problematic because of the likelihood of inflation of effect sizes due to the "winner's curse" [@hoenig2001;@button2013], but -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
+Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013].
+But -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
 For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered.
+In general, samples for course projects will be limited by the available resources.
+But for all replication research of the type advocated here, achieving high power for a smaller number of studies, perhaps conducted by groups, is preferable to conducting more lower-power studies, because results are much more likely to make a contribution to the replication literature (as well as to be interpretable by students).
+Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in the planning process.
 
-In this set of replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies.
-Though we discussed these allocations and bartered allocations as a class, we had a few guiding principles.
+<!-- In our replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies.
 We first prioritized achieving the participants required for either 80% or original N (whichever was greater) for the maximum number of studies.
-This benefitted studies which were under the budget allocated for each individual project (i.e.
-studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power.
+This rule benefitted studies which were under the budget allocated for each individual project (i.e., studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power.
 This allowed us to reach our budget goals with the exception of one particularly expensive study.
@@
 If this were not possible, we would have likely excluded this study from the pre-registration.
+-->
 
@@
 
-Finally, one of the barriers to more reproducible work in psychology is technical: Some of the tools (programmatic statistical analysis, version control) can feel inaccessible or intimidating to beginners.
-Indeed, our students, who came from a variety of disciplinary backgrounds, had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
-Yet by the end of the course, all had gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
-This experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
-
-All replication studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
+All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
 All analyses were written using R, a free and open-source platform for statistical analysis.
@@
 
-Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods.
-Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures).
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well.] This writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.
+Some of these tools can feel inaccessible or intimidating to beginners.
+Indeed, our students, who came from a variety of disciplinary backgrounds, typically have relatively little experience with web-based empirical studies or literate, reproducible data analysis.
+Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
+Our experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
+
+Our explicit class goal was to provide students with experiences navigating the full ecosystem of open-source scientific tools.
+For classes at different levels, however, instructors will likely have different goals.
+It may be preferrable for an intermediate course to focus on a single programming tool (e.g., R) and to use other GUI-based software for creating experiments, so as to minimize the learning burden for students.
+And for more introductory research methods course, instructors must gauge whether the added difficulty of a programming compoent is appropriate for the skills and backgrounds of their students.
 
@@
 
-Institutional Review Boards are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
-We address just two, with potential resolutions and comments.
-
-Instructors may first be concerned that IRB approval is not possible within the time constraints of the class.
-To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine how to either 1) create a standard protocol that encompassses all replications that will be conducted (in which details can be later added and quickly approved), or 2) plan to submit the protocol early in the course, in line with IRB meeting schedules for quick turnarounds.
-Both issues may be simplified if the study or pool of studies to be replicated is pre-determined and if these studies provide full open-source materials that can be used in the IRB protocol submitted.
-
-In addition, instructors and review boards may believe there is a greater potential for harm given constraints of class.
-That is, there may be less oversight to each individual project.
-However, we note that especially if the original studies have been previously approved by their respective institutional review board, the review process is similar to one might expect out of an advisee/advisor relationship.
-Particular consideration should be given to concerns of confidentiality of collected data, and we may suggest that for less experienced students, identifiable participant data should only be accessed by the instructor team.
-Lastly, this project can also be a useful tool to have class discussions around coersion, harm vs.
-benefit, and other ethical issues that may arise during reserach.
+Institutional Review Boards (IRBs) are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
+First, instructors may first be concerned that IRB approval is not possible within the time constraints of the class.
+To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine whether to create a standard protocol that encompassses all replications that will be conducted, or to determine a timeline for submitting individual protocols very early in the course.
+Both issues may be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
+Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters.
+We recommend building training around ethical issues into the syllabus of replication-based classes.
+This practice is both positive for studetns and mitigates potential IRB concerns via explicit training.
 
@@
 
-All reported results are from pre-registered, confirmatory analyses.
-
-**rxdh: re: Dan Simons' comment about the results being cumbersome w/o Table 1 showing individual replication outcomes, maybe we should explicitly state our motivation behind presenting these results and say something along the lines of "to avoid targeting particular authors for potential criticism on the basis of a single replication, we only present summary evaluations aggregated across our replications"**
-
-**rxdh: this next paragraph seems a bit minor and might be better in a footnote?**
-
-In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
+All reported results are from pre-registered, confirmatory analyses.^[In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
 In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
@@
 We report results from these corrected tests here.
-We return to this issue in the Discussion, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].
+We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).]
+
+<!-- **rxdh: re: Dan Simons' comment about the results being cumbersome w/o Table 1 showing individual replication outcomes, maybe we should explicitly state our motivation behind presenting these results and say something along the lines of "to avoid targeting particular authors for potential criticism on the basis of a single replication, we only present summary evaluations aggregated across our replications"** MCF: let's say this in the coverletter?
+-->
+
+<!-- **rxdh: this next paragraph seems a bit minor and might be better in a footnote?** -->
 
@@
 
-In addition, our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear.
+Our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear.
 For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials.
@@
 Future work would benefit from a statement of constraints on generality so as to provide a guide to the conditions under which an effect is likely to be present [@simons2016].
-Both of these explanations are consistent with our observations, and, based on the previous literature [@osf2015,@vanbavel2016], we speculate that both winner's curse and context effects were present to some degree.
+<!-- Both of these explanations are consistent with our observations, and, based on the previous literature [@osf2015,@vanbavel2016], we speculate that both winner's curse and context effects were present to some degree.
+-->
 
@@
 
-In our view, two recommendations will improve this situation.
+<!-- In our view, two recommendations will improve this situation.
 First, authors should specify their "key test" more clearly.
@@
 Second, the widespread adoption of open data and open analytic code practices would facilitate replication research.
-In addition to clarifying the summary report of results in a paper, the availability of data dramatically facilitates the computation of the relevant meta-analytic effect size for power analysis and statistical comparison.^[We note that, although we were grateful that several authors of the papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.]
+In addition to clarifying the summary report of results in a paper, the availability of data dramatically facilitates the computation of the relevant meta-analytic effect size for power analysis and statistical comparison.^[We note that, although we were grateful that several authors of the papers in our sample shared data and materials, the use of open (non-proprietary) formats for archiving data -- and in particular analytic code -- is often critical for investigators attempting to reproduce analyses.]  -->
 
@@
 Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible.
-For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/), selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
+For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
 
@@
 We are generally optimistic about the contributions of student work, but of course not every student project will be scientifically informative.
-To take an edge case, imagine a student makes an error in stimulus randomization that is not caught by the instructors until after data collection and that and creates a major confound in the collected data.
+To take an edge case, imagine a student makes an error in stimulus presentation that is not caught by the instructors until after data collection.
 In this case, we would argue that this work should not be deposited in a targeted replication repository.
-In the end, these decisions will be the responsibility of the course instructor -- much like decisions about when to publish other research.
+But in the end, these decisions will be the responsibility of the course instructor -- much like decisions about when to publish other research.
 
-In conclusion, our results here demonstrate the practical possibility of performing replication research in the classroom.
+In sum, our results here demonstrate the practical possibility of performing replication research in the classroom.
 There are many challenges for ensuring high-quality replications in a pedagogical setting -- from checking experimental methods to reviewing analytic code for errors -- but we would argue that these are not just pedagogical challenges.

### 2017-06-28 paper/paper.Rmd
Small edits + spellcheck

@@
 
-In the current article, we address the practical barriers of completing replcations as part of required coursework and discuss the methodological decisions that replication projects must address more braodly.
+In the current article, we address the practical barriers of completing replications as part of required coursework and discuss the methodological decisions that replication projects must address more broadly.
 Towards this aim, we report the results of replication projects conducted in a graduate-level experimental methods course.
@@
 To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/).
-In addition, all of our most recent lecture slides and materials are avaialable on our course website at [http://psych254.stanford.edu]().
+In addition, all of our most recent lecture slides and materials are available on our course website at [http://psych254.stanford.edu]().
 We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.
@@
 In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants.
-After selecting their replication targets, students' first milestone was to fill in the methods section of the @osc2015 replication report template, which was reviewed for feasability and concreteness.
+After selecting their replication targets, students' first milestone was to fill in the methods section of the @osc2015 replication report template, which was reviewed for feasibility and concreteness.
 This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template).
@@
 
-Project selection & \multicolumn{1}{p{2in}}{\raggedright Single class replication or small curated list} & \multicolumn{1}{p{2in}}{\raggedright Curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection*} \\
+Project selection & \multicolumn{1}{p{2in}}{\raggedright Single class replication or small curated list} & \multicolumn{1}{p{2in}}{\raggedright Curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection} \\
 
-Data source & \multicolumn{1}{p{2in}}{\raggedright University or classroom participant pool} & \multicolumn{1}{p{2in}}{\raggedright In-person or online convenience sample} & \multicolumn{1}{p{2in}}{\raggedright Targetted sampling of original populations} \\
+Subject population & \multicolumn{1}{p{2in}}{\raggedright University or classroom participant pool} & \multicolumn{1}{p{2in}}{\raggedright In-person or online convenience sample} & \multicolumn{1}{p{2in}}{\raggedright Targeted sampling of original populations} \\
 
@@
 
-<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->
-
 Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor (drafted by students)} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students (with instructor review)} \\
 
-Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default (subject to disucssion)} \\
+Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default (subject to discussion)} \\
 
@@
 \end{landscape}
+
+<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->
 
@@
 
-### Author contact
-
-Over half of our students contacted original authors to request study materials or clafication on methods and/or analysis, but for the purposes of our class, we chose not to require contact with all original authors.
-We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to empower students to engage with and build on the published literature directly -- without personal relationships or even personal contact.
-That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.
-Authors were contacted only in cases where there were issues about access to materials or ambiguities in design or analysis.
-There are benefits of contacting original authors, however.
-In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition).
-In the end, it is up to individual instructors to decide what they believe is best for their students.
-
-<!-- First, contact is a professional courtesy that lets the authors know that their study is being replicated and in some cases allows the original authors to pre-register their hypotheses or concerns with the replication study.
-Second, original authors can provide methodological feedback prior to replication.
-This second is a trickier issue on many fronts.
-By requesting feedback, discussion with authors perpetuates the dissemination of insider information or lab-specific folklore on methodology that produces the greatest effects.
-When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science.
-In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).
-In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies.
-Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.
--->
-
 ### Subject population
@@
 We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses due to failures to distinguish between related experimental paradigms.
-In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).] This choice was made to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
+In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).] We used AMT to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
 As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
@@
 Other classes many find participant pools or recruitment of community samples more feasible and appropriate.
+
+### Workflow tools
+
+All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
+All analyses were written using R, a free and open-source platform for statistical analysis.
+Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
+This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
+
+Some of these tools can feel inaccessible or intimidating to beginners.
+Indeed, our students, who came from a variety of disciplinary backgrounds, typically have relatively little experience with web-based empirical studies or literate, reproducible data analysis.
+Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
+Our experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
+
+Our explicit class goal was to provide students with experiences navigating the full ecosystem of open-source scientific tools.
+For classes at different levels, however, instructors will likely have different goals.
+It may be preferable for an intermediate course to focus on a single programming tool (e.g., R) and to use other GUI-based software for creating experiments, so as to minimize the learning burden for students.
+And for more introductory research methods course, instructors must gauge whether the added difficulty of a programming component is appropriate for the skills and backgrounds of their students.
 
@@
 
-### Workflow selection
+### Author contact
 
-All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
-All analyses were written using R, a free and open-source platform for statistical analysis.
-Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
-This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
+Over half of our students contacted original authors to request study materials or clarification on methods and/or analysis, but for the purposes of our class, we chose not to require contact with all original authors.
+We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to empower students to engage with and build on the published literature directly -- without personal relationships or even personal contact.
+That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.
+Authors were contacted only in cases where there were issues about access to materials or ambiguities in design or analysis.
+There are benefits of contacting original authors, however.
+In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition).
+In the end, it is up to individual instructors to decide what they believe is best for their students.
 
-Some of these tools can feel inaccessible or intimidating to beginners.
-Indeed, our students, who came from a variety of disciplinary backgrounds, typically have relatively little experience with web-based empirical studies or literate, reproducible data analysis.
-Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
-Our experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
-
-Our explicit class goal was to provide students with experiences navigating the full ecosystem of open-source scientific tools.
-For classes at different levels, however, instructors will likely have different goals.
-It may be preferrable for an intermediate course to focus on a single programming tool (e.g., R) and to use other GUI-based software for creating experiments, so as to minimize the learning burden for students.
-And for more introductory research methods course, instructors must gauge whether the added difficulty of a programming compoent is appropriate for the skills and backgrounds of their students.
+<!-- First, contact is a professional courtesy that lets the authors know that their study is being replicated and in some cases allows the original authors to pre-register their hypotheses or concerns with the replication study.
+Second, original authors can provide methodological feedback prior to replication.
+This second is a trickier issue on many fronts.
+By requesting feedback, discussion with authors perpetuates the dissemination of insider information or lab-specific folklore on methodology that produces the greatest effects.
+When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science.
+In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).
+In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies.
+Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.
+-->
 
@@
 First, instructors may first be concerned that IRB approval is not possible within the time constraints of the class.
-To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine whether to create a standard protocol that encompassses all replications that will be conducted, or to determine a timeline for submitting individual protocols very early in the course.
+To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine whether to create a standard protocol that encompasses all replications that will be conducted, or to determine a timeline for submitting individual protocols very early in the course.
 Both issues may be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
@@
 We recommend building training around ethical issues into the syllabus of replication-based classes.
-This practice is both positive for studetns and mitigates potential IRB concerns via explicit training.
+This practice is both positive for students and mitigates potential IRB concerns via explicit training.
 
@@
 
-Our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear.
+However, our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear.
 For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials.
@@
 We can envision a number of possible avenues for this kind of sharing.
-For example, if some products are shared openly in a repository like the [Open Science Framework](http://osf.io) or [figshare](http://figshare.com) and tagged appropriately, they will be discoverable via search engines.
-Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like [PsychFileDrawer](http://psychfiledrawer.org) or CurateScience (http://curatescience.org/).
+For example, if some products are shared openly in a repository like the Open Science Framework (osf.io) or figshare (figshare.com) and tagged appropriately, they will be discoverable via search engines.
+Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like PsychFileDrawer (psychfiledrawer.org) or CurateScience (curatescience.org).
 Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible.
-For example, the [Collaborative Replications and Education Project](https://osf.io/wfc6u/) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
+For example, the Collaborative Replications and Education Project (osf.io/wfc6u) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
 
@@
 
-For each project, we present a summary of the finding, the key statistical test, the impressionistic outcomes of the replication, and -- where applicable -- our assessement of the source of differences in results (often composed with the advice of the original authors).
+For each project, we present a summary of the finding, the key statistical test, the impressionistic outcomes of the replication, and -- where applicable -- our assessment of the source of differences in results (often composed with the advice of the original authors).
 Figure 3 shows a side-by-side comparison of the key visualization for each study.

### 2017-06-29 paper/paper.Rmd
Revise intro; removed osf from table

@@
 header-includes:
-   - \usepackage{lscape}
+   - \usepackage{pdflscape}
    - \usepackage{multicol}
@@
 
-In the current article, we address the practical barriers of completing replications as part of required coursework and discuss the methodological decisions that replication projects must address more broadly.
+In the current article, we address the practical barriers of completing replications as part of required coursework and discuss the methodological decisions that such replication projects must address more broadly.
 Towards this aim, we report the results of replication projects conducted in a graduate-level experimental methods course.
@@
 We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings.
-We consider a number of criteria for replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations.
-While each of these is imperfect, taken together these measures help provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in future work.
-But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions.
+We consider a number of criteria for evaluating replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations.
+While each of these is imperfect, taken together these measures suggest that replications performed in the classroom are representative of larger, more systematic efforts.
+Perhaps more importantly, these results provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in their own future work.
+<!-- But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions.
 Indeed, due to differences in population, timing, or method, some of our findings might be construed as assessing the boundary conditions of a particular effect rather than replicating the original exactly.
 Even in these cases, however, replication research of the type we conduct here contributes to an understanding of the robustness, generalizability, and expected effect sizes of previously published findings.
+-->
 
@@
 \specialcell{Citation\\(Psychological Science; 2015)} & Expt.
-& \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity} & \specialcell{Project link} \\
+& \specialcell{Open\\Data?} & \specialcell{Open\\Materials?} & \specialcell{On\\MTurk?} & \specialcell{N\\(orig)} & \specialcell{Power\\Standard} & \specialcell{N\\(rep)} & \specialcell{Instructor\\Fidelity}\\
   \hline
-Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & osf.io/uegk5/ \\ 
-Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 & osf.io/g6k2u/\\ 
-Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 & osf.io/rdw6e/ \\ 
-Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 & osf.io/sfxrb/ \\ 
-Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67 & osf.io/ne8ph/ \\ 
-Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67 & osf.io/32wsm/ \\ 
-Sofer et al. & 1 & Yes & Yes & No & 48 & Other &  95 & 4.33 & osf.io/5wmhn/ \\ 
-Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00 & osf.io/9cgpq/ \\ 
-Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33 & osf.io/ng96w/ \\ 
-Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00 & osf.io/cgvzs/ \\ 
-Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00 & osf.io/degwa/ \\ 
+Atir, Rosenzweig, \& Dunning & 1b & No & Yes & Yes & 202 & Other &  50 & 6.67 & \\ 
+Ko, Sadler, \& Galinksy & 2 & Yes & Some & No &  40 & Original &  40 & 4.67 &\\ 
+Lewis \& Oyserman & 4 & No & Yes & Yes & 122 & 80\% power & 128 & 6.67 &\\ 
+Liverence \& Scholl & 1 & No & Some & No &  18 & Original* &  19 & 5.33 &\\ 
+Proudfoot, Kay, \& Koval & 1 & No & No & Yes &  80 & 80\% power &  84 & 6.67&\\ 
+Scopelliti, Loewenstein, \& Vosgerau & 3 & Yes & Yes & Yes & 550 & Other & 124 & 5.67& \\ 
+Sofer et al. & 1 & Yes & Yes & No & 48 & Other &  95 & 4.33& \\ 
+Storm \& Stone & 3 & No & No & No & 48 & Original &  61 & 4.00& \\ 
+Wang et al. & 2 & No & No & No & 219 & 80\% power & 397 & 4.33&\\ 
+Xu \& Franconeri & 1a & No & No & No &  12 & Other* &  27 & 5.00& \\ 
+Zaval, Markowitz, \& Weber & 1 & Yes & Yes & Yes & 312 & Original & 321 & 5.00&\\ 
    \hline
 \end{tabular}
-\caption{\label{tab:summary} Summary characteristics of original studies and our replications, along with links to project pages for individual projects.
-All project materials available publicly at osf.io/98ta4/files/.
-* marks projects where the number of trials was modified.}
+\caption{\label{tab:summary} Summary characteristics of original studies and our replications.
+All project materials available publicly at osf.io/98ta4/files/, and links to individual project preregistrations, reports, and web experiments are available at osf.io/98ta4/wiki/ * marks projects where the number of trials was modified.}
 \label{tab:summary}
@@
 
+\begin{center}
 \begin{landscape}
-\centering
 
@@
 \end{landscape}
-
+\end{center}
 <!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->

### 2017-06-30 paper/paper.Rmd
Add more detail to course pipeline

@@
 
-## Writing, Preregistration, and Review
+## Milestones, Preregistration, and Review
 
-Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods.
-Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures).
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors (@nuijten2015), given that errors are often introduced by transferring results between statistics and word-processing software packages.]
+In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants (see Fig.
+1).
+In the second week of the course, students wrote a brief proposal selecting their replication targets, which were reviewed for feasibility and concreteness.
+After their selection was approved, students proceeded to write the methods section of the @osc2015 replication report template.
+This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template).
+At the same time, students worked on an experiment 'mock-up': a fully functional but unpolished outline of their experiment, potentially using placeholders for one or more unfinished elements of the design.
+Upon reviewing the completed methods and mockup, the teaching staff gave thorough feedback and suggested changes to be made before beginning any data collection.
 
-In addition to as-needed guidance on projects, students advanced through a formal review process in which each student's work was inspected and critiqued several times by both the instructor and the teaching assistants.
-After selecting their replication targets, students' first milestone was to fill in the methods section of the @osc2015 replication report template, which was reviewed for feasibility and concreteness.
-This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template).
-
-Further reviews were coordinated with completion of two pilot samples (see Fig.
-1).
+Further reviews were coordinated with completion of two pilot samples.
 The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
@@
 The goal of this pilot was to ensure that participants were able to complete the study and did not report any substantial issues with instructions or technical details of the study (all students were instructed to give participants a way to leave free-form comments at the end of the study, prior to debriefing).
-At the conclusion of Pilot B, both the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
+At the conclusion of Pilot B, *both* the instructor and a TA reviewed the student's analytic code and its outputs on the data for all confirmatory analyses.
 The goal of this code review was to ensure that all planned analyses were specified for the key test selected in the original article, and that all relevant exclusion criteria, manipulation checks, etc.
@@
 Prior to data collection, the analytic script containing all confirmatory analyses was pre-registered using the Open Science Framework.
+
+<!-- Using the template developed by @osc2015 for replication reports (included in our course materials), students first specified the scope and methods of their proposed replication study, including any differences from the original methods.
+Later, they added the code necessary to analyze their data, and after collecting their full sample, the results of their data analysis (e.g., statistical tests and figures).
+-->
 
@@
 This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
+This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors (@nuijten2015), given that errors are often introduced by transferring results between statistics and word-processing software packages.].
 

### 2017-06-30 paper/paper.Rmd
Add additional caveat to author contact

@@
 There are benefits of contacting original authors, however.
-In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition).
+In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition) prior to data collection, potentially heading off post-hoc debates about methodological choices.
 In the end, it is up to individual instructors to decide what they believe is best for their students.

### 2017-06-30 paper/paper.Rmd
Add details of BF default test to footnote

@@
 Next, following @etz2016, we compared Bayes Factors between the original and replication.
-We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[A default BF for one paper could not be computed based on the statistical test that was used.] This analysis revealed a number of interesting findings.
+We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[This default test assumes an alternative hypothesis that the effect is present with effect size $d=.707$; a default BF for one paper could not be computed based on the statistical test that was used.] This analysis revealed a number of interesting findings (Fig.
+2B).
 First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals.

### 2017-07-02 paper/paper.Rmd
mcf tweaks

@@
 
-We begin by describing the details of our course projects to give a sense of what a classroom replication project entails.
+We begin by providing the details of our course projects to give a sense of what a classroom replication project entails.
 We then discuss broader decision points for the course design that other instructors might consider.
@@
 \caption{\label{tab:summary} Summary characteristics of original studies and our replications.
-All project materials available publicly at osf.io/98ta4/files/, and links to individual project preregistrations, reports, and web experiments are available at osf.io/98ta4/wiki/ * marks projects where the number of trials was modified.}
+All project materials available publicly at osf.io/98ta4/files/, and links to individual project preregistrations, reports, and web experiments are available at osf.io/98ta4/wiki/.
+* marks projects where the number of trials was modified.}
 \label{tab:summary}
@@
 RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper.
-CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned their individual projects, programmed their studies, collected their data, and analyzed their data.
+CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned individual projects, programmed studies, collected data, analyzed data, and gave feedback on the paper.
 
@@
 Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
-Without a central focus on the replication project, students would not have the time or motivation to complete a high quality project; without multiple opportunities for instructor feedback, we would have far less confidence in the quality of the final projects.
+Without a central focus on the replication project, students will not have the time or motivation to complete a high quality project; without multiple opportunities for extensive (and often interactive) instructor feedback, the quality of the final projects will decline.
 
@@
 We encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design.
-This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at other levels.
-For example, in a large undergraduate class it may be logistically simpler for the instructors to choose 1 -- 3 replication projects that students can select from.
+This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at lower levels.
+For example, in a large undergraduate class it may be logistically simpler for the instructors to choose a small set of replication projects that students can select from.
 This step would both give instructors a greater degree of familiarity with the literature and allow for the development of more scaffolding with respect to the development of experimental materials.
@@
 
-Some of these tools can feel inaccessible or intimidating to beginners.
+Some of these tools can feel inaccessible or intimidating to students with a more limited programming background.
 Indeed, our students, who came from a variety of disciplinary backgrounds, typically have relatively little experience with web-based empirical studies or literate, reproducible data analysis.
-Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out a study independently.
-Our experience suggests that it is possible to convey key concepts in sufficient depth that -- within a supportive environment -- students can quickly learn to use a reproducible toolset.
+Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out an independent project (with support from their peers and the course staff).
+Our experience suggests that it is possible to convey key concepts in sufficient depth that students can learn to use a broad range of open and reproducible tools for their projects, even if mastery will require further experience.
 
@@
 In general, samples for course projects will be limited by the available resources.
-But for all replication research of the type advocated here, achieving high power for a smaller number of studies, perhaps conducted by groups, is preferable to conducting more lower-power studies, because results are much more likely to make a contribution to the replication literature (as well as to be interpretable by students).
-Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in the planning process.
+For all replication research of the type advocated here, achieving high power for a smaller number of studies, perhaps conducted by groups, is preferable to conducting more lower-power studies, because results are much more likely to make a contribution to the replication literature (as well as to be interpretable by students).
+Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.
 
@@
 In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition) prior to data collection, potentially heading off post-hoc debates about methodological choices.
-In the end, it is up to individual instructors to decide what they believe is best for their students.
+In the end, it is up to individual instructors to decide what they believe is best for their students in this area.
 
@@
 
-Institutional Review Boards (IRBs) are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
-First, instructors may first be concerned that IRB approval is not possible within the time constraints of the class.
-To mitigate this issue, we suggest contacting the IRB chair well in advance of the class to determine whether to create a standard protocol that encompasses all replications that will be conducted, or to determine a timeline for submitting individual protocols very early in the course.
-Both issues may be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
+Ethical review standards vary across countries and are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
+First, instructors may first be concerned that ethics approval is not possible within the time constraints of the class.
+To mitigate this issue, we suggest contacting your ethics body well in advance of the class to determine whether to create a standard protocol that encompasses all replications that will be conducted (as we did), or to determine a timeline for submitting individual protocols very early in the course.
+Both types of protocol will be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
 Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters.
 We recommend building training around ethical issues into the syllabus of replication-based classes.
-This practice is both positive for students and mitigates potential IRB concerns via explicit training.
+This practice is both positive for students and mitigates potential ethics approval concerns via the inclusion of explicit training.
 

### 2017-07-20 paper/paper.Rmd
Edit intro for flow & cohesion

@@
 As a proof-of-concept for this idea, here we report a series of 11 pre-registered replications of findings from the 2015 volume of Psychological Science, all conducted as part of a graduate-level course.
-Congruent with previous studies, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
+Congruent with larger, more systematic efforts, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
 This work documents the challenges facing motivated students in reproducing previously published results on a first attempt.
@@
 
+<!-- The problem, a solution, and the current lack of evidence for it -->
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012].
@@
 
-In the current article, we address the practical barriers of completing replications as part of required coursework and discuss the methodological decisions that such replication projects must address more broadly.
-Towards this aim, we report the results of replication projects conducted in a graduate-level experimental methods course.
-Students conducted replications of published articles from the 2015 volume of the journal *Psychological Science*.
-These studies provide insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.
+<!-- The kind of evidence we're going to provide -->
+In the current article, we address the practical barriers faced by instructors planning to incorporate replications into their courses.
+As a concrete guide for other instructors, we report the pedagogical and methodological approach taken in our graduate-level experimental methods course.
+In this course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science* with rigorous instructor review at each major stage.
+The results of these replications represent a microcosm of larger replication efforts, providing insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.
 
+<!-- The scientific value of that evidence  -->
 We assess the challenges facing a student in choosing an article of interest and -- in a single attempt, within constraints of budget, expertise, and effort -- reproducing the findings.
 We consider a number of criteria for evaluating replication success, including statistical significance, effect size, a Bayesian measure of evidence [@etz2016], and a subjective assessment with respect to the original authors' interpretations.
-While each of these is imperfect, taken together these measures suggest that replications performed in the classroom are representative of larger, more systematic efforts.
-Perhaps more importantly, these results provide a sense of how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in their own future work.
+While each of these is imperfect, taken together these measures help provide a sense of the robustness and generalizability of an effect, and perhaps more importantly, how easy it is for a student to reproduce an effect to the degree that they could confidently build on it in their own future work.
 <!-- But, as we discuss below, the results of these replications may have different interpretations: While some are more direct, others differ on theoretically-relevant dimensions.
@@
 
-We also describe our process for conducting replications as part of classroom pedagogy.
+<!-- The educational value of that evidence  -->
+We also describe in detail our process for conducting replications as part of classroom pedagogy.
 Although mentorship in experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
 And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- more directly than open-ended projects, which require new conceptual development [see @frank2012 for extended argument].
+
+<!-- Inspirational stuff and a call to join us... -->
 There are significant limitations on what can be done in a single term, within the constraints of a course budget and the instructors' expertise.
 Nevertheless, were this approach implemented more widely, we believe the dividends paid to the field as a whole -- both scientific and educational -- would be considerable.
-
-We begin by providing the details of our course projects to give a sense of what a classroom replication project entails.
-We then discuss broader decision points for the course design that other instructors might consider.
-Lastly, we report the results our replications, highlighting the importance of wide-scale replication efforts.
-
 To encourage others to share our materials, our course outline, project templates, and assignments are available publicly at [https://osf.io/98ta4/files/](https://osf.io/98ta4/files/).
@@
 We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.
+
+<!-- We begin by reporting the empirical results our replications, highlighting the importance of wide-scale replication efforts.
+We then provide the particular details of our course projects to give a sense of what a classroom replication project entails.
+We close with a discussion of broader decision points for the course design that other instructors might consider.
+-->
 
@@
 As described below, our procedure for individual project preregistrations was to register the analytic script with specific key hypothesis tests clearly marked.
-Individual project preregistration links are given in Table 1.
+Individual project preregistration links are given at [osf.io/98ta4/wiki/](osf.io/98ta4/wiki/).
 Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper at [https://osf.io/rxz8m/](https://osf.io/rxz8m/).

### 2017-07-20 paper/paper.Rmd
Switch parts over to sentence-per-line for better diffs...
mcf tweaks

@@
 Congruent with larger, more systematic efforts, replications typically yielded smaller effects than originals: The modal outcome was partial support for the original claim.
-This work documents the challenges facing motivated students in reproducing previously published results on a first attempt.
+This work documents the challenges facing motivated students as they attempt to replicate previously published results on a first attempt.
 We describe the workflow and pedagogical methods that were used in the class and discuss implications both for the adoption of this pedagogical model and for replication research more broadly."
@@
 Replicability is a core value for empirical research and there is increasing concern throughout psychology that more independent replication is necessary [@osc2015;@wagenmakers2012]. 
-Yet under the current incentive structure for science, replication is not typically valued for publication [@makel2012] or in metrics of research productivity [@koole2012].
+Yet under the current incentive structure for science, replication is not typically valued for publication in top journals [@makel2012] or in metrics of research productivity [@koole2012]. 
 One potential solution to this problem is to make replication an explicit part of pedagogy: that is, to teach students about experimental methods by asking them to run replication studies [@frank2012;@grahe2012].
-Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports or individual projects [@phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.
+Despite enthusiasm for this idea [@lebel2015;@everett2015;@standing2016;@king2016], there is limited data beyond anecdotal reports and individual projects [e.g., @phillips2015;@lakens2013] to support its efficacy in producing wide-scale pedagogical adoption.
 
 <!-- The kind of evidence we're going to provide -->
-In the current article, we address the practical barriers faced by instructors planning to incorporate replications into their courses.
-As a concrete guide for other instructors, we report the pedagogical and methodological approach taken in our graduate-level experimental methods course.
-In this course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science* with rigorous instructor review at each major stage.
-The results of these replications represent a microcosm of larger replication efforts, providing insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.
+In the current article, we describe the pedagogical and methodological approach to replication research taken in our graduate-level experimental methods course and address the practical barriers faced by instructors planning to incorporate replications into their courses.
+In our course, students conducted replications of published articles from the 2015 volume of the journal *Psychological Science* with rigorous instructor review at each major stage. 
+The results of these replications are a microcosm of larger replication efforts, providing insight into both the difficulties of pedagogical replications and their promise as a method for improving the robustness of psychological research.
 
@@
 We also describe in detail our process for conducting replications as part of classroom pedagogy. 
-Although mentorship in experimental methods is an important part of the standard advising relationship, the classroom context allows for elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
+Although mentorship in experimental methods is an important part of the standard advising relationship in psychology, the classroom context allows for the elucidation of general principles of good research and discussion of how they can be modified to fit specific instances.
 And replication research in particular illustrates a number of important concepts -- experimental design, power analysis, reporting standards, and preregistration, among others -- more directly than open-ended projects, which require new conceptual development [see @frank2012 for extended argument].
@@
 In addition, all of our most recent lecture slides and materials are available on our course website at [http://psych254.stanford.edu](). 
-We hope that others will share and reuse our materials as they consider how best to design a course customized to their context.
+We hope that others will share and reuse our materials as they consider how best to design a course customized to their aims and context.
 
@@
 As described below, our procedure for individual project preregistrations was to register the analytic script with specific key hypothesis tests clearly marked. 
-Individual project preregistration links are given at [osf.io/98ta4/wiki/](osf.io/98ta4/wiki/).
+Individual project preregistration links are given at [https://osf.io/98ta4/wiki/](osf.io/98ta4/wiki/). 
 Prior to data collection for all projects, we also pre-registered the confirmatory analyses reported in the current paper at [https://osf.io/rxz8m/](https://osf.io/rxz8m/).
@@
 
-All replications were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction" and was conducted in accordance with the Declaration of Helsinki.
+All replications were approved by the Stanford University Institutional Review Board under protocol \#23274, "Reproducibility of psychological science and instruction" and were conducted in accordance with the Declaration of Helsinki.
 
@@
 
-RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper.
+RXDH, ENS, and MCF designed the project, supported data planning and data collection for all projects, analyzed the data, and wrote the paper. MCF designed the course.
 CA, JMA, RC, EH, MK, AL, SR, JR, SS, JS, and JT planned individual projects, programmed studies, collected data, analyzed data, and gave feedback on the paper.
@@
 The requirements for joining the project were to conduct a pre-registered replication of a finding from the 2015 volume of *Psychological Science* and to contribute the code, data, and materials to the writeup.
-A schematic of our class timeline is shown in Figure 1.
+A schematic of our class timeline is shown in Fig. 1.
 
@@
 Individual sample sizes are given in Table \ref{tab:summary}.
-Each sample was recruited independently, using the same account but a different title.
+Each sample was recruited independently, using the same AMT account but a different task title.
 Of the `r nrow(d)` studies included in the final sample, `r sum(project_plan$original_on_turk=="Yes")` (`r 100 * round(mean(project_plan$original_on_turk=="Yes"), digits=2)`%) were originally conducted on AMT.
-For the other studies in our sample, demographic differences (in terms of age, sex, socio-economic status, and in some cases, national origin) are an important factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.
+For the other studies in our sample, demographic differences between the original sample and the AMT sample (in terms of age, sex, socio-economic status, and in some cases, national origin) are a factor in interpreting our findings; see Supplemental Material for more discussion of this issue in individual cases.^[Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
+We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses due to failures to distinguish between related experimental paradigms.
+In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).]
 
 We determined sample sizes using a case-by-case selection criterion that attempted to maximize the success of the project while staying within the constraints of our budget (see below for discussion).^[We initially were allocated \$1,500 but one student contributed personal research funds, leading to a total cost of $\approx$ \$1,700 for all studies.
-We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions.] For all criteria, experimenters recruited an additional 5% of participants to ensure we still achieved the desired criterion if some participants skipped through or did not complete the study.
+We attempted to set payment for our studies at approximately \$6/hour based on timing estimated from Pilot A sessions [@salehi2015].]
+To ensure they still achieved the desired criterion if some participants skipped through or did not complete the study, experimenters recruited 5% more participants than specified by their criterion. 
 In four cases, we powered the replication attempt to 80\% power based on post-hoc power calculations of the original effect sizes. 
 In four cases, we used the original sample size. 
-In one case, the original study was powered well above what would be required to find the effect of interest based on the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power for that effect.
+In one case, the original study was powered well above what would be required to find the effect of interest based on the post-hoc analysis, so we chose a smaller sample size that yielded sufficiently high power to detect that effect.
 In two others, we reduced the number of trials as part of the adaptation to Mechanical Turk (in one of these, changing the sample size to compensate). 
@@
 
-Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, following the methods specified by the original authors as closely as possible.
+Students used JavaScript and HTML/CSS to reimplement their respective target studies in the web browser, otherwise following the methods specified by the original authors as closely as possible.
 Of the `r nrow(d)` studies included in the final sample, `r 100 * round(mean(project_plan$open_materials == "Yes" | project_plan$open_materials == "Some"), digits=2)`% of studies had either some or all materials openly available.
@@
 This section included a power analysis, proposed sample size, and explicit description of differences from the original study (see course materials for complete template). 
-At the same time, students worked on an experiment 'mock-up': a fully functional but unpolished outline of their experiment, potentially using placeholders for one or more unfinished elements of the design.
+At the same time, students worked on an experiment "mock-up": a fully functional but unpolished outline of their experiment, potentially using placeholders for one or more unfinished elements of the design.
 Upon reviewing the completed methods and mockup, the teaching staff gave thorough feedback and suggested changes to be made before beginning any data collection.
 
-Further reviews were coordinated with completion of two pilot samples.
+For each project, further reviews were triggered by the completion of two pilot samples.
 The first, "Pilot A," consisted of a handful of non-naive participants (e.g., the experimenter, other students).
@@
 
-Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging for us to identify a single key statistical test for each study.
-Usually a substantial number of statistical tests were conducted, often within one or several regression models with multiple specifications.
+Despite the general emphasis in meta-analytic and reproducibility efforts on aggregating a single effect size of interest [@osc2015;@lipsey2001], it was often challenging to identify a single key statistical test for each study.
+Usually a substantial number of statistical tests were conducted, often within one or several ANOVA or regression models with multiple specifications.
 Thus, we interpret "key statistical test" results with caution (see Empirical Results and Discussion below).
@@
 All of the 15 students in the class completed projects (two with extensions going beyond the class period).
-Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[Note that these students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
+Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[These students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
 Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations, and materials to the final product.
@@
 
-Student group & \multicolumn{1}{p{2in}}{\raggedright General Undergraduate} & \multicolumn{1}{p{2in}}{\raggedright Advanced Undergraduate or Graduate} & \multicolumn{1}{p{2in}}{\raggedright Sophisticated Graduate} \\
+Student group & \multicolumn{1}{p{2in}}{\raggedright Mid-level undergraduates} & \multicolumn{1}{p{2in}}{\raggedright Advanced undergraduates or graduate students} & \multicolumn{1}{p{2in}}{\raggedright Advanced graduate students} \\
 
@@
 
-Group size & \multicolumn{1}{p{2in}}{\raggedright Full class / medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individual} \\
+Project group size & \multicolumn{1}{p{2in}}{\raggedright Full class or medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individuals} \\
 
-Project selection & \multicolumn{1}{p{2in}}{\raggedright Single class replication or small curated list} & \multicolumn{1}{p{2in}}{\raggedright Curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection} \\
+Project selection & \multicolumn{1}{p{2in}}{\raggedright Full class replication or choose from small curated list} & \multicolumn{1}{p{2in}}{\raggedright Choose from curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection or meta-science sampling frame} \\
 
-Subject population & \multicolumn{1}{p{2in}}{\raggedright University or classroom participant pool} & \multicolumn{1}{p{2in}}{\raggedright In-person or online convenience sample} & \multicolumn{1}{p{2in}}{\raggedright Targeted sampling of original populations} \\
+Subject population & \multicolumn{1}{p{2in}}{\raggedright In-person convenience samples} & \multicolumn{1}{p{2in}}{\raggedright University pool or AMT} & \multicolumn{1}{p{2in}}{\raggedright AMT or targeted sampling of original populations} \\
 
-Workflow tools & \multicolumn{1}{p{2in}}{\raggedright Use GUI tools / instructors implement studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key open-source tool (e.g., R)} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key open-source tools} \\
+Workflow tools & \multicolumn{1}{p{2in}}{\raggedright GUI tools, instructors code studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key coding-based tool, GUI tools otherwise} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key coding tools} \\
 
-Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor (drafted by students)} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students (with instructor review)} \\
+Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration drafted by students} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students with instructor review} \\
 
-Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default (subject to discussion)} \\
+Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default, subject to review} \\
 
@@
 
-In our class, students selected projects based on interest, rather than via a systematic sampling strategy.
-After selecting a paper, students chose a particular study from within that paper based on their judgment of interest and feasibility.
-We encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design.
+In our class, students selected projects based on interest, and we encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design.
 This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at lower levels.
-For example, in a large undergraduate class it may be logistically simpler for the instructors to choose a small set of replication projects that students can select from.
-This step would both give instructors a greater degree of familiarity with the literature and allow for the development of more scaffolding with respect to the development of experimental materials.
+For example, in a large undergraduate class it may be logistically simpler for the instructors to choose a small set of replication projects that students can select from, or perhaps even pool resources and collect multiple datasets for a single project.
+Limiting the set of projects both gives instructors a greater degree of familiarity with the relevant literature and allows for the development of more scaffolding of experimental materials.
 A mid-level course might split the difference between these two models, providing students with a broader -- but still curated -- list of potential projects.
@@
 
-We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.^[Repeat administration of empirical work on AMT has been raised as an issue in some prior work [e.g., @chandler2014], but tracking participation in specific paradigms is an open challenge.
-We did not ask participants whether they had participated in similar research previously, as we suspected that asking this sort of question would lead to a large number of inaccurate responses due to failures to distinguish between related experimental paradigms.
-In addition, half of the AMT population is estimated to change every six months [@stewart2015], and we expected that most of the studies in our sample that had been conducted on AMT had been performed at least a year previously (though see Supplemental Material for discussion of one particular paradigm that has been used more recently).] We used AMT to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
+We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.
+We used AMT to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
 As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
 Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers.
-Our general class structure does not depend on the use of AMT, however, and the use of this particular online sample should be viewed as limiting the interpretation of some of our results.
-Other classes many find participant pools or recruitment of community samples more feasible and appropriate.
+Other classes many find using university participant pools or recruitment of community samples more feasible and appropriate.
 
@@
 This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
-This method of writing allows students to share a single compiled document via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors (@nuijten2015), given that errors are often introduced by transferring results between statistics and word-processing software packages.].
+This method of writing allows students to share a single compiled document with instructors via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].
 
 Some of these tools can feel inaccessible or intimidating to students with a more limited programming background.
-Indeed, our students, who came from a variety of disciplinary backgrounds, typically have relatively little experience with web-based empirical studies or literate, reproducible data analysis.
-Yet by the end of the course, all gain sufficient proficiency with the suite of technical and conceptual tools necessary to carry out an independent project (with support from their peers and the course staff).
+Indeed, our students came from a variety of disciplinary backgrounds; many had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
+Yet by the end of the course, all gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out an independent project with support from their peers and the course staff.
 Our experience suggests that it is possible to convey key concepts in sufficient depth that students can learn to use a broad range of open and reproducible tools for their projects, even if mastery will require further experience.
@@
 For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered.
-In general, samples for course projects will be limited by the available resources.
-For all replication research of the type advocated here, achieving high power for a smaller number of studies, perhaps conducted by groups, is preferable to conducting more lower-power studies, because results are much more likely to make a contribution to the replication literature (as well as to be interpretable by students).
+Samples for course projects will be limited by the available resources, but for replication research of the type advocated here, achieving high power for a smaller number of studies is preferable to conducting more lower-power studies: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature.
 Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.
@@
 
-Ethical review standards vary across countries and are idiosyncratic across institutions, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
-First, instructors may first be concerned that ethics approval is not possible within the time constraints of the class.
-To mitigate this issue, we suggest contacting your ethics body well in advance of the class to determine whether to create a standard protocol that encompasses all replications that will be conducted (as we did), or to determine a timeline for submitting individual protocols very early in the course.
-Both types of protocol will be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
+Ethical review standards vary across instutitions and countries, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
+First, instructors may be concerned that ethics approval is not possible within the time constraints of the class.
+To mitigate this issue, we suggest contacting ethics bodies well in advance of classes to determine whether to create a standard protocol that encompasses all projects (as we did), or to set a timeline for students and instructors to submit individual study protocols very early in the course.
+Protocol development for both types -- umbrella and individual -- will be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
 Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters.
 We recommend building training around ethical issues into the syllabus of replication-based classes.
-This practice is both positive for students and mitigates potential ethics approval concerns via the inclusion of explicit training.
+This practice is both positive for students and also mitigates potential ethics approval concerns.
 
@@
 
-All reported results are from pre-registered, confirmatory analyses.^[In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
+All reported results are from pre-registered, confirmatory analyses.
+In two cases, in final review of the projects (after data analysis), the instructor team decided that the student's choice of key statistical test was not in fact a strong test of the original authors' primary theoretical claim.
 In both of these cases, the original authors had fit regression models to the data and there was not a single obvious test that corresponded directly to the authors' hypothesis.
@@
 We report results from these corrected tests here.
-We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).]
+We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).
 
@@
 The mean rating was `r round(mean(d$fidelity), digits = 2)` (range: `r round(min(d$fidelity), digits = 2)` -- `r round(max(d$fidelity), digits = 2)`).
-Several studies were essentially identical to the originals, but there was a group of others that included differences in population, number of trials, or method that might plausibly have had an effect on the results.
+Several studies were essentially identical to the originals, but there was a group of others that included differences in population, number of trials, or method -- all factors that might plausibly have had an effect on the results.
 
@@
 
-After data analysis, for each replication, the student carrying out each study and the instructors all gave independent "replication ratings" to assess the subjective success of the replication.
+After data analysis, for each replication, the student carrying out each study and each instructor gave independent "replication ratings" to assess the subjective success of the replication.
 Our three-point rating system was based on the theoretical support for the original finding, "None" (no support; 0\%), "Partial" (some support; 50\%), and "Full" (replication consistent with original interpretation; 100\%).
-We found that the ratings of the student carrying out the replication and the instructors were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
+Student and instructor ratings were in agreement for `r sum(d$replicated_TA == d$replicated_student,na.rm=T)` out of the `r nrow(d)` replications.
 The average rating given by instructors and students was `r 100 * round(mean(d$replicated_TA, na.rm=TRUE), digits = 2)`\% and `r 100 * round(mean(d$replicated_student, na.rm=TRUE), digits = 2)`\% respectively.
@@
 
-We next turn to an assessment of the replication $p$-value to determine whether the key statistic found a significant effect at the traditional $p=.05$ level.
-Only `r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value.
-The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+`r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value at $p < .05$. 
+<!-- The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.
+-->
 
@@
 
-Effect sizes and Bayes factors supplement inferences drawn from $p$-values in different ways.
+<!-- Effect sizes and Bayes factors supplement inferences drawn from $p$-values in different ways.
 The effect size is an estimate of the *magnitude* of an effect.
@@
 While the Bayes Factor often agrees with the $p$-value as to which hypothesis is more likely [@wetzels2011], they often substantially disagree on the strength of the evidence.
+-->
 
-These additional measures therefore give additional criteria for evaluating replications: If the replication shows roughly the same effect size or Bayes factor as the original results despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we may nonetheless consider it more of a success.
+<!-- These additional measures therefore give additional criteria for evaluating replications: If the replication shows roughly the same effect size or Bayes factor as the original results despite $p$-values on different sides of the arbitrary $p = 0.05$ threshold, we may nonetheless consider it more of a success.
+-->
+
 To compute a standardized effect size, we followed @osc2015 in converting test statistics to a measure of "correlation coefficient per df," which is bounded between 0 and 1.^[For example, the conversion from a $t$ statistic is given by $r = \sqrt{t^2/(t^2 + df)}$, where $df$ is the degrees of freedom.
-Other formulae are given in @osc2015, Supplemental Information.] We first compared effect sizes from the original and replication studies (Figure 2A).
-Effect sizes were highly correlated between the two sets of studies
-(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
-(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]), consistent with findings from multi-study replication projects [e.g.
-@osc2015].
-
-While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
+Other formulae are given in @osc2015, Supplemental Information.] While we preregistered an analysis determining whether the original reported effect size is included in the 95\% confidence interval found in the replication, we instead opted for a straightforward comparison of point estimates.
 This choice was motivated by the lack of consensus on how to conduct such a test [@anderson2016;@gilbert2016], recent concerns that using confidence intervals in this manner may lead to misleading interpretations [@morey2016], and discrepancies in the authors' reporting of effect sizes across the articles we included (which made computing confidence intervals difficult in some cases).
 
+We first compared effect sizes from the original and replication studies (Fig. 2A). Effect sizes were highly correlated between the two sets of studies 
+(r = `r signif(cor.test(d$original_ES_d,d$rep_es)$estimate, digits =2)`, p < .0001), but they were generally smaller in the replications 
+(`r signif(coef(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100`\% of the original; 95\% CI [`r signif(confint(lm(d$rep_es~d$original_ES_d-1))[1], digits = 2)*100` - `r signif(confint(lm(d$rep_es~d$original_ES_d-1))[2], digits = 2)*100`]), consistent with findings from multi-study replication projects [e.g., @osc2015].
+
 Next, following @etz2016, we compared Bayes Factors between the original and replication.
-We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[This default test assumes an alternative hypothesis that the effect is present with effect size $d=.707$; a default BF for one paper could not be computed based on the statistical test that was used.] This analysis revealed a number of interesting findings (Fig.
+We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[This default test assumes an alternative hypothesis that the effect is present with effect size $d=.707$; a default BF for one paper could not be computed based on the statistical test that was used.] As with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals (Fig.
 2B).
-First, as with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals.
-Second, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments.
-Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis is less than three times more likely than the null).
+In addition, it appeared that replication Bayes Factors generally tracked nicely with subjective replication judgments.
+Finally, the Bayes Factors for several of the original effects did not appear to show strong evidential value (e.g., BF < 3, indicating that the alternative hypothesis was less than three times more likely than the null).
 
@@
 
-However, our statistical findings mask a more optimistic message: In most of our projects, the next step for a motivated experimenter is clear.
-For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by titrating the particular planned analysis or the difficulty of the stimulus materials.
+Our statistical findings mask a more optimistic message, however: In most of our projects, the next step for a motivated experimenter is clear.
+For example, in some projects we suspect that a followup could find strong evidence for the phenomenon of interest by altering the particular planned analysis or titrating the difficulty of the stimulus materials.
 In others, the difficulty appeared to be statistical power, since differences were in the predicted direction and sometimes reached significance in subsidiary analyses, so a followup would likely require a larger sample.
@@
 First, we likely saw a "winner's curse," with initial publications tending to over-estimate effects.
-Second, we also might have seen a reduction in effect size because the original studies were tailored to their specific context and population, whereas our replications may not have been [@vanbavel2016, but cf.
+Second, we also might have seen a reduction in effect size because the original studies were tailored to their specific context and population, whereas our replications may not have been [@vanbavel2016; but cf.
 @inbar2016].
@@
 Almost every study conducted multiple statistical tests, often associated with several tersely-reported statistical models with differing specifications.
-And in some cases, there was no conventionally-reported and easily calculable effect size measures [e.g., for mixed- and random-effect models, cf.
+And in some cases, there was no conventionally-reported and easily calculable effect size measure [e.g., for mixed- and random-effect models, cf.
 @bakeman2005].
@@
 Our goal was to provide a proof of concept for pedagogical replications of recent findings in a top journal.
-Importantly, rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
-Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015].
+Rather than attempting to gauge the truth of particular effects, our project aimed to assess the challenges of replicating findings -- selected on grounds of feasibility and interest -- within the constraints of a course project.
+Such classes could become the backbone of future collaborative replication efforts [@frank2012;@everett2015], and could help provide a source of data on the robustness of the empirical literature more generally.
 
-<!-- MORE INSPIRATIONAL MATERIAL  -->
-
-This kind of cross-class collaboration would require instructors to make class results more broadly discoverable.
+This vision of collaborative pedagogical replication requires instructors to make class results more broadly discoverable.
 We can envision a number of possible avenues for this kind of sharing.
@@
 For example, the Collaborative Replications and Education Project (osf.io/wfc6u) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
+On these models, instructors must of course curate which projects are released publicly.
+But by pre-specifying review criteria, instructors can incorporate dissemination into their course as a reward for high quality work.
 
-One challenge for this kind of dissemination is how to curate which projects are released publicly.
-We are generally optimistic about the contributions of student work, but of course not every student project will be scientifically informative.
+<!-- We are generally optimistic about the contributions of student work, but of course not every student project will be scientifically informative.
 To take an edge case, imagine a student makes an error in stimulus presentation that is not caught by the instructors until after data collection.
@@
 But in the end, these decisions will be the responsibility of the course instructor -- much like decisions about when to publish other research.
+-->
 
@@
 For each project, we present a summary of the finding, the key statistical test, the impressionistic outcomes of the replication, and -- where applicable -- our assessment of the source of differences in results (often composed with the advice of the original authors).
-Figure 3 shows a side-by-side comparison of the key visualization for each study.
+Fig.
+3 shows a side-by-side comparison of the key visualization for each study.
 

### 2017-07-23 paper/paper.Rmd
Combine subject pool & sample size; discuss cost

@@
 
-### Subject population
+### Subject population and sample size
 
-We chose to use Amazon Mechanical Turk (AMT) as a platform for our replication studies.
-We used AMT to facilitate the process of recruiting samples large enough to enable replications of between-subjects designs (which typically require large samples) as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge.
-As much of psychological research is now conducted online, an additional pedagogical benefit of conducting online replications is to build competence in these skills.
+For pedagogical replications to also make a *scientific* contribution, they must be adequately powered and use subject populations comparable to those used in typical lab research.
+With these needs in mind, we chose to use Amazon Mechanical Turk (AMT) for our replication studies.
+AMT facilitates the process of recruiting diverse, high-quality samples [@BuhrmesterKwangGosling11;@CrumpEtAl13_Turk] that are large enough to enable replications of between-subjects designs (which typically require large samples).
+Because psychological research is increasingly conducted online, an additional pedagogical benefit is to build competence in these skills.
 Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers.
-Other classes many find using university participant pools or recruitment of community samples more feasible and appropriate.
 
+Still, collecting sufficiently large samples through AMT may strain financial resources.
+Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g.
+through teaching grants or departmental support), other populations may be more feasible and appropriate.
+For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a major technical component of the workflow.
+
+Cost considerations also enter decisions about determining appropriate sample sizes, a major challenge in replication research [@button2013;@simonsohn2015].
+Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013].
+But it may not be feasible to follow more conservative guidelines in all cases.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies, but be unnecessary for studies that were initially large and/or adequately powered.
+
+As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature.
+Regardless of the eventual sample collected, we find that the discussion of subject population & sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.
+
+<!-- as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. -->
 ### Workflow tools
@@
 Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
-This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of single unified document.
-This method of writing allows students to share a single compiled document with instructors via a hyperlink, facilitating review of writing, results, and code together in a single document.^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].
+This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of a single unified document that would become their final report.
+This method of writing allows students to easily share their cumulative work to date with instructors via a hyperlink, facilitating review of exposition, results, and code together in one location^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].
 
@@
 And for more introductory research methods course, instructors must gauge whether the added difficulty of a programming component is appropriate for the skills and backgrounds of their students.
-
-### Sample size and power analyses
-
-Determining appropriate sample sizes is a major challenge in replication research [@button2013;@simonsohn2015].
-Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013].
-But -- especially within the constraints of a limited budget -- it can be impossible to follow more conservative guidelines in all cases.
-For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies but may lead to impractical or unnecessary recommendations for studies that were initially large and/or adequately powered.
-Samples for course projects will be limited by the available resources, but for replication research of the type advocated here, achieving high power for a smaller number of studies is preferable to conducting more lower-power studies: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature.
-Regardless of the eventual sample collected, we find that the discussion of sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.
 

### 2017-07-24 paper/paper.Rmd
super minor tweak to sample size

@@
 Still, collecting sufficiently large samples through AMT may strain financial resources.
-Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g.
-through teaching grants or departmental support), other populations may be more feasible and appropriate.
-For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a major technical component of the workflow.
+Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g., through teaching grants or departmental support), other populations may be more feasible and appropriate.
+For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a technical challenge in data collection.
 

### 2017-07-26 paper/paper.Rmd
Small edits + costs section

@@
 1).
-In the second week of the course, students wrote a brief proposal selecting their replication targets, which were reviewed for feasibility and concreteness. 
+In the second week of the course, students wrote brief proposals selecting their replication targets, which were reviewed for feasibility and concreteness. 
 After their selection was approved, students proceeded to write the methods section of the @osc2015 replication report template. 
@@
 Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[These students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
-Thus we have no evidence that these students opted out systematically due to their belief that their project would fail.] The remaining 11 students contributed code, data, registrations, and materials to the final product.
+Thus we have no evidence that these students opted out systematically due to their belief that their project would not replicate.] The remaining 11 students contributed code, data, registrations, and materials to the final product.
 (In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review.
@@
 Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
-Without a central focus on the replication project, students will not have the time or motivation to complete a high quality project; without multiple opportunities for extensive (and often interactive) instructor feedback, the quality of the final projects will decline.
+Without a central focus on the replication project, students would likely not have the time or motivation to complete a high quality project; without multiple opportunities for extensive (and often interactive) instructor feedback, the quality of the final projects will decline.
 
@@
 
-Still, collecting sufficiently large samples through AMT may strain financial resources.
-Depending on the number of target studies, the needs of those studies, the level of the student group, and the total funds allocated to the course (e.g., through teaching grants or departmental support), other populations may be more feasible and appropriate.
+Depending on the course design and total funds allocated to the course (if any), populations other than AMT may be more feasible and appropriate.
+We recommend instructors explore funding opportunities through teaching grants or departmental support, but note that a replication course without funding would be possible.
 For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a technical challenge in data collection.
 
-Cost considerations also enter decisions about determining appropriate sample sizes, a major challenge in replication research [@button2013;@simonsohn2015].
+Cost considerations must also enter into decisions about adequate sample sizes, which has been a major challenge in replication research [@button2013;@simonsohn2015].
 Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013].
@@
 
-As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples: Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature.
+As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples.
+Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature.
 Regardless of the eventual sample collected, we find that the discussion of subject population & sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.
@@
 
-All our studies were coded in JavaScript, HTML, and CSS so as to be run in a standard web browser.
+All our studies were coded in JavaScript, HTML, and CSS to be run in a standard web browser.
 All analyses were written using R, a free and open-source platform for statistical analysis.
@@
 
-`r sum(d$rep_p_value_05)` of the studies (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value at $p < .05$. 
+Of the `r nrow(d)` studies, `r sum(d$rep_p_value_05)` (`r round(mean(d$rep_p_value_05)*100)`%) yielded a significant replication $p$-value at $p < .05$. 
 <!-- The well-documented "dance of the p-values" [@cumming2013] suggests that the inference drawn from a single replication $p$-value may not be conclusive, however, and other metrics such as effect sizes and Bayes factors may provide a more nuanced perspective.

### 2017-08-09 paper/paper.Rmd
add funding
resubmitted ampps

@@
 
-We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study (see @simmons2011).
+We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study [see @simmons2011].
 
@@
 Thanks to the Stanford Department of Psychology and the Vice Provost for Graduate Education for funding to support the class.
+This material is also based upon work supported by the National Science Foundation Graduate Research Fellowship under Grant No.
+DGE-1656518.
 We are grateful to the authors of the original studies who provided materials and gave extensive comments on an earlier draft of this manuscript.
@@
 
-# Pedagogy: Results and Discussion
-
-## Results: Pedagogical Assessment
-
-All of the 15 students in the class completed projects (two with extensions going beyond the class period).
-Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[These students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
-Thus we have no evidence that these students opted out systematically due to their belief that their project would not replicate.] The remaining 11 students contributed code, data, registrations, and materials to the final product.
-(In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review.
-We included this project in the final analysis.)
-
-Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
-But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
-Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
-
-## Discussion: Pedagogical Implications
-
-Our findings demonstrate that classroom replication projects are possible in one particular context.
-In the following subsections, we provide information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of coursework in their courses.
-We discuss practical recommendations for implementation in a variety of classroom settings, key decisions that instructors must make, and common issues that arise during replication projects.
-
-### Models for students of different levels
-
-Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
-Without a central focus on the replication project, students would likely not have the time or motivation to complete a high quality project; without multiple opportunities for extensive (and often interactive) instructor feedback, the quality of the final projects will decline.
-
-That said, depending on the student population and class constraints, there are many ways to include a replication project in a course.
-Table \ref{tab:classmodels} presents three different possible models of replication projects, for general undergraduate classes, advanced undergraduate/early graduate classes, and more advanced graduate classes.
-These models are not meant to be binding suggestions, but we hope that they inspire instructors to consider how replication research could be included in their own teaching practice.
-The sections below provide some discussion of individual choice-points.
-
-\begin{center}
-\begin{landscape}
-
-\newcommand{\specialcell}[2][c]{%
-  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
-
-\begin{table}[ht]
-\footnotesize
-\centering
-
-\def\arraystretch{1.2}
-
-\begin{tabular}{lccc}
-
- & \multicolumn{3}{c}{\underline{Classroom Models}} \\
-
-\multicolumn{1}{p{1.5in}}{\raggedright \underline{Course Attributes}} & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\
-
-Student group & \multicolumn{1}{p{2in}}{\raggedright Mid-level undergraduates} & \multicolumn{1}{p{2in}}{\raggedright Advanced undergraduates or graduate students} & \multicolumn{1}{p{2in}}{\raggedright Advanced graduate students} \\
-
-\hline
-
-Learning goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Gain research independence} & \multicolumn{1}{p{2in}}{\raggedright Master best practices and tools} \\
-
-Project group size & \multicolumn{1}{p{2in}}{\raggedright Full class or medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individuals} \\
-
-Project selection & \multicolumn{1}{p{2in}}{\raggedright Full class replication or choose from small curated list} & \multicolumn{1}{p{2in}}{\raggedright Choose from curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection or meta-science sampling frame} \\
-
-Subject population & \multicolumn{1}{p{2in}}{\raggedright In-person convenience samples} & \multicolumn{1}{p{2in}}{\raggedright University pool or AMT} & \multicolumn{1}{p{2in}}{\raggedright AMT or targeted sampling of original populations} \\
-
-Workflow tools & \multicolumn{1}{p{2in}}{\raggedright GUI tools, instructors code studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key coding-based tool, GUI tools otherwise} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key coding tools} \\
-
-Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration drafted by students} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students with instructor review} \\
-
-Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default, subject to review} \\
-
-\end{tabular}
-\caption{\label{tab:classmodels} Three potential models for incorporating replication projects into classes of different levels.} 
-\label{tab:classmodels}
-\end{table}
-
-\end{landscape}
-\end{center}
-<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->
-
-### Project selection
-
-In our class, students selected projects based on interest, and we encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design.
-This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at lower levels.
-For example, in a large undergraduate class it may be logistically simpler for the instructors to choose a small set of replication projects that students can select from, or perhaps even pool resources and collect multiple datasets for a single project.
-Limiting the set of projects both gives instructors a greater degree of familiarity with the relevant literature and allows for the development of more scaffolding of experimental materials.
-A mid-level course might split the difference between these two models, providing students with a broader -- but still curated -- list of potential projects.
-
-<!-- However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research.
-The modal study chosen was the first, but several students chose later studies in a set as well.
-Thus, all interpretation of our findings should be with respect to this non-probability sample.
-This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
--->
-
-### Subject population and sample size
-
-For pedagogical replications to also make a *scientific* contribution, they must be adequately powered and use subject populations comparable to those used in typical lab research.
-With these needs in mind, we chose to use Amazon Mechanical Turk (AMT) for our replication studies.
-AMT facilitates the process of recruiting diverse, high-quality samples [@BuhrmesterKwangGosling11;@CrumpEtAl13_Turk] that are large enough to enable replications of between-subjects designs (which typically require large samples).
-Because psychological research is increasingly conducted online, an additional pedagogical benefit is to build competence in these skills.
-Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers.
-
-Depending on the course design and total funds allocated to the course (if any), populations other than AMT may be more feasible and appropriate.
-We recommend instructors explore funding opportunities through teaching grants or departmental support, but note that a replication course without funding would be possible.
-For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a technical challenge in data collection.
-
-Cost considerations must also enter into decisions about adequate sample sizes, which has been a major challenge in replication research [@button2013;@simonsohn2015].
-Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013].
-But it may not be feasible to follow more conservative guidelines in all cases.
-For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies, but be unnecessary for studies that were initially large and/or adequately powered.
-
-As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples.
-Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature.
-Regardless of the eventual sample collected, we find that the discussion of subject population & sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.
-
-<!-- as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. -->
-### Workflow tools
-
-All our studies were coded in JavaScript, HTML, and CSS to be run in a standard web browser.
-All analyses were written using R, a free and open-source platform for statistical analysis.
-Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
-This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of a single unified document that would become their final report.
-This method of writing allows students to easily share their cumulative work to date with instructors via a hyperlink, facilitating review of exposition, results, and code together in one location^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].
-
-Some of these tools can feel inaccessible or intimidating to students with a more limited programming background.
-Indeed, our students came from a variety of disciplinary backgrounds; many had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
-Yet by the end of the course, all gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out an independent project with support from their peers and the course staff.
-Our experience suggests that it is possible to convey key concepts in sufficient depth that students can learn to use a broad range of open and reproducible tools for their projects, even if mastery will require further experience.
-
-Our explicit class goal was to provide students with experiences navigating the full ecosystem of open-source scientific tools.
-For classes at different levels, however, instructors will likely have different goals.
-It may be preferable for an intermediate course to focus on a single programming tool (e.g., R) and to use other GUI-based software for creating experiments, so as to minimize the learning burden for students.
-And for more introductory research methods course, instructors must gauge whether the added difficulty of a programming component is appropriate for the skills and backgrounds of their students.
-
-<!-- In our replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies.
-We first prioritized achieving the participants required for either 80% or original N (whichever was greater) for the maximum number of studies.
-This rule benefitted studies which were under the budget allocated for each individual project (i.e., studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power.
-This allowed us to reach our budget goals with the exception of one particularly expensive study.
-Fortunately, this student found external funding to reach 80% power.
-If this were not possible, we would have likely excluded this study from the pre-registration.
--->
-
-### Author contact
-
-Over half of our students contacted original authors to request study materials or clarification on methods and/or analysis, but for the purposes of our class, we chose not to require contact with all original authors.
-We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to empower students to engage with and build on the published literature directly -- without personal relationships or even personal contact.
-That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.
-Authors were contacted only in cases where there were issues about access to materials or ambiguities in design or analysis.
-There are benefits of contacting original authors, however.
-In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition) prior to data collection, potentially heading off post-hoc debates about methodological choices.
-In the end, it is up to individual instructors to decide what they believe is best for their students in this area.
-
-<!-- First, contact is a professional courtesy that lets the authors know that their study is being replicated and in some cases allows the original authors to pre-register their hypotheses or concerns with the replication study.
-Second, original authors can provide methodological feedback prior to replication.
-This second is a trickier issue on many fronts.
-By requesting feedback, discussion with authors perpetuates the dissemination of insider information or lab-specific folklore on methodology that produces the greatest effects.
-When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science.
-In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).
-In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies.
-Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.
--->
-
-### Ethical approvals
-
-Ethical review standards vary across instutitions and countries, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
-First, instructors may be concerned that ethics approval is not possible within the time constraints of the class.
-To mitigate this issue, we suggest contacting ethics bodies well in advance of classes to determine whether to create a standard protocol that encompasses all projects (as we did), or to set a timeline for students and instructors to submit individual study protocols very early in the course.
-Protocol development for both types -- umbrella and individual -- will be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
-Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters.
-We recommend building training around ethical issues into the syllabus of replication-based classes.
-This practice is both positive for students and also mitigates potential ethics approval concerns.
-
 # Empirical Findings: Results and Discussion
@@
 We report results from these corrected tests here.
-We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research (see e.g., @monin2016 for discussion).
+We return to this issue below, as we believe that test selection is a critical theoretical issue in replication research [see e.g., @monin2016 for discussion].
 
@@
 
+# Pedagogy: Results and Discussion
+
+## Results: Pedagogical Assessment
+
+All of the 15 students in the class completed projects (two with extensions going beyond the class period).
+Of these, one chose a project outside of the sampling frame, and three opted out of the broader project prior to data collection.^[These students did not express doubts about the success of their projects prior to opting out, and 2/3 of these projects were judged by the instructor team to have been successful replications.
+Thus we have no evidence that these students opted out systematically due to their belief that their project would not replicate.] The remaining 11 students contributed code, data, registrations, and materials to the final product.
+(In one case, a student did not complete the pre-registration procedure correctly but still submitted a pre-specified analysis plan to the instructors for review.
+We included this project in the final analysis.)
+
+Because they were conducted by students within the constraints of a course, our studies had a number of limitations, including: 1) limited time for iterative piloting and adjustment, 2) limits on funding for larger samples, and 3) limits on domain expertise with respect to the specific effects that were chosen.
+But within these limitations, our group was able to produce a set of relatively close replications with generally good statistical power.
+Thus, our work here shows what is possible for motivated students using freely-available tools and resources.
+
+## Discussion: Pedagogical Implications
+
+Our findings demonstrate that classroom replication projects are possible in one particular context.
+In the following subsections, we provide information that we hope will reduce barriers to entry and encourage more researchers and instructor to include replications as part of coursework in their courses.
+We discuss practical recommendations for implementation in a variety of classroom settings, key decisions that instructors must make, and common issues that arise during replication projects.
+
+### Models for students of different levels
+
+Though others' courses that incorporate replication projects will look quite different from our own, we recommend having the replication as a centerpiece of the course and giving ample opportunity for feedback throughout the study design.
+Without a central focus on the replication project, students would likely not have the time or motivation to complete a high quality project; without multiple opportunities for extensive (and often interactive) instructor feedback, the quality of the final projects will decline.
+
+That said, depending on the student population and class constraints, there are many ways to include a replication project in a course.
+Table \ref{tab:classmodels} presents three different possible models of replication projects, for general undergraduate classes, advanced undergraduate/early graduate classes, and more advanced graduate classes.
+These models are not meant to be binding suggestions, but we hope that they inspire instructors to consider how replication research could be included in their own teaching practice.
+The sections below provide some discussion of individual choice-points.
+
+\begin{center}
+\begin{landscape}
+
+\newcommand{\specialcell}[2][c]{%
+  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}
+
+\begin{table}[ht]
+\footnotesize
+\centering
+
+\def\arraystretch{1.2}
+
+\begin{tabular}{lccc}
+
+ & \multicolumn{3}{c}{\underline{Classroom Models}} \\
+
+\multicolumn{1}{p{1.5in}}{\raggedright \underline{Course Attributes}} & \underline{Model 1} & \underline{Model 2} & \underline{Model 3} \\
+
+Student group & \multicolumn{1}{p{2in}}{\raggedright Mid-level undergraduates} & \multicolumn{1}{p{2in}}{\raggedright Advanced undergraduates or graduate students} & \multicolumn{1}{p{2in}}{\raggedright Advanced graduate students} \\
+
+\hline
+
+Learning goal & \multicolumn{1}{p{2in}}{\raggedright Gain experience with research process} & \multicolumn{1}{p{2in}}{\raggedright Gain research independence} & \multicolumn{1}{p{2in}}{\raggedright Master best practices and tools} \\
+
+Project group size & \multicolumn{1}{p{2in}}{\raggedright Full class or medium-size groups (7-8 students)} & \multicolumn{1}{p{2in}}{\raggedright Small groups (2-4) or individuals} & \multicolumn{1}{p{2in}}{\raggedright Individuals} \\
+
+Project selection & \multicolumn{1}{p{2in}}{\raggedright Full class replication or choose from small curated list} & \multicolumn{1}{p{2in}}{\raggedright Choose from curated list} & \multicolumn{1}{p{2in}}{\raggedright Open project selection or meta-science sampling frame} \\
+
+Subject population & \multicolumn{1}{p{2in}}{\raggedright In-person convenience samples} & \multicolumn{1}{p{2in}}{\raggedright University pool or AMT} & \multicolumn{1}{p{2in}}{\raggedright AMT or targeted sampling of original populations} \\
+
+Workflow tools & \multicolumn{1}{p{2in}}{\raggedright GUI tools, instructors code studies} & \multicolumn{1}{p{2in}}{\raggedright Teach one key coding-based tool, GUI tools otherwise} & \multicolumn{1}{p{2in}}{\raggedright Teach full ecosystem of key coding tools} \\
+
+Pre-registration & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by instructor} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration drafted by students} & \multicolumn{1}{p{2in}}{\raggedright Pre-registration by students with instructor review} \\
+
+Dissemination & \multicolumn{1}{p{2in}}{\raggedright If meeting pre-specified quality standard} & \multicolumn{1}{p{2in}}{\raggedright With instructor approval} & \multicolumn{1}{p{2in}}{\raggedright As class default, subject to review} \\
+
+\end{tabular}
+\caption{\label{tab:classmodels} Three potential models for incorporating replication projects into classes of different levels.} 
+\label{tab:classmodels}
+\end{table}
+
+\end{landscape}
+\end{center}
+<!-- Review & \multicolumn{1}{p{2in}}{\raggedright Standardized review checkpoints} & \multicolumn{1}{p{2in}}{\raggedright Extensive group review and minimal instructor review} & \multicolumn{1}{p{2in}}{\raggedright Multiple reviews between students and with instructors} \\ -->
+
+### Project selection
+
+In our class, students selected projects based on interest, and we encouraged students with little programming background to opt for methodologically simple studies, and more advanced students to take on a challenging design.
+This level of freedom is not ideal for less advanced courses, and the set of available replication studies should likely be curated for students at lower levels.
+For example, in a large undergraduate class it may be logistically simpler for the instructors to choose a small set of replication projects that students can select from, or perhaps even pool resources and collect multiple datasets for a single project.
+Limiting the set of projects both gives instructors a greater degree of familiarity with the relevant literature and allows for the development of more scaffolding of experimental materials.
+A mid-level course might split the difference between these two models, providing students with a broader -- but still curated -- list of potential projects.
+
+<!-- However, this sample also reflects what is of most interest to beginning researchers, and we suspect may be a better sampling frame to better understand particularly impactful effects to be built upon in future research.
+The modal study chosen was the first, but several students chose later studies in a set as well.
+Thus, all interpretation of our findings should be with respect to this non-probability sample.
+This sampling strategy may thus bias our results towards more exciting or novel findings, as well as those that were more feasible for students.
+-->
+
+### Subject population and sample size
+
+For pedagogical replications to also make a *scientific* contribution, they must be adequately powered and use subject populations comparable to those used in typical lab research.
+With these needs in mind, we chose to use Amazon Mechanical Turk (AMT) for our replication studies.
+AMT facilitates the process of recruiting diverse, high-quality samples [@BuhrmesterKwangGosling11;@CrumpEtAl13_Turk] that are large enough to enable replications of between-subjects designs (which typically require large samples).
+Because psychological research is increasingly conducted online, an additional pedagogical benefit is to build competence in these skills.
+Even if students’ current research does not use AMT, these replications allow students to build a skillset that can be used throughout their academic careers.
+
+Depending on the course design and total funds allocated to the course (if any), populations other than AMT may be more feasible and appropriate.
+We recommend instructors explore funding opportunities through teaching grants or departmental support, but note that a replication course without funding would be possible.
+For instance, recruitment from community samples or university participant pools may provide high-quality data while reducing costs and eliminating a technical challenge in data collection.
+
+Cost considerations must also enter into decisions about adequate sample sizes, which has been a major challenge in replication research [@button2013;@simonsohn2015].
+Sample planning based on analysis of the achieved effect size in a previously-published study is problematic because of the likelihood of inflation of published effect sizes due to the "winner's curse" [@hoenig2001;@button2013].
+But it may not be feasible to follow more conservative guidelines in all cases.
+For example, @simonsohn2015 recommends 2.5x the original sample, which can be feasible for small or under-powered original studies, but be unnecessary for studies that were initially large and/or adequately powered.
+
+As a rule of thumb, for the type of replication research advocated here, conducting a small number of high-powered studies using representative samples is preferable to conducting a large number of under-powered studies in convenience samples.
+Results are much more likely to be to be interpretable by students and to make a contribution to the replication literature.
+Regardless of the eventual sample collected, we find that the discussion of subject population & sample size determination is one of the most eye-opening parts of our class and so we encourage instructors to allow students to participate in this planning process.
+
+<!-- as well as to help students learn about a valuable resource for recruitment whose use requires some specialized knowledge. -->
+### Workflow tools
+
+All our studies were coded in JavaScript, HTML, and CSS to be run in a standard web browser.
+All analyses were written using R, a free and open-source platform for statistical analysis.
+Students wrote their final reports using [R Markdown](http://rmarkdown.rstudio.com/), a "literate programming" environment in which statistical analysis code can be interspersed with text, figures, and tables.
+This part of our workflow was extremely useful both pedagogically and for encouraging reproducible research practices: each milestone in our course, corresponding to each phase of a research project, required students to fill in additional sections of a single unified document that would become their final report.
+This method of writing allows students to easily share their cumulative work to date with instructors via a hyperlink, facilitating review of exposition, results, and code together in one location^[The current manuscript is written in this fashion as well; this writing method is also likely to reduce the frequency of statistical reporting errors [@nuijten2015], given that errors are often introduced by transferring results between statistics and word-processing software packages.].
+
+Some of these tools can feel inaccessible or intimidating to students with a more limited programming background.
+Indeed, our students came from a variety of disciplinary backgrounds; many had relatively little experience with web-based empirical studies or literate, reproducible data analysis.
+Yet by the end of the course, all gained sufficient proficiency with the suite of technical and conceptual tools necessary to carry out an independent project with support from their peers and the course staff.
+Our experience suggests that it is possible to convey key concepts in sufficient depth that students can learn to use a broad range of open and reproducible tools for their projects, even if mastery will require further experience.
+
+Our explicit class goal was to provide students with experiences navigating the full ecosystem of open-source scientific tools.
+For classes at different levels, however, instructors will likely have different goals.
+It may be preferable for an intermediate course to focus on a single programming tool (e.g., R) and to use other GUI-based software for creating experiments, so as to minimize the learning burden for students.
+And for more introductory research methods course, instructors must gauge whether the added difficulty of a programming component is appropriate for the skills and backgrounds of their students.
+
+<!-- In our replications, we opted for a case-by-case weighing of the costs and benefits of increasing power across all studies.
+We first prioritized achieving the participants required for either 80% or original N (whichever was greater) for the maximum number of studies.
+This rule benefitted studies which were under the budget allocated for each individual project (i.e., studies that had large effect sizes and short participation times.)  Of those that achieved 80% power with sample sizes that were smaller than the original sample, we reduced the most expensive studies down to N required for 80% power.
+This allowed us to reach our budget goals with the exception of one particularly expensive study.
+Fortunately, this student found external funding to reach 80% power.
+If this were not possible, we would have likely excluded this study from the pre-registration.
+-->
+
+### Author contact
+
+Over half of our students contacted original authors to request study materials or clarification on methods and/or analysis, but for the purposes of our class, we chose not to require contact with all original authors.
+We strongly believe methods and materials should be open to allow for replication and productive science [@nosek2015], and hoped to empower students to engage with and build on the published literature directly -- without personal relationships or even personal contact.
+That is, we chose to do good-faith replications given all information in the original articles and supplemental online materials.
+Authors were contacted only in cases where there were issues about access to materials or ambiguities in design or analysis.
+There are benefits of contacting original authors, however.
+In addition to professional courtesy, authors can provide valuable feedback or guidance (albeit at the cost of some imposition) prior to data collection, potentially heading off post-hoc debates about methodological choices.
+In the end, it is up to individual instructors to decide what they believe is best for their students in this area.
+
+<!-- First, contact is a professional courtesy that lets the authors know that their study is being replicated and in some cases allows the original authors to pre-register their hypotheses or concerns with the replication study.
+Second, original authors can provide methodological feedback prior to replication.
+This second is a trickier issue on many fronts.
+By requesting feedback, discussion with authors perpetuates the dissemination of insider information or lab-specific folklore on methodology that produces the greatest effects.
+When these assumptions or limitations of a theory or paradigm are not made explicit in publically-available format, this does not count as a record of science.
+In fact, some replications have prompted these assumptions to be made explicit by the original authors (CITE?).
+In addition, when original materials of a study are not provided, it is on the reader to assume all neccessary information is provided to replicate, and is not due to idiosyncracies.
+Thus, we would generally advice against contacting authors for feedback or materials expect when replication is not viable without them.
+-->
+
+### Ethical approvals
+
+Ethical review standards vary across instutitions and countries, but we suspect certain ethical concerns will commonly arise when attempting to implement class replication projects.
+First, instructors may be concerned that ethics approval is not possible within the time constraints of the class.
+To mitigate this issue, we suggest contacting ethics bodies well in advance of classes to determine whether to create a standard protocol that encompasses all projects (as we did), or to set a timeline for students and instructors to submit individual study protocols very early in the course.
+Protocol development for both types -- umbrella and individual -- will be simplified if the study or pool of studies to be replicated is pre-selected by instructors.
+Second, review boards may be concerned about risks particular to the collection of data by students, e.g., lack of debriefing or greater risk of breach of confidentiality due to novice experimenters.
+We recommend building training around ethical issues into the syllabus of replication-based classes.
+This practice is both positive for students and also mitigates potential ethics approval concerns.
+
 # General Discussion
@@
 We can envision a number of possible avenues for this kind of sharing.
-For example, if some products are shared openly in a repository like the Open Science Framework (osf.io) or figshare (figshare.com) and tagged appropriately, they will be discoverable via search engines.
-Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like PsychFileDrawer (psychfiledrawer.org) or CurateScience (curatescience.org).
+For example, if some products are shared openly in a repository like the Open Science Framework (http://osf.io) or figshare (http://figshare.com) and tagged appropriately, they will be discoverable via search engines.
+Alternatively, a more structured method for sharing and discovery would be upload to specific replication curation websites like PsychFileDrawer (http://psychfiledrawer.org) or CurateScience (http://curatescience.org).
 Both of these models assume limited coordination across instructors, but more structured collaborations are of course possible.
-For example, the Collaborative Replications and Education Project (osf.io/wfc6u) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
+For example, the Collaborative Replications and Education Project (http://osf.io/wfc6u) selected a subsample of important and feasible studies for replication and helped provide materials to instructors with the explicit goal of encouraging cross-lab pedagogical replications.
 On these models, instructors must of course curate which projects are released publicly.

### 2017-08-18 paper/paper.Rmd
Update Bayes Factor footnote

@@
 Next, following @etz2016, we compared Bayes Factors between the original and replication.
-We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[This default test assumes an alternative hypothesis that the effect is present with effect size $d=.707$; a default BF for one paper could not be computed based on the statistical test that was used.] As with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals (Fig.
+We used the default test suggested by @rouder2009 and did not attempt to correct for publication bias.^[This default test compares the null hypothesis of no effect against an alternative hypothesis placing a Cauchy prior on effect size with mean $x_0 = 0$ and scale parameter $\gamma = 1$; this distribution corresponds to a median absolute effect size of $d=1$.
+A default BF for one paper could not be computed based on the statistical test that was used.] As with effect sizes, we saw generally smaller Bayes Factors for the replications than the originals (Fig.
 2B).

### 2017-11-20 paper/paper.Rmd
Clean up axis labels

@@
   scale_x_log10(limits = c(10**-1.75, 10**11), 
-                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c(".1", "1", "10","100", "1e3", 
-                           "1e6","1e9")) +
-  scale_y_log10(limits = c(10**-1.75, 10**11),
-                breaks = c(1/10, 1, 10, 100, 1e+3, 1e+6, 1e+9),
-                labels = c(".1", "1", "10","100", "1e3", 
-                           "1e6","1e9")) + 
+   breaks = 10^c(-1, 1, 3, 6, 9),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))) +
+ scale_y_log10(
+   limits = c(10**-1.75, 10**11),
+   breaks = 10^c(-1, 1, 3, 6, 9),
+   labels = scales::trans_format("log10", scales::math_format(10^.x))) +
   theme_bw(base_size=10) + 
